### 2021-06-09 article/tto2019.tex
article template

%
% File tto2019.tex
%
%% Based on the style files for ACL 2019, ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{tto2019}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{How to verify that the platforms are enforcing their regulation policies}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of TTO 2019. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted from the instructions
for ACL and NAACL proceedings,
including 
those for
ACL 2019 and
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
NAACL 2018 by Margaret Michell and Stephanie Lukin,
2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan, 
NAACL 2017 by Margaret Mitchell, 
ACL 2012 by Maggie Li and Michael White, 
those from ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
those for ACL 2008 by JohannaD. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
those for ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
those for ACL 2002 by Eugene Charniak and Dekang Lin, 
and earlier ACL and EACL formats.
Those versions were written by several
people, including John Chen, Henry S. Thompson and Donald
Walker. Additional elements were taken from the formatting
instructions of the \emph{International Joint Conference on Artificial
  Intelligence} and the \emph{Conference on Computer Vision and
  Pattern Recognition}.

\section{Introduction}

The following instructions are directed to authors of papers submitted
to TTO 2019 or accepted for publication in its proceedings. Authors of technical papers
are required to adhere to these specifications. The template is optional for 
authors of talk and dataset proposals. Authors are
required to provide a Portable Document Format (PDF) version of their
papers. \textbf{The proceedings are designed for printing on A4
paper.}

\section{General Instructions}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, authors' names and complete
addresses, which must be centered at the top of the first page, and
any full-width figures or tables (see the guidelines in
Subsection~\ref{ssec:first}). \textbf{Type single-spaced.}  Start all
pages directly under the top margin. See the guidelines later
regarding formatting the first page.  The manuscript should be
printed single-sided and its length
should not exceed the maximum page limit defined in the Call for Papers.
Pages are numbered for  initial submission. However, \textbf{do not number the pages in the camera-ready version}.

By uncommenting {\small\verb|\aclfinalcopy|} at the top of this 
 document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.

The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.  The TTO 2019 \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\aclfinalcopy|} is commented out.

\subsection{The Ruler}
The TTO 2019 style defines a printed ruler which should be presented in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document without the provided
style files, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment the {\small\verb|\aclfinalcopy|} command in the document preamble.)

Reviewers: note that the ruler measurements do not align well with
lines in the paper -- this turns out to be very difficult to do well
when the paper contains many figures and equations, and, when done,
looks ugly. In most cases one would expect that the approximate
location will be adequate, although you can also use fractional
references (\emph{e.g.}, the first paragraph on this page ends at mark $108.5$).

\subsection{Electronically-available resources}

TTO provides this description in \LaTeX2e{} (\texttt{\small tto2019.tex}) and PDF
format (\texttt{\small tto2019.pdf}), along with the \LaTeX2e{} style file used to
format it (\texttt{\small tto2019.sty}) and an ACL bibliography style (\texttt{\small acl\_natbib.bst})
and example bibliography (\texttt{\small acl2019.bib}).
%These files are all available at
%\texttt{\small http://acl2019.org/downloads/ acl2019-latex.zip}. 
 We
strongly recommend the use of these style files, which have been
appropriately tailored for the TTO 2019 proceedings.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). PDF files are usually produced from
\LaTeX\ using the \textit{pdflatex} command. If your version of
\LaTeX\ produces Postscript files, you can convert these into PDF
using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
Adobe Distiller to generate PDF.

Please make sure that your PDF file includes all the necessary fonts
(especially tree diagrams, symbols, and fonts with Asian
characters). When you print or create the PDF file, there is usually
an option in your printer setup to include none, all or just
non-standard fonts.  Please make sure that you select the option of
including ALL the fonts. \textbf{Before sending it, test your PDF by
  printing it from a computer different from the one where it was
  created.} Moreover, some word processors may generate very large PDF
files, where each page is rendered as an image. Such images may
reproduce poorly. In this case, try alternative ways to obtain the
PDF. One way on some systems is to install a driver for a postscript
printer, send your document to the printer specifying ``Output to a
file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm
x 29.7 cm) when formatting the paper. When working with
\texttt{dvips}, for instance, one should specify \texttt{-t a4}.
Or using the command \verb|\special{papersize=210mm,297mm}| in the latex
preamble (directly below the \verb|\usepackage| commands). Then using 
\texttt{dvipdf} and/or \texttt{pdflatex} which would make it easier for some.

Print-outs of the PDF file on A4 paper should be identical to the
hardcopy version. If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on A4
paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
 If you cannot meet the above requirements about the production of 
 your electronic submission, please contact the publication chairs 
 above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's \textbf{Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use \textbf{Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[t!]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
subsection titles & 11 pt & bold \\
document text & 11 pt  &\\
captions & 10 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns. Do not use footnotes for affiliations. Do not include the
paper ID number assigned during the submission process. Use the
two-column format only when you begin the abstract.

\textbf{Title}: Place the title centered at the top of the first page, in
a 15-point bold font. (For a complete guide to font sizes and styles,
see Table~\ref{font-table}) Long titles should be typed on two lines
without a blank line intervening. Approximately, put the title at 2.5
cm from the top of the page, followed by a blank line, then the
author's names(s), and the affiliation on the following line. Do not
use only initials for given names (middle initials are allowed). Do
not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not
``MITCHELL'').  Do not format title and section headings in all
capitals as well except for proper names (such as ``BLEU'') that are
conventionally in all capitals.  The affiliation should contain the
author's complete address, and if possible, an electronic mail
address. Start the body of the first page 7.5 cm from the top of the
page.

The title, author names and addresses should be completely identical
to those entered to the electronical paper submission website in order
to maintain the consistency of author information among all
publications of the conference. If they are different, the publication
chairs may resolve the difference without consulting with you; so it
is in your own interest to double-check that the information is
consistent.

\textbf{Abstract}: Type the abstract at the beginning of the first
column. The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.6 cm on each side. Center the word \textbf{Abstract} in a 12 point bold
font above the body of the abstract. The abstract should be a concise
summary of the general thesis and conclusions of the paper. It should
be no longer than 200 words. The abstract text should be in 10 point font.

\textbf{Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in the present document. Do not include page numbers.

\textbf{Indent}: Indent when starting a new paragraph, about 0.4 cm. Use 11 points for text and subsection headings, 12 points for section headings and 15 points for the title.

\begin{table}
\centering
\small
\begin{tabular}{cc}
\begin{tabular}{|l|l|}
\hline
\textbf{Command} & \textbf{Output}\\\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular} & 
\begin{tabular}{|l|l|}
\hline
\textbf{Command} & \textbf{Output}\\\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\\hline
\end{tabular}
\end{tabular}
\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\subsection{Sections}

\textbf{Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals.
Do not number subsubsections.

\begin{table*}[t!]
\centering
\begin{tabular}{lll}
  output & natbib & previous ACL style files\\
  \hline
  \citep{Gusfield:97} & \verb|\citep| & \verb|\cite| \\
  \citet{Gusfield:97} & \verb|\citet| & \verb|\newcite| \\
  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| & \verb|\shortcite| \\
\end{tabular}
\caption{Citation commands supported by the style file.
  The citation style is based on the natbib package and
  supports all natbib citation commands.
  It also supports commands defined in previous ACL style files
  for compatibility.
  }
\end{table*}

\textbf{Citations}: Citations within the text appear in parentheses
as~\cite{Gusfield:97} or, if the author's name appears in the text
itself, as Gusfield~\shortcite{Gusfield:97}.
Using the provided \LaTeX\ style, the former is accomplished using
{\small\verb|\cite|} and the latter with {\small\verb|\shortcite|} or {\small\verb|\newcite|}. Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\small\verb|\cite|} command, \emph{e.g.}, {\small\verb|\cite{Gusfield:97,Aho:72}|}. Append lowercase letters to the year in cases of ambiguities.  
 Treat double authors as
in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
authors are involved. Collapse multiple citations as
in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
as sentence constituents.

We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\citet| (cite in text)
to get ``author (year)'' citations.

You can use the command \verb|\citealp| (alternative cite without 
parentheses) to get ``author year'' citations (which is useful for 
using citations within parentheses, as in \citealp{Gusfield:97}).

If the Bib\TeX{} file contains DOI fields, the paper
title in the references section will appear as a hyperlink
to the DOI, using the hyperref \LaTeX{} package.
To disable the hyperref package, load the style file
with the \verb|nohyperref| option: \\{\small
\verb|\usepackage[nohyperref]{acl2019}|}

\textbf{Compilation Issues}: Some of you might encounter the following error during compilation:

``{\em \verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.}''

This happens when \verb|pdflatex| is used and a citation splits across a page boundary. To fix this, the style file contains a patch consisting of the following two lines: (1) \verb|\RequirePackage{etoolbox}| (line 454 in \texttt{tto2019.sty}), and (2) A long line below (line 455 in \texttt{tto2019.sty}).

If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \verb|hyperref| package (see above), recompile and see the problematic citation.
Next rewrite that sentence containing the citation. (See, {\em e.g.}, {\small\tt http://tug.org/errors.html})

%\textbf{Digital Object Identifiers}:  As part of our work to make ACL
%materials more widely used and cited outside of our discipline, ACL
%has registered as a CrossRef member, as a registrant of Digital Object
%Identifiers (DOIs), the standard for registering permanent URNs for
%referencing scholarly materials.  As of 2017, we are requiring all
%camera-ready references to contain the appropriate DOIs (or as a
%second resort, the hyperlinked ACL Anthology Identifier) to all cited
%works.  Thus, please ensure that you use Bib\TeX\ records that contain
%DOI or URLs for any of the ACL materials that you reference.
%Appropriate records should be found for most materials in the current
%ACL Anthology at \url{http://aclanthology.info/}.

%As examples, we cite \cite{P16-1001} to show you how papers with a DOI
%will appear in the bibliography.  We cite \cite{C14-1001} to show how
%papers without a DOI but with an ACL Anthology Identifier will appear
%in the bibliography.

As reviewing will be double-blind, the submitted version of the papers
should not include the authors' names and affiliations. Furthermore,
self-references that reveal the author's identity, \emph{e.g.},
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''  
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
``\citeauthor{Gusfield:97} \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper. TTO 2019 reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.

\textbf{Please do not use anonymous citations} and do not include
 when submitting your papers. Papers that do not
conform to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading \textbf{References}. 
Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
By using a .bib file, as in this template, this will be automatically 
handled for you. See the \verb|\bibliography| commands near the end for more.

Provide as complete a citation as possible, using a consistent format,
such as the one for \emph{Computational Linguistics\/} or the one in the 
\emph{Publication Manual of the American 
Psychological Association\/}~\cite{APA:83}. Use of full names for
authors rather than initials is preferred. A list of abbreviations
for common computer science journals can be found in the ACM 
\emph{Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations, 
short citations and multiple citations as described above.

\begin{itemize}
\item Example citing an arxiv paper: \cite{rasooli-tetrault-2015}. 
\item Example article in journal citation: \cite{Ando2005}.
\item Example article in proceedings, with location: \cite{borsch2011}.
\item Example article in proceedings, without location: \cite{andrew2007scalable}.
\end{itemize}
See corresponding .bib file for further details.

Submissions should accurately reference prior and related work, including code and data. If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced. If multiple versions of a piece of prior work exist, the one used by the authors should be referenced. Authors should not rely on automated citation indices to provide accurate references for prior and related work.

\subsection{Footnotes}

\textbf{Footnotes}: Put footnotes at the bottom of the page and use 9
point font. They may be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the line
separating the footnotes from the text.}

\subsection{Graphics}

\textbf{Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns.  Color
illustrations are discouraged, unless you have verified that  
they will be understandable when printed in black ink.

\textbf{Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and 
tables below the body, using 10 point text. Captions should be placed below illustrations. Captions that are one line are centered (see Table~\ref{font-table}). Captions longer than one line are left-aligned (see Table~\ref{tab:accents}). Do not overwrite the default caption sizes. The tto2019.sty file is compatible with the caption and subcaption packages; do not add optional arguments.

\subsection{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate people who are color-blind (as well as those printing
to paper), grayscale readability for all accepted papers will be
encouraged.  Color is not forbidden, but authors should ensure that
tables and figures do not rely solely on color to convey critical
distinctions. A simple criterion: All curves and points in your figures should be clearly distinguishable without color.

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section*{Acknowledgments}

The acknowledgments should go immediately before the references.  Do
not number the acknowledgments section. Do not include this section
when submitting your paper for review. \\

\noindent \textbf{Preparing References:} \\
Include your own bib file like this:
\verb|\bibliographystyle{acl_natbib}|
\verb|\bibliography{acl2019}|

where \verb|acl2019| corresponds to a acl2019.bib file.
\bibliography{acl2019}
\bibliographystyle{acl_natbib}

\end{document}

### 2021-06-10 code/create_figures.py
plot Trump Facebook page's daily number of posts to illustrate a temporary suspension

@@ -1,0 +1,61 @@
+import os
+from datetime import datetime, timedelta
+
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+def import_data(file_name):
+    data_path = os.path.join(".", "data", file_name)
+    df = pd.read_csv(data_path, low_memory=False)
+    return df
+
+
+def save_figure(figure_name):
+    figure_path = os.path.join('.', 'figure', figure_name)
+    plt.savefig(figure_path)
+    print("The '{}' figure is saved.".format(figure_name))
+
+
+def create_suspension_facebook_trump_figure():
+
+    df = import_data('crowdtangle_facebook_trump_2020_2021.csv')
+    df['date'] = pd.to_datetime(df['date'])
+    serie_to_plot = df.resample('D', on='date')['date'].agg('count')
+    serie_to_plot = serie_to_plot.append(pd.Series([0, 0], index=[pd.Timestamp(2021, 1, 7), pd.Timestamp(2021, 6, 8)]))
+
+    plt.figure(figsize=(8, 3.5))
+    plt.title(df.account_name.iloc[0])
+    plt.ylabel('Number of Facebook posts per day')
+
+    plt.plot(serie_to_plot)
+
+    ax = plt.subplot(111)
+    ax.spines['right'].set_visible(False)
+    ax.spines['left'].set_visible(False)
+    ax.spines['top'].set_visible(False)
+    ax.grid(axis="y")
+    plt.locator_params(axis='y', nbins=4)
+
+    plt.xlim(
+        np.datetime64(datetime.strptime('2019-12-31', '%Y-%m-%d')), 
+        np.datetime64(datetime.strptime('2021-06-10', '%Y-%m-%d'))
+    )
+    xticks = [np.datetime64('2020-01-01'), np.datetime64('2020-04-01'), 
+              np.datetime64('2020-07-01'), np.datetime64('2020-10-01'),
+              np.datetime64('2021-01-01'), np.datetime64('2021-04-01'),
+             ]
+    plt.xticks(xticks, rotation=30, ha='right')
+    plt.axvspan(np.datetime64('2021-01-06'), np.datetime64('2021-06-08'), 
+                ymin=0, ymax=200000, facecolor='r', alpha=0.05)
+
+    plt.text(np.datetime64('2021-01-31'), 45, 'Suspension period', color='r')
+
+    plt.tight_layout()
+    save_figure('suspension_facebook_trump.png')
+
[…]

### 2021-06-28 code/create_figures.py
colors easier to distinguish

@@ -148,7 +148,7 @@ def create_facebook_crowdtangle_infowars_figure():
 
     ax = plt.subplot(212)
     plt.plot(df.resample('D', on='date')['comment'].mean(),
-        label="Comments per post", color='cornflowerblue')
+        label="Comments per post", color='lightskyblue')
     plt.plot(df.resample('D', on='date')['share'].mean(),
         label="Shares per post", color='royalblue')
     plt.plot(df.resample('D', on='date')['reaction'].mean(),

### 2021-06-29 code/create_figures.py
add bz infowars figure

@@ -131,12 +131,12 @@ def create_facebook_crowdtangle_infowars_figure():
 
     print()
 
-    df = import_data('facebook_crowdtangle_infowars_2021-06-22.csv')
+    df = import_data('facebook_crowdtangle_infowars_2021-06-29.csv')
     df = clean_crowdtangle_data(df)
     print('There are {} posts after removing the indirect links in the CrowdTangle Infowars date.'.format(len(df)))
     print_the_percentage_changes(df, date='2019-05-02', period=60)
 
-    fig = plt.figure(figsize=(10, 6))
+    fig = plt.figure(figsize=(10, 8))
     fig.suptitle('Facebook posts sharing an Infowars link (CrowdTangle)')
     
     ax = plt.subplot(211)
@@ -161,7 +161,54 @@ def create_facebook_crowdtangle_infowars_figure():
     save_figure(figure_name='facebook_crowdtangle_infowars.png')
 
 
+def clean_buzzsumo_data(df):
+
+    df['date'] = [datetime.fromtimestamp(x).date() for x in df['published_date']]
+    df['date'] = pd.to_datetime(df['date'])
+
+    df = df.drop_duplicates(subset=['url'])
+
+    return df
+
+
+def filter(df, column):
+    
+    s0 = df.resample('D', on='date')['date'].agg('count')
+    dates_to_filter = s0[s0 < 5].index
+    
+    s = df.resample('D', on='date')[column].mean()
+    s[s.index.isin(dates_to_filter)] = np.nan
+
+    return s
+
+
+def create_facebook_buzzsumo_infowars_figure():
+
+    print()
+
+    df = import_data('facebook_buzzsumo_infowars_2021-06-29.csv')
+    df = clean_buzzsumo_data(df)
+
+    fig = plt.figure(figsize=(10, 4))
+    fig.suptitle('Facebook engagement for the Infowars articles (Buzzsumo)')
+
+    ax = plt.subplot(111)
+    plt.plot(filter(df, 'facebook_comments'),
+        label="Comments per article", color='lightskyblue')
+    plt.plot(filter(df, 'facebook_shares'),
+        label="Shares per article", color='royalblue')
+    plt.plot(filter(df, 'facebook_likes'),
+        label="Reactions (likes, ...) per article", color='navy')
+    plt.legend()
+    arrange_plot(ax)
+    plt.ylim(0, 3000)
+
+    plt.tight_layout()
[…]

### 2021-06-29 code/collect_facebook_buzzsumo_infowars_data.py
make the figures easier to understand

@@ -14,5 +14,5 @@ if __name__=="__main__":
         token=os.getenv('BUZZSUMO_TOKEN'),
         output_path=os.path.join('.', 'data', 'facebook_buzzsumo_infowars_' + str(date.today()) + '.csv'),
         begin_date='2019-01-01', 
-        end_date='2021-06-15'
+        end_date='2020-12-31'
     )

### 2021-06-29 code/collect_facebook_crowdtangle_infowars_data.sh

@@ -3,5 +3,5 @@
 TODAY_DATE=$(date +"%Y-%m-%d")
 
 minet ct search "infowars.com" --search-field include_query_strings \
-  --platform facebook --start-date 2019-01-01 --end-date 2021-06-15 > \
+  --platform facebook --start-date 2019-01-01 --end-date 2020-12-31 > \
   "./data/facebook_crowdtangle_infowars_${TODAY_DATE}.csv"

### 2021-06-29 code/create_figures.py

@@ -19,6 +19,22 @@ def save_figure(figure_name):
     print("The '{}' figure is saved.".format(figure_name))
 
 
+def arrange_plot(ax, df):
+
+    ax.set_frame_on(False)
+    ax.grid(axis="y")
+    plt.locator_params(axis='y', nbins=4)
+
+    plt.xticks(
+        [np.datetime64('2019-06-30'), np.datetime64('2020-06-30'), np.datetime64('2021-04-30')],
+        ['2019', '2020', '2021'], fontsize='large'
+    )
+    ax.xaxis.set_tick_params(length=0)
+    plt.axvspan(np.datetime64('2020-01-01'), np.datetime64('2020-12-31'), 
+                ymin=0, ymax=200000, facecolor='k', alpha=0.05)
+    plt.xlim(np.min(df['date']), np.max(df['date']))
+
+
 def create_suspension_facebook_trump_figure():
 
     print()
@@ -32,31 +48,20 @@ def create_suspension_facebook_trump_figure():
         index=[pd.Timestamp(2021, 1, 7), pd.Timestamp(2021, 6, 15)]
     ))
 
-    plt.figure(figsize=(8, 3))
-    plt.title(df.account_name.iloc[0])
-    plt.plot(serie_to_plot, color='royalblue', label='Number of Facebook posts per day')
-    plt.legend()
+    plt.figure(figsize=(10, 4))
+    plt.title("'" + df.account_name.iloc[0] + "' Facebook page (data from CrowdTangle)")
 
     ax = plt.subplot(111)
-    ax.set_frame_on(False)
-    ax.grid(axis="y")
-    plt.locator_params(axis='y', nbins=4)
+    plt.plot(serie_to_plot, color='royalblue', label='Number of posts per day')
+    plt.legend()
 
+    arrange_plot(ax, df)
+    plt.axvline(np.datetime64("2021-01-07"), color='C3', linestyle='--')
     plt.xlim(
         np.datetime64(datetime.strptime('2019-12-31', '%Y-%m-%d')), 
         np.datetime64(datetime.strptime('2021-06-15', '%Y-%m-%d'))
     )
-    plt.ylim(-1, 55)
-
-    xticks = [np.datetime64('2020-01-01'), np.datetime64('2020-04-01'), 
-              np.datetime64('2020-07-01'), np.datetime64('2020-10-01'),
-              np.datetime64('2021-01-01'), np.datetime64('2021-04-01'),
-             ]
-    plt.xticks(xticks, rotation=30, ha='right')
[…]

### 2021-06-29 code/create_figures.py
print percentage changes for the Bz data

@@ -87,10 +87,10 @@ def clean_crowdtangle_data(df):
 
 
 def calculate_percentage_change(before, after):
-    return int((after - before) * 100 / before)
+    return str(int((after - before) * 100 / before))
 
 
-def print_the_percentage_changes(df, date='2019-05-02', period=60):
+def print_the_percentage_changes(df, columns, date='2019-05-02', period=60):
 
     df_before = df[df['date'] < np.datetime64(date)]
     df_before = df_before[df_before['date'] >= np.datetime64(datetime.strptime(date, '%Y-%m-%d') - timedelta(days=period))]
@@ -98,14 +98,10 @@ def print_the_percentage_changes(df, date='2019-05-02', period=60):
     df_after = df[df['date'] > np.datetime64(date)]
     df_after = df_after[df_after['date'] <= np.datetime64(datetime.strptime(date, '%Y-%m-%d') + timedelta(days=period))]
 
-    print('Drop after the', date, ': Reactions:',
-        calculate_percentage_change(df_before['reaction'].sum(), df_after['reaction'].sum())
-        , '%, Shares:',
-        calculate_percentage_change(df_before['share'].sum(), df_after['share'].sum()), 
-        '%, Comments:',
-        calculate_percentage_change(df_before['comment'].sum(), df_after['comment'].sum()),
-        '%.'
-    )
+    text_to_print = 'Drop after the ' + date + ': '
+    for column in columns:
+        text_to_print += column + ': ' + calculate_percentage_change(df_before[column].sum(), df_after[column].sum()) + '%, '
+    print(text_to_print)
 
 
 def create_facebook_crowdtangle_infowars_figure():
@@ -115,7 +111,7 @@ def create_facebook_crowdtangle_infowars_figure():
     df = import_data('facebook_crowdtangle_infowars_2021-06-29.csv')
     df = clean_crowdtangle_data(df)
     print('There are {} posts after removing the indirect links in the CrowdTangle Infowars date.'.format(len(df)))
-    print_the_percentage_changes(df, date='2019-05-02', period=60)
+    print_the_percentage_changes(df, columns=['reaction', 'share', 'comment'])
 
     plt.figure(figsize=(10, 8))
     
@@ -175,6 +171,7 @@ def create_facebook_buzzsumo_infowars_figure():
     df = import_data('facebook_buzzsumo_infowars_2021-06-29.csv')
     df = clean_buzzsumo_data(df)
[…]

### 2021-06-29 code/create_figures.py
print some Bz statistics

@@ -173,6 +173,10 @@ def create_facebook_buzzsumo_infowars_figure():
     print('There are {} Infowars articles for 2019 and 2020 in the Buzzsumo API.'.format(len(df)))
     print_the_percentage_changes(df, columns=['facebook_likes', 'facebook_shares', 'facebook_comments'])
 
+    print('There are {} Infowars articles collected from Buzzsumo between 2020-06-11 and 2020-07-11.'.format(
+        np.sum(df.resample('D', on='date')['date'].agg('count').loc['2020-06-11':'2020-07-11']))
+    )
+
     fig = plt.figure(figsize=(10, 4))
     plt.title('Facebook engagement for the Infowars articles (data from Buzzsumo)')
 
@@ -196,5 +200,5 @@ def create_facebook_buzzsumo_infowars_figure():
 if __name__=="__main__":
 
     # create_suspension_facebook_trump_figure()
-    create_facebook_crowdtangle_infowars_figure()
+    # create_facebook_crowdtangle_infowars_figure()
     create_facebook_buzzsumo_infowars_figure()

### 2021-06-30 code/collect_youtube_data.py
update collect_youtube.py and readme

@@ -6,7 +6,7 @@ import re
 import sys
 
 
-def get_channel_videos(channel_id,youtube):
+def get_channel_videos(channel_id, youtube):
     # get Uploads playlist id
     res = youtube.channels().list(id=channel_id,
                                   part='contentDetails').execute()
@@ -27,30 +27,31 @@ def get_channel_videos(channel_id,youtube):
             break
     return videos
 
+
 def timestamp(video):
     return (datetime.strptime(video['snippet']['publishedAt'], "%Y-%m-%dT%H:%M:%fZ")
             + timedelta(hours=5, minutes=30))
 
+
 def video_title(video):
     return video['snippet']['title']
+
 
 def video_id(video):
         return video['snippet']['resourceId']['videoId']
 
+
 def collect_data(API_key, channel_id):
     youtube = build('youtube', 'v3', developerKey=API_key)
-
-
     videos = get_channel_videos(channel_id,youtube)
-
     titles = [video_title(video) for video in videos]
 
     publish_timestamps = [timestamp(video) for video in videos]
     video_ids = [video_id(video) for video in videos]
     videos_df = pd.DataFrame({'Upload_date':publish_timestamps,'video_titles':titles,'video_id':video_ids})
-    videos_df = videos_df[videos_df['Upload_date']>'2019-01-01']
+    videos_df = videos_df[videos_df['Upload_date']>'2021-01-01']
     videos_ids_filtered = list(videos_df['video_id'])
-    data = pd.DataFrame([], columns=[ 'video_title', 'view_counts', 'likes', 'dislikes', 'comments', 'video_id',
+    data = pd.DataFrame([], columns=['video_title', 'view_counts', 'likes', 'dislikes', 'comments', 'video_id',
                                        'channel_name', 'channel_id', 'published_at', 'duration'])
     for i in videos_ids_filtered:
         video_data = get_data_video(i, youtube)
@@ -61,7 +62,7 @@ def collect_data(API_key, channel_id):
     data.to_csv(path)
 
 
-def get_data_video( vid_id,youtube):
+def get_data_video(vid_id, youtube):
         data = np.array([])
         vid_suff = vid_id
         request = youtube.videos().list(
@@ -73,7 +74,6 @@ def get_data_video( vid_id,youtube):
             # print(response)
 
             main_info = response['items'][0]['snippet']
-
             channel_name = main_info['channelTitle']
[…]

### 2021-06-30 code/collect_youtube_data.py
update collect_youtube.py- date change

@@ -49,7 +49,7 @@ def collect_data(API_key, channel_id):
     publish_timestamps = [timestamp(video) for video in videos]
     video_ids = [video_id(video) for video in videos]
     videos_df = pd.DataFrame({'Upload_date':publish_timestamps,'video_titles':titles,'video_id':video_ids})
-    videos_df = videos_df[videos_df['Upload_date']>'2021-01-01']
+    videos_df = videos_df[videos_df['Upload_date']>'2019-01-01']
     videos_ids_filtered = list(videos_df['video_id'])
     data = pd.DataFrame([], columns=['video_title', 'view_counts', 'likes', 'dislikes', 'comments', 'video_id',
                                        'channel_name', 'channel_id', 'published_at', 'duration'])

### 2021-06-30 article/draft.tex
first iteration

\documentclass{article}
%\documentclass[a4paper,12pt,twoside]{book}
\usepackage{amsmath}
\usepackage{cite}
%\usepackage{tikz}
\usepackage{bm}
\usepackage{tikz,tkz-tab}
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{hyperref}
\usepackage{mathtools}
%\usepackage{subcaption}
\usepackage{color}
\usepackage{setspace}
\usepackage{empheq}
\usepackage{bbm, dsfont}
\usepackage{dsfont}
\usepackage{mathtools}
\usepackage{geometry}
\usepackage{enumitem} 
\usepackage[bottom]{footmisc}
\usetikzlibrary{arrows}
\usepackage{lscape}
\usepackage{tcolorbox}
\usepackage{caption}
%\usepackage{graphicx}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{cite}
\usetikzlibrary{shapes,snakes}
\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\diamond$}

\usepackage{titlesec}

\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\newtheorem{definition}{Definition}

\usetikzlibrary{positioning}
\tikzset{main node/.style={circle,draw,minimum size=0.5cm,inner sep=0pt},
            }

%-------------------------------------------
\newtheorem{example}{Example}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{assumption}{Assumption}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{observation}{Observation}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}
\title{Very Preliminary Draft}
\maketitle

%Using social media data to verify the platforms' regulation policies regarding misinformation"

\section{Introduction}

A number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense. \footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.''  }

Section $230$ in the United States Communications Decency Act\footnote{Similar regulation exists in the European Union, see articles $12$ and $15$ of the E-commerce Directive (2000). } provides immunity for website platforms against the content created by users. Nevertheless, there is growing pressure for Mainstream Social Media Platforms (hereafter MSMP), such as Facebook, Twitter or Youtube, to moderate the available content. In particular, platforms seem to take explicit actions when content is in violation of local laws in different jurisdictions, e.g. laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws. Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}. We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}

\smallskip

Furthermore, MSMP are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam.\footnote{For an exhaustive overview of the community standards of Facebook, see: \href{https://www.facebook.com/communitystandards/}{facebook.com/communitystandards/}. For the Twitter  Rules see: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}, and for Youtube community guidelines see: \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}.} While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries.

\smallskip

In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. The rise of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. {\color{red} Fact-checkers + no laws or not so much.}

\smallskip

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: } As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. {\color{red} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+ idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}

\smallskip

In the present article, we will explain how to verify with data mining MSMP's actions regarding content with low credibility or false information, through a series of examples for different actions and platforms. For the purpose of clarity, we only focus on three platforms: Facebook, Twitter and Youtube. Both Facebook and Youtube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited MSMP, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices. We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies. We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring. We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.  %the announced policy for a specific user was implemented or not.

%Second, we provide simple means to check how those policies are implemented in practice and discuss how to assess their impact, when possible.

%We do not aim for an exhaustive list of methods on how to investigate the platforms’ policies against misinformation, but rather to share the methods we currently know, and that we think can be useful to researchers or journalists interested in that question. We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.

\bigskip

%{\color{red} Policies not specific to misinformation, but to enforce laws + things already used for terrorism and hate speech. Intro or/and Discussion. accounts: hard to say suspension for which.}

%Content can be withheld in compliance to specific laws of each country, ex: ..;
% Misinformation : which law ? not defined !

\begin{table}[]
\centering
\begin{tabular}{|l|l|l|l}

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{Web Scraping}                                                                                                                                                                   \\ \hline
Facebook & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}: public content insights tool \\ owned and operated by Facebook. \\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content database  \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
\\ \hline
Twitter  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet twitter scrape}}                                                                                                                                                                           \\ \hline
Youtube  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

 %We We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.

%CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages. BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.

%Section 230 in the US + EU 
%Pressure to moderate and mix-up of platforms with public square… 
%Rôle dans la production/médiation : P-M-R 
%Pourquoi faut-il vérifier leurs politiques ? D’une part parce que ce sont les plateformes elles-mêmes qui annoncent leurs effets. D’autre part beaucoup de choses indirectes. 
%
%Add disclaimer in a footnote early on in the document : document not meant to be an exhaustive overview of all the existing regulations and point to three or four main legal sources for exhaustive references.

%Such policies include the introduction of notices (Twitter, see link) or flags (Facebook, see…) to signal to users inaccurate or false content, the temporary or permanent suspension of accounts (Twitter) or pages (Facebook), reducing the visibility of posts or pages (Facebook), or blocking users from sharing specific URL links (see link). The objective of this article is twofold. First, we study the impact of a number of  implemented measures by mainstream platforms to tackle (mis)disinformation.

\section{Policies}

\subsection{Temporary suspension and Permanent suspension}

Main stream social media platforms such as Facebook, Twitter and Youtube, may suspend the account of a specific user when they deem that the platforms' rules have been violated. Account suspension can be temporary or permanent.\footnote{A list of notable Twitter temporary and permanent suspensions can be found on wikipedia: \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{https://en.wikipedia.org/wiki/Twitter\_suspensions}.}  When the suspension is temporary the user is prohibited for a limited period of time from posting content on their account, but created content prior to suspension remains available to the user and their followers. However, when the suspension is permanent, in most cases, followers or subscribers have no longer access to the content prior to the suspension and the user can no longer use the account to create new content.  In what follows, we focus on the implementation of this policy by several platforms and provide simple examples to illustrate.

%\begin{figure}[h]
%\centering
%\includegraphics[scale=0.2]{./img/fig1.png}  \hfill \includegraphics[scale=0.2]{./img/crg.png} \hfill \includegraphics[scale=0.2]{./img/life.png} 
%\caption{Screenshots taken on June 14, 2021 at 4pm UTC. }
%\label{fig1}
%\end{figure}

\smallskip

\subsubsection{Facebook}

When an account is permanently suspended by Facebook, it disappears from the platform (so its data cannot be scrapped anymore), and its data also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.}

Interestingly, Facebook is regularly publishing a monthly {\it coordinated inauthentic behavior} report where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the April 2021 report for an example: \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.

Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed. For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API. Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{ (see the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data. We can verify on figure \ref{fig1_fb} that the {\it Donald J. Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.

\begin{figure}
	\centering
	\includegraphics[scale=0.35]{./img/fb/fig1_fb.png}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

\subsubsection{Twitter}

{\color{red} N.B. Manual decision, not the automatic strike system}
\begin{figure}
\centering
\includegraphics[scale=0.35]{./img/lifesite.jpg} 
\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

In this section, we discuss one case of temporary suspension on Twitter.\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account $@LifeSite$ via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

\smallskip

To further assess the impact of this double temporary suspension, we collect via Minet Command Line Tool\cite{minet}, all the tweets that have shared during the same period a url link containing lifesitenews.com. Panel $(b)$ of figure \ref{fig2}, shows that during both periods of temporary suspension, other users still shared lifesitenews.com links and that the level was only slightly below the tweeting and retweeting levels prior to the first temporary suspension. More specifically, there was an average of 960 tweets (including retweets) per day over the first temporary suspension period of 308 days from December 9, 2019 until October 12, 2020, against an average of 977 tweets (including retweets) per day during the exact same period one year earlier. Finally, panel $(b)$ points towards the limitations of suspending an account to limit the spread of its content.

\subsubsection{Youtube}

In this section, we turn to the channel's temporary or permanent suspension policy of Youtube. Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed. For the second time the channel will start receiving strikes. A first strike results in limiting the access of the Youtube channel  for one week, like uploading videos, streaming and other activities. Then a second strike is similar but the suspension will be for two weeks. A third strike results in the termination of the channel. The strike count of a channel lasts 90 days.  In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning.\footnote{See the ``Community Guidelines strike basics''. Youtube help, Google Developers,  \href{https://support.google.com/youtube/answer/2802032?hl=en. Accessed 21 6 2021}{https://support.google.com/youtube/answer/2802032?hl=en. Accessed 21 6 2021}.} To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two Youtube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.

\smallskip

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{./img/oann/fig1_oann.png}
	\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}. This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{Reference?} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021. For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}

\smallskip

In addition, as shown in figure \ref{fig1_oann} when comparing the week before the suspension from 2020/11/17 to 2020/11/23 and one week after from 2020/12/01 to 2020/12/07 it was found that the view count had decreased by ($-45\%$ or $-60\%$), even though the posted number of videos was similar (before $81$ videos; after 93 videos or 86 videos). In other words, the suspension period may have a good impact on reducing the audience interest or reach to the channel. Besides that, OANN decided to move officially to Rumble on March 17, 2021 as announced on their Twitter account (see figure \ref{fig2_oann}) and their upload activity on their Youtube channel is close to zero since that announcement.

\begin{figure}
	\centering
	\includegraphics[scale=0.2]{./img/oann/fig3_oann.png}
	\includegraphics[scale=0.3]{./img/tony/fig3_tony.png}
	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}. Panel (b): Tony Heller's tweet after getting suspended from Youtube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
	\label{fig2_oann}
\end{figure}

\smallskip

We now turn to our second example, the temporary suspension of the Youtube channel Tony Heller. This channel got its first strike after posting a video about an anti-covid-lockdown doctor getting arrested (see screenshot in figure \ref{fig2_oann}). The suspension period was for one week from September 29 until October 5. We applied the same methods as in the previous example for the data collection. Figure \ref{fig2_oann} shows the daily number of videos uploaded by the channel. The suspension period can be observed clearly in the historical data of the channel. Moreover, observing the reach of the audience using view counts one week before the suspension starting from 2020/09/22 to 2020/09/28 and one week after the suspension from 2020/10/06 to 2020/10/12 the channel witnessed a drop of $-65\%$ and the videos published in the channel were less by $-16\%$.

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{./img/tony/fig1_tony.png}
	\includegraphics[scale=0.3]{./img/tony/fig2_tony.png}
	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Panel (b): accumulated view counts for videos uploaded by the same Youtube channel. The date corresponds to the videos’  publishing date. 
}
	\label{fig1_tony}
\end{figure}

\subsection{Blocking links}

A third measure that main stream social media platforms can apply is to prevent users from sharing specific types of content, instead of deleting the content after posting, or users accounts. We will study here how the platforms prevent users from sharing urls coming from specific domain names.

\subsubsection{Facebook}

{\color{pink}The Beauty of life}

\subsection{Reducing the visibility}

Mainstream Social Media platforms can reduce the visibility of the content created or shared by specific users, whenever they violate the platforms' rules. The implementation of this policy varies across platforms and is not easy to verify ex-post. In what follows we provide means to verify this policy on Twitter and Facebook.

\subsubsection{Facebook}

One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through ranking. Facebook ranks each post and ad with a relevancy score, a high score leading to a high likelihood of the post or the ad appearing in someone’s newsfeed. Facebook can thus make a post or a whole account less visible by decreasing the rank of its content [12]. Such {\it reduce} action should be visible in the engagement metrics of the posts: if a post reaches less users because of a lower ranking, it is less likely to receive likes, comments and shares.

Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist [8], was classified among websites that have posted deceptive content according to FactCheck.org [9], and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource [10]. On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material [7].

To verify the measure, we used the CrowdTangle API at the ‘/posts/search’ endpoint (see the documentation [11] for more details) to collect the 37,242 Facebook public posts that shared a link containing ‘infowars.com’ and that were published between January 1, 2019 and December 31, 2020.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the 27,721 posts directly sharing an Infowars link.} The command used can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{here}.

The number of public posts sharing an Infowars link remained globally stable in 2019 (Figure X4 top panel), thus Facebook’s announced ‘ban’ did not appear to prevent users from sharing an Infowars link. Interestingly a clear drop in engagement was observed on May 2, 2019 (Figure X4 bottom panel). The number of reactions per post decreased by -94\% when we compared the two months before and after May 2, 2019, the shares decreased by -96\%, and the comments by -93\%.

This would suggest that Facebook’s measure taken in May 2019 is actually not a ban, but would rather correspond to a ‘reduce’ action, as users could still post Infowars links, but these posts generated vastly less engagement. It should be noted that the engagement metrics increased again at the end of 2019 / beginning of 2020, suggesting that the reducing measure may have been lifted a few months after its implementation.

As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ‘/search/articles’ endpoint of the Buzzsumo API, to gather more complete Facebook data. We collected the engagement data for the 14,232 articles crawled by Buzzsumo from the Infowars website between January 1, 2019 and Decembre 31, 2020. The command can be found here.
We observe that the articles published after May 2, 2019 received less Facebook engagement than the ones published before (Figure X5), with a percentage change of -97\% for the reactions, -59\% for the shares and -97\% for the comments. An increase in engagement was also observed in 2020. It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links during a few months in 2019.

We found irregularities in the number of Infowars articles collected from Buzzsumo. While Infowars usually publishes 20-30 articles per day, only 53 articles were collected in the 31-day period between June 11 to July 11, 2020. A temporary crawling problem coming from Buzzsumo may have caused this lack of data. Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.

\subsubsection{Twitter}

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{./img/globalresearch_2021-06-14.png}
	\includegraphics[scale=0.3]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
	\caption{Screenshots taken on June 14, 2021. }
	\label{fig3}
\end{figure}

Twitter can take action against a tweet which violates the Twitter rules\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.}, by limiting its visibility on users' timelines and in search results. To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}

\smallskip

%To illustrate we provide two examples linked to the Twitter accounts of the websites $globalresearch.ca$ and $off$-$guardian.org$. Both websites have several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and for $off-guardian.org$ see \href{https://mediabiasfactcheck.com/offguardian/}{https://mediabiasfactcheck.com/offguardian/}.  }

The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; that was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021. But to the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented. Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}). Furthermore, $globalresearch.ca$ has multiple failed fact-checks, see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}} When a user searches via the twitter search-box a url link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June 14, 2021. To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January 1, 2021 until June 10, 2021.  As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the URL link {\it globalresearch.ca} throughout May 2021 and the first week of June 2021. Hence, the visibility of tweets containing this URL link has been reduced because users can no longer access tweets containing the URL link {\it globalresearch.ca} via the search box. Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(c)$
 of figure \ref{fig4}, found by taking the tweet ID of one of the collected tweets via the Twitter API. Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}. Hence, the users who tweet articles from the {\it globalresearch.ca} website receive positive engagement from their own followers. Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (d) in figure \ref{fig4}).

\begin{figure}
\centering
\includegraphics[scale=0.3]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
\includegraphics[scale=0.3]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
\includegraphics[scale=0.3]{./img/globalresearch/tweet.png} 
\includegraphics[scale=0.3]{./img/globalresearch/warning.png}
%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearch.jpg} 
%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearchall_time.jpg}
\caption{}
\label{fig4}
\end{figure}

%We provide a second example with the website $off$-$guardian.org$. Unlike the previous example, the Twitter account linked to this website is not currently\footnote{The account can be accessed via the Twitter handle $@OffGuardian0$ and we verified on June 13, 2021 that the account is not suspended.} suspended.

%off guardian: people put space before .com but they can still share off-guardian links  (test Héloïse). why do they do that? 
%warning page before accessing the website - always 
%twitter API doesn't return the tweets tweeted by off-guardian themselves dating back to 2015
%twitter API returns both tweets with . org and .org: 320 tweets from 2017-01-15 until 2021-06-11. But off-guardian themselves posted one of their own links on June 16 2021. 
%minet returns almost nothing : 43 tweets 
% the tweets created by Off-Guardian: don't come up in the search box. Unlike nytimes.com their articles do appear in the search box , published by themselves! 
% Heloise's tweet June 15 doesn't come up in the API ! 
% people use variants with * and dot , so that they can find tweets speaking about those domains

\subsubsection{Youtube}

{\color{pink} What about something about recommendations ? authoritative content  }
\subsection{Flags and Notices}

\subsubsection{Twitter}

\href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}

We gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a not-for-profit organization verifying the credibility of influential claims and media coverage that claims to be scientific. As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets were marked with the notice { ``Get the facts about COVID-19''}, $5$ tweets were marked with { ``Learn about US 2020 election security efforts''} and only $1$ tweet was marked with the notice {``This claim about election fraud is disputed''}. Furthermore, we noticed that there exists tweets that share the exact same URL links marked as False, yet only a few get marked by a notice.

\smallskip

Furthermore,

\section{Discussion}

{ \color{pink} For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria. We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore. This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.

\bigskip

To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent. But too much transparency on how the regulation policies are exactly implemented can actually backfire. For example YouTube is certainly applying an 'information' banner on all videos mentioning Covid and related terms in their title. Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'. If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation. There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.

\bigskip

There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms. For example Newsguard, blablabla... In this tweet, we can see the interface of XXX being used in this study from a data journalist: https://twitter.com/Shayan86/status/1394742784683298818/photo/2

\bigskip

Recommendation: inform about sources, example inform users that this user shared x failed fact-checks. }
%→ Littérature liée aux effets psychologiques 
%→ multi-platforming, indirect effects, etc. 
%→ strategies

\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
\newpage

\bibliography{proj1}{}
\bibliographystyle{plain}

\end{document}

%Guillaume Plique, Pauline Breteau, Jules Farjas, Héloïse Théro, & Jean Descamps. (2019, October 14). Minet, a webmining CLI tool & library for python. Zenodo. http://doi.org/10.5281/zenodo.4564399

### 2021-06-30 article/test.tex
first iteration

--- 2021-06-30 article/draft.tex
@@
-\documentclass{article}
-%\documentclass[a4paper,12pt,twoside]{book}
-\usepackage{amsmath}
-\usepackage{cite}
-%\usepackage{tikz}
-\usepackage{bm}
-\usepackage{tikz,tkz-tab}
-\usepackage{amsfonts}%
-\usepackage{amssymb}%
-\usepackage{hyperref}
-\usepackage{mathtools}
-%\usepackage{subcaption}
-\usepackage{color}
-\usepackage{setspace}
-\usepackage{empheq}
-\usepackage{bbm, dsfont}
-\usepackage{dsfont}
-\usepackage{mathtools}
-\usepackage{geometry}
-\usepackage{enumitem} 
-\usepackage[bottom]{footmisc}
-\usetikzlibrary{arrows}
-\usepackage{lscape}
-\usepackage{tcolorbox}
-\usepackage{caption}
-%\usepackage{graphicx}
-\usepackage{subfig}
-\usepackage{multirow}
-\usepackage{cite}
-\usetikzlibrary{shapes,snakes}
-\renewcommand{\labelitemi}{$\bullet$}
-\renewcommand{\labelitemii}{$\diamond$}
+%
+% File tto2019.tex
+%
+%% Based on the style files for ACL 2019, ACL 2018, NAACL 2018/19, which were
+%% Based on the style files for ACL-2015, with some improvements
+%%  taken from the NAACL-2016 style
+%% Based on the style files for ACL-2014, which were, in turn,
+%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
+%% EACL-2009, IJCNLP-2008...
+%% Based on the style files for EACL 2006 by 
+%%e.agirre@ehu.es or Sergi.Balari@uab.es
+%% and that of ACL 08 by Joakim Nivre and Noah Smith
 
-\usepackage{titlesec}
+\documentclass[11pt,a4paper]{article}
+\usepackage[hyperref]{tto2019}
+\usepackage{times}
+\usepackage{latexsym}
+\usepackage{multicol}
+\usepackage{graphicx}
 
-\setcounter{secnumdepth}{4}
+\usepackage{url}
 
-\titleformat{\paragraph}
-{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
-\titlespacing*{\paragraph}
-{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+%\aclfinalcopy % Uncomment this line for the final submission
 
-\newtheorem{definition}{Definition}
+%\setlength\titlebox{5cm}
+% You can expand the titlebox if you need extra space
+% to show all the authors. Please do not make the titlebox
+% smaller than 5cm (the original size); we will check this
+% in the camera-ready version and ask you to change it back.
 
-\usetikzlibrary{positioning}
-\tikzset{main node/.style={circle,draw,minimum size=0.5cm,inner sep=0pt},
-            }
+\newcommand\BibTeX{B\textsc{ib}\TeX}
 
-%-------------------------------------------
-\newtheorem{example}{Example}
-\newtheorem{theorem}{Theorem}
-\newtheorem{acknowledgement}[theorem]{Acknowledgement}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{assumption}{Assumption}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}{Lemma}
-\newtheorem{observation}{Observation}
-\newtheorem{notation}[theorem]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
+\title{Instructions for TTO 2019 Proceedings}
+
+\author{First Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  \texttt{email@domain} \\\And
+  Second Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  \texttt{email@domain} \\}
+
+\date{}
 
 \begin{document}
-\title{Very Preliminary Draft}
 \maketitle
+\begin{abstract}
 
-%Using social media data to verify the platforms' regulation policies regarding misinformation"
+\end{abstract}
 
@@
 Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense.
-\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.''  }
 
@@
 laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws.
-Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}.
-We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}
+Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{https://transparency.fb.com/data/content\-restrictions}.
+We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{https://transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}
 
@@
 Furthermore, MSMP are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated.
-Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam.\footnote{For an exhaustive overview of the community standards of Facebook, see: \href{https://www.facebook.com/communitystandards/}{facebook.com/communitystandards/}.
-For the Twitter  Rules see: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}, and for Youtube community guidelines see: \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}.} While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries.
-
-\smallskip
-
+Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam.\footnote{For an exhaustive overview of the community guidelines of Facebook, see: \href{https://www.facebook.com/communitystandards/}{https://www.facebook.com/communitystandards/}, for Twitter see: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}, and for Youtube see: \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}.} While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries.
 In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al.
 (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
-The rise of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
-Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
-{\color{red} Fact-checkers + no laws or not so much.}
+The rise of social networking platforms over the last decade in terms of number of users worldwide, has modified the information ecosystem in terms of production of information and its mediation.
+In particular, many users can now produce content which contains news related information without having to abide by strict editorial processes that ensure accuracy of information.
 
@@
 Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
-{\color{red} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g.
-to tackle terrorism) and apply it to misinformation+ idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}
 
-\smallskip
+In this article, we will explain how to verify with data mining MSMP's actions regarding content with low credibility or false information, through a series of examples for different actions and platforms.
+For the purpose of clarity, we focus on three platforms: Facebook, Twitter and Youtube.
+Both Facebook and Youtube are in the top 3 most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}.
 
-In the present article, we will explain how to verify with data mining MSMP's actions regarding content with low credibility or false information, through a series of examples for different actions and platforms.
-For the purpose of clarity, we only focus on three platforms: Facebook, Twitter and Youtube.
-Both Facebook and Youtube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}.
-More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited MSMP, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
-We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.
-We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
-We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article.
+In this article, we survey a number of common policies used in order to tackle misinformation, across the three above cited MSMP, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
+Second, we provide simple means to check how those policies are implemented in practice and discuss how to assess their impact, when possible.
 Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
 %the announced policy for a specific user was implemented or not.
-
-%Second, we provide simple means to check how those policies are implemented in practice and discuss how to assess their impact, when possible.
-
-%We do not aim for an exhaustive list of methods on how to investigate the platforms’ policies against misinformation, but rather to share the methods we currently know, and that we think can be useful to researchers or journalists interested in that question.
-We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.
-
 \bigskip
@@
 
-\begin{table}[]
-\centering
-\begin{tabular}{|l|l|l|l}
-
-\hline
-&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{Web Scraping}                                                                                                                                                                   \\ \hline
-Facebook & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}: public content insights tool \\ owned and operated by Facebook.
+%\begin{table}[]
+%\centering
+%\begin{tabular}{|l|l|l|l}
+%
+%\hline
+%&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{Web Scraping}                                                                                                                                                                   \\ \hline
+%Facebook & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}: public content insights tool \\ owned and operated by Facebook.
 \\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content database  \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
-\\ \hline
-Twitter  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet twitter scrape}}                                                                                                                                                                           \\ \hline
-Youtube  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
-\end{tabular}
-\caption{Data collection}
-\label{tab1}
-\end{table}
-
- %We We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.
-
-%CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.
-BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.
-
-%Section 230 in the US + EU 
-%Pressure to moderate and mix-up of platforms with public square… 
-%Rôle dans la production/médiation : P-M-R 
-%Pourquoi faut-il vérifier leurs politiques ? D’une part parce que ce sont les plateformes elles-mêmes qui annoncent leurs effets. D’autre part beaucoup de choses indirectes. 
-%
-%Add disclaimer in a footnote early on in the document : document not meant to be an exhaustive overview of all the existing regulations and point to three or four main legal sources for exhaustive references.
-
-%Such policies include the introduction of notices (Twitter, see link) or flags (Facebook, see…) to signal to users inaccurate or false content, the temporary or permanent suspension of accounts (Twitter) or pages (Facebook), reducing the visibility of posts or pages (Facebook), or blocking users from sharing specific URL links (see link).
-The objective of this article is twofold.
-First, we study the impact of a number of  implemented measures by mainstream platforms to tackle (mis)disinformation.
+%\\ \hline
+%Twitter  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet twitter scrape}}                                                                                                                                                                           \\ \hline
+%Youtube  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
+%\end{tabular}
+%\caption{Data collection}
+%\end{table}
 
@@
 
-\subsubsection{Facebook}
+\subsubsection{Twitter}
 
-When an account is permanently suspended by Facebook, it disappears from the platform (so its data cannot be scrapped anymore), and its data also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.}
-
-Interestingly, Facebook is regularly publishing a monthly {\it coordinated inauthentic behavior} report where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the April 2021 report for an example: \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
-
-Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed.
-For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API.
-Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{ (see the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data.
-We can verify on figure \ref{fig1_fb} that the {\it Donald J.
-Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.
+%\begin{figure}
+%\centering
+%\includegraphics[scale=0.35]{./img/lifesite.jpg} 
+%\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
+%\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021.
+Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021.
+}
+%\label{fig2}
+%\end{figure}
 
@@
 \centering
-	\includegraphics[scale=0.35]{./img/fb/fig1_fb.png}
-	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J.
-Trump} between January $1$, $2020$ and June $15$, $2021$.
-The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
-	\label{fig1_fb}
-\end{figure}
-
-\subsubsection{Twitter}
-
-{\color{red} N.B. Manual decision, not the automatic strike system}
-\begin{figure}
-\centering
-\includegraphics[scale=0.35]{./img/lifesite.jpg} 
-\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
+\begin{multicols}{1}
+    \includegraphics[scale=0.32]{./img/lifesite.jpg}\par 
+    %\includegraphics[width=\linewidth]{./img/lifesite_rolling_7_lifesite.jpg}\par 
+    \end{multicols}
+\begin{multicols}{1}
+   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
+    \includegraphics[scale=0.32]{./img/lifesite_rolling_7_lifesite.jpg}\par
+\end{multicols}
 \caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021.
-Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021.
-}
+Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021.}
 \label{fig2}
@@
 
-In this section, we discuss one case of temporary suspension on Twitter.\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}.
+In this section, we discuss one case of temporary suspension on Twitter.\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason of the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}.
 Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}.
@@
 
+\subsubsection{Facebook}
+
+Unfortunately when an account is permanently suspended by Facebook, it disappears from the platform (so its data cannot be scrapped anymore), and its data also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
+We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
+This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.
+
+Interestingly, Facebook is regularly publishing a monthly {\it coordinated inauthentic behavior} report where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the April 2021 report for an example: \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
+
+Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed.
+For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API.
+Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{ (see the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data.
+We can verify on figure \ref{fig1_fb} that the {\it Donald J.
+Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.
+
+%\begin{figure}
+%	\centering
+%	%\includegraphics[scale=0.35]{./img/fb/fig1_fb.png}
+%	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J.
+Trump} between January $1$, $2020$ and June $15$, $2021$.
+The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
+%	\label{fig1_fb}
+%\end{figure}
+
+\begin{figure}
+\begin{multicols}{1}
+    \includegraphics[scale=0.22]{./img/fb/fig1_fb.png}\par 
+   % \includegraphics[width=\linewidth]{./img/lifesite_rolling_7_lifesite.jpg}\par 
+    \end{multicols}
+%\begin{multicols}{2}
+   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
+ %   \includegraphics[width=\linewidth]{./img/lifesite_rolling_7_lifesite.jpg}\par
+%\end{multicols}
+\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J.
+Trump} between January $1$, $2020$ and June $15$, $2021$.
+The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
+\label{fig1_fb}
+\end{figure}
+
 \subsubsection{Youtube}
 
-In this section, we turn to the channel's temporary or permanent suspension policy of Youtube.
+In this section, we turn to the channel temporary or permanent suspension policy of Youtube.
 Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed.
@@
 
+%\begin{figure}
+%	\centering
+%	%\includegraphics[scale=0.25]{./img/oann/fig1_oann.png}
+%	%\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
+%	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
+Panel (b): accumulated view counts for videos.
+The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints.
+}
+%	\label{fig1_oann}
+%\end{figure}
+
 \begin{figure}
 \centering
-	\includegraphics[scale=0.25]{./img/oann/fig1_oann.png}
-	\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
+\begin{multicols}{1}
+    \includegraphics[scale=0.3]{./img/oann/fig1_oann.png}\par 
+    %\includegraphics[width=\linewidth]{./img/lifesite_rolling_7_lifesite.jpg}\par 
+    \end{multicols}
+\begin{multicols}{1}
+   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
+    \includegraphics[scale=0.3]{./img/oann/fig2_oann.png}\par
+\end{multicols}
 \caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
@@
 
+%\begin{figure}
+%	\centering
+%	%\includegraphics[scale=0.2]{./img/oann/fig3_oann.png}
+%	%\includegraphics[scale=0.3]{./img/tony/fig3_tony.png}
+%	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), see: \href{https://twitter.com/OANN/status/1372238828425998336}{https://twitter.com/OANN/status/1372238828425998336}.
+Panel (b): Tony Heller's tweet after getting suspended from Youtube, see \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{https://twitter.com/Tony\_Heller/status/1310703852769796097}.}
+%	\label{fig2_oann}
+%\end{figure}
+
 \begin{figure}
 \centering
-	\includegraphics[scale=0.2]{./img/oann/fig3_oann.png}
-	\includegraphics[scale=0.3]{./img/tony/fig3_tony.png}
-	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
-Panel (b): Tony Heller's tweet after getting suspended from Youtube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
+\begin{multicols}{1}
+
+    \includegraphics[scale=0.25]{./img/oann/fig3_oann.png}\par 
+    %\includegraphics[scale=0.2]{./img/tony/fig3_tony.png}\par 
+    \end{multicols}
+\begin{multicols}{1}
+
+   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
+    \includegraphics[scale=0.25]{./img/tony/fig3_tony.png}\par
+\end{multicols}
+\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), tweet ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
+Panel (b): Tony Heller's tweet after getting suspended from Youtube, tweet ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.
+}
 \label{fig2_oann}
@@
 
+%\begin{figure}
+%	\centering
+%	%\includegraphics[scale=0.3]{./img/tony/fig1_tony.png}
+%	%\includegraphics[scale=0.3]{./img/tony/fig2_tony.png}
+%	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
+Panel (b): accumulated view counts for videos uploaded by the same Youtube channel.
+The date corresponds to the videos’  publishing date.
+%}
+%	\label{fig1_tony}
+%\end{figure}
+
 \begin{figure}
 \centering
-	\includegraphics[scale=0.3]{./img/tony/fig1_tony.png}
-	\includegraphics[scale=0.3]{./img/tony/fig2_tony.png}
+\begin{multicols}{1}
+
+    \includegraphics[scale=0.33]{./img/tony/fig1_tony.png}\par 
+    %\includegraphics[scale=0.2]{./img/tony/fig3_tony.png}\par 
+    \end{multicols}
+\begin{multicols}{1}
+
+   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
+    \includegraphics[scale=0.33]{./img/tony/fig2_tony.png}\par
+\end{multicols}
 \caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
@@
  }
-	\label{fig1_tony}
+\label{fig2_oann}
 \end{figure}
@@
 
-{\color{pink}The Beauty of life}
+The Beauty of life
 
@@
 Mainstream Social Media platforms can reduce the visibility of the content created or shared by specific users, whenever they violate the platforms' rules.
-The implementation of this policy varies across platforms and is not easy to verify ex-post.
+The implementation of this policy varies accros platforms and is not easy to verify ex-post.
 In what follows we provide means to verify this policy on Twitter and Facebook.
@@
 
-One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through ranking.
-Facebook ranks each post and ad with a relevancy score, a high score leading to a high likelihood of the post or the ad appearing in someone’s newsfeed.
-Facebook can thus make a post or a whole account less visible by decreasing the rank of its content [12].
-Such {\it reduce} action should be visible in the engagement metrics of the posts: if a post reaches less users because of a lower ranking, it is less likely to receive likes, comments and shares.
-
-Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist [8], was classified among websites that have posted deceptive content according to FactCheck.org [9], and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource [10].
-On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material [7].
-
-To verify the measure, we used the CrowdTangle API at the ‘/posts/search’ endpoint (see the documentation [11] for more details) to collect the 37,242 Facebook public posts that shared a link containing ‘infowars.com’ and that were published between January 1, 2019 and December 31, 2020.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the 27,721 posts directly sharing an Infowars link.} The command used can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{here}.
-
-The number of public posts sharing an Infowars link remained globally stable in 2019 (Figure X4 top panel), thus Facebook’s announced ‘ban’ did not appear to prevent users from sharing an Infowars link.
-Interestingly a clear drop in engagement was observed on May 2, 2019 (Figure X4 bottom panel).
-The number of reactions per post decreased by -94\% when we compared the two months before and after May 2, 2019, the shares decreased by -96\%, and the comments by -93\%.
-
-This would suggest that Facebook’s measure taken in May 2019 is actually not a ban, but would rather correspond to a ‘reduce’ action, as users could still post Infowars links, but these posts generated vastly less engagement.
-It should be noted that the engagement metrics increased again at the end of 2019 / beginning of 2020, suggesting that the reducing measure may have been lifted a few months after its implementation.
-
-As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ‘/search/articles’ endpoint of the Buzzsumo API, to gather more complete Facebook data.
-We collected the engagement data for the 14,232 articles crawled by Buzzsumo from the Infowars website between January 1, 2019 and Decembre 31, 2020.
-The command can be found here.
-We observe that the articles published after May 2, 2019 received less Facebook engagement than the ones published before (Figure X5), with a percentage change of -97\% for the reactions, -59\% for the shares and -97\% for the comments.
-An increase in engagement was also observed in 2020.
-It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links during a few months in 2019.
-
-We found irregularities in the number of Infowars articles collected from Buzzsumo.
-While Infowars usually publishes 20-30 articles per day, only 53 articles were collected in the 31-day period between June 11 to July 11, 2020.
-A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
-Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
+Infowars
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.3]{./img/globalresearch_2021-06-14.png}
-	\includegraphics[scale=0.3]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
-	\caption{Screenshots taken on June 14, 2021. }
-	\label{fig3}
-\end{figure}
+%\begin{figure}
+%	\centering
+%	%\includegraphics[scale=0.3]{./img/globalresearch_2021-06-14.png}
+%	%\includegraphics[scale=0.3]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
+%	\caption{Screenshots taken on June 14, 2021. }
+%	\label{fig3}
+%\end{figure}
+
+%\begin{figure}
+%\centering
+%\begin{multicols}{1}
+%
+%    \includegraphics[scale=0.33]{./img/globalresearch_2021-06-14.png}\par 
+%    %\includegraphics[scale=0.2]{./img/tony/fig3_tony.png}\par 
+%    \end{multicols}
+%\begin{multicols}{1}
+%
+%   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
+%    \includegraphics[scale=0.33]{./img/globalresearch_14_06_2021_16pm_UTC.png}\par
+%\end{multicols}
+%\caption{Screenshots taken on June 14, 2021. 
+% }
+%\label{fig3}
+%\end{figure}
 
 Twitter can take action against a tweet which violates the Twitter rules\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.}, by limiting its visibility on users' timelines and in search results.
-To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
+To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} .
+}
 
@@
 
-\begin{figure}
+%\begin{figure}
+%\centering
+%%\includegraphics[scale=0.3]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
+%%\includegraphics[scale=0.3]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
+%%\includegraphics[scale=0.3]{./img/globalresearch/tweet.png} 
+%%\includegraphics[scale=0.3]{./img/globalresearch/warning.png}
+%\caption{Panel (a):}
+%\label{fig4}
+%\end{figure}
+
+%\begin{figure}
+%\centering
+%\begin{multicols}{1}
+%
+%    \includegraphics[scale=0.33]{./img/globalresearch_2021-06-14.png}\par 
+%    %\includegraphics[scale=0.2]{./img/tony/fig3_tony.png}\par 
+%    \end{multicols}
+%\begin{multicols}{1}
+%
+%   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
+%    \includegraphics[scale=0.33]{./img/globalresearch_14_06_2021_16pm_UTC.png}\par
+%\end{multicols}
+%\caption{Screenshots taken on June 14, 2021. 
+% }
+%\label{fig3}
+%\end{figure}
+
+\begin{figure*}
 \centering
-\includegraphics[scale=0.3]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
-\includegraphics[scale=0.3]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
-\includegraphics[scale=0.3]{./img/globalresearch/tweet.png} 
-\includegraphics[scale=0.3]{./img/globalresearch/warning.png}
-%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearch.jpg} 
-%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearchall_time.jpg}
-\caption{}
+\begin{multicols}{1}
+
+    \includegraphics[scale=0.33]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg}\par 
+    \includegraphics[scale=0.33]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}\par 
+    \end{multicols}
+\begin{multicols}{1}
+
+  %  \includegraphics[scale=0.33]{./img/globalresearch/tweet.png}\par
+    \includegraphics[scale=0.33]{./img/globalresearch/warning.png}\par
+    \includegraphics[scale=0.33]{./img/globalresearch_14_06_2021_16pm_UTC.png}\par
+\end{multicols}
+
+%\begin{multicols}{1}
+%
+%  %  \includegraphics[scale=0.33]{./img/globalresearch_2021-06-14.png}\par
+%    \includegraphics[scale=0.33]{./img/globalresearch_14_06_2021_16pm_UTC.png}\par
+%\end{multicols}
+\caption{ 
+ }
 \label{fig4}
-\end{figure}
+\end{figure*}
 
@@
 % Heloise's tweet June 15 doesn't come up in the API ! 
-% people use variants with * and dot , so that they can find tweets speaking about those domains
-
-\subsubsection{Youtube}
-
-{\color{pink} What about something about recommendations ? authoritative content  }
+% people use variants with * and dot , so that they can find tweets speakign about those domains
 \subsection{Flags and Notices}
-
-\subsubsection{Twitter}
-
-\href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}
-
-We gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a not-for-profit organization verifying the credibility of influential claims and media coverage that claims to be scientific.
-As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$.
-This data collection resulted in $323$ $938$ tweets, excluding retweets.
-Only $28$ tweets were marked with the notice { ``Get the facts about COVID-19''}, $5$ tweets were marked with { ``Learn about US 2020 election security efforts''} and only $1$ tweet was marked with the notice {``This claim about election fraud is disputed''}.
-Furthermore, we noticed that there exists tweets that share the exact same URL links marked as False, yet only a few get marked by a notice.
-
-\smallskip
-
-Furthermore,
-
 \section{Discussion}
 
-{ \color{pink} For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
-We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
-This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.
-
-\bigskip
-
-To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
-But too much transparency on how the regulation policies are exactly implemented can actually backfire.
-For example YouTube is certainly applying an 'information' banner on all videos mentioning Covid and related terms in their title.
-Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'.
-If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation.
-There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.
-
-\bigskip
-
-There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
-For example Newsguard, blablabla...
-In this tweet, we can see the interface of XXX being used in this study from a data journalist: https://twitter.com/Shayan86/status/1394742784683298818/photo/2
-
-\bigskip
-
-Recommendation: inform about sources, example inform users that this user shared x failed fact-checks. }
 %→ Littérature liée aux effets psychologiques 
@@
 
-\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
 \newpage
@@
 \end{document}
-
-%Guillaume Plique, Pauline Breteau, Jules Farjas, Héloïse Théro, & Jean Descamps. (2019, October 14). Minet, a webmining CLI tool & library for python. Zenodo. http://doi.org/10.5281/zenodo.4564399

### 2021-06-30 article/draft.tex
just testing
just testing again!

@@
 
-%Using social media data to verify the platforms' regulation policies regarding misinformation"
+Using social media data to verify the platforms' regulation policies regarding ``misinformation''
 
@@
 Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
-{\color{red} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g.
+{\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g.
 to tackle terrorism) and apply it to misinformation+ idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}

### 2021-06-30 code/create_figures.py
Update create_figures.py:with youtube figures

@@ -1,5 +1,6 @@
 import os
 from datetime import datetime, timedelta
+import datetime
 
 import pandas as pd
 import numpy as np
@@ -194,11 +195,118 @@ def create_facebook_buzzsumo_infowars_figure():
     plt.ylim(0, 3000)
 
     plt.tight_layout()
-    save_figure(figure_name='facebook_buzzsumo_infowars.png')    
+    save_figure(figure_name='facebook_buzzsumo_infowars.png')
+
+def preprocess_youtube_data():
+    oann = import_data('One America News Network_youtube_data.csv')
+    tony_heller = import_data('Tony Heller_youtube_data.csv')
+    list_df = [oann,tony_heller]
+    for df in list_df:
+        df['published_at'] = pd.to_datetime(df['published_at'])
+        df['published_at'] = pd.to_datetime(df['published_at'], format='%m/%d/%Y')
+        df['date'] = ''
+        for i in range(0, df.shape[0]):
+            df['date'].iloc[i] = df['published_at'].iloc[i].date()
+            if (df['comments'].iloc[i] == 'non'):
+                df['comments'].iloc[i] = 0
+            if (df['likes'].iloc[i] == 'non'):
+                df['likes'].iloc[i] = 0
+            if (df['dislikes'].iloc[i] == 'non'):
+                df['dislikes'].iloc[i] = 0
+        df['likes'] = df['likes'].astype('int64')
+        df['dislikes'] = df['dislikes'].astype('int64')
+        df['comments'] = df['comments'].astype('int64')
+        df['view_counts'] = df['view_counts'].astype('int64')
+    return oann,tony_heller
+
+
+
+
+def plot_view_count_youtube(data, date_begin_sus, date_end_sus, date_begin_graph, date_end_graph, height_keyword,fig_name):
+    window_num = 1
+
+    df_tlm_views = data.groupby(['published_at'])['view_counts'].sum().to_frame('view_counts')
+
+    df_tlm_views = df_tlm_views.resample('D').sum().fillna(0).reset_index()
+    df_tlm_vol_rolling_views = df_tlm_views.groupby(['published_at']).mean().rolling(window=window_num,
+                                                                                     win_type='triang',
+                                                                                     center=True).mean()
[…]

### 2021-06-30 code/create_figures.py
create_figure.py: fix x label cutoff

@@ -259,6 +259,7 @@ def plot_view_count_youtube(data, date_begin_sus, date_end_sus, date_begin_graph
     plt.ylabel('View count')
     plt.xlabel('Date')
     plt.legend()
+    plt.tight_layout()
     save_figure(figure_name=fig_name)
 
 
@@ -289,6 +290,7 @@ def plot_video_count_youtube(data, date_begin_sus, date_end_sus, date_begin_grap
     plt.ylabel('Video count')
     plt.xlabel('Date')
     plt.legend()
+    plt.tight_layout()
     save_figure(figure_name=fig_name)
 
 

### 2021-06-30 code/create_figures.py
syntax fixing

@@ -197,6 +197,7 @@ def create_facebook_buzzsumo_infowars_figure():
     plt.tight_layout()
     save_figure(figure_name='facebook_buzzsumo_infowars.png')
 
+
 def preprocess_youtube_data():
     oann = import_data('One America News Network_youtube_data.csv')
     tony_heller = import_data('Tony Heller_youtube_data.csv')
@@ -220,13 +221,10 @@ def preprocess_youtube_data():
     return oann,tony_heller
 
 
-
-
-def plot_view_count_youtube(data, date_begin_sus, date_end_sus, date_begin_graph, date_end_graph, height_keyword,fig_name):
+def plot_view_count_youtube(data, date_begin_sus, date_end_sus, date_begin_graph, date_end_graph, height_keyword, fig_name):
     window_num = 1
 
     df_tlm_views = data.groupby(['published_at'])['view_counts'].sum().to_frame('view_counts')
-
     df_tlm_views = df_tlm_views.resample('D').sum().fillna(0).reset_index()
     df_tlm_vol_rolling_views = df_tlm_views.groupby(['published_at']).mean().rolling(window=window_num,
                                                                                      win_type='triang',
@@ -240,6 +238,7 @@ def plot_view_count_youtube(data, date_begin_sus, date_end_sus, date_begin_graph
     fig, ax1 = plt.subplots(1, figsize=(15, 4))
     plt.locator_params(axis='y', nbins=4)
     plt.setp(ax1.get_xticklabels(), rotation=45)
+
     ax1.xaxis.set_tick_params(length=0)
     ax1.plot(df_tlm_vol_rolling_views['published_at'],
              df_tlm_vol_rolling_views['view_counts'],
@@ -249,7 +248,6 @@ def plot_view_count_youtube(data, date_begin_sus, date_end_sus, date_begin_graph
     ax1.spines['right'].set_visible(False)
     ax1.spines['left'].set_visible(False)
     ax1.spines['top'].set_visible(False)
-
     ax1.grid(axis="y")
     ax1.xaxis.set_tick_params(length=0)
 
@@ -263,8 +261,7 @@ def plot_view_count_youtube(data, date_begin_sus, date_end_sus, date_begin_graph
     save_figure(figure_name=fig_name)
 
 
-
-def plot_video_count_youtube(data, date_begin_sus, date_end_sus, date_begin_graph, date_end_graph, height_keyword,fig_name):
[…]

### 2021-07-01 code/create_figures.py
add thebl bz figure

@@ -1,6 +1,5 @@
 import os
-from datetime import datetime, timedelta
-import datetime
+from datetime import datetime, timedelta, date
 
 import pandas as pd
 import numpy as np
@@ -22,6 +21,8 @@ def save_figure(figure_name):
 
 def arrange_plot(ax, df):
 
+    plt.legend()
+
     ax.set_frame_on(False)
     ax.grid(axis="y")
     plt.locator_params(axis='y', nbins=4)
@@ -36,7 +37,7 @@ def arrange_plot(ax, df):
     plt.xlim(np.min(df['date']), np.max(df['date']))
 
 
-def create_suspension_facebook_trump_figure():
+def create_facebook_trump_figure():
 
     print()
 
@@ -54,18 +55,48 @@ def create_suspension_facebook_trump_figure():
 
     ax = plt.subplot(111)
     plt.plot(serie_to_plot, color='royalblue', label='Number of posts per day')
-    plt.legend()
-
     arrange_plot(ax, df)
     plt.axvline(np.datetime64("2021-01-07"), color='C3', linestyle='--')
     plt.xlim(
         np.datetime64(datetime.strptime('2019-12-31', '%Y-%m-%d')), 
         np.datetime64(datetime.strptime('2021-06-15', '%Y-%m-%d'))
     )
-    plt.ylim(0, 55)
+    plt.ylim(-.3, 55)
 
     plt.tight_layout()
     save_figure('facebook_crowdtangle_trump.png')
+
+
+def create_buzzsumo_thebl_figure():
+
+    print()
+
+    df = import_data('facebook_buzzsumo_thebl_2021-07-01.csv')
+    df = clean_buzzsumo_data(df)
+
+    fig = plt.figure(figsize=(10, 8))
+    fig.suptitle('The Beauty of Life (data from Buzzsumo)')
+
+    ax = plt.subplot(211)
+    plt.plot(df.resample('D', on='date')['facebook_comments'].mean(),
+        label="Facebook comments per article", color='lightskyblue')
+    plt.plot(df.resample('D', on='date')['facebook_shares'].mean(),
+        label="Facebook shares per article", color='royalblue')
+    plt.plot(df.resample('D', on='date')['facebook_likes'].mean(),
+        label="Facebook reactions (likes, ...) per article", color='navy')
+    arrange_plot(ax, df)
+    plt.axvline(np.datetime64("2019-12-01"), color='C3', linestyle='--')
+    plt.ylim(-100, 10000)
+
[…]

### 2021-07-01 code/create_figures.py
testing the code

@@ -332,7 +332,7 @@ if __name__=="__main__":
 
     create_facebook_trump_figure()
     create_buzzsumo_thebl_figure()
-    # create_facebook_crowdtangle_infowars_figure()
-    # create_facebook_buzzsumo_infowars_figure()
+    create_facebook_crowdtangle_infowars_figure()
+    create_facebook_buzzsumo_infowars_figure()
 
-    # create_youtube_graph()
+    create_youtube_graph()

### 2021-07-05 article/draft.tex
upadate

@@
 \usepackage{color}
+\usepackage{multicol}
 \usepackage{setspace}
@@
 \begin{document}
+
 \title{Very Preliminary Draft}
+
 \maketitle
@@
 (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
-The rise of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
+The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
 Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
-{\color{red} Fact-checkers + no laws or not so much.}
+In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
+This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
 
@@
 Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
-{\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g.
-to tackle terrorism) and apply it to misinformation+ idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}
+{\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community,  idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}
 
@@
 
-\bigskip
+%\bigskip
 
 %{\color{red} Policies not specific to misinformation, but to enforce laws + things already used for terrorism and hate speech. Intro or/and Discussion. accounts: hard to say suspension for which.} 
-
-%Content can be withheld in compliance to specific laws of each country, ex: ..;
 % Misinformation : which law ? not defined !
@@
  %We We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.
-
 %CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.
 BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.
-
 %Section 230 in the US + EU 
@@
 %Pourquoi faut-il vérifier leurs politiques ? D’une part parce que ce sont les plateformes elles-mêmes qui annoncent leurs effets. D’autre part beaucoup de choses indirectes. 
-%
 %Add disclaimer in a footnote early on in the document : document not meant to be an exhaustive overview of all the existing regulations and point to three or four main legal sources for exhaustive references.
-
 %Such policies include the introduction of notices (Twitter, see link) or flags (Facebook, see…) to signal to users inaccurate or false content, the temporary or permanent suspension of accounts (Twitter) or pages (Facebook), reducing the visibility of posts or pages (Facebook), or blocking users from sharing specific URL links (see link).
@@
 
-Main stream social media platforms such as Facebook, Twitter and Youtube, may suspend the account of a specific user when they deem that the platforms' rules have been violated.
+Mainstream social media platforms may suspend the account of a specific user when they deem that the platforms' rules have been violated.
 Account suspension can be temporary or permanent.\footnote{A list of notable Twitter temporary and permanent suspensions can be found on wikipedia: \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{https://en.wikipedia.org/wiki/Twitter\_suspensions}.}  When the suspension is temporary the user is prohibited for a limited period of time from posting content on their account, but created content prior to suspension remains available to the user and their followers.
@@
 In what follows, we focus on the implementation of this policy by several platforms and provide simple examples to illustrate.
-
-%\begin{figure}[h]
-%\centering
-%\includegraphics[scale=0.2]{./img/fig1.png}  \hfill \includegraphics[scale=0.2]{./img/crg.png} \hfill \includegraphics[scale=0.2]{./img/life.png} 
-%\caption{Screenshots taken on June 14, 2021 at 4pm UTC. }
-%\label{fig1}
-%\end{figure}
 
@@
 
-When an account is permanently suspended by Facebook, it disappears from the platform (so its data cannot be scrapped anymore), and its data also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.}
-
-Interestingly, Facebook is regularly publishing a monthly {\it coordinated inauthentic behavior} report where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the April 2021 report for an example: \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
+When an account is permanently suspended by Facebook, it disappears from the platform.
+That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the April 2021 report for an example: \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
 
@@
 For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API.
-Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{ (see the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data.
-We can verify on figure \ref{fig1_fb} that the {\it Donald J.
+Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{ (see the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data.\footnote{The exact command can be found : \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_trump_data.sh}{here}.} We can verify on figure \ref{fig1_fb} that the {\it Donald J.
 Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.
@@
 	\centering
-	\includegraphics[scale=0.35]{./img/fb/fig1_fb.png}
+		\begin{multicols}{1}
+			\includegraphics[scale=0.2]{./img/fb/fig1_fb.png}
+		\end{multicols}
 	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J.
@@
 
-{\color{red} N.B. Manual decision, not the automatic strike system}
 \begin{figure}
 \centering
-\includegraphics[scale=0.35]{./img/lifesite.jpg} 
-\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/lifesite.jpg} 
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/lifesite_rolling_7_lifesite.jpg}
+	\end{multicols}
 \caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021.
@@
 
-In this section, we discuss one case of temporary suspension on Twitter.\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}.
+%paragraph strike system + say following example is a manual decision. 
+Twitter has implemented a strike system as part of their Civi Integrity Policy\footnote{See \href{https://help.twitter.com/en/rules-and-policies/election-integrity-policy}{help.twitter.com/en/rules-and-policies/election-integrity-policy}} and their COVID19 misleading information policy.\footnote{See \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}{blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}} Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform.
+The 12-hour account lock is hard to observe in the data, especially for users who do not have an over the clock tweeting activity.
+In this section, we provide one example of a temporary suspension\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.
+
+The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}.
 Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}.
@@
 	\centering
+	\begin{multicols}{1}
 		\includegraphics[scale=0.25]{./img/oann/fig1_oann.png}
+	\end{multicols}
+	\begin{multicols}{1}
 		\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
+	\end{multicols}
 	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
@@
 First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}.
-This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{Reference?} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021.
+This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{See nbcnews,  ``YouTube suspends OANN for violating its Covid-19 policy''.
+nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021.
 For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
@@
 
-In addition, as shown in figure \ref{fig1_oann} when comparing the week before the suspension from 2020/11/17 to 2020/11/23 and one week after from 2020/12/01 to 2020/12/07 it was found that the view count had decreased by ($-45\%$ or $-60\%$), even though the posted number of videos was similar (before $81$ videos; after 93 videos or 86 videos).
-In other words, the suspension period may have a good impact on reducing the audience interest or reach to the channel.
+In addition, as shown in figure \ref{fig1_oann} when comparing the month before the suspension from 2020/10/24 to 2020/11/24 and one month after from 2020/12/01 to 2021/01/01 it was found that the view count decreased by -73\% and the videos uploaded by -55\%.
 Besides that, OANN decided to move officially to Rumble on March 17, 2021 as announced on their Twitter account (see figure \ref{fig2_oann}) and their upload activity on their Youtube channel is close to zero since that announcement.
@@
 	\centering
+	\begin{multicols}{1}
 		\includegraphics[scale=0.2]{./img/oann/fig3_oann.png}
+	\end{multicols}
+
+	\begin{multicols}{1}
 		\includegraphics[scale=0.3]{./img/tony/fig3_tony.png}
+	\end{multicols}
+
 	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
@@
 The suspension period can be observed clearly in the historical data of the channel.
-Moreover, observing the reach of the audience using view counts one week before the suspension starting from 2020/09/22 to 2020/09/28 and one week after the suspension from 2020/10/06 to 2020/10/12 the channel witnessed a drop of $-65\%$ and the videos published in the channel were less by $-16\%$.
+observing the reach of the audience
+Figure 3: Tony heller tweet after getting suspended from youtube (Twitter)
+using view counts one month before the suspension starting from 2020/08/28 to 2020/09/28 and one month after the suspension from 2020/10/05 to 2020/11/05 the channel witnessed a drop of view counts by $-69.5\%$ and the videos published in the channel were less by $-29\%$.
+This drop in views can show that the  suspension  period
+may  have  a  good  impact  on  reducing  the  audience interest or reach to the channel.
 
@@
 	\centering
+		\begin{multicols}{1}
 			\includegraphics[scale=0.3]{./img/tony/fig1_tony.png}
+		\end{multicols}
+
+		\begin{multicols}{1}
 			\includegraphics[scale=0.3]{./img/tony/fig2_tony.png}
+		\end{multicols}
 	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
@@
 Facebook ranks each post and ad with a relevancy score, a high score leading to a high likelihood of the post or the ad appearing in someone’s newsfeed.
-Facebook can thus make a post or a whole account less visible by decreasing the rank of its content [12].
-Such {\it reduce} action should be visible in the engagement metrics of the posts: if a post reaches less users because of a lower ranking, it is less likely to receive likes, comments and shares.
+Facebook can thus make a post or a whole account less visible by decreasing the rank of its content.\footnote{Lyons, T.
+(2018, May 22).
+The three-part recipe for cleaning up your news feed.
+Facebook Newsroom.
+\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} Such {\it reduce} action should be visible in the engagement metrics of the posts: if a post reaches less users because of a lower ranking, it is less likely to receive likes, comments and shares.
 
-Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist [8], was classified among websites that have posted deceptive content according to FactCheck.org [9], and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource [10].
-On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material [7].
+Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.}, was classified among websites that have posted deceptive content according to FactCheck.org\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}, and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.} On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}.}
 
-To verify the measure, we used the CrowdTangle API at the ‘/posts/search’ endpoint (see the documentation [11] for more details) to collect the 37,242 Facebook public posts that shared a link containing ‘infowars.com’ and that were published between January 1, 2019 and December 31, 2020.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the 27,721 posts directly sharing an Infowars link.} The command used can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{here}.
+To verify the measure, we used the CrowdTangle API at the ‘/posts/search’ endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} to collect the 37,242 Facebook public posts that shared a link containing ‘infowars.com’ and that were published between January 1, 2019 and December 31, 2020.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the 27,721 posts directly sharing an Infowars link.} The command used can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{here}.
 
-The number of public posts sharing an Infowars link remained globally stable in 2019 (Figure X4 top panel), thus Facebook’s announced ‘ban’ did not appear to prevent users from sharing an Infowars link.
-Interestingly a clear drop in engagement was observed on May 2, 2019 (Figure X4 bottom panel).
+The number of public posts sharing an Infowars link remained globally stable in 2019 (Figure \ref{infowars1} top panel), thus Facebook’s announced ‘ban’ did not appear to prevent users from sharing an Infowars link.
+Interestingly a clear drop in engagement was observed on May 2, 2019 (Figure \ref{infowars1} bottom panel).
 The number of reactions per post decreased by -94\% when we compared the two months before and after May 2, 2019, the shares decreased by -96\%, and the comments by -93\%.
+
+\begin{figure}
+	\centering
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
+	\end{multicols}
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
+	\end{multicols}
+
+	\caption{Public Facebook posts sharing an Infowars link in 2019 and 2020 gathered from the CrowdTangle API.
+The red line marks the date of May 2, 2019, when Facebook has announced the ban regarding Infowars.
+(Top panel) Number of daily posts.
+(Bottom panel) Engagement metrics (average number of reactions, shares and comments per post).
+}
+	\label{infowars1}
+\end{figure}
 
@@
 	\centering
+		\begin{multicols}{1}	
 			\includegraphics[scale=0.3]{./img/globalresearch_2021-06-14.png}
+		\end{multicols}
+
+		\begin{multicols}{1}
 			\includegraphics[scale=0.3]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
+		\end{multicols}
 		\caption{Screenshots taken on June 14, 2021. }
@@
 
+\begin{figure*}
+\centering
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
+		\includegraphics[scale=0.2]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
+	\end{multicols}
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/globalresearch/tweet.png} 
+		\includegraphics[scale=0.2]{./img/globalresearch/warning.png}
+	\end{multicols}
+\caption{}
+\label{fig4}
+\end{figure*}
+
 The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; that was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021.
@@
 Hence, the visibility of tweets containing this URL link has been reduced because users can no longer access tweets containing the URL link {\it globalresearch.ca} via the search box.
-Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(c)$
- of figure \ref{fig4}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
+Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(c)$ of figure \ref{fig4}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
 Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
@@
 Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (d) in figure \ref{fig4}).
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.3]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
-\includegraphics[scale=0.3]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
-\includegraphics[scale=0.3]{./img/globalresearch/tweet.png} 
-\includegraphics[scale=0.3]{./img/globalresearch/warning.png}
-%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearch.jpg} 
-%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearchall_time.jpg}
-\caption{}
-\label{fig4}
-\end{figure}
 
@@
 {\color{pink} What about something about recommendations ? authoritative content  }
-\subsection{Flags and Notices}
+
+\subsection{Flags, Notices and labels}
+
+\subsubsection{Facebook}
 
@@
 
-\href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}
+\begin{figure}
+\centering
+	\begin{multicols}{1}
+		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30_2.png}
+   	 \end{multicols}
+	\begin{multicols}{1} 
+		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30.png}
+	\end{multicols}
+	\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021.
+Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label.
+Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
+	\label{fig8}
+\end{figure}
 
-We gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a not-for-profit organization verifying the credibility of influential claims and media coverage that claims to be scientific.
-As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$.
-This data collection resulted in $323$ $938$ tweets, excluding retweets.
-Only $28$ tweets were marked with the notice { ``Get the facts about COVID-19''}, $5$ tweets were marked with { ``Learn about US 2020 election security efforts''} and only $1$ tweet was marked with the notice {``This claim about election fraud is disputed''}.
-Furthermore, we noticed that there exists tweets that share the exact same URL links marked as False, yet only a few get marked by a notice.
+Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial.
+Labels are context specific (e.g.
+COVID19 or presidential elections) and  redirect users to a URL link to get more context.
+Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts.
+At the account level, notices can indicate whether an account has been temporarily or permanently suspended.
 
@@
 
-Furthermore,
+In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false.
+To that end, we gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
+As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$.
+This data collection resulted in $323$ $938$ tweets, excluding retweets.
+Only $28$ tweets contained the label { ``Get the facts about COVID-19''}, $5$ tweets contained the label { ``Learn about US 2020 election security efforts''} and only $1$ had the following label {``This claim about election fraud is disputed''}.
+Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same URL link, among the set of collected tweets.
+More specifically, exactly $657$ tweets had shared a URL link redirecting to a video on Bitchute, entitled ``Important information on coronavirus 5G Kung Flu''.
+Among those $657$ tweets only $3$ contained the label ``Get the facts about COVID-19'' (see figure \ref{fig8}).
+This points towards the non-automation of the tweet labelling process and that it might be that only $3$ tweets got labelled after being reported by a user.
+
+We further examine the placement of interstitials that indicate a possibly sensitive content.
+We find that only $2.97\%$ out of $323$ $938$ tweets containing a URL marked as False, have an interstitial ``potentially sensitive content''.
+In particular, many speak about COVID19 and do not contain a label to provide users with more context from authoritative sources.
+Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''.
+We find 32 other tweets, among our set of collected tweets, who share the exact same URL link in our the previous example and among those 32 only 5 tweets had the interstitial ``potentially sensitive content''.
+Again this points towards the non-automation of the interstitials placement.
+
+Finally, to the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
+
+\begin{figure}
+	\centering
+	\begin{multicols}{1}
+		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01.png} 
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01_2.png}
+	\end{multicols}
+	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
+	\label{fig_notice}
+\end{figure}
+
+\subsubsection{Youtube}
+
+\begin{figure}
+	\centering
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/yt_1.png} 
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/yt_2.png} 
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/yt_3.png}
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/yt_4.png} 
+	\end{multicols}
+	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}
+	\label{fig9}
+\end{figure}
+
+Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} The information panel contains main information about the topic from independent third party partners.
+Youtube states that these panels exist regardless of the video point of view.
+In addition , these panels are not available in all languages and countries yet.
+(“Information panel giving topical context”)
+
+Based on a video list (171 videos) checked by fact checkers and marked to have misinformation.
+We collected the information panels in each video by scrapping the content of the web and connecting to a US server.
+Four types of information panels were found in the list of visited videos.
+The first information panel gives info about COVID19 as in Fig \ref{fig9}, the second is about Vaccine as in Fig \ref{fig9} , the third is about Climate change as in Fig \ref{fig9} and last information panel showed on a COVID19 video about the US voting as in Fig \ref{fig9}.
+
+We classified the list of videos examined for the information panel based on its content as in Table \ref{tab2}.
+The Table shows the number of videos with a panel in each category.
+For COVID and vaccine related videos more than half of the videos had a panel, nevertheless, we noticed that some videos get uploaded multiple times by different channels under different video titles but others didn’t even though the video was the same.
+In addition, we noticed for COVID when the video title doesn’t include keywords like (Testing, Pandemic, COVID, coronavirus) , the video wouldn’t have a panel associated with it, and in some cases when the video title have variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
+Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.
+For climate change we only examined 18 misleading videos and we found 72\% of them didn’t have a panel.
+Lastly , for the general health category, we included the videos that weren’t related to COVID but had misinformation in topics like fake cures for cancer, abortion,  and viruses; there was no information panel in all these videos.
+Therefore, we suspect that youtube just add information panels to  the most controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.
+
+\begin{table}[] 
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Category       & \begin{tabular}[c]{@{}c@{}}With information \\ panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Without Information \\ panel\end{tabular} & Total & \begin{tabular}[c]{@{}c@{}}IP\\ percentage\end{tabular} \\ \hline
+General Health & 0                                                                 & 11                                                                   & 11    & 0                                                       \\ \hline
+Vaccine        & 21                                                                & 7                                                                    & 28    & 75                                                      \\ \hline
+COVID          & 73                                                                & 43                                                                   & 116   & 63                                                      \\ \hline
+Climate change & 5                                                                 & 13                                                                   & 18    & 28                                                      \\ \hline
+\end{tabular}
+\caption{}
+\label{tab2}
+\end{table}
 
@@
 
-{ \color{pink} For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
+{ \color{pink}
+
+\begin{itemize}
+
+	\item For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
 We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
@@
 
-\bigskip
-
-To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
+	\item To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
 But too much transparency on how the regulation policies are exactly implemented can actually backfire.
@@
 
-\bigskip
+	\item There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
+For example Newsguard, blablabla...
+In this tweet, we can see the interface of XXX being used in this study from a data journalist: \href{https://twitter.com/Shayan86/status/1394742784683298818/photo/2}{ex}
 
-There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
-For example Newsguard, blablabla...
-In this tweet, we can see the interface of XXX being used in this study from a data journalist: https://twitter.com/Shayan86/status/1394742784683298818/photo/2
+	\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
 
-\bigskip
+	\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+
 
-Recommendation: inform about sources, example inform users that this user shared x failed fact-checks. }
-%→ Littérature liée aux effets psychologiques 
-%→ multi-platforming, indirect effects, etc. 
-%→ strategies
+	\item Make point about the communication of platforms for their policy: 4R of Youtube, RRI of Facebook,
+
+	\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason. E.g. beauty of life, coordinated inauthentic behavior.
 
 \href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
-\newpage
+
+	\item After a channel gets suspended or a video is deleted the data related to them is removed from the youtube API.
+This is a problem that affected the study to investigate the suspension reasons or the removal.
+For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from youtube because they contain content that is against the youtube guidelines and their data got removed from the API.
+
+	\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies...
+
+	\item business model
+
+\end{itemize}
+}
 
@@
 
+\section{Appendix}
+
 \end{document}
-
-%Guillaume Plique, Pauline Breteau, Jules Farjas, Héloïse Théro, & Jean Descamps. (2019, October 14). Minet, a webmining CLI tool & library for python. Zenodo. http://doi.org/10.5281/zenodo.4564399

### 2021-07-05 article/test.tex
upadate

--- 2021-06-30 article/draft.tex
@@
 Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
-{\color{red} Fact-checkers + no laws or not so much.}
+In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
+This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
 
@@
 Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
-{\color{red} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g.
-to tackle terrorism) and apply it to misinformation+ idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}
+{\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community,  idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}
 
@@
 \centering
-\includegraphics[scale=0.35]{./img/lifesite.jpg} 
-\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.25]{./img/lifesite.jpg} 
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.25]{./img/lifesite_rolling_7_lifesite.jpg}
+	\end{multicols}
 \caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021.
@@
 }
+\begin{figure*}
+\centering
+	\begin{multicols}{2}
+		\includegraphics[scale=0.2]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
+		\includegraphics[scale=0.2]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
+	\end{multicols}
+	\begin{multicols}{2}
+		\includegraphics[scale=0.2]{./img/globalresearch/tweet.png} 
+		\includegraphics[scale=0.2]{./img/globalresearch/warning.png}
+	\end{multicols}
+%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearch.jpg} 
+%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearchall_time.jpg}
+\caption{}
+\label{fig4}
+\end{figure*}
 
@@
 
-\href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}
+\begin{figure}
+\centering
+\begin{multicols}{1}
+\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30_2.png}
+    \end{multicols}
+\begin{multicols}{1} 
+\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30.png}
+\end{multicols}
+\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021.
+Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label.
+Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
+\label{fig8}
+\end{figure}
 
-We gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a not-for-profit organization verifying the credibility of influential claims and media coverage that claims to be scientific.
+Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial.
+Labels are context specific (e.g.
+COVID19 or presidential elections) and  redirect users to a URL link to get more context.
+Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts.
+At the account level, notices can indicate whether an account has been temporarily or permanently suspended.
+\smallskip
+
+In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false.
+To that end, we gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
 As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$.
 This data collection resulted in $323$ $938$ tweets, excluding retweets.
-Only $28$ tweets were marked with the notice { ``Get the facts about COVID-19''}, $5$ tweets were marked with { ``Learn about US 2020 election security efforts''} and only $1$ tweet was marked with the notice {``This claim about election fraud is disputed''}.
-Furthermore, we noticed that there exists tweets that share the exact same URL links marked as False, yet only a few get marked by a notice.
+Only $28$ tweets contained the label { ``Get the facts about COVID-19''}, $5$ tweets contained the label { ``Learn about US 2020 election security efforts''} and only $1$ had the following label {``This claim about election fraud is disputed''}.
+Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same URL link, among the set of collected tweets.
+More specifically, exactly $657$ tweets had shared a URL link redirecting to a video on Bitchute, entitled ``Important information on coronavirus 5G Kung Flu''.
+Among those $657$ tweets only $3$ contained the label ``Get the facts about COVID-19'' (see figure \ref{fig8}).
+This points towards the non-automation of the tweet labelling process and that it might be that only $3$ tweets got labelled after being reported by a user.
 
-\smallskip
+We further examine the placement of interstitials that indicate a possibly sensitive content.
+We find that only $2.97\%$ out of $323$ $938$ tweets containing a URL marked as False, have an interstitial ``potentially sensitive content''.
+In particular, many speak about COVID19 and do not contain a label to provide users with more context from authoritative sources.
+Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''.
+We find 32 other tweets, among our set of collected tweets, who share the exact same URL link in our the previous example and among those 32 only 5 tweets had the interstitial ``potentially sensitive content''.
+Again this points towards the non-automation of the interstitials placement.
 
-Furthermore,
+Finally, to the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
+
+\begin{figure}
+	\centering
+	\begin{multicols}{1}
+		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01.png} 
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01_2.png}
+	\end{multicols}
+	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
+	\label{fig_notice}
+\end{figure}
+
+\subsubsection{Youtube}
+
+\begin{figure}
+	\centering
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/yt_1.png} 
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/yt_2.png} 
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/yt_3.png}
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/yt_4.png} 
+	\end{multicols}
+	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}
+	\label{fig9}
+\end{figure}
+
+Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} The information panel contains main information about the topic from independent third party partners.
+Youtube states that these panels exist regardless of the video point of view.
+In addition , these panels are not available in all languages and countries yet.
+(“Information panel giving topical context”)
+
+Based on a video list (171 videos) checked by fact checkers and marked to have misinformation.
+We collected the information panels in each video by scrapping the content of the web and connecting to a US server.
+Four types of information panels were found in the list of visited videos.
+The first information panel gives info about COVID19 as in Fig \ref{fig9}, the second is about Vaccine as in Fig \ref{fig9} , the third is about Climate change as in Fig \ref{fig9} and last information panel showed on a COVID19 video about the US voting as in Fig \ref{fig9}.
+
+We classified the list of videos examined for the information panel based on its content as in Table \ref{tab2}.
+The Table shows the number of videos with a panel in each category.
+For COVID and vaccine related videos more than half of the videos had a panel, nevertheless, we noticed that some videos get uploaded multiple times by different channels under different video titles but others didn’t even though the video was the same.
+In addition, we noticed for COVID when the video title doesn’t include keywords like (Testing, Pandemic, COVID, coronavirus) , the video wouldn’t have a panel associated with it, and in some cases when the video title have variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
+Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.
+For climate change we only examined 18 misleading videos and we found 72\% of them didn’t have a panel.
+Lastly , for the general health category, we included the videos that weren’t related to COVID but had misinformation in topics like fake cures for cancer, abortion,  and viruses; there was no information panel in all these videos.
+Therefore, we suspect that youtube just add information panels to  the most controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.
+
+\begin{table}[] 
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Category       & \begin{tabular}[c]{@{}c@{}}With information \\ panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Without Information \\ panel\end{tabular} & Total & \begin{tabular}[c]{@{}c@{}}IP\\ percentage\end{tabular} \\ \hline
+General Health & 0                                                                 & 11                                                                   & 11    & 0                                                       \\ \hline
+Vaccine        & 21                                                                & 7                                                                    & 28    & 75                                                      \\ \hline
+COVID          & 73                                                                & 43                                                                   & 116   & 63                                                      \\ \hline
+Climate change & 5                                                                 & 13                                                                   & 18    & 28                                                      \\ \hline
+\end{tabular}
+\caption{}
+\label{tab2}
+\end{table}
 
@@
 
-{ \color{pink} For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
+{ \color{pink} 
+\begin{itemize}
+
+	\item For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
 We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
@@
 
-\bigskip
-
-There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
+	\item There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
 For example Newsguard, blablabla...
@@
 
-\bigskip
+	\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
 
-Recommendation: inform about sources, example inform users that this user shared x failed fact-checks. }
-%→ Littérature liée aux effets psychologiques 
-%→ multi-platforming, indirect effects, etc. 
-%→ strategies
+	\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+
+
+	\item Make point about the communication of platforms for their policy: 4R of Youtube, RRI of Facebook,
+
+	\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason. E.g. beauty of life, coordinated inauthentic behavior.
 
 \href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
+
+	\item After a channel gets suspended or a video is deleted the data related to them is removed from the youtube API.
+This is a problem that affected the study to investigate the suspension reasons or the removal.
+For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from youtube because they contain content that is against the youtube guidelines and their data got removed from the API.
+
+	\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... 
+	\item business model
+
+\end{itemize}}
 \newpage

### 2021-07-05 article/draft.tex
updates

@@
 
-One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through ranking.
-Facebook ranks each post and ad with a relevancy score, a high score leading to a high likelihood of the post or the ad appearing in someone’s newsfeed.
-Facebook can thus make a post or a whole account less visible by decreasing the rank of its content.\footnote{Lyons, T.
+One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through a ranking system.
+Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed.
+doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure.\footnote{Lyons, T.
 (2018, May 22).
@@
 Facebook Newsroom.
-\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} Such {\it reduce} action should be visible in the engagement metrics of the posts: if a post reaches less users because of a lower ranking, it is less likely to receive likes, comments and shares.
+\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} Such {\it reduce} measure should be visible in the engagement metrics of a given post.
+That is, if a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.
 
+To illustrate, we investigate the case of the website $Infowars$.
 Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.}, was classified among websites that have posted deceptive content according to FactCheck.org\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}, and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.} On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}.}

### 2021-07-05 article/draft.tex
update

@@
 
-One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through a ranking system.
+One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through their ranking system.
 Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed.
-doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure.\footnote{Lyons, T.
+Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure.\footnote{Lyons, T.
 (2018, May 22).
@@
 Facebook Newsroom.
-\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} Such {\it reduce} measure should be visible in the engagement metrics of a given post.
-That is, if a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.
+\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the CrowdTangle API or on Buzzsumo.
+Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available via the CrowdTangle API and Buzzsumo.
+If a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.
+
+%phrase pas accès au reach, mais seulement les engagement metrics
+% Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.},
+%CrowdTangle and Buzzsumo provide access to the interaction metrics on content (engagement), but not to the number of views (or reach), therefore we can only verify the {\it reduce} measure indirectly through a decrease in engagement.
+If Facebook was reducing the reach of a content via a lower ranking, we would expect the content to be less likely to receive likes, comments and shares, relative to a post with a higher ranking.
+
+\smallskip
 
 To illustrate, we investigate the case of the website $Infowars$.
-Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.}, was classified among websites that have posted deceptive content according to FactCheck.org\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}, and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.} On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}.}
+This website appears in the Misinformation Directory of FactCheck.org, among other websites who have posted deceptive content\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}.
+Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.}
 
-To verify the measure, we used the CrowdTangle API at the ‘/posts/search’ endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} to collect the 37,242 Facebook public posts that shared a link containing ‘infowars.com’ and that were published between January 1, 2019 and December 31, 2020.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the 27,721 posts directly sharing an Infowars link.} The command used can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{here}.
+\smallskip
 
-The number of public posts sharing an Infowars link remained globally stable in 2019 (Figure \ref{infowars1} top panel), thus Facebook’s announced ‘ban’ did not appear to prevent users from sharing an Infowars link.
-Interestingly a clear drop in engagement was observed on May 2, 2019 (Figure \ref{infowars1} bottom panel).
-The number of reactions per post decreased by -94\% when we compared the two months before and after May 2, 2019, the shares decreased by -96\%, and the comments by -93\%.
+On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/} and \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}.
+The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel).
+Thus the measure announced by Facebook doesn't seem to have prevented users from sharing an $Infowars$ link.
+Nevertheless, a clear drop in engagement was observed on May 2, 2019 (see figure \ref{infowars1} bottom panel).
+The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May 2, 2019.
+This suggests the measure taken by Facebook in May $2019$, is not a ban per se, but rather a $reduce$ measure.
+This is because users could still post $Infowars$ links, but these posts generated less engagement.
+It should be noted that the engagement metrics increased again by the end of $2019$ / beginning of $2020$, suggesting that the $reduce$ measure may have been lifted a few months after its implementation.
 
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
+		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_1.png}
 	\end{multicols}
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
+		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_2.png} 
 	\end{multicols}
 
-	\caption{Public Facebook posts sharing an Infowars link in 2019 and 2020 gathered from the CrowdTangle API.
-The red line marks the date of May 2, 2019, when Facebook has announced the ban regarding Infowars.
+	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API.
+The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars.
 (Top panel) Number of daily posts.
-(Bottom panel) Engagement metrics (average number of reactions, shares and comments per post).
+(Bottom panel) Engagement metrics: average number of reactions, shares and comments per post.
 }
@@
 
-This would suggest that Facebook’s measure taken in May 2019 is actually not a ban, but would rather correspond to a ‘reduce’ action, as users could still post Infowars links, but these posts generated vastly less engagement.
-It should be noted that the engagement metrics increased again at the end of 2019 / beginning of 2020, suggesting that the reducing measure may have been lifted a few months after its implementation.
+As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset.
+We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.
+\footnote{The command can be found here: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
+An increase in engagement was also observed in $2020$.
+It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.
 
-As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ‘/search/articles’ endpoint of the Buzzsumo API, to gather more complete Facebook data.
-We collected the engagement data for the 14,232 articles crawled by Buzzsumo from the Infowars website between January 1, 2019 and Decembre 31, 2020.
-The command can be found here.
-We observe that the articles published after May 2, 2019 received less Facebook engagement than the ones published before (Figure X5), with a percentage change of -97\% for the reactions, -59\% for the shares and -97\% for the comments.
-An increase in engagement was also observed in 2020.
-It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links during a few months in 2019.
+\smallskip
 
-We found irregularities in the number of Infowars articles collected from Buzzsumo.
-While Infowars usually publishes 20-30 articles per day, only 53 articles were collected in the 31-day period between June 11 to July 11, 2020.
+{\color{pink} Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
+While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
 A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
-Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
+Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.}
+
+\begin{figure}
+	\centering
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
+	\end{multicols}
+
+	\caption{Facebook engagement metrics (average number of reactions, shares and comments per article) for the Infowars articles published in $2019-2020$ and gathered from the Buzzsumo API.
+The red line marks the date of May $2$, $2019$, when Facebook has announced the ban regarding Infowars.}
+	\label{infowars2}
+\end{figure}
 
@@
 		\begin{multicols}{1}	
-			\includegraphics[scale=0.3]{./img/globalresearch_2021-06-14.png}
+			\includegraphics[scale=0.35]{./img/globalresearch_2021-06-14.png}
 		\end{multicols}
@@
 		\begin{multicols}{1}
-			\includegraphics[scale=0.3]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
+			\includegraphics[scale=0.35]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
 		\end{multicols}
-		\caption{Screenshots taken on June 14, 2021. }
+		\caption{Screenshots taken on June 14, 2021.
+Top panel: screenshot that shows the account of $globalresearch.ca$ suspended on Twitter.
+Bottom panel: screenshot that shows that no results can be found when searching for $globalresearch.ca$.
+}
 		\label{fig3}
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
-		\includegraphics[scale=0.2]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
+		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
+		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
 	\end{multicols}
-
-	\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/globalresearch/tweet.png} 
-		\includegraphics[scale=0.2]{./img/globalresearch/warning.png}
-	\end{multicols}
-\caption{}
+\caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+Bottom panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+Data collected via the Twitter API v2 on June $16$, 2021.
+}
 \label{fig4}
@@
 
-The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; that was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021.
+The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; which was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021.
 But to the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
 Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}).
-Furthermore, $globalresearch.ca$ has multiple failed fact-checks, see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}} When a user searches via the twitter search-box a url link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June 14, 2021.
-To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January 1, 2021 until June 10, 2021.
-As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the URL link {\it globalresearch.ca} throughout May 2021 and the first week of June 2021.
+Furthermore, $globalresearch.ca$ has multiple failed fact-checks, see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}} When a user searches via the twitter search-box for any URL link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June $14$, $2021$.
+To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the URL link {\it globalresearch.ca} throughout May $2021$ and the first week of June $2021$.
 Hence, the visibility of tweets containing this URL link has been reduced because users can no longer access tweets containing the URL link {\it globalresearch.ca} via the search box.
-Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(c)$ of figure \ref{fig4}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
+Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(a)$ of figure \ref{fig4bis}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
 Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
-Hence, the users who tweet articles from the {\it globalresearch.ca} website receive positive engagement from their own followers.
-Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (d) in figure \ref{fig4}).
+Hence, the users who tweet articles from the {\it globalresearch.ca} website receive tweet level engagement from their own followers.
+Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (b) in figure \ref{fig4bis}).
+
+\begin{figure*}
+\centering	
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
+		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
+	\end{multicols}
+\caption{}
+\label{fig4bis}
+\end{figure*}
 
@@
 
+	\item Pas accès au ``reach" !  ranking not available. Fb nous a donné certaines données (les données Condor) et dedans on a le nombre de clicks par exemple
+
+	\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
+While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
 \end{itemize}

### 2021-07-05 article/test.tex
update

@@
 }
-\begin{figure*}
+\begin{figure}
 \centering
-	\begin{multicols}{2}
-		\includegraphics[scale=0.2]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
-		\includegraphics[scale=0.2]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
+		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
 	\end{multicols}
-	\begin{multicols}{2}
-		\includegraphics[scale=0.2]{./img/globalresearch/tweet.png} 
-		\includegraphics[scale=0.2]{./img/globalresearch/warning.png}
-	\end{multicols}
-%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearch.jpg} 
-%\includegraphics[scale=0.3]{./img/globalresearch/sum_rolling_7_globalresearchall_time.jpg}
 \caption{}
 \label{fig4}
-\end{figure*}
+\end{figure}
+
+\begin{figure}
+\centering	
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
+		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
+	\end{multicols}
+\caption{}
+\label{fig4bis}
+\end{figure}
 

### 2021-07-05 article/draft.tex
n-th update

@@
 \usepackage{cite}
+\usepackage{lscape}
 \usetikzlibrary{shapes,snakes}
@@
 		\begin{multicols}{1}
-			\includegraphics[scale=0.3]{./img/tony/fig1_tony.png}
+			\includegraphics[scale=0.35]{./img/tony/fig1_tony.png}
 		\end{multicols}
@@
 		\begin{multicols}{1}
-			\includegraphics[scale=0.3]{./img/tony/fig2_tony.png}
+			\includegraphics[scale=0.35]{./img/tony/fig2_tony.png}
 		\end{multicols}
@@
 
-A third measure that main stream social media platforms can apply is to prevent users from sharing specific types of content, instead of deleting the content after posting, or users accounts.
-We will study here how the platforms prevent users from sharing urls coming from specific domain names.
+A third measure that mainstream social media platforms can apply is to prevent users from sharing specific types of content, instead of deleting the content after posting, or users accounts.
+We will show through examples how platforms prevent users from sharing urls coming from specific domain names.
 
@@
 
-{\color{pink}The Beauty of life}
+In this section, we provide one case study of how Facebook can block a URL as part of its policy enforcement tools.
+The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}.} Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook'' for coordinated inauthentic behavior\footnote{\href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}, which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
+Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.}
+
+Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior are interlinked, according to the fact-checking organization Snopes which had reported about The BL’s activity to Facebook and other various public articles.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}} It took Facebook five months to complete its investigation of The BL before taking action\footnote{See \href{https://www.businessinsider.com/facebook-bans-beauty-of-life-for-inauthentic-behavior-2019-12}{https://www.businessinsider.com/facebook-bans-beauty-of-life-for-inauthentic-behavior-2019-12}.} and Snopes ended its fact-checking partnership with them in February 2020.\footnote{See \href{https://www.snopes.com/2019/02/01/snopes-fb-partnership-ends/}{https://www.snopes.com/2019/02/01/snopes-fb-partnership-ends/}.}
+
+\begin{figure}
+	\centering
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_1.png}
+	\end{multicols}
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_2.png} 
+	\end{multicols}
+
+	\caption{Articles from The Beauty of Life website (thebl.com) published between January 1, 2019 and June 15, 2021 and gathered from the Buzzsumo API.
+(Top) Facebook engagement metrics (average number of reactions, shares and comments per article).
+(Bottom) Number of articles published per day.
+The red line marks the date of December 1, 2019.
+}
+	\label{fb_bl}
+\end{figure}
+%BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.
+
+To verify Facebook’s ban of The BL domain name, we first tested whether we could post a Facebook message containing a url from thebl.com.
+This turned out to be impossible.
+But such manual verification cannot inform us whether the ban applies indeed to all Facebook users and accounts (as we used only our own personal accounts), nor when it has started.
+To further investigate this policy, we collected data from Buzzsumo.\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.} We used the ``/search/articles'' endpoint of the Buzzsumo API, to collect the engagement metrics $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.\footnote{The command can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}.}
+
+The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban.
+We can note that although the ban was communicated in an article published\footnote{See \href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}.} on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
+The number of articles published per day was around $50$ until December $20$, $2019$.
+The this number decreased drastically to reach a {\color{pink} plateau} around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).
+The communication around the ban may have discouraged The Beauty of Life to proceed with their activity.
+Using Buzzsumo data, a global ban over sharing a thebl.com URL link on Facebook was ascertained.
+It started on December $1$, $2019$, and was still enforced in June 2021.
 
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30_2.png}
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
    	 \end{multicols}
 	\begin{multicols}{1} 
-		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30.png}
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30.png}
 	\end{multicols}
@@
 While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
+	\item Researchers should be able to access the data of deleted accounts on the main platforms.
+
+	\item Currently the flag or notice banners data is not present in the platforms’ API datasource, and this prevents researchers and journalists from easily investigating that matter.
+They have to use or build a scraper to access the data.
+
+	\item Lack of transparency in the platforms’ communication that makes their policies harder to verify.
+
 \end{itemize}
@@
 
+\begin{table}[]
+\begin{tabular}{|c|c|c|}
+\hline
+\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/communitystandards/recentupdates/                         \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://help.twitter.com/en/rules-and-policies/twitter-rules                       \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/} \\ \hline
+\multirow{3}{*}{Rules enforcement }         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & https://transparency.fb.com/data/community-standards-enforcement/                  \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://transparency.twitter.com/en/reports/rules-enforcement.html                 \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & https://transparencyreport.google.com/youtube-policy/                              \\ \hline
+\multirow{3}{*}{Transparency center}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://transparency.twitter.com/en/reports.html                                   \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & https://transparencyreport.google.com/?hl=en                                       \\ \hline
+\multirow{3}{*}{Policy regarding Covid-19} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy       \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & https://support.google.com/youtube/answer/9891785                                  \\ \hline
+\end{tabular}
+\end{table}
+
 \end{document}

### 2021-07-05 article/draft.tex
n-th update

@@
 
-\smallskip
-
-{\color{pink} Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
-While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
-A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
-Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.}
-
 \begin{figure}
@@
 Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''.
-We find 32 other tweets, among our set of collected tweets, who share the exact same URL link in our the previous example and among those 32 only 5 tweets had the interstitial ``potentially sensitive content''.
+We find 32 other Tweets, among our set of collected tweets, who share the exact same URL link as in the previous example.
+Among those 32 Tweets, only 5 tweets had the interstitial ``potentially sensitive content''.
 Again this points towards the non-automation of the interstitials placement.
@@
 \hline
-Category       & \begin{tabular}[c]{@{}c@{}}With information \\ panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Without Information \\ panel\end{tabular} & Total & \begin{tabular}[c]{@{}c@{}}IP\\ percentage\end{tabular} \\ \hline
-General Health & 0                                                                 & 11                                                                   & 11    & 0                                                       \\ \hline
+Category       & \begin{tabular}[c]{@{}c@{}}With \\ information \\ panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Without  \\\ information \\ panel\end{tabular} & Total & \begin{tabular}[c]{@{}c@{}}IP \% \end{tabular} \\ \hline
+\begin{tabular}[c]{@{}c@{}} General \\ Health \end{tabular} & 0                                                                 & 11                                                                   & 11    & 0                                                       \\ \hline
 Vaccine        & 21                                                                & 7                                                                    & 28    & 75                                                      \\ \hline
-COVID          & 73                                                                & 43                                                                   & 116   & 63                                                      \\ \hline
-Climate change & 5                                                                 & 13                                                                   & 18    & 28                                                      \\ \hline
+COVID19          & 73                                                                & 43                                                                   & 116   & 63                                                      \\ \hline
+\begin{tabular}[c]{@{}c@{}}  Climate \\ change \end{tabular} & 5                                                                 & 13                                                                   & 18    & 28                                                      \\ \hline
 \end{tabular}
@@
 { \color{pink} 
+Sporadic points for the discussion, no structure yet.
 
@@
 
+	\item Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
+While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
+A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
+Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
 \end{itemize}

### 2021-07-05 article/draft.tex
cosmetic changes

@@
 In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
-This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
+This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.\footnote{For an overview of Facebook's third-party fact checking program see see \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}.
+For an overview of Youtube's policy on fact-checking see:  }
 
@@
 
-During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: } As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms.
+During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: \href{https://support.google.com/youtube/answer/9891785}{https://support.google.com/youtube/answer/9891785}.} As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms.
 Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
-{\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community,  idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}
+In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}.
+The 2019 report of the Facebook Data Transparency Advisory Group\footnote{See \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}.} (DTAG) states clearly that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
+Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
+It is explained via a blog post on the facebook Newsroom.\footnote{See: \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{https://about.fb.com/news/2018/05/hard-questions-false-news/}.}.
+Similarly, Twitter communicates about actions related to misinformation via their Twitter Safety Blog/accout\footnote{See \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{https://blog.twitter.com/en\_us/authors.TwitterSafety}.}.
+
+{\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community,  idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.
+Violations fall into other categories: deceptive practices, impersonation, hate speech.
+}
 
@@
 % Misinformation : which law ? not defined ! 
+%: Public content insights tool owned and operated by Facebook.
+%\footnote{Public content insights tool owned and operated by Facebook.}
+%: commercial content \\ database
 
@@
 \centering
-\begin{tabular}{|l|l|l|l}
+\begin{tabular}{|l|c|l|l|l}
 
 \hline
-&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{Web Scraping}                                                                                                                                                                   \\ \hline
-Facebook & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}: public content insights tool \\ owned and operated by Facebook.
-\\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content database  \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
+&  \begin{tabular}[c]{@{}l@{}} Application Programming \\ Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web \\ Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
+ \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} \\ \href{https://buzzsumo.com}{Buzzsumo}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
 \\ \hline
-Twitter  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet twitter scrape}}                                                                                                                                                                           \\ \hline
-Youtube  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
+ \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
+ \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
 \end{tabular}
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/lifesite.jpg} 
+		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
 	\end{multicols}
 	\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/lifesite_rolling_7_lifesite.jpg}
+		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
 	\end{multicols}
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.25]{./img/oann/fig1_oann.png}
+		\includegraphics[scale=0.29]{./img/oann/fig1_oann.png}
 	\end{multicols}
 	\begin{multicols}{1}
-		\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
+		\includegraphics[scale=0.3]{./img/oann/fig2_oann.png} 
 	\end{multicols}
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/oann/fig3_oann.png}
+		\includegraphics[scale=0.32]{./img/oann/fig3_oann.png}
 	\end{multicols}
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/tony/fig3_tony.png}
+		\includegraphics[scale=0.35]{./img/tony/fig3_tony.png}
 	\end{multicols}
@@
 In this section, we provide one case study of how Facebook can block a URL as part of its policy enforcement tools.
-The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}.} Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook'' for coordinated inauthentic behavior\footnote{\href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}, which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
+The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook'' for coordinated inauthentic behavior\footnote{\href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}, which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
 Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.}
@@
 
+\begin{figure}
+	\centering
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_1.png}
+	\end{multicols}
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_2.png} 
+	\end{multicols}
+
+	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API.
+The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars.
+(Top panel) Number of daily posts.
+(Bottom panel) Engagement metrics: average number of reactions, shares and comments per post.
+}
+	\label{infowars1}
+\end{figure}
+
 One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through their ranking system.
@@
 
-\smallskip
-
-On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/} and \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}.
-The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel).
-Thus the measure announced by Facebook doesn't seem to have prevented users from sharing an $Infowars$ link.
-Nevertheless, a clear drop in engagement was observed on May 2, 2019 (see figure \ref{infowars1} bottom panel).
-The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May 2, 2019.
-This suggests the measure taken by Facebook in May $2019$, is not a ban per se, but rather a $reduce$ measure.
-This is because users could still post $Infowars$ links, but these posts generated less engagement.
-It should be noted that the engagement metrics increased again by the end of $2019$ / beginning of $2020$, suggesting that the $reduce$ measure may have been lifted a few months after its implementation.
-
-\begin{figure}
-	\centering
-
-	\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_1.png}
-	\end{multicols}
-
-	\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_2.png} 
-	\end{multicols}
-
-	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API.
-The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars.
-(Top panel) Number of daily posts.
-(Bottom panel) Engagement metrics: average number of reactions, shares and comments per post.
-}
-	\label{infowars1}
-\end{figure}
-
-As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset.
-We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.
-\footnote{The command can be found here: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
-An increase in engagement was also observed in $2020$.
-It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.
-
 \begin{figure}
@@
 \end{figure}
+
+On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/} and \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}.
+The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel).
+Thus the measure announced by Facebook doesn't seem to have prevented users from sharing an $Infowars$ link.
+Nevertheless, a clear drop in engagement was observed on May 2, 2019 (see figure \ref{infowars1} bottom panel).
+The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May 2, 2019.
+This suggests the measure taken by Facebook in May $2019$, is not a ban per se, but rather a $reduce$ measure.
+This is because users could still post $Infowars$ links, but these posts generated less engagement.
+It should be noted that the engagement metrics increased again by the end of $2019$ / beginning of $2020$, suggesting that the $reduce$ measure may have been lifted a few months after its implementation.
+
+As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset.
+We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.
+\footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
+An increase in engagement was also observed in $2020$.
+It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.
 
@@
 
-\begin{figure*}
-\centering
-	\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
-		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
-	\end{multicols}
-\caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-Bottom panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-Data collected via the Twitter API v2 on June $16$, 2021.
-}
-\label{fig4}
-\end{figure*}
-
 The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; which was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021.
@@
 
-\begin{figure*}
+\begin{figure}
+\centering
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
+	\end{multicols}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
+	\end{multicols}
+\caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+Bottom panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+Data collected via the Twitter API v2 on June $16$, 2021.
+}
+\label{fig4}
+\end{figure}
+
+\begin{figure}
 \centering	
@@
 		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
+	\end{multicols}
+	\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
@@
 \label{fig4bis}
-\end{figure*}
+\end{figure}
 
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01.png} 
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png} 
 	\end{multicols}
 	\begin{multicols}{1}
-		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01_2.png}
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png}
 	\end{multicols}
@@
 
-Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} The information panel contains main information about the topic from independent third party partners.
-Youtube states that these panels exist regardless of the video point of view.
-In addition , these panels are not available in all languages and countries yet.
-(“Information panel giving topical context”)
+Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} Information panels provide ressources concerning a potentially controversial topic from independent third party partners or authoritative ressources.
+Youtube states that these panels exist regardless of the point of view expressed in a given video.
+In addition, these panels are not yet available in all languages and countries.
+%(“Information panel giving topical context”)
 
-Based on a video list (171 videos) checked by fact checkers and marked to have misinformation.
-We collected the information panels in each video by scrapping the content of the web and connecting to a US server.
-Four types of information panels were found in the list of visited videos.
-The first information panel gives info about COVID19 as in Fig \ref{fig9}, the second is about Vaccine as in Fig \ref{fig9} , the third is about Climate change as in Fig \ref{fig9} and last information panel showed on a COVID19 video about the US voting as in Fig \ref{fig9}.
+To further study the assignment of information panels to videos, we implemented the following exercice.
+We compiled a list of $171$ Youtube videos, checked by independent fact-checkers\footnote{Is it science Feedback ?
+if so add.} and marked as containing false or inaccurate information.
+We collected the information panels, when present, in each video by scrapping the content of the web and connecting to a US server.
+Four types of information panels were found in the list of visited videos as shown in figure\ref{fig9}:  information about COVID19, Vaccines, Climate change and US elections.
 
-We classified the list of videos examined for the information panel based on its content as in Table \ref{tab2}.
-The Table shows the number of videos with a panel in each category.
-For COVID and vaccine related videos more than half of the videos had a panel, nevertheless, we noticed that some videos get uploaded multiple times by different channels under different video titles but others didn’t even though the video was the same.
-In addition, we noticed for COVID when the video title doesn’t include keywords like (Testing, Pandemic, COVID, coronavirus) , the video wouldn’t have a panel associated with it, and in some cases when the video title have variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
-Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.
-For climate change we only examined 18 misleading videos and we found 72\% of them didn’t have a panel.
-Lastly , for the general health category, we included the videos that weren’t related to COVID but had misinformation in topics like fake cures for cancer, abortion,  and viruses; there was no information panel in all these videos.
-Therefore, we suspect that youtube just add information panels to  the most controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.
+We classified the list of Youtube videos by topic based on its content as shown in table \ref{tab2}.
+We recorded the number of videos containing an information panel within each category.
+For COVID19 and vaccine related videos more than half of the videos contained an information panel.
+{\color{pink} Nevertheless, we noticed that some videos get uploaded multiple times by different channels under different video titles but others didn’t even though the video was the same.} In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
+Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.
+
+\smallskip
+
+For climate change we only examined $18$ misleading videos and we found that $72\%$ did not display an information panel.
+Lastly , for the general health category, we included the videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion,  and viruses; no information panels were displayed for that set of Youtube videos.
+Therefore, it is likely that Youtube add information panels below videos conecrning controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.
 
@@
 
+\newpage
+
 \section{Appendix}
 
-\begin{table}[]
+\begin{table*}[h]
 \begin{tabular}{|c|c|c|}
 \hline
-\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/communitystandards/recentupdates/                         \\ \cline{2-3} 
-                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://help.twitter.com/en/rules-and-policies/twitter-rules                       \\ \cline{2-3} 
+\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/communitystandards/recentupdates/}{facebook.com/communitystandards/recentupdates/}                         \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}                       \\ \cline{2-3}
                                            & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/} \\ \hline
-\multirow{3}{*}{Rules enforcement }         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & https://transparency.fb.com/data/community-standards-enforcement/                  \\ \cline{2-3} 
-                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://transparency.twitter.com/en/reports/rules-enforcement.html                 \\ \cline{2-3} 
-                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & https://transparencyreport.google.com/youtube-policy/                              \\ \hline
-\multirow{3}{*}{Transparency center}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3} 
-                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://transparency.twitter.com/en/reports.html                                   \\ \cline{2-3} 
-                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & https://transparencyreport.google.com/?hl=en                                       \\ \hline
-\multirow{3}{*}{Policy regarding Covid-19} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3} 
-                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy       \\ \cline{2-3} 
-                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & https://support.google.com/youtube/answer/9891785                                  \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Rules \\ enforcement \end{tabular}}         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & \href{https://transparency.fb.com/data/community-standards-enforcement/}{transparency.fb.com/data/community-standards-enforcement/}                 \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports/rules-enforcement.html}{transparency.twitter.com/en/reports/rules-enforcement.html}                \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/youtube-policy/}{transparencyreport.google.com/youtube-policy/}                              \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Transparency \\ center \end{tabular}}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports.html}{transparency.twitter.com/en/reports.html}                                  \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/?hl=en}{transparencyreport.google.com/?hl=en}                                      \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Policy regarding \\  Covid-19 \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy}       \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}                                 \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Fact-checking \\ policy \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}                                    \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & x       \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9229632}{support.google.com/youtube/answer/9229632}                                  \\ \hline
+
 \end{tabular}
-\end{table}
+\caption{Summary of ressources, last accessed on July 5, 2021. }
+\label{summary}
+\end{table*}
 
+%https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works
 \end{document}

### 2021-07-05 article/test.tex
n-th update
cosmetic changes

@@
 \usepackage{graphicx}
-
+\usepackage{lscape}
 \usepackage{url}
@@
 (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
-The rise of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
+The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
 Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
 In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
-This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
+This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.\footnote{For an overview of Facebook's third-party fact checking program see see \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}.
+For an overview of Youtube's policy on fact-checking see:  }
 
@@
 
-\bigskip
+%\bigskip
 
 %{\color{red} Policies not specific to misinformation, but to enforce laws + things already used for terrorism and hate speech. Intro or/and Discussion. accounts: hard to say suspension for which.} 
+% Misinformation : which law ? not defined !
 
-%Content can be withheld in compliance to specific laws of each country, ex: ..;
-% Misinformation : which law ? not defined !
+%public content\\  insights tool \\ owned and operated by \\ Facebook. \\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content \\ database
 
@@
 \centering
-\begin{tabular}{|l|l|l|l}
+\begin{tabular}{|l|c|l|l|l}
 
 \hline
-&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{Web Scraping}                                                                                                                                                                   \\ \hline
-Facebook & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}: public content insights tool \\ owned and operated by Facebook.
-\\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content database  \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
+&  \begin{tabular}[c]{@{}l@{}} Application Programming \\ Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web \\ Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
+ \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}  \\ \href{https://buzzsumo.com}{Buzzsumo} \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
 \\ \hline
-Twitter  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet twitter scrape}}                                                                                                                                                                           \\ \hline
-Youtube  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
+ \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
+ \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
 \end{tabular}
@@
 
-{\color{red} N.B. Manual decision, not the automatic strike system}
 \begin{figure}
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.25]{./img/lifesite.jpg} 
+		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
 	\end{multicols}
 	\begin{multicols}{1}
-		\includegraphics[scale=0.25]{./img/lifesite_rolling_7_lifesite.jpg}
+		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
 	\end{multicols}
@@
 
-{\color{pink}The Beauty of life}
+In this section, we provide one case study of how Facebook can block a URL as part of its policy enforcement tools.
+The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook'' for coordinated inauthentic behavior\footnote{\href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}, which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
+Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.}
+
+Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior are interlinked, according to the fact-checking organization Snopes which had reported about The BL’s activity to Facebook and other various public articles.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}} It took Facebook five months to complete its investigation of The BL before taking action\footnote{See \href{https://www.businessinsider.com/facebook-bans-beauty-of-life-for-inauthentic-behavior-2019-12}{https://www.businessinsider.com/facebook-bans-beauty-of-life-for-inauthentic-behavior-2019-12}.} and Snopes ended its fact-checking partnership with them in February 2020.\footnote{See \href{https://www.snopes.com/2019/02/01/snopes-fb-partnership-ends/}{https://www.snopes.com/2019/02/01/snopes-fb-partnership-ends/}.}
+
+\begin{figure}
+	\centering
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_1.png}
+	\end{multicols}
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_2.png} 
+	\end{multicols}
+
+	\caption{Articles from The Beauty of Life website (thebl.com) published between January 1, 2019 and June 15, 2021 and gathered from the Buzzsumo API.
+(Top) Facebook engagement metrics (average number of reactions, shares and comments per article).
+(Bottom) Number of articles published per day.
+The red line marks the date of December 1, 2019.
+}
+	\label{fb_bl}
+\end{figure}
+%BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.
+
+To verify Facebook’s ban of The BL domain name, we first tested whether we could post a Facebook message containing a url from thebl.com.
+This turned out to be impossible.
+But such manual verification cannot inform us whether the ban applies indeed to all Facebook users and accounts (as we used only our own personal accounts), nor when it has started.
+To further investigate this policy, we collected data from Buzzsumo.\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.} We used the ``/search/articles'' endpoint of the Buzzsumo API, to collect the engagement metrics $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.\footnote{The command can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}.}
+
+The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban.
+We can note that although the ban was communicated in an article published\footnote{See \href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}.} on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
+The number of articles published per day was around $50$ until December $20$, $2019$.
+The this number decreased drastically to reach a {\color{pink} plateau} around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).
+The communication around the ban may have discouraged The Beauty of Life to proceed with their activity.
+Using Buzzsumo data, a global ban over sharing a thebl.com URL link on Facebook was ascertained.
+It started on December $1$, $2019$, and was still enforced in June 2021.
 
@@
 
-One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through ranking.
-Facebook ranks each post and ad with a relevancy score, a high score leading to a high likelihood of the post or the ad appearing in someone’s newsfeed.
-Facebook can thus make a post or a whole account less visible by decreasing the rank of its content.\footnote{Lyons, T.
+\begin{figure}
+	\centering
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_1.png}
+	\end{multicols}
+
+	\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_2.png} 
+	\end{multicols}
+
+	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API.
+The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars.
+(Top panel) Number of daily posts.
+(Bottom panel) Engagement metrics: average number of reactions, shares and comments per post.
+}
+	\label{infowars1}
+\end{figure}
+
+One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through their ranking system.
+Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed.
+Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure.\footnote{Lyons, T.
 (2018, May 22).
@@
 Facebook Newsroom.
-\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} Such {\it reduce} action should be visible in the engagement metrics of the posts: if a post reaches less users because of a lower ranking, it is less likely to receive likes, comments and shares.
+\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the CrowdTangle API or on Buzzsumo.
+Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available via the CrowdTangle API and Buzzsumo.
+If a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.
 
-Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.}, was classified among websites that have posted deceptive content according to FactCheck.org\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}, and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.} On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}.}
+%phrase pas accès au reach, mais seulement les engagement metrics
+% Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.},
+%CrowdTangle and Buzzsumo provide access to the interaction metrics on content (engagement), but not to the number of views (or reach), therefore we can only verify the {\it reduce} measure indirectly through a decrease in engagement.
+If Facebook was reducing the reach of a content via a lower ranking, we would expect the content to be less likely to receive likes, comments and shares, relative to a post with a higher ranking.
 
-To verify the measure, we used the CrowdTangle API at the ‘/posts/search’ endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} to collect the 37,242 Facebook public posts that shared a link containing ‘infowars.com’ and that were published between January 1, 2019 and December 31, 2020.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the 27,721 posts directly sharing an Infowars link.} The command used can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{here}.
+\smallskip
 
-The number of public posts sharing an Infowars link remained globally stable in 2019 (Figure \ref{infowars1} top panel), thus Facebook’s announced ‘ban’ did not appear to prevent users from sharing an Infowars link.
-Interestingly a clear drop in engagement was observed on May 2, 2019 (Figure \ref{infowars1} bottom panel).
-The number of reactions per post decreased by -94\% when we compared the two months before and after May 2, 2019, the shares decreased by -96\%, and the comments by -93\%.
+To illustrate, we investigate the case of the website $Infowars$.
+This website appears in the Misinformation Directory of FactCheck.org, among other websites who have posted deceptive content\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}.
+Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.}
 
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
+		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
 	\end{multicols}
 
-	\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
-	\end{multicols}
-
-	\caption{Public Facebook posts sharing an Infowars link in 2019 and 2020 gathered from the CrowdTangle API.
-The red line marks the date of May 2, 2019, when Facebook has announced the ban regarding Infowars.
-(Top panel) Number of daily posts.
-(Bottom panel) Engagement metrics (average number of reactions, shares and comments per post).
-}
-	\label{infowars1}
+	\caption{Facebook engagement metrics (average number of reactions, shares and comments per article) for the Infowars articles published in $2019-2020$ and gathered from the Buzzsumo API.
+The red line marks the date of May $2$, $2019$, when Facebook has announced the ban regarding Infowars.}
+	\label{infowars2}
 \end{figure}
 
-This would suggest that Facebook’s measure taken in May 2019 is actually not a ban, but would rather correspond to a ‘reduce’ action, as users could still post Infowars links, but these posts generated vastly less engagement.
-It should be noted that the engagement metrics increased again at the end of 2019 / beginning of 2020, suggesting that the reducing measure may have been lifted a few months after its implementation.
+On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/} and \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}.
+The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel).
+Thus the measure announced by Facebook doesn't seem to have prevented users from sharing an $Infowars$ link.
+Nevertheless, a clear drop in engagement was observed on May 2, 2019 (see figure \ref{infowars1} bottom panel).
+The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May 2, 2019.
+This suggests the measure taken by Facebook in May $2019$, is not a ban per se, but rather a $reduce$ measure.
+This is because users could still post $Infowars$ links, but these posts generated less engagement.
+It should be noted that the engagement metrics increased again by the end of $2019$ / beginning of $2020$, suggesting that the $reduce$ measure may have been lifted a few months after its implementation.
 
-As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ‘/search/articles’ endpoint of the Buzzsumo API, to gather more complete Facebook data.
-We collected the engagement data for the 14,232 articles crawled by Buzzsumo from the Infowars website between January 1, 2019 and Decembre 31, 2020.
-The command can be found here.
-We observe that the articles published after May 2, 2019 received less Facebook engagement than the ones published before (Figure X5), with a percentage change of -97\% for the reactions, -59\% for the shares and -97\% for the comments.
-An increase in engagement was also observed in 2020.
-It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links during a few months in 2019.
-
-We found irregularities in the number of Infowars articles collected from Buzzsumo.
-While Infowars usually publishes 20-30 articles per day, only 53 articles were collected in the 31-day period between June 11 to July 11, 2020.
-A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
-Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
+As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset.
+We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.
+\footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
+An increase in engagement was also observed in $2020$.
+It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.
 
@@
 }
+
+The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; which was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021.
+But to the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
+Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}).
+Furthermore, $globalresearch.ca$ has multiple failed fact-checks, see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}} When a user searches via the twitter search-box for any URL link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June $14$, $2021$.
+To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the URL link {\it globalresearch.ca} throughout May $2021$ and the first week of June $2021$.
+Hence, the visibility of tweets containing this URL link has been reduced because users can no longer access tweets containing the URL link {\it globalresearch.ca} via the search box.
+Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(a)$ of figure \ref{fig4bis}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
+Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
+Hence, the users who tweet articles from the {\it globalresearch.ca} website receive tweet level engagement from their own followers.
+Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (b) in figure \ref{fig4bis}).
 \begin{figure}
@@
 		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
-		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
 	\end{multicols}
-\caption{}
+	\begin{multicols}{1}
+		\includegraphics[scale=0.33]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
+	\end{multicols}
+\caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+Bottom panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+Data collected via the Twitter API v2 on June $16$, 2021.
+}
 \label{fig4}
@@
 	\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
-		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
+		\includegraphics[scale=0.3]{./img/globalresearch/tweet.png}
+	\end{multicols}
+	\begin{multicols}{1} 
+		\includegraphics[scale=0.3]{./img/globalresearch/warning.png}
 	\end{multicols}
@@
 \end{figure}
-
-The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; that was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021.
-But to the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
-Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}).
-Furthermore, $globalresearch.ca$ has multiple failed fact-checks, see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}} When a user searches via the twitter search-box a url link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June 14, 2021.
-To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January 1, 2021 until June 10, 2021.
-As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the URL link {\it globalresearch.ca} throughout May 2021 and the first week of June 2021.
-Hence, the visibility of tweets containing this URL link has been reduced because users can no longer access tweets containing the URL link {\it globalresearch.ca} via the search box.
-Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(c)$
- of figure \ref{fig4}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
-Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
-Hence, the users who tweet articles from the {\it globalresearch.ca} website receive positive engagement from their own followers.
-Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (d) in figure \ref{fig4}).
 
@@
 	\begin{multicols}{1}
-\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30_2.png}
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
    	 \end{multicols}
 	\begin{multicols}{1} 
-\includegraphics[scale=0.25]{./img/tweets/Capture_2021-06-30.png}
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30.png}
 	\end{multicols}
@@
 At the account level, notices can indicate whether an account has been temporarily or permanently suspended.
+
 \smallskip
@@
 { \color{pink} 
+Sporadic points for the discussion, no structure yet.
+
 \begin{itemize}
@@
 For example Newsguard, blablabla...
-In this tweet, we can see the interface of XXX being used in this study from a data journalist: https://twitter.com/Shayan86/status/1394742784683298818/photo/2
+In this tweet, we can see the interface of XXX being used in this study from a data journalist: \href{https://twitter.com/Shayan86/status/1394742784683298818/photo/2}{ex}
 
@@
 	\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies...
+
 	\item business model
 
-\end{itemize}}
-\newpage
+	\item Pas accès au ``reach" !  ranking not available. Fb nous a donné certaines données (les données Condor) et dedans on a le nombre de clicks par exemple
+
+	\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
+While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
+	\item Researchers should be able to access the data of deleted accounts on the main platforms.
+
+	\item Currently the flag or notice banners data is not present in the platforms’ API datasource, and this prevents researchers and journalists from easily investigating that matter.
+They have to use or build a scraper to access the data.
+
+	\item Lack of transparency in the platforms’ communication that makes their policies harder to verify.
+
+	\item Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
+While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
+A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
+Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
+\end{itemize}
+}
 
@@
 
+\newpage
+
 \section{Appendix}
 
+\begin{table*}[h]
+\begin{tabular}{|c|c|c|}
+\hline
+\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/communitystandards/recentupdates/}{facebook.com/communitystandards/recentupdates/}                         \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}                       \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/} \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Rules \\ enforcement \end{tabular}}         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & \href{https://transparency.fb.com/data/community-standards-enforcement/}{transparency.fb.com/data/community-standards-enforcement/}                 \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports/rules-enforcement.html}{transparency.twitter.com/en/reports/rules-enforcement.html}                \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/youtube-policy/}{transparencyreport.google.com/youtube-policy/}                              \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Transparency \\ center \end{tabular}}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports.html}{transparency.twitter.com/en/reports.html}                                  \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/?hl=en}{transparencyreport.google.com/?hl=en}                                      \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Policy regarding \\  Covid-19 \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy}       \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}                                 \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Fact-checking \\ policy \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}                                    \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & x       \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9229632}{support.google.com/youtube/answer/9229632}                                  \\ \hline
+
+\end{tabular}
+\caption{Summary of ressources, last accessed on July 5, 2021. }
+\label{summary}
+\end{table*}
+
 \end{document}

### 2021-07-06 article/draft.tex
some changes

@@
 	\centering
-		\begin{multicols}{1}
+		%\begin{multicols}{1}
 			\includegraphics[scale=0.2]{./img/fb/fig1_fb.png}
-		\end{multicols}
+		%\end{multicols}
 	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J.
@@
 \centering
-	\begin{multicols}{1}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
-	\end{multicols}
-	\begin{multicols}{1}
+	%\end{multicols}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
-	\end{multicols}
+	%\end{multicols}
 \caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021.
@@
 	\centering
-	\begin{multicols}{1}
-		\includegraphics[scale=0.29]{./img/oann/fig1_oann.png}
-	\end{multicols}
-	\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/oann/fig2_oann.png} 
-	\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.24]{./img/oann/fig1_oann.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
+	%\end{multicols}
 	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
@@
 	\centering
-	\begin{multicols}{1}
-		\includegraphics[scale=0.32]{./img/oann/fig3_oann.png}
-	\end{multicols}
-
-	\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/tony/fig3_tony.png}
-	\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.21]{./img/oann/fig3_oann.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.21]{./img/tony/fig3_tony.png}
+	%\end{multicols}
 
@@
 	\centering
-		\begin{multicols}{1}
-			\includegraphics[scale=0.35]{./img/tony/fig1_tony.png}
-		\end{multicols}
-
-		\begin{multicols}{1}
-			\includegraphics[scale=0.35]{./img/tony/fig2_tony.png}
-		\end{multicols}
+		%\begin{multicols}{1}
+			\includegraphics[scale=0.25]{./img/tony/fig1_tony.png}
+		%\end{multicols}
+		%\begin{multicols}{1}
+			\includegraphics[scale=0.25]{./img/tony/fig2_tony.png}
+		%\end{multicols}
 	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
@@
 
-	\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_1.png}
-	\end{multicols}
-
-	\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_2.png} 
-	\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/beautyoflife/fb_bl_1.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/beautyoflife/fb_bl_2.png} 
+	%\end{multicols}
 
@@
 
-	\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_1.png}
-	\end{multicols}
-
-	\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_2.png} 
-	\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
+	%\end{multicols}
 
@@
 
-	\begin{multicols}{1}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
-	\end{multicols}
+	%\end{multicols}
 
@@
 	\centering
-		\begin{multicols}{1}	
+		%\begin{multicols}{1}	
 			\includegraphics[scale=0.35]{./img/globalresearch_2021-06-14.png}
-		\end{multicols}
-
-		\begin{multicols}{1}
+		%\end{multicols}
+		%\begin{multicols}{1}
 			\includegraphics[scale=0.35]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
-		\end{multicols}
+		%\end{multicols}
 		\caption{Screenshots taken on June 14, 2021.
@@
 \centering
-	\begin{multicols}{1}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
-	\end{multicols}
-	\begin{multicols}{1}
+	%\end{multicols}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
-	\end{multicols}
+	%\end{multicols}
 \caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
@@
 \centering	
-	\begin{multicols}{1}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
-	\end{multicols}
-	\begin{multicols}{1}
+	%\end{multicols}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
-	\end{multicols}
+	%\end{multicols}
 \caption{}
@@
 \centering
-	\begin{multicols}{1}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
-   	 \end{multicols}
-	\begin{multicols}{1} 
+   	 %\end{multicols}
+	%\begin{multicols}{1} 
 		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30.png}
-	\end{multicols}
+	%\end{multicols}
 	\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021.
@@
 	\centering
-	\begin{multicols}{1}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png} 
-	\end{multicols}
-	\begin{multicols}{1}
+	%\end{multicols}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png}
-	\end{multicols}
+	%\end{multicols}
 	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
@@
 	\centering
-	\begin{multicols}{1}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.2]{./img/youtube_panels/yt_1.png} 
-	\end{multicols}
-	\begin{multicols}{1}
+	%\end{multicols}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.2]{./img/youtube_panels/yt_2.png} 
-	\end{multicols}
-	\begin{multicols}{1}
+	%\end{multicols}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.2]{./img/youtube_panels/yt_3.png}
-	\end{multicols}
-	\begin{multicols}{1}
+	%\end{multicols}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.2]{./img/youtube_panels/yt_4.png} 
-	\end{multicols}
+	%\end{multicols}
 	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}

### 2021-07-07 article/draft.tex
updates

@@
 
-\title{Very Preliminary Draft}
+\title{Big Tech is censoring me: \\ Using social media data to verify the platforms' regulation policies regarding ``misinformation''}
 
@@
 
-Using social media data to verify the platforms' regulation policies regarding ``misinformation''
+'Big Tech is censoring me': Using social media data to verify the platforms' regulation policies regarding ``misinformation''
 
@@
 &  \begin{tabular}[c]{@{}l@{}} Application Programming \\ Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web \\ Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
- \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} \\ \href{https://buzzsumo.com}{Buzzsumo}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
+ \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} \\ \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
 \\ \hline
@@
 First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}.
-This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{See nbcnews,  ``YouTube suspends OANN for violating its Covid-19 policy''.
-nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021.
+This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021.
 For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
@@
 The number of articles published per day was around $50$ until December $20$, $2019$.
-The this number decreased drastically to reach a {\color{pink} plateau} around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).
+This number decreased drastically to reach around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).
 The communication around the ban may have discouraged The Beauty of Life to proceed with their activity.
@@
 
+\subsubsection{Twitter}
+
+\href{https://help.twitter.com/en/safety-and-security/phishing-spam-and-malware-links}{link}
 \subsection{Reducing the visibility}
@@
 Labels are context specific (e.g.
-COVID19 or presidential elections) and  redirect users to a URL link to get more context.
-Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts.
+COVID19 or presidential elections) and  redirect users to a URL link to get more context (see figure \ref{fig8} for an example).
+Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts (see figure \ref{fig_notice} for an example).
 At the account level, notices can indicate whether an account has been temporarily or permanently suspended.
+
+\smallskip
+
+{\color{red} To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
+...............
+so say minet tw scrape, scraper was enriched to get information about labels!}
 
@@
 
-Finally, to the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
+The Twitter Safety announced in a Tweet that 
+%https://twitter.com/TwitterSafety/status/1379515615954620418
 
@@
 	%\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
+	%\end{multicols}
+	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
 	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png}
-	%\end{multicols}
-	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
+	\caption{Panel (a): Tweet containing a URL link hidden behind an interstitial.
+Panel (b): when clicking on $view$, to view the content hidden behind the interstitial.
+Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}.
+Screenshots taken on July 1, 2021.
+}
 	\label{fig_notice}
@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/yt_1.png} 
+		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
 	%\end{multicols}
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/yt_2.png} 
+		\includegraphics[scale=0.3]{./img/youtube_panels/yt_2.png} 
 	%\end{multicols}
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/yt_3.png}
+		\includegraphics[scale=0.3]{./img/youtube_panels/yt_3.png}
 	%\end{multicols}
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/yt_4.png} 
+		\includegraphics[scale=0.3]{./img/youtube_panels/yt_4.png} 
 	%\end{multicols}
@@
 For COVID19 and vaccine related videos more than half of the videos contained an information panel.
-{\color{pink} Nevertheless, we noticed that some videos get uploaded multiple times by different channels under different video titles but others didn’t even though the video was the same.} In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
+Nevertheless, we noticed that duplicates of the same Youtube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
+In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
 Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.
@@
 
-For climate change we only examined $18$ misleading videos and we found that $72\%$ did not display an information panel.
+For climate change we only examined $18$ misleading videos and we found that $28\%$ did not display an information panel.
 Lastly , for the general health category, we included the videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion,  and viruses; no information panels were displayed for that set of Youtube videos.
-Therefore, it is likely that Youtube add information panels below videos conecrning controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.
-
+Therefore, it is likely that Youtube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.
+%drop last colum
+%add % in a second line
 \begin{table}[] 
@@
 \hline
-Category       & \begin{tabular}[c]{@{}c@{}}With \\ information \\ panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Without  \\\ information \\ panel\end{tabular} & Total & \begin{tabular}[c]{@{}c@{}}IP \% \end{tabular} \\ \hline
-\begin{tabular}[c]{@{}c@{}} General \\ Health \end{tabular} & 0                                                                 & 11                                                                   & 11    & 0                                                       \\ \hline
-Vaccine        & 21                                                                & 7                                                                    & 28    & 75                                                      \\ \hline
-COVID19          & 73                                                                & 43                                                                   & 116   & 63                                                      \\ \hline
-\begin{tabular}[c]{@{}c@{}}  Climate \\ change \end{tabular} & 5                                                                 & 13                                                                   & 18    & 28                                                      \\ \hline
+Category       & \begin{tabular}[c]{@{}c@{}}Number of Youtube \\ videos with \\ an information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of Youtube \\ videos without \\ an information panel\end{tabular}    \\ \hline
+\begin{tabular}[c]{@{}c@{}} General \\ Health \end{tabular} & \begin{tabular}[c]{@{}c@{}} 0  \\ (0\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 11 \\ (100\%) \end{tabular}         \\ \hline
+Vaccine        & \begin{tabular}[c]{@{}c@{}} 21     \\ (75\%) \end{tabular}   & \begin{tabular}[c]{@{}c@{}}  7 \\ (25\%)  \end{tabular}     \\ \hline
+COVID19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
+\begin{tabular}[c]{@{}c@{}}  Climate \\ change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
 \end{tabular}
@@
                                            & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/} \\ \hline
-\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Rules \\ enforcement \end{tabular}}         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & \href{https://transparency.fb.com/data/community-standards-enforcement/}{transparency.fb.com/data/community-standards-enforcement/}                 \\ \cline{2-3}
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Rules \\ enforcement \end{tabular}}         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & \href{https://transparency.fb.com/data/community-standards-enforcement/}{transparency.fb.com/data/community-standards-enforcement/}                 \\ \cline{2-3}
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports/rules-enforcement.html}{transparency.twitter.com/en/reports/rules-enforcement.html}                \\ \cline{2-3}
                                            & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/youtube-policy/}{transparencyreport.google.com/youtube-policy/}                              \\ \hline
-\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Transparency \\ center \end{tabular}}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3}
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Transparency \\ center \end{tabular}}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3}
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports.html}{transparency.twitter.com/en/reports.html}                                  \\ \cline{2-3}
                                            & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/?hl=en}{transparencyreport.google.com/?hl=en}                                      \\ \hline
-\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Policy regarding \\  Covid-19 \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3}
-                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy}       \\ \cline{2-3}
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Policy \\ regarding \\  Covid-19 \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \begin{tabular}[c]{@{}cl@{}} \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} \\  \href{https://blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}{blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation} \\  \href{https://blog.twitter.com/en\_us/topics/company/2020/covid-19}{blog.twitter.com/en\_us/topics/company/2020/covid-19}\end{tabular}      \\ \cline{2-3}
                                            & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}                                 \\ \hline
-\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Fact-checking \\ policy \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}                                    \\ \cline{2-3}
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Fact-checking \\ policy \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}                                    \\ \cline{2-3}
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   & x       \\ \cline{2-3} 
                                            & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9229632}{support.google.com/youtube/answer/9229632}                                  \\ \hline
-
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Fighting \\ misinformation \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}} \href{https://www.facebook.com/formedia/blog/working-to-stop-misinformation-and-false-news}{facebook.com/formedia/blog/working-to-stop-misinformation-and-false-news}     \\ \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{about.fb.com/news/2018/05/hard-questions-false-news/}   \end{tabular}                            \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   &        \\ \cline{2-3} 
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}                                  \\ \hline
  \end{tabular}

### 2021-07-08 code/collect_facebook_crowdtangle_false_link.sh
add data collection for manual flag count

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+TODAY_DATE=$(date +"%Y-%m-%d")
+
+minet ct search \
+"https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html" \
+  --search-field include_query_strings --platform facebook --start-date 2019-01-01 > \
+  "./data/facebook_crowdtangle_false_link_${TODAY_DATE}.csv"

### 2021-07-08 article/draft.tex
updates

@@
 
-\title{Big Tech is censoring me: \\ Using social media data to verify the platforms' regulation policies regarding ``misinformation''}
+\title{Preliminary Draft}
 
@@
 
-'Big Tech is censoring me': Using social media data to verify the platforms' regulation policies regarding ``misinformation''
+Title proposition 1: Big Tech is censoring me: using social media data to verify the platforms' regulation policies regarding ``misinformation''. 
+%'Big Tech is censoring me': Using social media data to verify the platforms' regulation policies regarding ``misinformation''
 
@@
 In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al.
-(2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
+(2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
 The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
@@
 In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
-This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.\footnote{For an overview of Facebook's third-party fact checking program see see \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}.
-For an overview of Youtube's policy on fact-checking see:  }
+This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
+For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.
+\footnote{For an overview of Facebook's third-party fact checking program see: \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}.} Facebook use a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
+The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1.
+Twitter shouldn’t determine the truthfulness of Tweets 2.
+Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed.
+Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation.\footnote{See Twitter Birdwatch: \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}.}
 
@@
 
-During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: \href{https://support.google.com/youtube/answer/9891785}{https://support.google.com/youtube/answer/9891785}.} As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms.
+{\color{pink} Note, put here something along the following lines: cite misinformation review article about support for fact-checking + hard to correct beliefs once it goes viral.
+cite Pennycook / Rand?
++ where to put or cite \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{this} ?
+}
+%In particular, determining the truthfulness of content over controversial topics or ongoing political events proves to be a tricky task and correcting beliefs about viral content, fact-checked as false ...
+%For an overview of Youtube's policy on fact-checking see: \href{https://support.google.com/youtube/answer/9229632}{support.google.com/youtube/answer/9229632}.
+To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
+The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1.
+Twitter shouldn’t determine the truthfulness of Tweets 2.
+Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed.
+Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.}
+
+%In particular, the peculiar task of determining the truthfulness of content over controversial topics or ongoing political events 
+\smallskip
+
+During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates concerning COVID19 related misinformation policies: \href{https://support.google.com/youtube/answer/9891785}{https://support.google.com/youtube/answer/9891785}, \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}.} Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged\footnote{{\color{pink} put here the list of Facebook and Twitter terms about covid.}}, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
+As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms.
 Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
 In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}.
-The 2019 report of the Facebook Data Transparency Advisory Group\footnote{See \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}.} (DTAG) states clearly that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
+The 2019 report of the Facebook Data Transparency Advisory Group\footnote{To read the full report, see: \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}.} (DTAG) states clearly that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
 Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
 It is explained via a blog post on the facebook Newsroom.\footnote{See: \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{https://about.fb.com/news/2018/05/hard-questions-false-news/}.}.
-Similarly, Twitter communicates about actions related to misinformation via their Twitter Safety Blog/accout\footnote{See \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{https://blog.twitter.com/en\_us/authors.TwitterSafety}.}.
+Similarly, Twitter communicates about actions related to misinformation via their Twitter Safety Blog/account\footnote{See \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{https://blog.twitter.com/en\_us/authors.TwitterSafety}.}.
+In a post on Youtube Official Blog\footnote{See \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}.}, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content reduces borderline content and harmful misinformation.
 
-{\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community,  idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.
+{\color{pink} Note, put here something along the following line: make point here about the fact that in the transparency centers we find things for the violations in the platforms rules but not misinformation....
+needed so that the academic community can study the reach and impact of this phenomena and provide guidelines for adequate actions...
++ where to put this \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} ?
+}
+%{\color{pink}  idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.
 Violations fall into other categories: deceptive practices, impersonation, hate speech.
@@
 
-\smallskip
+\begin{table}[]
+\centering
+\begin{tabular}{|l|c|l|l|l}
+
+\hline
+&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
+ \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} and  \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
+\\ \hline
+ \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
+ \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
+\end{tabular}
+\caption{Data collection}
+\label{tab1}
+\end{table}
 
@@
 
-\begin{table}[]
-\centering
-\begin{tabular}{|l|c|l|l|l}
-
-\hline
-&  \begin{tabular}[c]{@{}l@{}} Application Programming \\ Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web \\ Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
- \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} \\ \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
-\\ \hline
- \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
- \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
-\end{tabular}
-\caption{Data collection}
-\label{tab1}
-\end{table}
-
  %We We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.
@@
 
-\smallskip
+\subsubsection{Facebook}
 
-\subsubsection{Facebook}
+\begin{figure}
+	\centering
+		%\begin{multicols}{1}
+			\includegraphics[scale=0.3]{./img/fb/fig1_fb.png}
+		%\end{multicols}
+	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J.
+Trump} between January $1$, $2020$ and June $15$, $2021$.
+The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
+	\label{fig1_fb}
+\end{figure}
 
@@
 Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.
-
-\begin{figure}
-	\centering
-		%\begin{multicols}{1}
-			\includegraphics[scale=0.2]{./img/fb/fig1_fb.png}
-		%\end{multicols}
-	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J.
-Trump} between January $1$, $2020$ and June $15$, $2021$.
-The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
-	\label{fig1_fb}
-\end{figure}
 
@@
 
+To the best of our knowledge, two types of flags can currently be seen on Facebook posts, videos and pictures: information banners that do not refute the message in the post but that give a link to an authoritative source (such as ‘Visit the COVID-19 Information Centre for vaccine resources’) and fact-check flags that provide a ‘judgement’ on the text of the post or the link shared (such as ‘False information Checked by independent fact-checkers.’) (see Figure \ref{fb_flags}).
+The fact-check flags can be of varied nature : False, Partly false, Missing context, False headline, Altered media, Opinion, Satire, Not eligible and even True.
+
+No information regarding the flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data.
+To verify Facebook’s flag policy, only two options are possible: manually or by scraping Facebook.
+
+To better understand the banners implemented by Facebook, we searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the `search` endpoint in minet.
+\footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}).
+The command can be found here: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_crowdtangle\_false\_link.sh}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_crowdtangle\_false\_link.sh}.} We collected 20 Facebook posts and we manually opened them to verify whether they were flagged with an information banner, a fact-check flag, both or none (2 posts were unavailable so only 18 were categorized).
+As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
+\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
+\includegraphics[scale=0.45]{./img/fb_flags/fb_flag_3.png}
+\caption{Examples of the Facebook posts having shared a link fact-checked False by one of Facebook’s partners (Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}).}
+\label{fb_flags}
+\end{figure}
+
+We observed that 11 posts out of 18 had a ‘False information’ flag.
+We observed that the posts with the ‘False information’ flag were also the ones with a preview of the link (i.e.
+the banner with an image of the link that we can click on).
+As the ‘False information’ flag is applied on the preview of the link, and not on the link itself, a user could share a link without the ‘False information’ banner as in the first example of Figure  \ref{fb_flags}.
+
+We also observed that most of the posts (14 out of 18) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}).
+We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post message for example).
+
+\begin{table}[]
+\begin{tabular}{|c|c|c|c|}
+\hline
+\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
+with no flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check \\ and an information flags\end{tabular} \\ \hline
+0            & 7                        & 4                      & 7                                                                                     \\ \hline
+\end{tabular}
+%\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
+%\label{tab_flags}
+\end{table}
+
 \subsubsection{Twitter}
@@
 
-{\color{red} To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
-...............
-so say minet tw scrape, scraper was enriched to get information about labels!}
+To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
+Hence, in order to investigate the presence of labels, we resorted to scrape Twitter data using Minet [5].
+This tool was recently enriched upon our request in order to capture whether a tweet contains a label or not, via the {\it minet twitter scrape} command.
 
@@
 
-The Twitter Safety announced in a Tweet that 
-%https://twitter.com/TwitterSafety/status/1379515615954620418
+\smallskip
+
+Finally, the Twitter Safety announced in a Tweet\footnote{See Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}} on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".
+%we don't know what it means the articl xxx which was retracted by the journal and fack-check still appears in xx tweets with no label
 
@@
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   &        \\ \cline{2-3} 
-                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}                                  \\ \hline
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}  \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}  \\ \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}    \end{tabular}                            \\ \hline
  \end{tabular}

### 2021-07-09 code/check_flag_youtube.py
update collect_youtube_data:: upload check_flag_youtube

@@ -1,0 +1,39 @@
+import sys
+import time
+
+from selenium import webdriver
+from selenium.webdriver.common.keys import Keys
+from selenium import webdriver
+from selenium.common.exceptions import NoSuchElementException
+
+
+def check_exists_by_xpath(xpath,driver):
+    try:
+        driver.find_element_by_xpath(xpath)
+    except NoSuchElementException:
+        return False
+    return True
+
+def information_panel(video_id):
+    try:
+            # replace with your driver path
+            chrome_path = '/usr/local/bin/chromedriver'
+            driver = webdriver.Chrome(chrome_path)
+            web = 'https://www.youtube.com/watch?v='+video_id
+            driver.get(web)
+            time.sleep(5)
+            exist = check_exists_by_xpath('//*[@id="clarify-box"]',driver)
+            print(exist)
+            if (exist ==True):
+                content = driver.find_element_by_xpath('//*[@id="clarify-box"]').text
+            else:
+                content =''
+            time.sleep(3)
+            driver.close()
+
+            return content
+    except:
+            return 'Error'
+
+if __name__=="__main__":
+    print(information_panel(sys.argv[1]))

### 2021-07-09 code/collect_youtube_data.py

@@ -1,9 +1,11 @@
-from googleapiclient.discovery import build
 from datetime import datetime, timedelta
+import re
+import os
+
 import pandas as pd
 import numpy as np
-import re
-import sys
+from googleapiclient.discovery import build
+from dotenv import load_dotenv
 
 
 def get_channel_videos(channel_id, youtube):
@@ -51,15 +53,26 @@ def collect_data(API_key, channel_id):
     videos_df = pd.DataFrame({'Upload_date':publish_timestamps,'video_titles':titles,'video_id':video_ids})
     videos_df = videos_df[videos_df['Upload_date']>'2019-01-01']
     videos_ids_filtered = list(videos_df['video_id'])
-    data = pd.DataFrame([], columns=['video_title', 'view_counts', 'likes', 'dislikes', 'comments', 'video_id',
-                                       'channel_name', 'channel_id', 'published_at', 'duration'])
-    for i in videos_ids_filtered:
-        video_data = get_data_video(i, youtube)
-        r_series = pd.Series(video_data, index=data.columns)
-        data = data.append(r_series, ignore_index=True)
-    channel_name = data['channel_name'].iloc[0]
-    path = 'data/' + channel_name + '_youtube_data.csv'
-    data.to_csv(path)
+
+
+    for i in range(0,len(videos_ids_filtered)):
+        data_header = pd.DataFrame([],
+                                   columns=['video_title', 'view_counts', 'likes', 'dislikes', 'comments', 'video_id',
+                                            'channel_name', 'channel_id', 'published_at', 'duration'])
+        video_data = get_data_video(videos_ids_filtered[i], youtube)
+        r_series = pd.Series(video_data, index=data_header.columns)
+        channel_name = r_series['channel_name']
+        path = 'data/' + channel_name + '_youtube_data.csv'
+        if (i==0):
+            data_header.to_csv(path,index=False)
+        data_header = data_header.append(r_series, ignore_index=True)
+        data_header.to_csv(path, mode='a', header=False,index=False)
+
+
+
+
+    #path = 'data/' + channel_name + '_youtube_data.csv'
+    #data.to_csv(path)
 
 
 def get_data_video(vid_id, youtube):
@@ -104,7 +117,8 @@ def get_data_video(vid_id, youtube):
         return data
 
[…]

### 2021-07-09 code/check_flag_youtube.py
update check_flag_youtube.py

@@ -2,8 +2,6 @@ import sys
 import time
 
 from selenium import webdriver
-from selenium.webdriver.common.keys import Keys
-from selenium import webdriver
 from selenium.common.exceptions import NoSuchElementException
 
 
@@ -23,7 +21,6 @@ def information_panel(video_id):
             driver.get(web)
             time.sleep(5)
             exist = check_exists_by_xpath('//*[@id="clarify-box"]',driver)
-            print(exist)
             if (exist ==True):
                 content = driver.find_element_by_xpath('//*[@id="clarify-box"]').text
             else:

### 2021-07-09 code/check_flag_youtube.py
check_flag_yt.py:syntax fixing

@@ -5,32 +5,33 @@ from selenium import webdriver
 from selenium.common.exceptions import NoSuchElementException
 
 
-def check_exists_by_xpath(xpath,driver):
+def check_exists_by_xpath(xpath, driver):
     try:
         driver.find_element_by_xpath(xpath)
     except NoSuchElementException:
         return False
     return True
 
+
 def information_panel(video_id):
     try:
-            # replace with your driver path
-            chrome_path = '/usr/local/bin/chromedriver'
-            driver = webdriver.Chrome(chrome_path)
-            web = 'https://www.youtube.com/watch?v='+video_id
-            driver.get(web)
-            time.sleep(5)
-            exist = check_exists_by_xpath('//*[@id="clarify-box"]',driver)
-            if (exist ==True):
-                content = driver.find_element_by_xpath('//*[@id="clarify-box"]').text
-            else:
-                content =''
-            time.sleep(3)
-            driver.close()
+        # replace with your driver path
+        chrome_path = '/usr/local/bin/chromedriver'
+        driver = webdriver.Chrome(chrome_path)
+        web = 'https://www.youtube.com/watch?v='+video_id
+        driver.get(web)
+        time.sleep(5)
 
-            return content
+        exist = check_exists_by_xpath('//*[@id="clarify-box"]',driver)
+        if (exist ==True):
+             content = driver.find_element_by_xpath('//*[@id="clarify-box"]').text
+        else:
+            content =''
+        driver.close()
+        return content
     except:
-            return 'Error'
+        return 'Error'
 
-if __name__=="__main__":
+
+if __name__ == "__main__":
     print(information_panel(sys.argv[1]))

### 2021-07-15 code/collect_facebook_crowdtangle_false_link.sh
add temp code for scraping the flag on Facebook posts

@@ -5,4 +5,10 @@ TODAY_DATE=$(date +"%Y-%m-%d")
 minet ct search \
 "https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html" \
   --search-field include_query_strings --platform facebook --start-date 2019-01-01 > \
-  "./data/facebook_crowdtangle_false_link_${TODAY_DATE}.csv"
+  "./data/facebook_crowdtangle_raw_false_link_${TODAY_DATE}.csv"
+
+# On minet's new banch only for now. 
+# TO DO: change when minet's new version will be released.
+
+lminet fb post-stats post_url "./data/facebook_crowdtangle_raw_false_link_${TODAY_DATE}.csv" \
+  -s post_url > "./data/facebook_crowdtangle_false_link_${TODAY_DATE}.csv"

### 2021-07-15 article/draft.tex
correct a bit the section about Facebook flags

@@
 No information regarding the flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data.
-To verify Facebook’s flag policy, only two options are possible: manually or by scraping Facebook.
+The only way to verify Facebook’s flag policy is thus to scrap Facebook.
+For this paper, we added a new feature in minet to scrape Facebook posts and automatically verify for the presence of the flags.
 
-To better understand the banners implemented by Facebook, we searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the `search` endpoint in minet.
-\footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}).
-The command can be found here: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_crowdtangle\_false\_link.sh}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_crowdtangle\_false\_link.sh}.} We collected 20 Facebook posts and we manually opened them to verify whether they were flagged with an information banner, a fact-check flag, both or none (2 posts were unavailable so only 18 were categorized).
+We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the `search` endpoint in minet\footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}).}.
+20 Facebook posts were collected this way, and the newly developed scraper was used to verify whether they were flagged with an information banner, a fact-check flag, both or none.
+3 posts were unavailable, and thus could not be categorized by the scraper.
 As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.
@@
 \includegraphics[scale=0.45]{./img/fb_flags/fb_flag_3.png}
-\caption{Examples of the Facebook posts having shared a link fact-checked False by one of Facebook’s partners (Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}).}
+\caption{Examples of the Facebook posts having shared a link fact-checked False by one of Facebook’s partners (Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{https://www.facebook.com/691911990845585/posts/3835629366473816}).}
 \label{fb_flags}
@@
 
-We observed that 11 posts out of 18 had a ‘False information’ flag.
-We observed that the posts with the ‘False information’ flag were also the ones with a preview of the link (i.e.
-the banner with an image of the link that we can click on).
-As the ‘False information’ flag is applied on the preview of the link, and not on the link itself, a user could share a link without the ‘False information’ banner as in the first example of Figure  \ref{fb_flags}.
+Surprinsingly only 11 posts out of the remaining 17 had a ‘False information’ flag  (see Table \ref{tab_flags_fb}).
+We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples).
+As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user could share a link without the ‘False information’ banner as in the first example of Figure \ref{fb_flags}.
 
-We also observed that most of the posts (14 out of 18) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}).
-We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post message for example).
+We also observed that most of the posts (13 out of 17, see Table \ref{tab_flags_fb}) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}).
+We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example).
+It should be noted that some posts displayed both the information and the fact-check banners, as in the right panel of Figure \ref{fb_flags}.
 
@@
 \end{tabular}
-%\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
-%\label{tab_flags}
+\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
+\label{tab_flags_fb}
 \end{table}

### 2021-07-15 article/draft.tex
correct typos and add details

@@
 
-Title proposition 1: Big Tech is censoring me: using social media data to verify the platforms' regulation policies regarding ``misinformation''. 
-%'Big Tech is censoring me': Using social media data to verify the platforms' regulation policies regarding ``misinformation''
+Title proposition 1: ``Big Tech is censoring me'': using social media data to verify the platforms' regulation policies regarding misinformation.
+
+Title proposition 2: Illustrating Facebook, Twitter and YouTube regulation policies against misinformation with a few chosen examples
 
@@
 Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense.
-\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.''  }
+\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.''}
 
@@
 When an account is permanently suspended by Facebook, it disappears from the platform.
-That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the April 2021 report for an example: \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
+That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{April 2021 report} as an example.} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
 
@@
 For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API.
-Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{ (see the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data.\footnote{The exact command can be found : \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_trump_data.sh}{here}.} We can verify on figure \ref{fig1_fb} that the {\it Donald J.
+Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data.\footnote{The exact command can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_trump_data.sh}{here}.} We can verify on figure \ref{fig1_fb} that the {\it Donald J.
 Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.
@@
 
-The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}.
+The Twitter account $@LifeSite$ of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}.
 Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}.
@@
 In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}.
-We collected the activity (tweets, replies, quotes, retweets) on their Twitter account $@LifeSite$ via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}).
+We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}).
 The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.
@@
 
-A third measure that mainstream social media platforms can apply is to prevent users from sharing specific types of content, instead of deleting the content after posting, or users accounts.
-We will show through examples how platforms prevent users from sharing urls coming from specific domain names.
+Another measure that mainstream social media platforms can apply is to prevent users from sharing specific types of content, in this example URLs coming from a specific domain name.
 
@@
 
-In this section, we provide one case study of how Facebook can block a URL as part of its policy enforcement tools.
 The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook'' for coordinated inauthentic behavior\footnote{\href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}, which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
-Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.}
-
-Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior are interlinked, according to the fact-checking organization Snopes which had reported about The BL’s activity to Facebook and other various public articles.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}} It took Facebook five months to complete its investigation of The BL before taking action\footnote{See \href{https://www.businessinsider.com/facebook-bans-beauty-of-life-for-inauthentic-behavior-2019-12}{https://www.businessinsider.com/facebook-bans-beauty-of-life-for-inauthentic-behavior-2019-12}.} and Snopes ended its fact-checking partnership with them in February 2020.\footnote{See \href{https://www.snopes.com/2019/02/01/snopes-fb-partnership-ends/}{https://www.snopes.com/2019/02/01/snopes-fb-partnership-ends/}.}
+Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested, according to the fact-checking organization Snopes which had reported about The BL’s activity to Facebook and other various public articles\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}}.
 
@@
 But such manual verification cannot inform us whether the ban applies indeed to all Facebook users and accounts (as we used only our own personal accounts), nor when it has started.
-To further investigate this policy, we collected data from Buzzsumo.\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.} We used the ``/search/articles'' endpoint of the Buzzsumo API, to collect the engagement metrics $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.\footnote{The command can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}.}
+To further investigate this policy, we collected data from the Buzzsumo API\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.}.
+We used the ``/search/articles'' endpoint to collect the engagement metrics of the $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.\footnote{The command can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}.}
 
 The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban.
-We can note that although the ban was communicated in an article published\footnote{See \href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}.} on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
-The number of articles published per day was around $50$ until December $20$, $2019$.
-This number decreased drastically to reach around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).
-The communication around the ban may have discouraged The Beauty of Life to proceed with their activity.
-Using Buzzsumo data, a global ban over sharing a thebl.com URL link on Facebook was ascertained.
-It started on December $1$, $2019$, and was still enforced in June 2021.
+We can note that although the ban was communicated in an article\footnote{See \href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}.} published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
+
+The communication around the ban appeared to have discouraged The Beauty of Life to proceed with their activity.
+Indeed the number of articles they published daily was around $50$ until December $20$, $2019$, when it decreased drastically to reach around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).
+Using Buzzsumo data, we ascertained that links from thebl.com were not shared on Facebook anymore.
+The ban started on December $1$, $2019$, and appeared to be still enforced in June 2021.
 

### 2021-07-19 article/draft.tex
small rewriting

@@
 Facebook Newsroom.
-\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the CrowdTangle API or on Buzzsumo.
-Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available via the CrowdTangle API and Buzzsumo.
+\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the APIs used to access Facebook data: CrowdTangle or Buzzsumo.
+Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available on CrowdTangle and Buzzsumo.
 If a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.
@@
 
+We found irregularities in the number of Infowars articles collected from Buzzsumo.
+While Infowars usually publishes around 800 articles per month, only 53 articles were collected between June 11 to July 11, 2020\footnote{In Figure \ref{infowars2} the engagement metrics were only shown for days in which at least 5 Infowars articles were collected from Buzzsumo, to ensure reliable results.}.
+A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
+Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
+
 \subsubsection{Twitter}
@@
 But to the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
-Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}).
-Furthermore, $globalresearch.ca$ has multiple failed fact-checks, see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}} When a user searches via the twitter search-box for any URL link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June $14$, $2021$.
+Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}).} When a user searches via the twitter search-box for any URL link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June $14$, $2021$.
+
 To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
@@
 Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
-Hence, the users who tweet articles from the {\it globalresearch.ca} website receive tweet level engagement from their own followers.
+Hence, the users who tweet articles from the {\it globalresearch.ca} website receive tweet level engagement only from their own followers.
+
 Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (b) in figure \ref{fig4bis}).
@@
 To the best of our knowledge, two types of flags can currently be seen on Facebook posts, videos and pictures: information banners that do not refute the message in the post but that give a link to an authoritative source (such as ‘Visit the COVID-19 Information Centre for vaccine resources’) and fact-check flags that provide a ‘judgement’ on the text of the post or the link shared (such as ‘False information Checked by independent fact-checkers.’) (see Figure \ref{fb_flags}).
-The fact-check flags can be of varied nature : False, Partly false, Missing context, False headline, Altered media, Opinion, Satire, Not eligible and even True.
+The fact-check flags can be of varied nature : `False', `Partly false', `Missing context', `False headline', `Altered media', `Opinion', `Satire', `Not eligible' and even `True'.
 
@@
 
-Surprinsingly only 11 posts out of the remaining 17 had a ‘False information’ flag  (see Table \ref{tab_flags_fb}).
+Surprinsingly only 11 posts out of the remaining 17 had a ‘False information’ flag  (Table \ref{tab_flags_fb}, see left panel of Figure \ref{fb_flags} for an example).
 We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples).
-As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user could share a link without the ‘False information’ banner as in the first example of Figure \ref{fb_flags}.
+As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user is thus able to share a False link on Facebook without the ‘False information’ banner if the link is not expanded.
 
-We also observed that most of the posts (13 out of 17, see Table \ref{tab_flags_fb}) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}).
+We also observed that most of the posts sharing this False link (13 out of 17, Table \ref{tab_flags_fb}) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}).
 We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example).
-It should be noted that some posts displayed both the information and the fact-check banners, as in the right panel of Figure \ref{fb_flags}.
+It should be noted that some posts displayed both the information and the fact-check banners, as in the middle panel of Figure \ref{fb_flags}.
 
@@
 Labels are context specific (e.g.
-COVID19 or presidential elections) and  redirect users to a URL link to get more context (see figure \ref{fig8} for an example).
-Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts (see figure \ref{fig_notice} for an example).
-At the account level, notices can indicate whether an account has been temporarily or permanently suspended.
+COVID19 or presidential elections) and  redirect users to a URL link to get more context (for example `Get the facts about COVID-19', see right panel of figure \ref{fig8}).
+Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts (for example `The following media includes potentially sensitive content', see left panel of figure \ref{fig_notice}).
+At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.
 
@@
 To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
-Hence, in order to investigate the presence of labels, we resorted to scrape Twitter data using Minet [5].
+Hence, in order to investigate the presence of labels of all types, we resorted to scrape Twitter data using Minet [5].
 This tool was recently enriched upon our request in order to capture whether a tweet contains a label or not, via the {\it minet twitter scrape} command.
@@
 Among those $657$ tweets only $3$ contained the label ``Get the facts about COVID-19'' (see figure \ref{fig8}).
-This points towards the non-automation of the tweet labelling process and that it might be that only $3$ tweets got labelled after being reported by a user.
+This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by a user.
 
@@
 	%\end{multicols}
-	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}
+	\caption{Examples of YouTube information panels displayed under some videos.}
 	\label{fig9}
@@
 
-To further study the assignment of information panels to videos, we implemented the following exercice.
-We compiled a list of $171$ Youtube videos, checked by independent fact-checkers\footnote{Is it science Feedback ?
+To further study the assignment of information panels to videos, we compiled a list of $171$ Youtube videos, checked by independent fact-checkers\footnote{Is it science Feedback ?
 if so add.} and marked as containing false or inaccurate information.
-We collected the information panels, when present, in each video by scrapping the content of the web and connecting to a US server.
-Four types of information panels were found in the list of visited videos as shown in figure\ref{fig9}:  information about COVID19, Vaccines, Climate change and US elections.
+We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page.
+Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about COVID19, Vaccines, Climate change and US elections.
 
@@
 In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
-Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.
+Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video.
 
@@
 
-For climate change we only examined $18$ misleading videos and we found that $28\%$ did not display an information panel.
-Lastly , for the general health category, we included the videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion,  and viruses; no information panels were displayed for that set of Youtube videos.
+For climate change we found that most of the videos (13 out of 18) did not display an information panel.
+Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion, and viruses.
 Therefore, it is likely that Youtube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID19, flat earth and vaccine.

### 2021-07-19 article/draft.tex
minor changes

--- 2021-07-15 article/draft.tex
@@
 
+Title proposition 3: Misinformation Policies of Mainstream Social Media Platforms: third-party verification methods and illustration
+
 \section{Introduction}
@@
 Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense.
-\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.''}
+\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.
+{\color{pink} Add more examples to show that this problem is highlighted by different institutions with different/neutral political color..
+}}
 
-Section $230$ in the United States Communications Decency Act\footnote{Similar regulation exists in the European Union, see articles $12$ and $15$ of the E-commerce Directive (2000).
-} provides immunity for website platforms against the content created by users.
-Nevertheless, there is growing pressure for Mainstream Social Media Platforms (hereafter MSMP), such as Facebook, Twitter or Youtube, to moderate the available content.
-In particular, platforms seem to take explicit actions when content is in violation of local laws in different jurisdictions, e.g.
+Section $230$ in the United States Communications Decency Act provides immunity for website platforms against the content created by users.
+Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for Mainstream Social Media Platforms (hereafter MSMP), such as Facebook, Twitter or Youtube, to moderate the available content.
+In particular, platforms take explicit actions when content is in violation of local laws in different jurisdictions, e.g.
 laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws.
@@
 Furthermore, MSMP are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated.
-Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam.\footnote{For an exhaustive overview of the community standards of Facebook, see: \href{https://www.facebook.com/communitystandards/}{facebook.com/communitystandards/}.
+Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam.\footnote{For an exhaustive overview of the community standards of Facebook, see: \href{https://www.facebook.com/communitystandards/}{facebook.com/communitystandards/}.
 For the Twitter  Rules see: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}, and for Youtube community guidelines see: \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}.} While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries.
+
+\smallskip
+
+During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates concerning COVID19 related misinformation policies: \href{https://support.google.com/youtube/answer/9891785}{https://support.google.com/youtube/answer/9891785}, \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}.} Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged\footnote{{\color{pink} put here the list of Facebook and Twitter terms about covid.}}, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
+As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms.
+Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
+In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}.
+The 2019 report of the Facebook Data Transparency Advisory Group\footnote{To read the full report, see: \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}.} (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
+Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
+It is explained via a blog post on the facebook Newsroom.\footnote{See: \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{https://about.fb.com/news/2018/05/hard-questions-false-news/}.}.
+Similarly, Twitter communicates about actions related to misinformation via their Twitter Safety Blog/account\footnote{See \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{https://blog.twitter.com/en\_us/authors.TwitterSafety}.}.
+In a post on Youtube Official Blog\footnote{See \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}.}, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation.
 
@@
 (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
-The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
+In particular, the intricacies of constructing a legal framework concerning misinformation and disinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
 Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
@@
 This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
-For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.
-\footnote{For an overview of Facebook's third-party fact checking program see: \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}.} Facebook use a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
+For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.\footnote{For an overview of Facebook's third-party fact checking program see: \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}.} Facebook use a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
 The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1.
@@
 Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed.
-Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation.\footnote{See Twitter Birdwatch: \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}.}
+Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}).
+As for Youtube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels.
+\footnote{See \href{https://support.google.com/youtube/answer/9229632}{https://support.google.com/youtube/answer/9229632}.}
 
@@
 
-{\color{pink} Note, put here something along the following lines: cite misinformation review article about support for fact-checking + hard to correct beliefs once it goes viral.
+%{\color{pink} Note, put here something along the following lines: cite misinformation review article about support for fact-checking + hard to correct beliefs once it goes viral.
 cite Pennycook / Rand?
-+ where to put or cite \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{this} ?
 }
@@
 Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.}
+%In particular, the peculiar task of determining the truthfulness of content over controversial topics or ongoing political events 
+%\smallskip
 
-%In particular, the peculiar task of determining the truthfulness of content over controversial topics or ongoing political events 
-\smallskip
-
-During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates concerning COVID19 related misinformation policies: \href{https://support.google.com/youtube/answer/9891785}{https://support.google.com/youtube/answer/9891785}, \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}.} Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged\footnote{{\color{pink} put here the list of Facebook and Twitter terms about covid.}}, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
-As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms.
-Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
-In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}.
-The 2019 report of the Facebook Data Transparency Advisory Group\footnote{To read the full report, see: \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}.} (DTAG) states clearly that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
-Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
-It is explained via a blog post on the facebook Newsroom.\footnote{See: \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{https://about.fb.com/news/2018/05/hard-questions-false-news/}.}.
-Similarly, Twitter communicates about actions related to misinformation via their Twitter Safety Blog/account\footnote{See \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{https://blog.twitter.com/en\_us/authors.TwitterSafety}.}.
-In a post on Youtube Official Blog\footnote{See \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}.}, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content reduces borderline content and harmful misinformation.
-
-{\color{pink} Note, put here something along the following line: make point here about the fact that in the transparency centers we find things for the violations in the platforms rules but not misinformation....
+%{\color{pink} Note, put here something along the following line: make point here about the fact that in the transparency centers we find things for the violations in the platforms rules but not misinformation....
 needed so that the academic community can study the reach and impact of this phenomena and provide guidelines for adequate actions...
@@
 
-In the present article, we will explain how to verify with data mining MSMP's actions regarding content with low credibility or false information, through a series of examples for different actions and platforms.
+Nevertheless, misinformation specific interventions by MSMP are hard to monitor, study or verify by third parties (e.g.
+academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports.
+This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community.
+Hence, in the present article we explain how to verify with data mining MSMP's current actions regarding content with low credibility or false information.
+We do so by providing a series of examples for different interventions and platforms.
 For the purpose of clarity, we only focus on three platforms: Facebook, Twitter and Youtube.
@@
 More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited MSMP, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
-We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.
-We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
+We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.\footnote{For a detailed list of interventions check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
+} We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
 We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article.
+We compile in Appendix \ref{links} in table \ref{summary}, URL links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and Youtube.
 Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
@@
 When an account is permanently suspended by Facebook, it disappears from the platform.
-That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{April 2021 report} as an example.} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
+That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged to.\footnote{See the \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{April 2021 report} as an example.} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
 
@@
 For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API.
-Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used the minet command line tool \cite{minet} to collect data.\footnote{The exact command can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_trump_data.sh}{here}.} We can verify on figure \ref{fig1_fb} that the {\it Donald J.
+Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used Minet command line tool \cite{minet} to collect the data.\footnote{The exact command can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_trump_data.sh}{here}.} We can verify on figure \ref{fig1_fb} that the {\it Donald J.
 Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.
@@
 Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}).
-Furthermore, $globalresearch.ca$ has multiple failed fact-checks, see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}} When a user searches via the twitter search-box for any URL link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June $14$, $2021$.
+Furthermore, $globalresearch.ca$ has multiple failed fact-checks, see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and \href{https://feedback.news/media/AEKA}{https://feedback.news/media/AEKA}.} When a user searches via the twitter search-box for any URL link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June $14$, $2021$.
 To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
@@
 Among those 32 Tweets, only 5 tweets had the interstitial ``potentially sensitive content''.
-Again this points towards the non-automation of the interstitials placement.
+Again this points towards the non-automation of the placement of interstitials.\footnote{Notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations.
+In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}.
+Hence the numbers given are an upper bound of the number of interstitials indicating  possibly sensitive content.}
 
@@
 
-Finally, the Twitter Safety announced in a Tweet\footnote{See Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}} on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".
+Finally, Twitter Safety account announced in a Tweet\footnote{See Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}} on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".
 %we don't know what it means the articl xxx which was retracted by the journal and fack-check still appears in xx tweets with no label
@@
 \hline
-Category       & \begin{tabular}[c]{@{}c@{}}Number of Youtube \\ videos with \\ an information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of Youtube \\ videos without \\ an information panel\end{tabular}    \\ \hline
-\begin{tabular}[c]{@{}c@{}} General \\ Health \end{tabular} & \begin{tabular}[c]{@{}c@{}} 0  \\ (0\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 11 \\ (100\%) \end{tabular}         \\ \hline
+Category       & \begin{tabular}[c]{@{}c@{}}Number of Youtube videos {\bf with} an \\ information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of Youtube videos {\bf without} an \\ information panel\end{tabular}    \\ \hline
+\begin{tabular}[c]{@{}c@{}} General Health \end{tabular} & \begin{tabular}[c]{@{}c@{}} 0  \\ (0\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 11 \\ (100\%) \end{tabular}         \\ \hline
 Vaccine        & \begin{tabular}[c]{@{}c@{}} 21     \\ (75\%) \end{tabular}   & \begin{tabular}[c]{@{}c@{}}  7 \\ (25\%)  \end{tabular}     \\ \hline
 COVID19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
-\begin{tabular}[c]{@{}c@{}}  Climate \\ change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
+\begin{tabular}[c]{@{}c@{}}  Climate change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
 \end{tabular}
@@
 
+\subsection{Quick access to community guidelines and policies} \label{links}
+
+\begin{landscape}
+
 \begin{table*}[h]
@@
 
+\end{landscape}
 %https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works

### 2021-07-20 article/draft.tex
few changes

@@
 \usepackage{titlesec}
+\usepackage[font=footnotesize,labelfont=bf]{caption}
 
@@
 
+\tableofcontents
+
 \section{Introduction}
 
-A number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g.
+Section $230$ in the United States Communications Decency Act provides immunity for website platforms against the content created by users.
+Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for Mainstream Social Media Platforms, such as Facebook, Twitter or Youtube, to moderate the available content.
+In particular, platforms take explicit actions when content is in violation of local laws in different jurisdictions, such as laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws.
+For example, Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}.
+We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} %Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}
+
+\smallskip
+
+Furthermore, mainstream platforms are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated.
+Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see table \ref{summary} in Appendix \ref{links}).
+While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation.
+The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g.
 Grinberg et al.
@@
 
-Section $230$ in the United States Communications Decency Act provides immunity for website platforms against the content created by users.
-Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for Mainstream Social Media Platforms (hereafter MSMP), such as Facebook, Twitter or Youtube, to moderate the available content.
-In particular, platforms take explicit actions when content is in violation of local laws in different jurisdictions, e.g.
-laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws.
-Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}.
-We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}
+\smallskip
+
+In this article, we focus on mainstream platforms' policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (for an overview of the concept see Lazer et al.
+(2018)~\cite{lazer}).
+The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
+The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
+Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
+In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
+This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
+For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.
+Facebook use a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
+The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1.
+Twitter shouldn’t determine the truthfulness of Tweets 2.
+Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed.
+Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}).
+As for Youtube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see table \ref{summary} in Appendix \ref{links}).
 
@@
 
-Furthermore, MSMP are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated.
-Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam.\footnote{For an exhaustive overview of the community standards of Facebook, see: \href{https://www.facebook.com/communitystandards/}{facebook.com/communitystandards/}.
-For the Twitter  Rules see: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}, and for Youtube community guidelines see: \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}.} While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries.
-
-\smallskip
-
-During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates concerning COVID19 related misinformation policies: \href{https://support.google.com/youtube/answer/9891785}{https://support.google.com/youtube/answer/9891785}, \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}.} Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged\footnote{{\color{pink} put here the list of Facebook and Twitter terms about covid.}}, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
+During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}).
+Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged\footnote{{\color{pink} put here the list of Facebook and Twitter terms about covid.}}, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
 As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms.
-Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
+Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
 In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}.
@@
 In a post on Youtube Official Blog\footnote{See \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}.}, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation.
-
-\smallskip
-
-In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al.
-(2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
-In particular, the intricacies of constructing a legal framework concerning misinformation and disinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
-Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
-In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
-This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
-For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.\footnote{For an overview of Facebook's third-party fact checking program see: \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}.} Facebook use a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
-The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1.
-Twitter shouldn’t determine the truthfulness of Tweets 2.
-Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed.
-Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}).
-As for Youtube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels.
-\footnote{See \href{https://support.google.com/youtube/answer/9229632}{https://support.google.com/youtube/answer/9229632}.}
 
@@
 
-Nevertheless, misinformation specific interventions by MSMP are hard to monitor, study or verify by third parties (e.g.
+Nevertheless, misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g.
 academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports.
 This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community.
-Hence, in the present article we explain how to verify with data mining MSMP's current actions regarding content with low credibility or false information.
+Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information.
 We do so by providing a series of examples for different interventions and platforms.
-For the purpose of clarity, we only focus on three platforms: Facebook, Twitter and Youtube.
+We only focus on three platforms: Facebook, Twitter and Youtube.
 Both Facebook and Youtube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}.
-More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited MSMP, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
+More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited mainstream platforms, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
 We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.\footnote{For a detailed list of interventions check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
@@
 
-\section{Policies}
-
-\subsection{Temporary suspension and Permanent suspension}
+\section{Temporary \& permanent suspension}
 
@@
 
-\subsubsection{Facebook}
+\subsection{Facebook}
 
-\begin{figure}
+When an account is permanently suspended by Facebook, it disappears from the platform.
+That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged to.\footnote{See the \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{April 2021 report} as an example.} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
+
+\begin{figure}[h]
 	\centering
@@
 
-When an account is permanently suspended by Facebook, it disappears from the platform.
-That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged to.\footnote{See the \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{April 2021 report} as an example.} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
-
 Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed.
@@
 
-\subsubsection{Twitter}
+\subsection{Twitter}
 
-\begin{figure}
+%paragraph strike system + say following example is a manual decision. 
+Twitter has implemented a strike system as part of their Civi Integrity Policy\footnote{See \href{https://help.twitter.com/en/rules-and-policies/election-integrity-policy}{help.twitter.com/en/rules-and-policies/election-integrity-policy}} and their COVID19 misleading information policy.\footnote{See \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}{blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}} Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform.
+The 12-hour account lock is hard to observe in the data, especially for users who do not have an over the clock tweeting activity.
+In this section, we provide one example of a temporary suspension\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.
+
+The Twitter account $@LifeSite$ of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}.
+Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}.
+}.
+In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}.
+We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}).
+The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.
+
+\begin{figure}[h]
 \centering
@@
 
-%paragraph strike system + say following example is a manual decision. 
-Twitter has implemented a strike system as part of their Civi Integrity Policy\footnote{See \href{https://help.twitter.com/en/rules-and-policies/election-integrity-policy}{help.twitter.com/en/rules-and-policies/election-integrity-policy}} and their COVID19 misleading information policy.\footnote{See \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}{blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}} Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform.
-The 12-hour account lock is hard to observe in the data, especially for users who do not have an over the clock tweeting activity.
-In this section, we provide one example of a temporary suspension\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.
-
-The Twitter account $@LifeSite$ of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}.
-Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}.
-}.
-In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}.
-We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}).
-The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.
-
-\smallskip
-
 To further assess the impact of this double temporary suspension, we collect via Minet Command Line Tool\cite{minet}, all the tweets that have shared during the same period a url link containing lifesitenews.com.
@@
 
-\subsubsection{Youtube}
+\subsection{Youtube}
 
@@
 
-\smallskip
-
-\begin{figure}
+\begin{figure}[h]
 	\centering
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.24]{./img/oann/fig1_oann.png}
+		\includegraphics[scale=0.21]{./img/oann/fig3_oann.png}
 	%\end{multicols}
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
+		\includegraphics[scale=0.31]{./img/tony/fig3_tony.png}
+	%\end{multicols}
+
+	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
+Panel (b): Tony Heller's tweet after getting suspended from Youtube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
+	\label{fig2_oann}
+\end{figure}
+
+%\smallskip
+
+First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}.
+This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021.
+For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
+
+\begin{figure}[h]
+	\centering
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.27]{./img/oann/fig1_oann.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.26]{./img/oann/fig2_oann.png} 
 	%\end{multicols}
@@
 
-First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}.
-This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021.
-For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
-
-\smallskip
-
 In addition, as shown in figure \ref{fig1_oann} when comparing the month before the suspension from 2020/10/24 to 2020/11/24 and one month after from 2020/12/01 to 2021/01/01 it was found that the view count decreased by -73\% and the videos uploaded by -55\%.
@@
 
-\begin{figure}
+%\smallskip
+\begin{figure}[h]
 	\centering
 		%\begin{multicols}{1}
-		\includegraphics[scale=0.21]{./img/oann/fig3_oann.png}
+			\includegraphics[scale=0.35]{./img/tony/fig1_tony.png}
 		%\end{multicols}
 		%\begin{multicols}{1}
-		\includegraphics[scale=0.21]{./img/tony/fig3_tony.png}
+			\includegraphics[scale=0.34]{./img/tony/fig2_tony.png}
 		%\end{multicols}
-
-	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
-Panel (b): Tony Heller's tweet after getting suspended from Youtube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
-	\label{fig2_oann}
+	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
+Panel (b): accumulated view counts for videos uploaded by the same Youtube channel.
+The date corresponds to the videos’  publishing date.
+}
+	\label{fig1_tony}
 \end{figure}
-
-\smallskip
 
@@
 
-\begin{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Flags, Notices and labels}
+
+\subsection{Facebook}
+
+To the best of our knowledge, two types of flags can currently be seen on Facebook posts, videos and pictures: $(i)$ information banners that do not refute the message in the post but that give a link to an authoritative source, such as ``Visit the COVID-19 Information Centre for vaccine resources'' and $(ii)$ fact-check flags that provide a ``judgement'' on the text of the post or the link, shared, such as ``False information Checked by independent fact-checkers'' (see Figure \ref{fb_flags}).
+The fact-check flags can be of varied nature : `False', `Partly false', `Missing context', `False headline', `Altered media', `Opinion', `Satire', `Not eligible' and even `True'.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
+\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
+\includegraphics[scale=0.49]{./img/fb_flags/fb_flag_3.png}
+\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners.
+Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/3835629366473816}).}
+\label{fb_flags}
+\end{figure}
+
+No information regarding the flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data.
+The only way to verify Facebook’s flag policy is thus to scrap Facebook.
+For this paper, we added a new feature in minet to scrape Facebook posts and automatically verify for the presence of the flags.
+
+We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the {\it search} endpoint in minet\footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}).}.
+Twenty Facebook posts were collected this way, and the newly developed scraper was used to verify whether they were flagged with an information banner, a fact-check flag, both or none.
+Three posts were unavailable, and thus could not be categorized by the scraper.
+As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.
+
+\smallskip
+
+Surprisingly only $11$ posts out of the remaining $17$ had a ‘False information’ flag  (Table \ref{tab_flags_fb}, see left panel of Figure \ref{fb_flags} for an example).
+We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples).
+As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user is thus able to share a False link on Facebook without the ‘False information’ banner if the link is not expanded.
+
+\begin{table}[h]
+\begin{tabular}{|c|c|c|c|}
+\hline
+\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
+with no flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check and an \\  information flags\end{tabular} \\ \hline
+0            & 7                        & 4                      & 7                                                                                     \\ \hline
+\end{tabular}
+\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
+\label{tab_flags_fb}
+\end{table}
+
+We also observed that most of the posts sharing this False link (13 out of 17, Table \ref{tab_flags_fb}) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}).
+We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example).
+It should be noted that some posts displayed both the information and the fact-check banners, as in the middle panel of Figure \ref{fb_flags}.
+
+\subsection{Twitter}
+
+Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial.
+Labels are context specific (e.g.
+COVID19 or presidential elections) and  redirect users to a URL to get more context, for example ``Get the facts about COVID-19'' (see right panel of figure \ref{fig8}).
+Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example ``The following media includes potentially sensitive content'' (see left panel of figure \ref{fig_notice}).
+At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.
+
+%\smallskip
+
+\begin{figure}[h]
 \centering
 	%\begin{multicols}{1}
-			\includegraphics[scale=0.25]{./img/tony/fig1_tony.png}
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
    	 %\end{multicols}
 	%\begin{multicols}{1} 
-			\includegraphics[scale=0.25]{./img/tony/fig2_tony.png}
+		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
 	%\end{multicols}
-	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
-Panel (b): accumulated view counts for videos uploaded by the same Youtube channel.
-The date corresponds to the videos’  publishing date.
-}
-	\label{fig1_tony}
+	\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021.
+Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label.
+Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
+	\label{fig8}
 \end{figure}
 
-\subsection{Blocking links}
+To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
+Hence, in order to investigate the presence of labels of all types, we resorted to scrape Twitter data using Minet [5].
+This tool was recently enriched upon our request in order to capture whether a tweet contains a label or not, via the {\it minet twitter scrape} command.
 
-Another measure that mainstream social media platforms can apply is to prevent users from sharing specific types of content, in this example URLs coming from a specific domain name.
+\smallskip
+
+In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false.
+To that end, we gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
+As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$.
+This data collection resulted in $323$ $938$ tweets, excluding retweets.
+Only $28$ tweets contained the label { ``Get the facts about COVID-19''}, $5$ tweets contained the label { ``Learn about US 2020 election security efforts''} and only $1$ had the following label {``This claim about election fraud is disputed''}.
+Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same URL link, among the set of collected tweets.
+More specifically, exactly $657$ tweets had shared a URL link redirecting to a video on Bitchute, entitled ``Important information on coronavirus 5G Kung Flu''.
+Among those $657$ tweets only $3$ contained the label ``Get the facts about COVID-19'' (see figure \ref{fig8}).
+This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by a user.
+
+\begin{figure}[h]
+	\centering
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
+	%\end{multicols}
+	\caption{Panel (a): Tweet containing a URL link hidden behind an interstitial.
+Panel (b): when clicking on $view$, to view the content hidden behind the interstitial.
+Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}.
+Screenshots taken on July 1, 2021.
+}
+	\label{fig_notice}
+\end{figure}
+
+We further examine the placement of interstitials that indicate a possibly sensitive content.
+We find that only $2.97\%$ out of $323$ $938$ tweets containing a URL marked as False, have an interstitial ``potentially sensitive content''.
+{\color{pink}In particular, many tweets speak about COVID19 and do not contain a label to provide users with more context from authoritative sources.
+Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''.} We find 32 other Tweets, among our set of collected tweets, who share the exact same URL link as in the previous example.
+Among those 32 Tweets, only 5 tweets had the interstitial ``potentially sensitive content''.
+Again this points towards the non-automation of the placement of interstitials.\footnote{Notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations.
+In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}.
+Hence the numbers given are an upper bound of the number of interstitials indicating  possibly sensitive content.}
+{\color{pink} can we have both at the same time (see example facebook)  + dire pour l'exemple get the facts about covid. }
+\smallskip
+
+Finally, Twitter Safety account announced in a Tweet\footnote{See Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}} on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".
+%we don't know what it means the article xxx which was retracted by the journal and fack-check still appears in xx tweets with no label
+
+\subsection{Youtube}
+
+Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} Information panels provide ressources concerning a potentially controversial topic from independent third party partners or authoritative ressources.
+Youtube states that these panels exist regardless of the point of view expressed in a given video.
+In addition, these panels are not yet available in all languages and countries.
+%(“Information panel giving topical context”)
+
+To further study the assignment of information panels to videos, we compiled a list of $171$ Youtube videos, checked by independent fact-checkers\footnote{Is it science Feedback ?
+if so add.} and marked as containing false or inaccurate information.
+We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page.
+Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about COVID19, Vaccines, Climate change and US elections.
+
+\begin{figure}[h]
+	\centering
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/youtube_panels/yt_2.png} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/youtube_panels/yt_3.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/youtube_panels/yt_4.png} 
+	%\end{multicols}
+	\caption{Examples of YouTube information panels displayed under some videos.}
+	\label{fig9}
+\end{figure}
+
+We classified the list of Youtube videos by topic based on its content as shown in table \ref{tab2}.
+We recorded the number of videos containing an information panel within each category.
+For COVID19 and vaccine related videos more than half of the videos contained an information panel.
+Nevertheless, we noticed that duplicates of the same Youtube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
+In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
+Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video.
+
+\smallskip
+
+For climate change we found that most of the videos (13 out of 18) did not display an information panel.
+Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion, and viruses.
+Therefore, it is likely that Youtube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID19, flat earth and vaccine.
+%drop last colum
+%add % in a second line
+\begin{table}[] 
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Category       & \begin{tabular}[c]{@{}c@{}}Number of Youtube videos {\bf with} an \\ information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of Youtube videos {\bf without} an \\ information panel\end{tabular}    \\ \hline
+\begin{tabular}[c]{@{}c@{}} General Health \end{tabular} & \begin{tabular}[c]{@{}c@{}} 0  \\ (0\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 11 \\ (100\%) \end{tabular}         \\ \hline
+Vaccine        & \begin{tabular}[c]{@{}c@{}} 21     \\ (75\%) \end{tabular}   & \begin{tabular}[c]{@{}c@{}}  7 \\ (25\%)  \end{tabular}     \\ \hline
+COVID19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
+\begin{tabular}[c]{@{}c@{}}  Climate change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
+\end{tabular}
+\caption{}
+\label{tab2}
+\end{table}
+
+%\subsection{Blocking links}
+
+%Another measure that mainstream social media platforms can apply is to prevent users from sharing specific types of content, in this example URLs coming from a specific domain name.
+
+%\subsubsection{Twitter}
+
+%\href{https://help.twitter.com/en/safety-and-security/phishing-spam-and-malware-links}{link}
+
+\section{Reducing the visibility}
+
+Mainstream Social Media platforms can reduce the visibility of the content created or shared by specific users, whenever they violate the platforms' rules.
+The implementation of this policy varies across platforms and is not easy to verify ex-post.
+In what follows we provide means to verify this policy on Twitter and Facebook.
+
+\subsection{Facebook}
+
+One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through their ranking system.
+Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed.
+Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure.\footnote{Lyons, T.
+(2018, May 22).
+The three-part recipe for cleaning up your news feed.
+Facebook Newsroom.
+\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the APIs used to access Facebook data: CrowdTangle or Buzzsumo.
+Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available on CrowdTangle and Buzzsumo.
+If a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.
+
+%phrase pas accès au reach, mais seulement les engagement metrics
+% Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.},
+%CrowdTangle and Buzzsumo provide access to the interaction metrics on content (engagement), but not to the number of views (or reach), therefore we can only verify the {\it reduce} measure indirectly through a decrease in engagement.
+If Facebook was reducing the reach of a content via a lower ranking, we would expect the content to be less likely to receive likes, comments and shares, relative to a post with a higher ranking.
+
+\smallskip
+
+To illustrate, we investigate the case of the website $Infowars$.
+This website appears in the Misinformation Directory of FactCheck.org, among other websites who have posted deceptive content\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}.
+Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.}
+
+\begin{figure}[h]
+	\centering
+
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
+	%\end{multicols}
+
+	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API.
+The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars.
+(Top panel) Number of daily posts.
+(Bottom panel) Engagement metrics: average number of reactions, shares and comments per post.
+}
+	\label{infowars1}
+\end{figure}
+
+On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/} and \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}.
+The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel).
+Thus the measure announced by Facebook doesn't seem to have prevented users from sharing an $Infowars$ link.
+Nevertheless, a clear drop in engagement was observed on May 2, 2019 (see figure \ref{infowars1} bottom panel).
+The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May 2, 2019.
+This suggests the measure taken by Facebook in May $2019$, is not a ban per se, but rather a $reduce$ measure.
+This is because users could still post $Infowars$ links, but these posts generated less engagement.
+It should be noted that the engagement metrics increased again by the end of $2019$ / beginning of $2020$, suggesting that the $reduce$ measure may have been lifted a few months after its implementation.
+
+\begin{figure}[h]
+	\centering
+
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
+	%\end{multicols}
+
+	\caption{Facebook engagement metrics (average number of reactions, shares and comments per article) for the Infowars articles published in $2019-2020$ and gathered from the Buzzsumo API.
+The red line marks the date of May $2$, $2019$, when Facebook has announced the ban regarding Infowars.}
+	\label{infowars2}
+\end{figure}
+
+As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset.
+We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.
+\footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
+An increase in engagement was also observed in $2020$.
+It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.
+
+We found irregularities in the number of Infowars articles collected from Buzzsumo.
+While Infowars usually publishes around 800 articles per month, only 53 articles were collected between June 11 to July 11, 2020\footnote{In Figure \ref{infowars2} the engagement metrics were only shown for days in which at least 5 Infowars articles were collected from Buzzsumo, to ensure reliable results.}.
+A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
+Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
 
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
 
-\subsubsection{Twitter}
+\subsection{Twitter}
 
-\href{https://help.twitter.com/en/safety-and-security/phishing-spam-and-malware-links}{link}
-\subsection{Reducing the visibility}
+Twitter can take action against a tweet which violates the Twitter rules\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.}, by limiting its visibility on users' timelines and in search results.
+To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
 
-Mainstream Social Media platforms can reduce the visibility of the content created or shared by specific users, whenever they violate the platforms' rules.
-The implementation of this policy varies across platforms and is not easy to verify ex-post.
-In what follows we provide means to verify this policy on Twitter and Facebook.
+%\smallskip
 
-\subsubsection{Facebook}
-
-\begin{figure}
-	\centering
-
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
-	%\end{multicols}
-
-	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API.
-The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars.
-(Top panel) Number of daily posts.
-(Bottom panel) Engagement metrics: average number of reactions, shares and comments per post.
+%To illustrate we provide two examples linked to the Twitter accounts of the websites $globalresearch.ca$ and $off$-$guardian.org$.
+Both websites have several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and for $off-guardian.org$ see \href{https://mediabiasfactcheck.com/offguardian/}{https://mediabiasfactcheck.com/offguardian/}.
 }
-	\label{infowars1}
-\end{figure}
-
-One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through their ranking system.
-Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed.
-Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure.\footnote{Lyons, T.
-(2018, May 22).
-The three-part recipe for cleaning up your news feed.
-Facebook Newsroom.
-\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the CrowdTangle API or on Buzzsumo.
-Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available via the CrowdTangle API and Buzzsumo.
-If a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.
-
-%phrase pas accès au reach, mais seulement les engagement metrics
-% Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.},
-%CrowdTangle and Buzzsumo provide access to the interaction metrics on content (engagement), but not to the number of views (or reach), therefore we can only verify the {\it reduce} measure indirectly through a decrease in engagement.
-If Facebook was reducing the reach of a content via a lower ranking, we would expect the content to be less likely to receive likes, comments and shares, relative to a post with a higher ranking.
-
-\smallskip
-
-To illustrate, we investigate the case of the website $Infowars$.
-This website appears in the Misinformation Directory of FactCheck.org, among other websites who have posted deceptive content\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}.
-Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.}
-
-\begin{figure}
-	\centering
-
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
-	%\end{multicols}
-
-	\caption{Facebook engagement metrics (average number of reactions, shares and comments per article) for the Infowars articles published in $2019-2020$ and gathered from the Buzzsumo API.
-The red line marks the date of May $2$, $2019$, when Facebook has announced the ban regarding Infowars.}
-	\label{infowars2}
-\end{figure}
-
-On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/} and \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}.
-The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel).
-Thus the measure announced by Facebook doesn't seem to have prevented users from sharing an $Infowars$ link.
-Nevertheless, a clear drop in engagement was observed on May 2, 2019 (see figure \ref{infowars1} bottom panel).
-The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May 2, 2019.
-This suggests the measure taken by Facebook in May $2019$, is not a ban per se, but rather a $reduce$ measure.
-This is because users could still post $Infowars$ links, but these posts generated less engagement.
-It should be noted that the engagement metrics increased again by the end of $2019$ / beginning of $2020$, suggesting that the $reduce$ measure may have been lifted a few months after its implementation.
-
-As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset.
-We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.
-\footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
-An increase in engagement was also observed in $2020$.
-It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.
-
-\subsubsection{Twitter}
-
-\begin{figure}
+\begin{figure}[h]
 	\centering
 		%\begin{multicols}{1}	
-			\includegraphics[scale=0.35]{./img/globalresearch_2021-06-14.png}
+			\includegraphics[scale=0.32]{./img/globalresearch/tweet.png} 
 		%\end{multicols}
@@
 		%\end{multicols}
-		\caption{Screenshots taken on June 14, 2021.
-Top panel: screenshot that shows the account of $globalresearch.ca$ suspended on Twitter.
-Bottom panel: screenshot that shows that no results can be found when searching for $globalresearch.ca$.
-}
+		\caption{Screenshots taken on June 14, 2021. Top panel: ? . Bottom panel: screenshot that shows that no results can be found when searching for $globalresearch.ca$.    }
 		\label{fig3}
 \end{figure}
-
-Twitter can take action against a tweet which violates the Twitter rules\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.}, by limiting its visibility on users' timelines and in search results.
-To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
-
-\smallskip
-
-%To illustrate we provide two examples linked to the Twitter accounts of the websites $globalresearch.ca$ and $off$-$guardian.org$.
-Both websites have several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and for $off-guardian.org$ see \href{https://mediabiasfactcheck.com/offguardian/}{https://mediabiasfactcheck.com/offguardian/}.
-}
 
@@
 
-\begin{figure}
+The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; which was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021.
+But to the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
+Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}).} When a user searches via the twitter search-box for any URL link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June $14$, $2021$.
+
+\begin{figure}[h]
 \centering
@@
 
-\begin{figure}
+To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the URL link {\it globalresearch.ca} throughout May $2021$ and the first week of June $2021$.
+Hence, the visibility of tweets containing this URL link has been reduced because users can no longer access tweets containing the URL link {\it globalresearch.ca} via the search box.
+Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(a)$ of figure \ref{fig4bis}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
+Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
+Hence, the users who tweet articles from the {\it globalresearch.ca} website receive tweet level engagement only from their own followers.
+
+Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (b) in figure \ref{fig4bis}).
+
+\begin{figure}[h]
 \centering	
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
+		%\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
 	%\end{multicols}
@@
 
-\subsubsection{Youtube}
+\subsection{Youtube}
 
 {\color{pink} What about something about recommendations ? authoritative content  }
-
-\subsection{Flags, Notices and labels}
-
-\subsubsection{Facebook}
-
-To the best of our knowledge, two types of flags can currently be seen on Facebook posts, videos and pictures: information banners that do not refute the message in the post but that give a link to an authoritative source (such as ‘Visit the COVID-19 Information Centre for vaccine resources’) and fact-check flags that provide a ‘judgement’ on the text of the post or the link shared (such as ‘False information Checked by independent fact-checkers.’) (see Figure \ref{fb_flags}).
-The fact-check flags can be of varied nature : False, Partly false, Missing context, False headline, Altered media, Opinion, Satire, Not eligible and even True.
-
-No information regarding the flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data.
-The only way to verify Facebook’s flag policy is thus to scrap Facebook.
-For this paper, we added a new feature in minet to scrape Facebook posts and automatically verify for the presence of the flags.
-
-We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the `search` endpoint in minet\footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}).}.
-20 Facebook posts were collected this way, and the newly developed scraper was used to verify whether they were flagged with an information banner, a fact-check flag, both or none.
-3 posts were unavailable, and thus could not be categorized by the scraper.
-As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
-\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
-\includegraphics[scale=0.45]{./img/fb_flags/fb_flag_3.png}
-\caption{Examples of the Facebook posts having shared a link fact-checked False by one of Facebook’s partners (Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{https://www.facebook.com/691911990845585/posts/3835629366473816}).}
-\label{fb_flags}
-\end{figure}
-
-Surprinsingly only 11 posts out of the remaining 17 had a ‘False information’ flag  (see Table \ref{tab_flags_fb}).
-We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples).
-As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user could share a link without the ‘False information’ banner as in the first example of Figure \ref{fb_flags}.
-
-We also observed that most of the posts (13 out of 17, see Table \ref{tab_flags_fb}) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}).
-We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example).
-It should be noted that some posts displayed both the information and the fact-check banners, as in the right panel of Figure \ref{fb_flags}.
-
-\begin{table}[]
-\begin{tabular}{|c|c|c|c|}
-\hline
-\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
-with no flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check \\ and an information flags\end{tabular} \\ \hline
-0            & 7                        & 4                      & 7                                                                                     \\ \hline
-\end{tabular}
-\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
-\label{tab_flags_fb}
-\end{table}
-
-\subsubsection{Twitter}
-
-\begin{figure}
-\centering
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
-   	 %\end{multicols}
-	%\begin{multicols}{1} 
-		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30.png}
-	%\end{multicols}
-	\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021.
-Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label.
-Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
-	\label{fig8}
-\end{figure}
-
-Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial.
-Labels are context specific (e.g.
-COVID19 or presidential elections) and  redirect users to a URL link to get more context (see figure \ref{fig8} for an example).
-Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts (see figure \ref{fig_notice} for an example).
-At the account level, notices can indicate whether an account has been temporarily or permanently suspended.
-
-\smallskip
-
-To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
-Hence, in order to investigate the presence of labels, we resorted to scrape Twitter data using Minet [5].
-This tool was recently enriched upon our request in order to capture whether a tweet contains a label or not, via the {\it minet twitter scrape} command.
-
-\smallskip
-
-In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false.
-To that end, we gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
-As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$.
-This data collection resulted in $323$ $938$ tweets, excluding retweets.
-Only $28$ tweets contained the label { ``Get the facts about COVID-19''}, $5$ tweets contained the label { ``Learn about US 2020 election security efforts''} and only $1$ had the following label {``This claim about election fraud is disputed''}.
-Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same URL link, among the set of collected tweets.
-More specifically, exactly $657$ tweets had shared a URL link redirecting to a video on Bitchute, entitled ``Important information on coronavirus 5G Kung Flu''.
-Among those $657$ tweets only $3$ contained the label ``Get the facts about COVID-19'' (see figure \ref{fig8}).
-This points towards the non-automation of the tweet labelling process and that it might be that only $3$ tweets got labelled after being reported by a user.
-
-We further examine the placement of interstitials that indicate a possibly sensitive content.
-We find that only $2.97\%$ out of $323$ $938$ tweets containing a URL marked as False, have an interstitial ``potentially sensitive content''.
-In particular, many speak about COVID19 and do not contain a label to provide users with more context from authoritative sources.
-Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''.
-We find 32 other Tweets, among our set of collected tweets, who share the exact same URL link as in the previous example.
-Among those 32 Tweets, only 5 tweets had the interstitial ``potentially sensitive content''.
-Again this points towards the non-automation of the placement of interstitials.\footnote{Notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations.
-In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}.
-Hence the numbers given are an upper bound of the number of interstitials indicating  possibly sensitive content.}
-
-\smallskip
-
-Finally, Twitter Safety account announced in a Tweet\footnote{See Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}} on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".
-%we don't know what it means the articl xxx which was retracted by the journal and fack-check still appears in xx tweets with no label
-
-\begin{figure}
-	\centering
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
-	%\end{multicols}
-	\caption{Panel (a): Tweet containing a URL link hidden behind an interstitial.
-Panel (b): when clicking on $view$, to view the content hidden behind the interstitial.
-Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}.
-Screenshots taken on July 1, 2021.
-}
-	\label{fig_notice}
-\end{figure}
-
-\subsubsection{Youtube}
-
-\begin{figure}
-	\centering
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/youtube_panels/yt_2.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/youtube_panels/yt_3.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/youtube_panels/yt_4.png} 
-	%\end{multicols}
-	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}
-	\label{fig9}
-\end{figure}
-
-Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} Information panels provide ressources concerning a potentially controversial topic from independent third party partners or authoritative ressources.
-Youtube states that these panels exist regardless of the point of view expressed in a given video.
-In addition, these panels are not yet available in all languages and countries.
-%(“Information panel giving topical context”)
-
-To further study the assignment of information panels to videos, we implemented the following exercice.
-We compiled a list of $171$ Youtube videos, checked by independent fact-checkers\footnote{Is it science Feedback ?
-if so add.} and marked as containing false or inaccurate information.
-We collected the information panels, when present, in each video by scrapping the content of the web and connecting to a US server.
-Four types of information panels were found in the list of visited videos as shown in figure\ref{fig9}:  information about COVID19, Vaccines, Climate change and US elections.
-
-We classified the list of Youtube videos by topic based on its content as shown in table \ref{tab2}.
-We recorded the number of videos containing an information panel within each category.
-For COVID19 and vaccine related videos more than half of the videos contained an information panel.
-Nevertheless, we noticed that duplicates of the same Youtube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
-In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
-Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.
-
-\smallskip
-
-For climate change we only examined $18$ misleading videos and we found that $28\%$ did not display an information panel.
-Lastly , for the general health category, we included the videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion,  and viruses; no information panels were displayed for that set of Youtube videos.
-Therefore, it is likely that Youtube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.
-%drop last colum
-%add % in a second line
-\begin{table}[] 
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-Category       & \begin{tabular}[c]{@{}c@{}}Number of Youtube videos {\bf with} an \\ information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of Youtube videos {\bf without} an \\ information panel\end{tabular}    \\ \hline
-\begin{tabular}[c]{@{}c@{}} General Health \end{tabular} & \begin{tabular}[c]{@{}c@{}} 0  \\ (0\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 11 \\ (100\%) \end{tabular}         \\ \hline
-Vaccine        & \begin{tabular}[c]{@{}c@{}} 21     \\ (75\%) \end{tabular}   & \begin{tabular}[c]{@{}c@{}}  7 \\ (25\%)  \end{tabular}     \\ \hline
-COVID19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
-\begin{tabular}[c]{@{}c@{}}  Climate change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
-\end{tabular}
-\caption{}
-\label{tab2}
-\end{table}
 

### 2021-07-20 article/draft.tex
updates

@@
 Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense.
-\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.
-{\color{pink} Add more examples to show that this problem is highlighted by different institutions with different/neutral political color..
-}}
+\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.}
 
@@
 
-In this article, we focus on mainstream platforms' policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (for an overview of the concept see Lazer et al.
+Hence, in the present article, we focus on mainstream platforms' policies and interventions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (see Lazer et al.
 (2018)~\cite{lazer}).
@@
 For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.
-Facebook use a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
+Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
 The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1.
@@
 In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}.
-The 2019 report of the Facebook Data Transparency Advisory Group\footnote{To read the full report, see: \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}.} (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
+The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
 Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
-It is explained via a blog post on the facebook Newsroom.\footnote{See: \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{https://about.fb.com/news/2018/05/hard-questions-false-news/}.}.
-Similarly, Twitter communicates about actions related to misinformation via their Twitter Safety Blog/account\footnote{See \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{https://blog.twitter.com/en\_us/authors.TwitterSafety}.}.
-In a post on Youtube Official Blog\footnote{See \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}.}, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation.
+It is explained via a blog post on the facebook Newsroom.
+Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account.
+In a post on Youtube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
 
@@
 We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article.
-We compile in Appendix \ref{links} in table \ref{summary}, URL links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and Youtube.
+We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and Youtube that we discuss throughout the article.
 Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
@@
 %paragraph strike system + say following example is a manual decision. 
-Twitter has implemented a strike system as part of their Civi Integrity Policy\footnote{See \href{https://help.twitter.com/en/rules-and-policies/election-integrity-policy}{help.twitter.com/en/rules-and-policies/election-integrity-policy}} and their COVID19 misleading information policy.\footnote{See \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}{blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}} Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform.
+Twitter has implemented a strike system as part of their Civic Integrity Policy and their COVID19 misleading information policy.
+Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform.
 The 12-hour account lock is hard to observe in the data, especially for users who do not have an over the clock tweeting activity.
@@
 Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
+
+	\item We hope this paper can illustrate how the platforms policies can be verified.
+All the code needed to collect the data, and create the figures can be found on a public GitHub repo: https://github.com/medialab/truth-and-trust-online-2021/, so that other researchers and journalists can easily reuse our methodology.
 \end{itemize}
@@
 \hline
-\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/communitystandards/recentupdates/}{facebook.com/communitystandards/recentupdates/}                         \\ \cline{2-3}
+\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}}   \href{https://www.facebook.com/communitystandards/recentupdates/}{facebook.com/communitystandards/recentupdates/}    \end{tabular}                     \\ \cline{2-3}
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}                       \\ \cline{2-3}
@@
                                            & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/youtube-policy/}{transparencyreport.google.com/youtube-policy/}                              \\ \hline
-\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Transparency \\ center \end{tabular}}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3}
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Transparency \\ center \end{tabular}}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}}  \href{https://transparency.fb.com/data/}{transparency.fb.com/data/}    \\ \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report} \end{tabular}                                               \\ \cline{2-3}
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports.html}{transparency.twitter.com/en/reports.html}                                  \\ \cline{2-3}
@@
                                            & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}  \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}  \\ \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}    \end{tabular}                            \\ \hline
+
+%
+
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}} Strike System \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}} See in the following link the section {\it What is the number of strikes a person or } \\ { \it Page has to get to before you ban them?} \\  \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}   \end{tabular}                            \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   &  \begin{tabular}[c]{@{}cl@{}}  See in the following links the section:  {\it Account locks and permanent suspension }   \\ \href{https://help.twitter.com/en/rules-and-policies/election-integrity-policy}{help.twitter.com/en/rules-and-policies/election-integrity-policy}  \\ \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy}  \end{tabular}    \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}    \end{tabular}                            \\ \hline 
  \end{tabular}

### 2021-07-20 article/draft.tex
updates

@@
 For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.
-Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
+Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
 The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1.
@@
 During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}).
-Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged\footnote{{\color{pink} put here the list of Facebook and Twitter terms about covid.}}, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
+Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
 As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms.
 Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
-In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}.
+In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines (as of July 2021).
 The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
@@
 More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited mainstream platforms, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
-We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.\footnote{For a detailed list of interventions check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
-} We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
+We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.
+We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
+For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
+
+\smallskip
+
  We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article.
@@
 Mainstream social media platforms may suspend the account of a specific user when they deem that the platforms' rules have been violated.
-Account suspension can be temporary or permanent.\footnote{A list of notable Twitter temporary and permanent suspensions can be found on wikipedia: \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{https://en.wikipedia.org/wiki/Twitter\_suspensions}.}  When the suspension is temporary the user is prohibited for a limited period of time from posting content on their account, but created content prior to suspension remains available to the user and their followers.
+Account suspension can be temporary or permanent.
+When the suspension is temporary the user is prohibited for a limited period of time from posting content on their account, but created content prior to suspension remains available to the user and their followers.
 However, when the suspension is permanent, in most cases, followers or subscribers have no longer access to the content prior to the suspension and the user can no longer use the account to create new content.
@@
 For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API.
-Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used Minet command line tool \cite{minet} to collect the data.\footnote{The exact command can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_trump_data.sh}{here}.} We can verify on figure \ref{fig1_fb} that the {\it Donald J.
+Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used Minet command line tool \cite{minet} to collect the data.
+We can verify on figure \ref{fig1_fb} that the {\it Donald J.
 Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.
@@
 %paragraph strike system + say following example is a manual decision. 
-Twitter has implemented a strike system as part of their Civic Integrity Policy and their COVID19 misleading information policy.
+Twitter has implemented a strike system as part of their Civic Integrity Policy and their COVID-19 misleading information policy.
 Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform.
+A list of notable Twitter temporary and permanent suspensions can be found on  \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{Wikipedia}.
 The 12-hour account lock is hard to observe in the data, especially for users who do not have an over the clock tweeting activity.
-In this section, we provide one example of a temporary suspension\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.
+In this section, we provide one example of a temporary suspension of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.
 
@@
 In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}.
-We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}).
+We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint.
+We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}).
 The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.
@@
 The strike count of a channel lasts 90 days.
-In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning.\footnote{See the ``Community Guidelines strike basics''.
-Youtube help, Google Developers,  \href{https://support.google.com/youtube/answer/2802032?hl=en.
-Accessed 21 6 2021}{https://support.google.com/youtube/answer/2802032?hl=en.
-Accessed 21 6 2021}.} To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two Youtube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
+In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning.
+To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two Youtube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
 
@@
 First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}.
-This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021.
-For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
+This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID-19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021.
+For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
 
@@
 
-We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the {\it search} endpoint in minet\footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}).}.
+We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the {\it search} endpoint in minet\footnote{ Click \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{here} to access the link and  \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{its fact-check by Health Feedback}.}.
 Twenty Facebook posts were collected this way, and the newly developed scraper was used to verify whether they were flagged with an information banner, a fact-check flag, both or none.
@@
 
-Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial.
+Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.
+At the tweet level, notices take the form of a label or an interstitial.
 Labels are context specific (e.g.
-COVID19 or presidential elections) and  redirect users to a URL to get more context, for example ``Get the facts about COVID-19'' (see right panel of figure \ref{fig8}).
-Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example ``The following media includes potentially sensitive content'' (see left panel of figure \ref{fig_notice}).
+COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it Get the facts about COVID-19'} (see right panel of figure \ref{fig8}).
+Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example {\it The following media includes potentially sensitive content} (see left panel of figure \ref{fig_notice}).
 At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.
@@
 	%\end{multicols}
-	\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021.
+	\caption{Two tweets sharing the same link marked as False by Science Feedback, screenshots taken on June $20$, 2021.
 Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label.
@@
 \end{figure}
+
+\smallskip
 
@@
 In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false.
-To that end, we gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
-As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$.
+To that end, we gathered a set of $3094$ links redirecting to articles which were marked as $False$ between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
+As a second step, we collected (on June $30$, $2021$) via Minet Command line tool~\cite{minet} all the tweets that have shared a link which belongs to the set of $3094$ links marked as $False$.
 This data collection resulted in $323$ $938$ tweets, excluding retweets.
-Only $28$ tweets contained the label { ``Get the facts about COVID-19''}, $5$ tweets contained the label { ``Learn about US 2020 election security efforts''} and only $1$ had the following label {``This claim about election fraud is disputed''}.
-Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same URL link, among the set of collected tweets.
-More specifically, exactly $657$ tweets had shared a URL link redirecting to a video on Bitchute, entitled ``Important information on coronavirus 5G Kung Flu''.
-Among those $657$ tweets only $3$ contained the label ``Get the facts about COVID-19'' (see figure \ref{fig8}).
-This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by a user.
+Only $28$ tweets contained the label { \it Get the facts about COVID-19}, $5$ tweets contained the label {\it Learn about US 2020 election security efforts} and only $1$ had the following label {\it This claim about election fraud is disputed}.
+Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same link, among the set of collected tweets.
+To give an example, $657$ tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}.
+Among those $657$ tweets only $3$ contained the label {\it Get the facts about COVID-19} (see figure \ref{fig8}).
+This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by other users.
 
@@
 
-We further examine the placement of interstitials that indicate a possibly sensitive content.
-We find that only $2.97\%$ out of $323$ $938$ tweets containing a URL marked as False, have an interstitial ``potentially sensitive content''.
-{\color{pink}In particular, many tweets speak about COVID19 and do not contain a label to provide users with more context from authoritative sources.
-Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''.} We find 32 other Tweets, among our set of collected tweets, who share the exact same URL link as in the previous example.
-Among those 32 Tweets, only 5 tweets had the interstitial ``potentially sensitive content''.
-Again this points towards the non-automation of the placement of interstitials.\footnote{Notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations.
-In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}.
-Hence the numbers given are an upper bound of the number of interstitials indicating  possibly sensitive content.}
-{\color{pink} can we have both at the same time (see example facebook)  + dire pour l'exemple get the facts about covid. }
 \smallskip
 
-Finally, Twitter Safety account announced in a Tweet\footnote{See Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}} on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".
-%we don't know what it means the article xxx which was retracted by the journal and fack-check still appears in xx tweets with no label
+We further examine the placement of interstitials that indicate a possibly sensitive content.
+We find that only $9344$ ($2.97\%$) tweets out of $323$ $938$ containing a link marked as False, have an interstitial {\it potentially sensitive content}.
+To check whether the interstitial {\it potentially sensitive content} is automated or not, we pick out one tweet having shared a link marked as False\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.}, which also contains the interstitial {\it potentially sensitive content}.
+Then we look in the set of $323$ $938$ tweets for other tweets who have shared the exact same link.
+We find a total of $32$ tweets.
+Among those $32$ tweets only $5$ tweets had the interstitial ``potentially sensitive content''.
+Again this points towards the non-automation of interstitials placement.
+Furthermore, notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations.
+In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}.
+
+\smallskip
+
+Finally, the number of tweets containing the interstitial {\it potentially sensitive content} ($9344$ tweets) widely outnumbers the tweets which contain a flag ($32$ tweets), among the set of $323$ $938$ tweets containing a link marked as False (see table \ref{flags_tab}).
+Furthermore, we noticed that among the tweets which contain the interstitial {\it potentially sensitive content}, there are tweets which contain links redirecting to misleading articles about COVID-19 and yet they are not marked by the flag { \it Get the facts about COVID-19}.
+We also noticed that the $9344$ tweets marked with the interstitial {\it potentially sensitive content} do not necessarily contain graphic violent\footnote{The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.} content but rather links that redirect to articles marked as $False$ by Science Feedback.
+When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it potentially sensitive content} and flags which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".}
+
+\begin{table}[h]
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+\multicolumn{4}{|c|}{$323$ $938$ Tweets containing a link marked as False}                                                                                                                                                                                                                                                                                                                           \\ \hline
+\begin{tabular}[c]{@{}c@{}}with the interstitial\\ ``potentially sensitive \\ content'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Get the facts \\ about COVID-19'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Learn about US \\ 2020 election \\ security efforts'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag\\ ``This claim about \\ election fraud \\ is disputed''\end{tabular} \\ \hline
+\begin{tabular}[c]{@{}c@{}}9344\\ ( 2.88450 \%)\end{tabular}                                  & \begin{tabular}[c]{@{}c@{}}28\\ (0.00864\%)\end{tabular}                              & \begin{tabular}[c]{@{}c@{}}5\\ (0.00154\%)\end{tabular}                                                & \begin{tabular}[c]{@{}c@{}}1\\ (0.00030\%)\end{tabular}                                             \\ \hline
+\end{tabular}
+\caption{Summary of the number of tweets among the set of collected tweets containing a link marked as False by Science Feedback, which contain a flag or an interstitial.}
+\label{flags_tab}
+\end{table}
 
@@
 
-Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} Information panels provide ressources concerning a potentially controversial topic from independent third party partners or authoritative ressources.
+Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID-19, moon landing, and climate change.
+Information panels provide ressources concerning a potentially controversial topic from independent third party partners or authoritative ressources.
 Youtube states that these panels exist regardless of the point of view expressed in a given video.
@@
 
-To further study the assignment of information panels to videos, we compiled a list of $171$ Youtube videos, checked by independent fact-checkers\footnote{Is it science Feedback ?
-if so add.} and marked as containing false or inaccurate information.
+To further study the assignment of information panels to videos, we compiled a list of $171$ Youtube videos, {\color{red}checked by independent fact-checkers} and marked as containing false or inaccurate information.
 We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page.
-Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about COVID19, Vaccines, Climate change and US elections.
+Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about COVID-19, Vaccines, Climate change and US elections.
 
@@
 We recorded the number of videos containing an information panel within each category.
-For COVID19 and vaccine related videos more than half of the videos contained an information panel.
+For COVID-19 and vaccine related videos more than half of the videos contained an information panel.
 Nevertheless, we noticed that duplicates of the same Youtube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
-In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
+In addition, we noticed for COVID-19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID-19, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
 Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video.
@@
 For climate change we found that most of the videos (13 out of 18) did not display an information panel.
-Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion, and viruses.
-Therefore, it is likely that Youtube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID19, flat earth and vaccine.
+Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID-19 but contained misinformation concerning cures for cancer, abortion, and viruses.
+Therefore, it is likely that Youtube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID-19, flat earth and vaccine.
 %drop last colum
@@
 Vaccine        & \begin{tabular}[c]{@{}c@{}} 21     \\ (75\%) \end{tabular}   & \begin{tabular}[c]{@{}c@{}}  7 \\ (25\%)  \end{tabular}     \\ \hline
-COVID19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
+COVID-19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
 \begin{tabular}[c]{@{}c@{}}  Climate change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
@@
 Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed.
-Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure.\footnote{Lyons, T.
-(2018, May 22).
-The three-part recipe for cleaning up your news feed.
-Facebook Newsroom.
-\href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the APIs used to access Facebook data: CrowdTangle or Buzzsumo.
+Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure (see the article on Facebook Newsroom (2018)~\cite{newsroom2}).
+This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the APIs used to access Facebook data: CrowdTangle or Buzzsumo.
 Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available on CrowdTangle and Buzzsumo.
@@
 This website appears in the Misinformation Directory of FactCheck.org, among other websites who have posted deceptive content\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}.
-Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.}
+Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news and it has several failed fact-checks reported by Feedback.org.\footnote{See the Iffy.news page \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/} and Feedback.org \href{https://open.feedback.org/media/RM}{https://open.feedback.org/media/RM}.}
 
@@
 
-On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/} and \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}.
+On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See the article in Wired by Martineau (2020)~\cite{wiredalexjones} and see the section {\it So what happened with InfoWars?
+They were up on Friday and now they are down?} \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}.
 The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel).
@@
 We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.
-\footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
+%\footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.}
+We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
 An increase in engagement was also observed in $2020$.
@@
 
-The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook'' for coordinated inauthentic behavior\footnote{\href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}, which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
+The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that {\it The BL is now banned from Facebook} for coordinated inauthentic behavior (see Facebook Newsroom (2019)~\cite{newsroom1}), which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
 Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested, according to the fact-checking organization Snopes which had reported about The BL’s activity to Facebook and other various public articles\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}}.
@@
 To further investigate this policy, we collected data from the Buzzsumo API\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.}.
-We used the ``/search/articles'' endpoint to collect the engagement metrics of the $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.\footnote{The command can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}.}
+We used the ``/search/articles'' endpoint to collect the engagement metrics of the $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.%\footnote{The command can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}.}
 
 The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban.
-We can note that although the ban was communicated in an article\footnote{See \href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}.} published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
+We can note that although the ban was communicated in an article~\cite{newsroom1} published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
 
@@
 
-Twitter can take action against a tweet which violates the Twitter rules\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.}, by limiting its visibility on users' timelines and in search results.
-To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
+Twitter can take action against a tweet which violates the Twitter rules, by limiting its visibility\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.} on users' timelines and in search results.
+To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://open.feedback.org/media/AEKA}{Feedback.org} and \href{https://iffy.news}{iffy.news} - two websites which provides databases of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://open.feedback.org/media/AEKA}{open.feedback.org/media/AEKA} and \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
 
@@
 		%\begin{multicols}{1}	
+					\includegraphics[scale=0.35]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
+		%\end{multicols}
+		%\begin{multicols}{1}
 					\includegraphics[scale=0.32]{./img/globalresearch/tweet.png} 
 		%\end{multicols}
-		%\begin{multicols}{1}
-			\includegraphics[scale=0.35]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
-		%\end{multicols}
-		\caption{Screenshots taken on June 14, 2021. Top panel: ? . Bottom panel: screenshot that shows that no results can be found when searching for $globalresearch.ca$.    }
+		\caption{Screenshots taken on June 14, 2021.
+Panel (a): screenshot that shows that no results can be found when searching for $globalresearch.ca$.
+Panel (b): example of a tweet posted on June $14$ containing the domain name {\it globalresearch.ca}.
+}
 		\label{fig3}
@@
 
-The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; which was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021.
-But to the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
-Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}).
-Furthermore, $globalresearch.ca$ has multiple failed fact-checks, see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and \href{https://feedback.news/media/AEKA}{https://feedback.news/media/AEKA}.} When a user searches via the twitter search-box for any URL link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June $14$, $2021$.
+\smallskip
+
+The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}.
+When a user searches via the twitter search-box for this domain name, no results appear as shown in the screenshot in panel $(a)$ of figure \ref{fig3}, taken on June $14$, $2021$.
 To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the URL link {\it globalresearch.ca} throughout May $2021$ and the first week of June $2021$.
-Hence, the visibility of tweets containing this URL link has been reduced because users can no longer access tweets containing the URL link {\it globalresearch.ca} via the search box.
-Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(a)$ of figure \ref{fig4bis}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
+As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the domain name {\it globalresearch.ca} throughout May $2021$ and the first week of June $2021$.
+Hence, the visibility of tweets containing this domain name has been reduced because users can no longer access tweets containing the domain name {\it globalresearch.ca} via the search box.
+Nevertheless users are not restrained from posting tweets containing this domain name, as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
 Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
 Hence, the users who tweet articles from the {\it globalresearch.ca} website receive tweet level engagement from their own followers.
-Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (b) in figure \ref{fig4bis}).
-
-The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}; which was recently suspended.\footnote{We noticed the message about the account suspension on May 25, 2021.
-But to the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
-Hence the account may have gotten suspended anytime between April 15, 2021 and May 25, 2021 (see the suspension screenshot in panel $(a)$ of figure \ref{fig3}).} When a user searches via the twitter search-box for any URL link of this website, no results appear as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, taken on June $14$, $2021$.
 
@@
 	%\end{multicols}
-\caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-Bottom panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+\caption{Panel (a): daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+Panel (b): engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
 Data collected via the Twitter API v2 on June $16$, 2021.
@@
 
-To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the URL link {\it globalresearch.ca} throughout May $2021$ and the first week of June $2021$.
-Hence, the visibility of tweets containing this URL link has been reduced because users can no longer access tweets containing the URL link {\it globalresearch.ca} via the search box.
-Nevertheless users are not restrained from posting tweets containing this URL, as shown in the screenshot in panel $(a)$ of figure \ref{fig4bis}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
-Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
-Hence, the users who tweet articles from the {\it globalresearch.ca} website receive tweet level engagement only from their own followers.
-
-Finally, when a user attempts to click on the URL link {\it globalresearch.ca} contained in the Tweet, a warning message appears and indicates that the link may be unsafe (see screenshot in panel (b) in figure \ref{fig4bis}).
+Finally, the above mentioned account was recently suspended from Twitter.
+We noticed the message about the account suspension (see panel (b) in figure \ref{fig4bis}) on May $25$, 2021.
+To the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
+Hence the account may have gotten suspended before that date.
+Furthermore when a user attempts to click on a link which contains {\it globalresearch.ca} in a Tweet, a warning message appears and indicates that the link may be unsafe (see panel (a) in figure \ref{fig4bis}).
+For the case of this Twitter account, it is likely that a mix of interventions was used: reducing the visibility via the search box, suspending the related Twitter account and returning a warning message when users click on a link containing this domain name.
 
 \begin{figure}[h]
-\centering	
-	%\begin{multicols}{1}
-		%\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
-	%\end{multicols}
-\caption{}
+	\begin{center}
+	\resizebox{.9\textwidth}{!}{%
+		\includegraphics[height=3cm]{./img/globalresearch/warning.png} 
+		\quad
+		\includegraphics[height=3cm]{./img/globalresearch/globalresearch_2021-06-14.png}
+	}
+	\end{center}
+	\caption{Screenshots taken on June 14, 2021.
+Panel (a): warning message that appears when a user attempts to click on a link which contains the domain name {\it globalresearch.ca}.
+Panel (b): account suspension message of $@CRG$\_$CRM$ linked to {\it globalresearch.ca}.
+}
 	\label{fig4bis}
@@
 
-	\item For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
+	\item For a previous research project (add reference to the article) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
 We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
@@
 But too much transparency on how the regulation policies are exactly implemented can actually backfire.
-For example YouTube is certainly applying an 'information' banner on all videos mentioning Covid and related terms in their title.
+For example YouTube is certainly applying an 'information' banner on all videos mentioning COVID-19 and related terms in their title.
 Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'.
@@
 \begin{landscape}
+\thispagestyle{empty}
 
-\begin{table*}[h]
+\begin{table}[p]
+\centering
+\setlength{\tabcolsep}{2pt}
 \begin{tabular}{|c|c|c|}
@@
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   &  \begin{tabular}[c]{@{}cl@{}}  See in the following links the section:  {\it Account locks and permanent suspension }   \\ \href{https://help.twitter.com/en/rules-and-policies/election-integrity-policy}{help.twitter.com/en/rules-and-policies/election-integrity-policy}  \\ \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy}  \end{tabular}    \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}  \href{https://support.google.com/youtube/answer/2802032?hl=en.
+Accessed 21 6 2021}{https://support.google.com/youtube/answer/2802032?hl=en.
+Accessed 21 6 2021}   \end{tabular}                            \\ \hline
+
+%
+
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}} Account suspension \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}}    \end{tabular}                            \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   &  \begin{tabular}[c]{@{}cl@{}} \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }    \end{tabular}    \\ \cline{2-3}
                                            & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}    \end{tabular}                            \\ \hline
+
+%
+
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}} Flags, Notice \\ and Information Panels \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}}    \end{tabular}                            \\ \cline{2-3}
+                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   &  \begin{tabular}[c]{@{}cl@{}} \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}    \end{tabular}    \\ \cline{2-3}
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}   \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}  \end{tabular}                            \\ \hline
+
  \end{tabular}
@@
 \label{summary}
-\end{table*}
+\end{table}
 

### 2021-07-20 article/draft.tex
small date precision for YT flags and Youtube -> YouTube

@@
 Section $230$ in the United States Communications Decency Act provides immunity for website platforms against the content created by users.
-Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for Mainstream Social Media Platforms, such as Facebook, Twitter or Youtube, to moderate the available content.
+Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for Mainstream Social Media Platforms, such as Facebook, Twitter or YouTube, to moderate the available content.
 In particular, platforms take explicit actions when content is in violation of local laws in different jurisdictions, such as laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws.
 For example, Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}.
-We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} %Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}
+We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} %Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned YouTube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}
 
@@
 Furthermore, mainstream platforms are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated.
-Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see table \ref{summary} in Appendix \ref{links}).
+Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see table \ref{summary} in Appendix \ref{links}).
 While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation.
@@
 Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}).
-As for Youtube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see table \ref{summary} in Appendix \ref{links}).
+As for YouTube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see table \ref{summary} in Appendix \ref{links}).
 
@@
 Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account.
-In a post on Youtube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
+In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
 
@@
 %In particular, determining the truthfulness of content over controversial topics or ongoing political events proves to be a tricky task and correcting beliefs about viral content, fact-checked as false ...
-%For an overview of Youtube's policy on fact-checking see: \href{https://support.google.com/youtube/answer/9229632}{support.google.com/youtube/answer/9229632}.
+%For an overview of YouTube's policy on fact-checking see: \href{https://support.google.com/youtube/answer/9229632}{support.google.com/youtube/answer/9229632}.
 To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
@@
  \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
- \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
+ \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
 \end{tabular}
@@
 We do so by providing a series of examples for different interventions and platforms.
-We only focus on three platforms: Facebook, Twitter and Youtube.
-Both Facebook and Youtube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}.
-More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited mainstream platforms, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
+We only focus on three platforms: Facebook, Twitter and YouTube.
+Both Facebook and YouTube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}.
+More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited mainstream platforms, Facebook, Twitter and YouTube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
 We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.
@@
 
- We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article.
-We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and Youtube that we discuss throughout the article.
+ We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and YouTube, that we use in multiple examples throughout the present article.
+We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
 Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
@@
 
-\subsection{Youtube}
+\subsection{YouTube}
 
-In this section, we turn to the channel's temporary or permanent suspension policy of Youtube.
+In this section, we turn to the channel's temporary or permanent suspension policy of YouTube.
 Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed.
 For the second time the channel will start receiving strikes.
-A first strike results in limiting the access of the Youtube channel  for one week, like uploading videos, streaming and other activities.
+A first strike results in limiting the access of the YouTube channel  for one week, like uploading videos, streaming and other activities.
 Then a second strike is similar but the suspension will be for two weeks.
@@
 In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning.
-To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two Youtube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
+To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two YouTube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
 
@@
 	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
-Panel (b): Tony Heller's tweet after getting suspended from Youtube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
+Panel (b): Tony Heller's tweet after getting suspended from YouTube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
 	\label{fig2_oann}
@@
 
-First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}.
-This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID-19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021.
+First, we investigate the temporary suspension case of the YouTube channel of {\it One America News channel}.
+This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID-19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the YouTube API v3, between November 2020 and January 2021.
 For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
@@
 	%\end{multicols}
-	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
+	\caption{panel (a): Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
 Panel (b): accumulated view counts for videos.
@@
 In addition, as shown in figure \ref{fig1_oann} when comparing the month before the suspension from 2020/10/24 to 2020/11/24 and one month after from 2020/12/01 to 2021/01/01 it was found that the view count decreased by -73\% and the videos uploaded by -55\%.
-Besides that, OANN decided to move officially to Rumble on March 17, 2021 as announced on their Twitter account (see figure \ref{fig2_oann}) and their upload activity on their Youtube channel is close to zero since that announcement.
+Besides that, OANN decided to move officially to Rumble on March 17, 2021 as announced on their Twitter account (see figure \ref{fig2_oann}) and their upload activity on their YouTube channel is close to zero since that announcement.
 
@@
 		%\end{multicols}
-	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
-Panel (b): accumulated view counts for videos uploaded by the same Youtube channel.
+	\caption{Panel (a): Number of YouTube videos uploaded each day by the YouTube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
+Panel (b): accumulated view counts for videos uploaded by the same YouTube channel.
 The date corresponds to the videos’  publishing date.
@@
 
-We now turn to our second example, the temporary suspension of the Youtube channel Tony Heller.
+We now turn to our second example, the temporary suspension of the YouTube channel Tony Heller.
 This channel got its first strike after posting a video about an anti-covid-lockdown doctor getting arrested (see screenshot in figure \ref{fig2_oann}).
@@
 observing the reach of the audience
-Figure 3: Tony heller tweet after getting suspended from youtube (Twitter)
+Figure 3: Tony heller tweet after getting suspended from YouTube (Twitter)
 using view counts one month before the suspension starting from 2020/08/28 to 2020/09/28 and one month after the suspension from 2020/10/05 to 2020/11/05 the channel witnessed a drop of view counts by $-69.5\%$ and the videos published in the channel were less by $-29\%$.
@@
 
-\subsection{Youtube}
+\subsection{YouTube}
 
-Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID-19, moon landing, and climate change.
+YouTube may provide an information panel for videos with topics that are prone to misinformation like COVID-19, moon landing, and climate change.
 Information panels provide ressources concerning a potentially controversial topic from independent third party partners or authoritative ressources.
-Youtube states that these panels exist regardless of the point of view expressed in a given video.
+YouTube states that these panels exist regardless of the point of view expressed in a given video.
 In addition, these panels are not yet available in all languages and countries.
@@
 
-To further study the assignment of information panels to videos, we compiled a list of $171$ Youtube videos, {\color{red}checked by independent fact-checkers} and marked as containing false or inaccurate information.
+To further study the assignment of information panels to videos, we compiled a list of $171$ YouTube videos, fact-checked by Science Feedback between April 2019 and March 2021 and marked as containing false or inaccurate information.
 We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page.
@@
 
-We classified the list of Youtube videos by topic based on its content as shown in table \ref{tab2}.
+We classified the list of YouTube videos by topic based on its content as shown in table \ref{tab2}.
 We recorded the number of videos containing an information panel within each category.
 For COVID-19 and vaccine related videos more than half of the videos contained an information panel.
-Nevertheless, we noticed that duplicates of the same Youtube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
+Nevertheless, we noticed that duplicates of the same YouTube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
 In addition, we noticed for COVID-19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID-19, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
-Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video.
+Therefore, we suspect that YouTube is automatically adding panels to the videos based on the video title and not the content of the video.
 
@@
 Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID-19 but contained misinformation concerning cures for cancer, abortion, and viruses.
-Therefore, it is likely that Youtube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID-19, flat earth and vaccine.
+Therefore, it is likely that YouTube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID-19, flat earth and vaccine.
 %drop last colum
@@
 \hline
-Category       & \begin{tabular}[c]{@{}c@{}}Number of Youtube videos {\bf with} an \\ information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of Youtube videos {\bf without} an \\ information panel\end{tabular}    \\ \hline
+Category       & \begin{tabular}[c]{@{}c@{}}Number of YouTube videos {\bf with} an \\ information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of YouTube videos {\bf without} an \\ information panel\end{tabular}    \\ \hline
 \begin{tabular}[c]{@{}c@{}} General Health \end{tabular} & \begin{tabular}[c]{@{}c@{}} 0  \\ (0\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 11 \\ (100\%) \end{tabular}         \\ \hline
@@
 
-\subsection{Youtube}
+\subsection{YouTube}
 
@@
 
-	\item Make point about the communication of platforms for their policy: 4R of Youtube, RRI of Facebook,
+	\item Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook,
 
@@
 
-	\item After a channel gets suspended or a video is deleted the data related to them is removed from the youtube API.
+	\item After a channel gets suspended or a video is deleted the data related to them is removed from the YouTube API.
 This is a problem that affected the study to investigate the suspension reasons or the removal.
-For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from youtube because they contain content that is against the youtube guidelines and their data got removed from the API.
+For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from YouTube because they contain content that is against the YouTube guidelines and their data got removed from the API.
 

### 2021-07-21 article/draft.tex
minor changes

@@
 	%\end{multicols}
-\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021.
-Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021.
+\caption{Left Panel: number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021.
+Right Panel: number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021.
 }
@@
 
-	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
-Panel (b): Tony Heller's tweet after getting suspended from YouTube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
+	\caption{Left Panel: Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
+Right Panel: Tony Heller's tweet after getting suspended from YouTube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
 	\label{fig2_oann}
@@
 	%\end{multicols}
-	\caption{panel (a): Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
-Panel (b): accumulated view counts for videos.
+	\caption{Left Panel: Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
+Right Panel: accumulated view counts for videos.
 The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints.
@@
 		%\end{multicols}
-	\caption{Panel (a): Number of YouTube videos uploaded each day by the YouTube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
-Panel (b): accumulated view counts for videos uploaded by the same YouTube channel.
+	\caption{Left Panel: Number of YouTube videos uploaded each day by the YouTube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
+Right Panel: accumulated view counts for videos uploaded by the same YouTube channel.
 The date corresponds to the videos’  publishing date.
@@
 	\caption{Two tweets sharing the same link marked as False by Science Feedback, screenshots taken on June $20$, 2021.
-Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label.
-Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
+Left Panel: Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label.
+Right Panel: Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
 	\label{fig8}
@@
 	%\end{multicols}
-	\caption{Panel (a): Tweet containing a URL link hidden behind an interstitial.
-Panel (b): when clicking on $view$, to view the content hidden behind the interstitial.
+	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial.
+Right Panel: when clicking on $view$, to view the content hidden behind the interstitial.
 Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}.
@@
 
-To further study the assignment of information panels to videos, we compiled a list of $171$ YouTube videos, fact-checked by Science Feedback between April 2019 and March 2021 and marked as containing false or inaccurate information.
+To further study the assignment of information panels to videos, we compiled a list of $171$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information.
 We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page.
@@
 	\caption{Articles from The Beauty of Life website (thebl.com) published between January 1, 2019 and June 15, 2021 and gathered from the Buzzsumo API.
-(Top) Facebook engagement metrics (average number of reactions, shares and comments per article).
-(Bottom) Number of articles published per day.
+Left panel: Facebook engagement metrics (average number of reactions, shares and comments per article).
+Right panel: Number of articles published per day.
 The red line marks the date of December 1, 2019.
@@
 		\caption{Screenshots taken on June 14, 2021.
-Panel (a): screenshot that shows that no results can be found when searching for $globalresearch.ca$.
-Panel (b): example of a tweet posted on June $14$ containing the domain name {\it globalresearch.ca}.
+Left Panel: screenshot that shows that no results can be found when searching for $globalresearch.ca$ via the Twitter search box.
+Right Panel: example of a tweet posted on June $14$ containing the domain name {\it globalresearch.ca}.
 }
@@
 The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}.
-When a user searches via the twitter search-box for this domain name, no results appear as shown in the screenshot in panel $(a)$ of figure \ref{fig3}, taken on June $14$, $2021$.
+When a user searches via the twitter search-box for this domain name, no results appear as shown in the screenshot in the left panel of figure \ref{fig3}, taken on June $14$, $2021$.
 To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-As shown in panel (a) in figure \ref{fig4}, we find a strictly positive number of tweets containing the domain name {\it globalresearch.ca} throughout May $2021$ and the first week of June $2021$.
+As shown in the left panel in figure \ref{fig4}, we find a strictly positive number of tweets containing the domain name {\it globalresearch.ca} throughout May $2021$ and the first week of June $2021$.
 Hence, the visibility of tweets containing this domain name has been reduced because users can no longer access tweets containing the domain name {\it globalresearch.ca} via the search box.
@@
 	%\end{multicols}
-\caption{Panel (a): daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-Panel (b): engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
+Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
 Data collected via the Twitter API v2 on June $16$, 2021.
@@
 Finally, the above mentioned account was recently suspended from Twitter.
-We noticed the message about the account suspension (see panel (b) in figure \ref{fig4bis}) on May $25$, 2021.
+We noticed the message about the account suspension (see the right panel in figure \ref{fig4bis}) on May $25$, 2021.
 To the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
 Hence the account may have gotten suspended before that date.
-Furthermore when a user attempts to click on a link which contains {\it globalresearch.ca} in a Tweet, a warning message appears and indicates that the link may be unsafe (see panel (a) in figure \ref{fig4bis}).
+Furthermore when a user attempts to click on a link which contains {\it globalresearch.ca} in a Tweet, a warning message appears and indicates that the link may be unsafe (see the left panel in figure \ref{fig4bis}).
 For the case of this Twitter account, it is likely that a mix of interventions was used: reducing the visibility via the search box, suspending the related Twitter account and returning a warning message when users click on a link containing this domain name.
@@
 	\caption{Screenshots taken on June 14, 2021.
-Panel (a): warning message that appears when a user attempts to click on a link which contains the domain name {\it globalresearch.ca}.
-Panel (b): account suspension message of $@CRG$\_$CRM$ linked to {\it globalresearch.ca}.
+Left Panel: warning message that appears when a user attempts to click on a link which contains the domain name {\it globalresearch.ca}.
+Right Panel: account suspension message of $@CRG$\_$CRM$ linked to {\it globalresearch.ca}.
 }

### 2021-07-21 article/draft.tex
updates

@@
 YouTube may provide an information panel for videos with topics that are prone to misinformation like COVID-19, moon landing, and climate change.
-Information panels provide ressources concerning a potentially controversial topic from independent third party partners or authoritative ressources.
+Information panels provide ressources concerning a potentially controversial topic from independent third parties or authoritative ressources.
 YouTube states that these panels exist regardless of the point of view expressed in a given video.
@@
 
+\smallskip
+
 To further study the assignment of information panels to videos, we compiled a list of $171$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information.
 We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page.
-Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about COVID-19, Vaccines, Climate change and US elections.
+Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about Climate change, COVID-19 Vaccine, COVID-19 and US elections.\footnote{See: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{youtube.com/watch?v=8PAwc8nlE\_Q}.
+Last accessed on  21/07/2021.
+}
+%\footnote{The links of the YouTube videos where the information panel appeared are the following: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE_Q}{youtube.com/watch?v=8PAwc8nlE_Q}.
+}
 
@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/youtube_panels/yt_2.png} 
+		\includegraphics[scale=0.29]{./img/youtube_panels/yt_2.png} 
 	%\end{multicols}
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/youtube_panels/yt_3.png}
+		\includegraphics[scale=0.294]{./img/youtube_panels/yt_3.png}
 	%\end{multicols}
@@
 	%\end{multicols}
-	\caption{Examples of YouTube information panels displayed under some videos.}
+	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}.
+}
 	\label{fig9}
 \end{figure}
+%Nevertheless, we noticed that duplicates of the same YouTube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
 
-We classified the list of YouTube videos by topic based on its content as shown in table \ref{tab2}.
+We classified the list of $171$ YouTube videos by topic based on its content as shown in table \ref{tab2}.
 We recorded the number of videos containing an information panel within each category.
-For COVID-19 and vaccine related videos more than half of the videos contained an information panel.
-Nevertheless, we noticed that duplicates of the same YouTube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
-In addition, we noticed for COVID-19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID-19, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either.
+For COVID-19 and COVID-19 vaccine related videos, more than half of the videos contained an information panel.
+Nevertheless we noticed that among a set of duplicates of the exact same YouTube video uploaded with different video titles, some contained an information panel while others did not (see figure \ref{duplicates_yt}).
+In addition, we noticed for COVID-19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID-19, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C O V I D 19 or Cv19) it wouldn’t include a panel either.
 Therefore, we suspect that YouTube is automatically adding panels to the videos based on the video title and not the content of the video.
+
+\begin{figure}[h]
+	\centering
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/graph_no_banner.png} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/news_without_banner_2.png} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/graph_with_banner.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/news_with_banner.png} 
+	%\end{multicols}
+	\caption{Screenshots taken on July 21, 2021.
+The screenshots show two duplicates of the same YouTube video uploaded under different titles.
+Left panel: contains no information panel.
+Right panel: contains an information panel.
+}
+	\label{duplicates_yt}
+\end{figure}
 
@@
 Therefore, it is likely that YouTube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID-19, flat earth and vaccine.
+
 %drop last colum
@@
 Category       & \begin{tabular}[c]{@{}c@{}}Number of YouTube videos {\bf with} an \\ information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of YouTube videos {\bf without} an \\ information panel\end{tabular}    \\ \hline
+
+\begin{tabular}[c]{@{}c@{}}  Climate change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
+%
+COVID-19 Vaccine        & \begin{tabular}[c]{@{}c@{}} 21     \\ (75\%) \end{tabular}   & \begin{tabular}[c]{@{}c@{}}  7 \\ (25\%)  \end{tabular}     \\ \hline
+%
+COVID-19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
+%
 \begin{tabular}[c]{@{}c@{}} General Health \end{tabular} & \begin{tabular}[c]{@{}c@{}} 0  \\ (0\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 11 \\ (100\%) \end{tabular}         \\ \hline
-Vaccine        & \begin{tabular}[c]{@{}c@{}} 21     \\ (75\%) \end{tabular}   & \begin{tabular}[c]{@{}c@{}}  7 \\ (25\%)  \end{tabular}     \\ \hline
-COVID-19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
-\begin{tabular}[c]{@{}c@{}}  Climate change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
 \end{tabular}

### 2021-07-21 article/draft.tex
typo

@@
 Section $230$ in the United States Communications Decency Act provides immunity for website platforms against the content created by users.
-Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for Mainstream Social Media Platforms, such as Facebook, Twitter or YouTube, to moderate the available content.
+Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for mainstream social media platforms, such as Facebook, Twitter or YouTube, to moderate the available content.
 In particular, platforms take explicit actions when content is in violation of local laws in different jurisdictions, such as laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws.
@@
 
-During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}).
+During the COVID-19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}).
 Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc.

### 2021-07-21 article/draft.tex
add the data mining part and change a bit the last part of the intro

@@
 
-\begin{table}[]
+Nevertheless, misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g.
+academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports.
+This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community.
+Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information.
+We do so by providing a series of examples for different interventions and platforms.
+We chose to focus on three platforms: Facebook, Twitter and YouTube.
+Both Facebook and YouTube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}.
+To collect data from these three platforms, we either used the APIs (Application Programming Interfaces), or web scraping (i.e.
+retro-engineering the HMTL code of a web page to extract meaningful data, see Table \ref{tab1} for a summary).
+Minet, a webmining tool developed by the médialab \cite{minet}, was often used, and we scripted our own data mining code when it was necessary.
+
+\begin{table}[h]
 \centering
@@
 &  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
- \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} and  \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}
+ \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} and  \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{Code created for this article}
 \\ \hline
  \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
- \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
+ \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API V3}      &                                                                                                                            \multicolumn{1}{l|}{Code created for this article}                                                                                                                                                                           \\ \hline
 \end{tabular}
@@
 
-Nevertheless, misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g.
-academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports.
-This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community.
-Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information.
-We do so by providing a series of examples for different interventions and platforms.
-We only focus on three platforms: Facebook, Twitter and YouTube.
-Both Facebook and YouTube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}.
-More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited mainstream platforms, Facebook, Twitter and YouTube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
+\smallskip
+
+In this article, we survey a number of common policies against misinformation used by Facebook, Twitter and YouTube, that we seperated in three broad categories: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
+Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
+
+\smallskip
+
 We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.
@@
 
- We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and YouTube, that we use in multiple examples throughout the present article.
 We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
-Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
 %the announced policy for a specific user was implemented or not.

### 2021-07-21 article/draft.tex
put a part of the intro in discussion
remove two small parts of intro

@@
 Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
-In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
 This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
@@
 
+% In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
+
 \smallskip
@@
 The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
-Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
+%Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
 It is explained via a blog post on the facebook Newsroom.
@@
 
-We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.
-We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
-For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
-
-\smallskip
-
 We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
-%the announced policy for a specific user was implemented or not.
-
-%Second, we provide simple means to check how those policies are implemented in practice and discuss how to assess their impact, when possible.
-
-%We do not aim for an exhaustive list of methods on how to investigate the platforms’ policies against misinformation, but rather to share the methods we currently know, and that we think can be useful to researchers or journalists interested in that question.
-We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.
 
@@
 
+	\item We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies, as other APIs and some databases could be useful for that matter.
+We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
+For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
+
 	\item For a previous research project (add reference to the article) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.

### 2021-07-21 article/draft.tex
minor changes

@@
 In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines (as of July 2021).
-The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''.
+The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report}''.
 %Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
@@
 
-Nevertheless, misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g.
+Misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g.
 academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports.
@@
 In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning.
+
+\smallskip
+
 To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two YouTube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
+The website of One America News Network has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/}.}  Tony Heller posts regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}} Both are active on YouTube and both have communicated via their Twitter account about restrictions applied by YouTube over their content (see figure \ref{fig2_oann}).
 
@@
 	%\end{multicols}
-
 	\caption{Left Panel: Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
@@
 
-%\smallskip
+\smallskip
 
-First, we investigate the temporary suspension case of the YouTube channel of {\it One America News channel}.
-This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID-19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the YouTube API v3, between November 2020 and January 2021.
-For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
+First, we investigate the temporary suspension of the YouTube channel of {\it One America News channel}.
+This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID-19 according to the News outlet NBCnews (2020)~\cite{nbcnews}.
+We collected the activity of the channel OANN (video counts, view counts) using  the YouTube API v3, between November $2020$ and January $2021$.
+For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June $2021$.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
 
@@
 
-\smallskip
-
-Surprisingly only $11$ posts out of the remaining $17$ had a ‘False information’ flag  (Table \ref{tab_flags_fb}, see left panel of Figure \ref{fb_flags} for an example).
-We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples).
-As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user is thus able to share a False link on Facebook without the ‘False information’ banner if the link is not expanded.
-
 \begin{table}[h]
@@
 \end{table}
+
+\smallskip
+
+Surprisingly only $11$ posts out of the remaining $17$ had a ‘False information’ flag  (Table \ref{tab_flags_fb}, see left panel of Figure \ref{fb_flags} for an example).
+We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples).
+As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user is thus able to share a False link on Facebook without the ‘False information’ banner if the link is not expanded.
+
+\smallskip
 
@@
 We find that only $9344$ ($2.97\%$) tweets out of $323$ $938$ containing a link marked as False, have an interstitial {\it potentially sensitive content}.
-To check whether the interstitial {\it potentially sensitive content} is automated or not, we pick out one tweet having shared a link marked as False\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.}, which also contains the interstitial {\it potentially sensitive content}.
+To check whether the interstitial {\it potentially sensitive content} is automated or not, we pick out one tweet having shared a link marked as False\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.}, which also contains the interstitial {\it potentially sensitive content} (see figure \ref{fig_notice}).
 Then we look in the set of $323$ $938$ tweets for other tweets who have shared the exact same link.
@@
 For COVID-19 and COVID-19 vaccine related videos, more than half of the videos contained an information panel.
-Nevertheless we noticed that among a set of duplicates of the exact same YouTube video uploaded with different video titles, some contained an information panel while others did not (see figure \ref{duplicates_yt}).
+Nevertheless we noticed that among a set of duplicates of the exact same YouTube video uploaded with different video titles, some contained an information panel while others did not (see figure \ref{duplicates_yt} for an example).
 In addition, we noticed for COVID-19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID-19, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C O V I D 19 or Cv19) it wouldn’t include a panel either.
@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/graph_no_banner.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/news_without_banner_2.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.2]{./img/youtube_panels/graph_with_banner.png} 
@@
 	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/graph_no_banner.png} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.2]{./img/youtube_panels/news_without_banner.png} 
+	%\end{multicols}
 	\caption{Screenshots taken on July 21, 2021.
 The screenshots show two duplicates of the same YouTube video uploaded under different titles.
-Left panel: contains no information panel.
-Right panel: contains an information panel.
+Top panels: a YouTube video about COVID-19 which contains an information panel, see \href{https://www.youtube.com/watch?v=d9GbVZOcT18}{https://www.youtube.com/watch?v=d9GbVZOcT18}.
+Bottom panels: a duplicate of the YouTube video in the top panels uploaded under a different title and it does not contain an information panel, see \href{https://www.youtube.com/watch?v=A4RvrEKoNxc}{https://www.youtube.com/watch?v=A4RvrEKoNxc}.
 }
@@
 
-For climate change we found that most of the videos (13 out of 18) did not display an information panel.
+For climate change we found that most of the videos ($13$ out of $18$) did not display an information panel.
 Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID-19 but contained misinformation concerning cures for cancer, abortion, and viruses.
 Therefore, it is likely that YouTube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID-19, flat earth and vaccine.
+It appears as if YouTube is focusing its efforts on the current ``hot'' topics with a wide public impact (elections, COVID), leaving room for misinformation to spread concerning other topics.
 

### 2021-07-21 article/draft.tex
rewrite and reduce a bit the Fb reduce section

@@
 
-%Another measure that mainstream social media platforms can apply is to prevent users from sharing specific types of content, in this example URLs coming from a specific domain name.
+%
 
@@
 
-Mainstream Social Media platforms can reduce the visibility of the content created or shared by specific users, whenever they violate the platforms' rules.
+Mainstream social media platforms can reduce the visibility of the content created or shared by specific users, whenever they violate the platforms' rules.
 The implementation of this policy varies across platforms and is not easy to verify ex-post.
@@
 
-%phrase pas accès au reach, mais seulement les engagement metrics
 % Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.},
@@
 Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news and it has several failed fact-checks reported by Feedback.org.\footnote{See the Iffy.news page \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/} and Feedback.org \href{https://open.feedback.org/media/RM}{https://open.feedback.org/media/RM}.}
+
+On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See the article in Wired by Martineau (2020)~\cite{wiredalexjones} and see the section {\it So what happened with InfoWars?
+They were up on Friday and now they are down?} \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.}
 
@@
 
-On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See the article in Wired by Martineau (2020)~\cite{wiredalexjones} and see the section {\it So what happened with InfoWars?
-They were up on Friday and now they are down?} \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}.
 The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel).
@@
 
-\begin{figure}[h]
-	\centering
-
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
-	%\end{multicols}
-
-	\caption{Facebook engagement metrics (average number of reactions, shares and comments per article) for the Infowars articles published in $2019-2020$ and gathered from the Buzzsumo API.
-The red line marks the date of May $2$, $2019$, when Facebook has announced the ban regarding Infowars.}
-	\label{infowars2}
-\end{figure}
-
-As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset.
+%As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset.
 We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.
 %\footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.}
-We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
+%We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
 An increase in engagement was also observed in $2020$.
@@
 
-We found irregularities in the number of Infowars articles collected from Buzzsumo.
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
+%	\caption{Facebook engagement metrics (average number of reactions, shares and comments per article) %for the Infowars articles published in $2019-2020$ and gathered from the Buzzsumo API.
+The red line marks %the date of May $2$, $2019$, when Facebook has announced the ban regarding Infowars.}
+%	\label{infowars2}
+%\end{figure}
+
+%We found irregularities in the number of Infowars articles collected from Buzzsumo.
 While Infowars usually publishes around 800 articles per month, only 53 articles were collected between June 11 to July 11, 2020\footnote{In Figure \ref{infowars2} the engagement metrics were only shown for days in which at least 5 Infowars articles were collected from Buzzsumo, to ensure reliable results.}.
@@
 
-\subsubsection{Facebook}
+Another measure that platforms can apply is to prevent users from sharing specific types of content, in this example URLs coming from a specific domain name.
+The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that {\it The BL is now banned from Facebook} for coordinated inauthentic behavior (see Facebook Newsroom (2019)~\cite{newsroom1}), which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
+Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested, according to the fact-checking organization Snopes which had reported about The BL’s activity to Facebook\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}}.
 
-The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that {\it The BL is now banned from Facebook} for coordinated inauthentic behavior (see Facebook Newsroom (2019)~\cite{newsroom1}), which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
-Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested, according to the fact-checking organization Snopes which had reported about The BL’s activity to Facebook and other various public articles\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}}.
+To verify Facebook’s ban of The BL domain name, we first tested whether we could post a Facebook message containing a url from thebl.com.
+This turned out to be impossible.
+But such manual verification cannot inform us whether the ban applies indeed to all Facebook users and accounts (as we used only our own personal accounts), nor when it has started.
+To further investigate this policy, we collected data from the Buzzsumo API\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.}.
+We used the ``/search/articles'' endpoint to collect the engagement metrics of the $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.
 
@@
 
-To verify Facebook’s ban of The BL domain name, we first tested whether we could post a Facebook message containing a url from thebl.com.
-This turned out to be impossible.
-But such manual verification cannot inform us whether the ban applies indeed to all Facebook users and accounts (as we used only our own personal accounts), nor when it has started.
-To further investigate this policy, we collected data from the Buzzsumo API\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.}.
-We used the ``/search/articles'' endpoint to collect the engagement metrics of the $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.%\footnote{The command can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}.}
-
 The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban.
 We can note that although the ban was communicated in an article~\cite{newsroom1} published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
-
 The communication around the ban appeared to have discouraged The Beauty of Life to proceed with their activity.
 Indeed the number of articles they published daily was around $50$ until December $20$, $2019$, when it decreased drastically to reach around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).
-Using Buzzsumo data, we ascertained that links from thebl.com were not shared on Facebook anymore.
-The ban started on December $1$, $2019$, and appeared to be still enforced in June 2021.
+
+Using Buzzsumo data, we ascertained that links from thebl.com were not shared on Facebook anymore. The ban started on December $1$, $2019$, and appeared to be still enforced in June 2021.
 

### 2021-07-22 code/collect_facebook_buzzsumo_infowars_data.py
utils -> utils_buzzsumo

@@ -3,7 +3,7 @@ from datetime import date
 
 from dotenv import load_dotenv
 
-from utils import collect_buzzsumo_data_for_one_domain
+from utils_buzzsumo import collect_buzzsumo_data_for_one_domain
 
 
 if __name__=="__main__":

### 2021-07-22 article/draft.tex
ignored uneeded files

@@
 Furthermore, mainstream platforms are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated.
-Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see table \ref{summary} in Appendix \ref{links}).
+Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see Appendix \ref{links} for references).
 While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation.
@@
 Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}).
-As for YouTube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see table \ref{summary} in Appendix \ref{links}).
+As for YouTube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see Appendix \ref{links} for references).
 
@@
 
-During the COVID-19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}).
+During the COVID-19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see Appendix \ref{links} for references).
 Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
@@
 \multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
-with no flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check and an \\  information flags\end{tabular} \\ \hline
+without a flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check and an \\  information flags\end{tabular} \\ \hline
 0            & 7                        & 4                      & 7                                                                                     \\ \hline
@@
 	%\end{multicols}
-	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}.
+	\caption{Screenshots taken on July 21, 2021.
+Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}.
 }

### 2021-07-22 code/collect_twitter_lifesitenews_data.py
code to collect twitter data

@@ -1,0 +1,20 @@
+import os
+from datetime import date
+from dotenv import load_dotenv
+from utils_twitter import collect_twitter_data
+from utils_twitter import tic
+from utils_twitter import toc
+
+tic()
+
+if __name__=="__main__":
+
+    load_dotenv()
+    collect_twitter_data(
+        query = 'from:LifeSite',
+        start_time = '2018-12-31T23:00:00Z',
+        end_time = '2021-07-01T23%3A59%3A59Z',
+        bearer_token= os.getenv('TWITTER_TOKEN'),
+        filename = os.path.join('.', 'data', 'twitter_lifesitenews_' + str(date.today()) + '.csv'),
+    )
+    toc()

### 2021-07-22 code/utils_twitter.py

@@ -1,0 +1,286 @@
+#from __future__ import absolute_import
+
+import requests
+import csv
+#import dotenv
+import time
+import json
+import os
+import os.path
+
+from csv import writer
+#from dotenv import load_dotenv
+from time import sleep
+
+#documentation: https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all
+#max_results: A number between 10 and the system limit (currently 500). By default, a request response will return 10 results.
+#300 requests per 15-minute window (app auth)
+#Updates: max results is now 100
+
+
+def connect_to_endpoint(bearer_token, query, start_time, end_time, next_token=None):
+
+    max_results=100
+
+    headers = {"Authorization": "Bearer {}".format(bearer_token)}
+
+    params = {"tweet.fields" : "in_reply_to_user_id,author_id,context_annotations,created_at,public_metrics,entities,geo,id,possibly_sensitive,lang,referenced_tweets", "user.fields":"username,name,description,location,created_at,entities,public_metrics","expansions":"author_id,referenced_tweets.id"}
+
+    if (next_token is not None):
+        url = "https://api.twitter.com/2/tweets/search/all?max_results={}&query={}&start_time={}&end_time={}&next_token={}".format(max_results, query, start_time, end_time, next_token)
+    else:
+        url = "https://api.twitter.com/2/tweets/search/all?max_results={}&start_time={}&end_time={}&query={}".format(max_results, start_time, end_time, query)
+
+    with requests.request("GET", url, params=params, headers=headers) as response:
+
+        if response.status_code != 200:
+            raise Exception(response.status_code, response.text)
+
+        return response.json()
+
+
+def write_results(json_response, filename):
+
+    with open(filename, "a+") as tweet_file:
+
+        writer = csv.DictWriter(tweet_file,
+                                ["type_of_tweet",
+                                 "id", "author_id",
+                                 "username",
+                                 "name",
+                                 "created_at",
+                                 "text",
+                                 "possibly_sensitive",
+                                 "in_reply_to_user_id",
+                                 "mentions_username",
+                                 "retweet_count",
+                                 "reply_count",
+                                 "like_count",
+                                 "lang",
+                                 "expanded_urls",
+                                 "theme",
+                                 "theme_description",
+                                 "user_created_at",
+                                 "user_profile_description",
+                                 "user_location",
+                                 "user_expanded_url",
+                                 "followers_count",
+                                 "following_count",
[…]

### 2021-07-23 article/draft.tex
I made some minor changes to the introduction

@@
 Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
+In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
 This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
@@
 Both Facebook and YouTube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}.
-To collect data from these three platforms, we either used the APIs (Application Programming Interfaces), or web scraping (i.e.
-retro-engineering the HMTL code of a web page to extract meaningful data, see Table \ref{tab1} for a summary).
-Minet, a webmining tool developed by the médialab \cite{minet}, was often used, and we scripted our own data mining code when it was necessary.
+To collect data from these three platforms, we either used the APIs (Application Programming Interfaces), or web scraping, i.e.
+retro-engineering the HMTL code of a web page to extract meaningful data, see Table \ref{tab1} for a summary.
+Minet \cite{minet}, a webmining tool developed by the Médialab SciencesPo, was often used, and we scripted our own data mining code when it was necessary.
 
@@
 
-In this article, we survey a number of common policies against misinformation used by Facebook, Twitter and YouTube, that we seperated in three broad categories: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices.
+More specifically, we survey in this article a number of common policies against misinformation used by Facebook, Twitter and YouTube.
+We classified those common policies into three broad categories: $(i)$ temporary or permanent suspension of users, $(ii)$ introducing flags and notices, and $(iii)$ reducing the visibility of some content.
+We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
+Furthermore, the examples provided to illustrate how to monitor a given policies were picked out of a list of domain names with several failed fact-checks.
+To be more precise, some domain names with failed fact-checks were picked because a given platform communicated about an intervention or because an intervention (e.g.
+suspension) was announced on the social media accounts linked to a given domain name.
 Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
@@
 \smallskip
-
-We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
 

### 2021-07-23 article/draft.tex
typos in intro

@@
 \end{tabular}
-\caption{Data collection}
+\caption{Summary of ressources used for data collection.}
 \label{tab1}
@@
 We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
-Furthermore, the examples provided to illustrate how to monitor a given policies were picked out of a list of domain names with several failed fact-checks.
+Furthermore, the examples provided to illustrate how to monitor a given policy were picked out of a list of domain names with several failed fact-checks.
 To be more precise, some domain names with failed fact-checks were picked because a given platform communicated about an intervention or because an intervention (e.g.

### 2021-07-23 article/draft.tex
added the code to collect twitter data for the domain name lifesitenews

@@
 
-Title proposition 3: Misinformation Policies of Mainstream Social Media Platforms: third-party verification methods and illustration
+Title proposition 3: Misinformation Policies of Mainstream Social Media Platforms: third-party monitoring, methods and illustration.
 
@@
 \\ \hline
- \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
- \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API V3}      &                                                                                                                            \multicolumn{1}{l|}{Code created for this article}                                                                                                                                                                           \\ \hline
+ \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API v2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
+ \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API v3}      &                                                                                                                            \multicolumn{1}{l|}{Code created for this article}                                                                                                                                                                           \\ \hline
 \end{tabular}

### 2021-07-23 code/collect_twitter_lifesitenews_domain_data.py

@@ -1,0 +1,22 @@
+import os
+from datetime import date
+from dotenv import load_dotenv
+from utils_twitter import collect_twitter_data
+from utils_twitter import tic
+from utils_twitter import toc
+
+tic()
+
+#collect tweets that share lifesitenews.com domain name
+
+if __name__=="__main__":
+
+    load_dotenv()
+    collect_twitter_data(
+        query = 'lifesitenews.com',
+        start_time = '2018-12-31T23:00:00Z',
+        end_time = '2021-07-01T23%3A59%3A59Z',
+        bearer_token= os.getenv('TWITTER_TOKEN'),
+        filename = os.path.join('.', 'data', 'twitter_lifesitenews_domain_name_' + str(date.today()) + '.csv'),
+    )
+    toc()

### 2021-07-23 code/collect_twitter_globalresearch_domain_data.py
code to collect twtter data of the domain name globalresearch.ca

@@ -1,0 +1,22 @@
+import os
+from datetime import date
+from dotenv import load_dotenv
+from utils_twitter import collect_twitter_data
+from utils_twitter import tic
+from utils_twitter import toc
+
+tic()
+
+#collect tweets that share globalresearch.ca domain name
+
+if __name__=="__main__":
+
+    load_dotenv()
+    collect_twitter_data(
+        query = 'globalresearch.ca',
+        start_time = '2020-12-31T23:00:00Z',
+        end_time = '2021-07-01T23%3A59%3A59Z',
+        bearer_token= os.getenv('TWITTER_TOKEN'),
+        filename = os.path.join('.', 'data', 'twitter_globalresearch_domain_name_' + str(date.today()) + '.csv'),
+    )
+    toc()

### 2021-07-23 code/create_figures.py
updated the figures function

@@ -4,6 +4,7 @@ from datetime import datetime, timedelta, date
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches #new addition to create the boxes in the legend for the shaded areas
 import ural
 
 
@@ -12,6 +13,9 @@ def import_data(file_name):
     df = pd.read_csv(data_path, low_memory=False)
     return df
 
+#note by shaden for Héloïse: I suggest for this function to use:
+# df = pd.concat([pd.read_csv(f) for f in glob.glob('./somefilename_*.csv')], ignore_index = True)
+# because when we recollect the dates will change, like this in our function we can put lifesite_*.csv for example
 
 def save_figure(figure_name):
     figure_path = os.path.join('.', 'figure', figure_name)
@@ -32,7 +36,7 @@ def arrange_plot(ax, df):
         ['2019', '2020', '2021'], fontsize='large'
     )
     ax.xaxis.set_tick_params(length=0)
-    plt.axvspan(np.datetime64('2020-01-01'), np.datetime64('2020-12-31'), 
+    plt.axvspan(np.datetime64('2020-01-01'), np.datetime64('2020-12-31'),
                 ymin=0, ymax=200000, facecolor='k', alpha=0.05)
     plt.xlim(np.min(df['date']), np.max(df['date']))
 
@@ -46,7 +50,7 @@ def create_facebook_trump_figure():
     df['date'] = pd.to_datetime(df['date'])
     serie_to_plot = df.resample('D', on='date')['date'].agg('count')
     serie_to_plot = serie_to_plot.append(pd.Series(
-        [0, 0], 
+        [0, 0],
         index=[pd.Timestamp(2021, 1, 7), pd.Timestamp(2021, 6, 15)]
     ))
 
@@ -58,7 +62,7 @@ def create_facebook_trump_figure():
     arrange_plot(ax, df)
     plt.axvline(np.datetime64("2021-01-07"), color='C3', linestyle='--')
     plt.xlim(
-        np.datetime64(datetime.strptime('2019-12-31', '%Y-%m-%d')), 
+        np.datetime64(datetime.strptime('2019-12-31', '%Y-%m-%d')),
         np.datetime64(datetime.strptime('2021-06-15', '%Y-%m-%d'))
     )
     plt.ylim(-.3, 55)
@@ -146,7 +150,7 @@ def create_facebook_crowdtangle_infowars_figure():
[…]

### 2021-07-23 article/draft.tex
updates to code create_figures to include twitter lifesite

@@
 
-{\color{pink} What about something about recommendations ? authoritative content  }
+{\color{pink}
+
+Youtube recommends content to the users based on the watch history and searchers they do in google and youtube.
+It is possible for the user to change the recommendation based on his preferences by removing videos from his history or by pausing the watch history.
+This type of system can influence what a user gets recommended in a negative way especially if the user is constantly watching misleading videos or conspiracy theory type of videos.
+Youtube says that they set out to prevent their systems from serving up content that could misinform users in a harmful way, particularly in domains that rely on veracity, such as science, medicine, news, or historical events.
+The way that youtube determines misinformation is by using external human evaluators and experts to examine if the video is promoting misleading information or conspiracy theories.
+Then using the feedback of the evaluators, they use machine learning systems to develop models that generate recommendations.
+The models work on reviewing videos daily to reduce the spread of misinformation.
+
+\smallskip
+
+To examine this effect, we designed an experiment that simulates user behavior in youtube using selenium library and python.
+The experiment starts with one misleading video identified by fact checkers and a clean watch history.
+Then the system collects the recommendation for this video and clicks on the top 10 recommendations in sequential order and collects their recommendations.
+The experiment is repeated for 65 misleading videos.
+In addition, to copy the user behavior, the system watches the videos for a couple of minutes to half of it.
+After the data collection, a fact checker examined the top 80 recommended videos (Videos that have been recommended many times during the experiment).
+The results showed little misinformation (less than 10\%) in the top recommendations.
+Therefore, this can be the result of youtube reducing the visibility of videos with misinformation or there is little misinformation in youtube or the experiment setup didn’t influence the recommendation engine behavior since we start with only one misleading video every time.
+
+}
 

### 2021-07-23 code/create_figures.py

@@ -1,6 +1,7 @@
 import os
 from datetime import datetime, timedelta, date
 
+import datetime
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
@@ -321,6 +322,7 @@ def plot_video_count_youtube(data, date_begin_sus, date_end_sus, date_begin_grap
 
 
 def create_youtube_graph():
+
     oann, tony_heller = preprocess_youtube_data()
     plot_view_count_youtube(oann, '2020-11-25', '2020-12-01', date(2020, 11, 1), date(2021, 1, 1),
                             2680000,'OANN_views_yt.png')
@@ -331,9 +333,9 @@ def create_youtube_graph():
     plot_video_count_youtube(tony_heller, '2020-09-29', '2020-10-05', date(2020, 9, 1),
                              date(2020, 11, 15), 10,'Tony_Heller_videos_yt.png')
 
-def create_twitter_Lifesite_figure():
+def create_twitter_Lifesite_figure(filename, figure_name, title, zeros):
 
-    df = import_data('twitter_lifesitenews_2021-07-22.csv')
+    df = import_data(filename)
     df = df.drop_duplicates()
 
     df['type_of_tweet'] = df['type_of_tweet'].replace(np.nan, 'created_content')
@@ -341,10 +343,11 @@ def create_twitter_Lifesite_figure():
     df['date'] = pd.to_datetime(df['created_at']).dt.date
     df_volume = df.groupby(['date','type_of_tweet'], as_index=False).size()
 
[…]

### 2021-07-26 article/draft.tex
discussion section + code figures

@@
 
-\section{Flags, Notices and labels}
+\section{Flags, Notices and labels} \label{flags}
 
@@
 
-\subsection{YouTube}
+\subsection{YouTube} \label{youtube_panels}
 
@@
 
-\subsection{Facebook}
+\subsection{Facebook} \label{reduce_fb}
 
@@
 
-\subsection{Twitter}
+\subsection{Twitter}  \label{globalresearch}
 
@@
 
-{ \color{pink} 
-Sporadic points for the discussion, no structure yet.
-
-\begin{itemize}
-
-	\item We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies, as other APIs and some databases could be useful for that matter.
-We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
-For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
-
-	\item For a previous research project (add reference to the article) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
-We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
-This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.
-
-	\item To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
+In this article we have reviewed three broad categories of mainstream platforms' interventions to tackle misinformation: suspension of accounts, introduction of notices and flags and reducing the visibility of content.
+For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab} and to read the related article.
+We have provided a methodology that can be useful for third-party monitoring, which aims to investigate platforms' interventions regarding content.
+All the code needed to collect the data, create the figures and reproduce the study can be found on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}.
+Hence the academic community can easily implement and reproduce our methodology for the purposes of bringing to the society insights concerning the debate around misinformation.
+In the light of the present research, we discuss in this section data and policy related recommandations.
+
+%\smallskip
+
+\subsection{Data related recommendations}
+
+Mainstream platforms such as Facebook, Twitter and Youtube are increasingly working towards higher data transparency (see links that redirect to the respective transparency centers in Appendix \ref{links}).
+Yet the present research sheds light on the lack and the splintering of data, which impede the academic community from studying successfully online misinformation and assessing the impact of platforms' interventions regarding this phenomenon.
+Hence, few comments are in order regarding the lack of data, the lack of transparency regarding misinformation related interventions and the splintering of data.
+
+\smallskip
+
+{\bf Lack of data.} First, when Facebook, Twitter or YouTube intervene by suspending an account, a page or a channel, the data disappears.
+It can no longer be accessed via scrapping or via the available APIs for the purposes of scientific research.
+This hampers the investigation of how platforms moderate content.
+To further illustrate this point, in a related research project (see Thero and Vincent (2020)~\cite{therovincent}) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$.
+We selected $94$ Facebook pages corresponding to our criteria.
+We then tried to collect the posts on these pages in January $2021$.
+But we discovered that $11$ pages could no longer be found and that the related data had disappeared from the CrowdTangle API.
+Similarly, when a YouTube channel gets suspended or a YouTube video is deleted the data related to them is removed from the YouTube API.
+For instance, the original list of YouTube videos from table \ref{tab2} with failed fact-checks, had over $200$ YouTube videos available in March $2021$.
+However, by June $2021$, thirty videos had disappeared both from YouTube and the YouTube API for policy violation.
+
+\smallskip
+
+Aside from the lack of data availability due to account or channel suspensions, some essential metrics for the study of misinformation are not accessible via main APIs.
+In particular, the $reach$ of posts on Facebook cannot be recovered from the CrowdTangle API and researchers can only build proxies for this metric from the available data (see section \ref{reduce_fb} for an example).
+Furthermore, to the best of our knowledge, fields related to flags, notices, interstitials and information panels are not available on the APIs linked to Facebook, Twitter and YouTube.
+For the purposes of the present research we had to scrape this information (see section \ref{flags}).
+Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact.
+
+\smallskip
+
+{\bf Lack of transparency.} Second, mainstream platforms generally lack transparency regarding their misinformation related interventions.
+The broad lines of policies regarding misinformation are communicated via blog posts and are not typically part of the set of rules or community guidelines of mainstream platforms (see Appendix \ref{links}).
+For example, Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
+It is explained via a blog post on the facebook Newsroom.
+Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account.
+In a post on YouTube Official Blog, the platform explains its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
+Nevertheless, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube.
+To provide an example, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content.
+More precisely, the academic community can only be aware of interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets.
+For example, while conducting the present research, it was brought to our attention that during our study, the Twitter account related to the domain name $globalresearch.ca$ was suspended, yet there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).
+
+Finally, we are aware that full transparency regarding how misinformation related interventions are operated, can backfire, as the prospective aimed users might find means to circumvent the partly automated interventions.
+To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}).
+Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''.
+Hence, a balance is needed between fully transparent communication about misinformation related interventions so the users can know precisely, how the platforms are regulating their content, and not explicitly giving too much information which would allow the policies to be bypassed.
+
+		%To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
 But too much transparency on how the regulation policies are exactly implemented can actually backfire.
@@
 
+\smallskip
+
+{\bf Scattered data.} Third, to study online misinformation, researchers, NGOs and data journalists turn to multiple APIs besides the official ones managed by the mainstream platforms themselves (e.g.
+BuzzSumo).
+They do so, because multiple data sources can be complementary and no specific API has complete data.
+{\color{red} [to be drafted by HT...
+and cite the article ~\cite{api} about APIs].}
+
+%There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
+For example Newsguard, blablabla...
+In this tweet, we can see the interface of XXX being used in this study from a data journalist: \href{https://twitter.com/Shayan86/status/1394742784683298818/photo/2}{ex}
+
+%Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
+While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
+A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
+Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
+
+\subsection{Policy recommendations}
+
+{ \color{pink} 
+\bigskip
+
+\noindent * Brouillon / esquisse / organisation des bullet points: (N.B. the bullet point ${\color{green}\surd}$ means that the item/idea was used in the above paragraphs)
+
+\begin{itemize}
+
+\item[Idea 1:] Not an exhaustive list of interventions + brief summary of what we do.
+
+	\begin{itemize}
+
+	\item[${\color{green}\surd}$] We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies, as other APIs and some databases could be useful for that matter.
+We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
+For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
+
+	\item[${\color{green}\surd}$] We hope this paper can illustrate how the platforms policies can be verified.
+All the code needed to collect the data, and create the figures can be found on a public GitHub repo: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, so that other researchers and journalists can easily implement and reproduce our methodology for the purposes of bringing to the society insights concerning the debate around misinformation.
+
+	\end{itemize}
+
+\item[Idea 2:] Lack of data. Scattered data, indirect methods.
+
+	\begin{itemize}
+
+		\item[${\color{green}\surd}$] For a previous research project (add reference to the article) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
+We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
+This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.
+
+		\item[${\color{green}\surd}$] After a channel gets suspended or a video is deleted the data related to them is removed from the YouTube API.
+This is a problem that affected the study to investigate the suspension reasons or the removal.
+For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from YouTube because they contain content that is against the YouTube guidelines and their data got removed from the API.
+
+		\item[${\color{green}\surd}$] Pas accès au ``reach" !  ranking not available. Fb nous a donné certaines données (les données Condor) et dedans on a le nombre de clicks par exemple
+
+		\item[${\color{green}\surd}$] Researchers should be able to access the data of deleted accounts on the main platforms.
+
+		\item[${\color{green}\surd}$] Currently the flag or notice banners data is not present in the platforms’ API datasource, and this prevents researchers and journalists from easily investigating that matter.
+They have to use or build a scraper to access the data.
+
+		\item[${\color{green}\surd}$] Lack of transparency in the platforms’ communication that makes their policies harder to verify.
+
+		\item[${\color{green}\surd}$] To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
+But too much transparency on how the regulation policies are exactly implemented can actually backfire.
+For example YouTube is certainly applying an 'information' banner on all videos mentioning COVID-19 and related terms in their title.
+Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'.
+If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation.
+There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.
+
+		\item[${\color{green}\surd}$] Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook.
+Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
+It is explained via a blog post on the facebook Newsroom.
+Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account.
+In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
+
 		\item There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
@@
 In this tweet, we can see the interface of XXX being used in this study from a data journalist: \href{https://twitter.com/Shayan86/status/1394742784683298818/photo/2}{ex}
-
-	\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
-
-	\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+
-
-	\item Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook,
-
-	\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason. E.g. beauty of life, coordinated inauthentic behavior.
-
-\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
-
-	\item After a channel gets suspended or a video is deleted the data related to them is removed from the YouTube API.
-This is a problem that affected the study to investigate the suspension reasons or the removal.
-For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from YouTube because they contain content that is against the YouTube guidelines and their data got removed from the API.
-
-	\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies...
-
-	\item business model
-
-	\item Pas accès au ``reach" !  ranking not available. Fb nous a donné certaines données (les données Condor) et dedans on a le nombre de clicks par exemple
-
-	\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
-While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
-	\item Researchers should be able to access the data of deleted accounts on the main platforms.
-
-	\item Currently the flag or notice banners data is not present in the platforms’ API datasource, and this prevents researchers and journalists from easily investigating that matter.
-They have to use or build a scraper to access the data.
-
-	\item Lack of transparency in the platforms’ communication that makes their policies harder to verify.
 
@@
 
-	\item We hope this paper can illustrate how the platforms policies can be verified.
+	\end{itemize}
+
+\item[Idea 3:] Policies not specific to misinformation. New for smart design (recycling point) - New policy: coordination for informative notices, based on fact-checks.
+
+	\begin{itemize}
+
+		\item Networked public square / private companies / regulations...
+
+		\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
+
+		\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+
+
+		\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason.
+E.g.
+beauty of life, coordinated inauthentic behavior.
+\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
+
+		\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
+While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
+
+		\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model
+
+	\end{itemize}
+
+\end{itemize}
+}
+
+%\begin{itemize}
+
+	%\item We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies, as other APIs and some databases could be useful for that matter.
+We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
+For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
+
+	%\item For a previous research project (add reference to the article) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
+We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
+This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.
+
+	%\item To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
+But too much transparency on how the regulation policies are exactly implemented can actually backfire.
+For example YouTube is certainly applying an 'information' banner on all videos mentioning COVID-19 and related terms in their title.
+Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'.
+If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation.
+There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.
+
+	%\item There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
+For example Newsguard, blablabla...
+In this tweet, we can see the interface of XXX being used in this study from a data journalist: \href{https://twitter.com/Shayan86/status/1394742784683298818/photo/2}{ex}
+
+	%\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
+
+	%\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+
+
+	%\item Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook
+
+	%\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason.
+E.g.
+beauty of life, coordinated inauthentic behavior.
+\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
+
+	%\item After a channel gets suspended or a video is deleted the data related to them is removed from the YouTube API.
+This is a problem that affected the study to investigate the suspension reasons or the removal.
+For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from YouTube because they contain content that is against the YouTube guidelines and their data got removed from the API.
+
+	%\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model
+
+	%\item Pas accès au ``reach" !  ranking not available. Fb nous a donné certaines données (les données Condor) et dedans on a le nombre de clicks par exemple
+
+	%\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
+While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
+	%\item Researchers should be able to access the data of deleted accounts on the main platforms.
+
+	%\item Currently the flag or notice banners data is not present in the platforms’ API datasource, and this prevents researchers and journalists from easily investigating that matter.
+They have to use or build a scraper to access the data.
+
+	%\item Lack of transparency in the platforms’ communication that makes their policies harder to verify.
+
+	%\item Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
+While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
+A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
+Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
+
+	%\item We hope this paper can illustrate how the platforms policies can be verified.
 All the code needed to collect the data, and create the figures can be found on a public GitHub repo: https://github.com/medialab/truth-and-trust-online-2021/, so that other researchers and journalists can easily reuse our methodology.
-\end{itemize}
-}
+%\end{itemize}
 
@@
 
-\newpage
+%\newpage
 
@@
 \begin{landscape}
+
 \thispagestyle{empty}

### 2021-07-26 code/create_figures.py

@@ -15,8 +15,8 @@ def import_data(file_name):
     return df
 
 #note by shaden for Héloïse: I suggest for this function to use:
-# df = pd.concat([pd.read_csv(f) for f in glob.glob('./somefilename_*.csv')], ignore_index = True)
-# because when we recollect the dates will change, like this in our function we can put lifesite_*.csv for example
+# df = pd.concat([pd.read_csv(f) for f in glob.glob('./somefile_name_*.csv')], ignore_index = True)
+# because when we recollect the dates will change, like this in our function we can put facebook_crowdtangle_trump__*.csv for example
 
 def save_figure(figure_name):
     figure_path = os.path.join('.', 'figure', figure_name)

### 2021-07-26 article/draft.tex
section 5.1 in the discussion

@@
 
-Aside from the lack of data availability due to account or channel suspensions, some essential metrics for the study of misinformation are not accessible via main APIs.
+Aside from the lack of data due to account or channel suspensions, some essential metrics for the study of misinformation are not accessible via main APIs.
 In particular, the $reach$ of posts on Facebook cannot be recovered from the CrowdTangle API and researchers can only build proxies for this metric from the available data (see section \ref{reduce_fb} for an example).
-Furthermore, to the best of our knowledge, fields related to flags, notices, interstitials and information panels are not available on the APIs linked to Facebook, Twitter and YouTube.
+Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the APIs linked to Facebook, Twitter and YouTube.
 For the purposes of the present research we had to scrape this information (see section \ref{flags}).
@@
 More precisely, the academic community can only be aware of interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets.
-For example, while conducting the present research, it was brought to our attention that during our study, the Twitter account related to the domain name $globalresearch.ca$ was suspended, yet there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).
-
-Finally, we are aware that full transparency regarding how misinformation related interventions are operated, can backfire, as the prospective aimed users might find means to circumvent the partly automated interventions.
+For example, while conducting the present research, it was brought to our attention that during our study, the Twitter account related to the domain name $globalresearch.ca$ was suspended.
+Yet, there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).
+
+Finally, we are aware that full transparency regarding operational aspects of misinformation related interventions can backfire.
+This is because, the prospective aimed users might find means to circumvent the partly automated interventions.
 To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}).
 Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''.
-Hence, a balance is needed between fully transparent communication about misinformation related interventions so the users can know precisely, how the platforms are regulating their content, and not explicitly giving too much information which would allow the policies to be bypassed.
+Similarly, we came across  notational variants on Twitter of domain names with several failed fact-checks.
+To provide an example, Twitter users introduce  the following notational variants when sharing an article from the website\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}} {\it off-guardian.org}: {\it off-guardian.
+org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}.
+For the case of this domain name, we successfully managed to post a Tweet containing the domain name {\it off-guardian.org}, which we deleted after a few seconds.
+In other words, users can include in their Tweets links containing  {\it off-guardian.org} and only a warning message appears when a user clicks on the link.
+For this case, we failed to understand precisely what kind of intervention the users were circumventing.
+Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
 

### 2021-07-26 article/draft.tex
some typos in the discussion section

@@
 
+\smallskip
+
+{\color{pink} \noindent N.B: we will redo all the figures (to harmonize the legend, etc.) and the table of contents will be deleted.} 
 \tableofcontents
@@
 
-Finally, we are aware that full transparency regarding operational aspects of misinformation related interventions can backfire.
+We are aware that full transparency regarding operational aspects of misinformation related interventions can backfire.
 This is because, the prospective aimed users might find means to circumvent the partly automated interventions.
@@
 {\color{red} [to be drafted by HT...
-and cite the article ~\cite{api} about APIs].}
+and cite the article ~\cite{api} about APIs]....} we found irregularities in the number of Infowars articles collected from Buzzsumo.
+While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
+A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
+Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
 

### 2021-07-26 article/draft.tex
minor updates

@@
 Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
-In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines (as of July 2021).
 The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report}''.
+In particular, policies regarding misinformation are generally not part of the set of platform rules or community guidelines (as of July 2021).
 %Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
@@
 
+In this section, we further provide some policy recommendations. It is very likely that interventions used to tackle misinformation ...
+
+%what do i want to say ?
+
 { \color{pink} 
@@
 While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
+
+		\item YouTube page that says, misinformation falls under other categories existing in the guidelines.
 

### 2021-07-26 article/draft.tex
small changes after discussion with Shaden

@@
 
-In this article we have reviewed three broad categories of mainstream platforms' interventions to tackle misinformation: suspension of accounts, introduction of notices and flags and reducing the visibility of content.
-For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab} and to read the related article.
-We have provided a methodology that can be useful for third-party monitoring, which aims to investigate platforms' interventions regarding content.
-All the code needed to collect the data, create the figures and reproduce the study can be found on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}.
-Hence the academic community can easily implement and reproduce our methodology for the purposes of bringing to the society insights concerning the debate around misinformation.
+In this article we have assessed three broad categories of interventions to tackle misinformation by Facebook, Twitter and YouTube: suspension of accounts, introduction of notices and flags and reducing the visibility of content.
+We have provided a methodology that can be useful for third-party monitoring.
+The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, and we hope it can be useful to those working on addressing online misinformation.
 In the light of the present research, we discuss in this section data and policy related recommandations.
 
-%\smallskip
-
-\subsection{Data related recommendations}
+% For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab} and to read the related article.
+
+\smallskip
+
+%\subsection{Data related recommendations}
 
@@
 {\bf Lack of data.} First, when Facebook, Twitter or YouTube intervene by suspending an account, a page or a channel, the data disappears.
-It can no longer be accessed via scrapping or via the available APIs for the purposes of scientific research.
+It can no longer be accessed via scraping or via the official APIs (Twitter, YouTube, CrowdTangle) for the purposes of scientific research.
 This hampers the investigation of how platforms moderate content.
@@
 
-Aside from the lack of data due to account or channel suspensions, some essential metrics for the study of misinformation are not accessible via main APIs.
-In particular, the $reach$ of posts on Facebook cannot be recovered from the CrowdTangle API and researchers can only build proxies for this metric from the available data (see section \ref{reduce_fb} for an example).
-Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the APIs linked to Facebook, Twitter and YouTube.
-For the purposes of the present research we had to scrape this information (see section \ref{flags}).
-Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact.
+Aside from the lack of data due to suspensions, some essential metrics for the study of misinformation are not accessible via main APIs.
+In particular, the $reach$ of posts on Facebook {\color{red}(i.e.
+the number of people who actually see a given post)} cannot be recovered from the CrowdTangle API and researchers can only build proxies for this metric from the available data (see section \ref{reduce_fb} for an example).
+Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs (with the only exceptions of two types of interstitials in Twitter API).
+For the purposes of the present research we thus had to scrape this information from Facebook, Twitter and YouTube (see section \ref{flags}).
+Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact {\color{red} Misinformation review REF + others to show that we are not the only ones to say that}.
 
@@
 The broad lines of policies regarding misinformation are communicated via blog posts and are not typically part of the set of rules or community guidelines of mainstream platforms (see Appendix \ref{links}).
-For example, Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
+{\color{red} For example, Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
 It is explained via a blog post on the facebook Newsroom.
@@
 In a post on YouTube Official Blog, the platform explains its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
-Nevertheless, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube.
-To provide an example, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content.
+Nevertheless, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube.} To provide an example, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content.
 More precisely, the academic community can only be aware of interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets.
@@
 This is because, the prospective aimed users might find means to circumvent the partly automated interventions.
-To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}).
+{\color{red} To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}).
 Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''.
@@
 For the case of this domain name, we successfully managed to post a Tweet containing the domain name {\it off-guardian.org}, which we deleted after a few seconds.
-In other words, users can include in their Tweets links containing  {\it off-guardian.org} and only a warning message appears when a user clicks on the link.
-For this case, we failed to understand precisely what kind of intervention the users were circumventing.
+In other words, users can include in their Tweets links containing  {\it off-guardian.org} and only a warning message appears when a user clicks on the link.} For this case, we failed to understand precisely what kind of intervention the users were circumventing.
 Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
@@
 They do so, because multiple data sources can be complementary and no specific API has complete data.
-{\color{red} [to be drafted by HT...
-and cite the article ~\cite{api} about APIs]....} we found irregularities in the number of Infowars articles collected from Buzzsumo.
-While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
-A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
-Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
+{\color{red} vs.
+scraping.
+[to be drafted by HT...
+and cite the article ~\cite{api} about APIs]...., article du NYTimes sur CT, APIs qui ouvrent et qui ferment, limites de l'API de Twitter entre la V1 et la V2.}
 
@@
 
-%Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
-While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
-A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
-Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
-
-\subsection{Policy recommendations}
+{\bf Lack of coordination between platforms.}
+
+{\bf Policies recommandations.}
+
+\smallskip
+%\subsection{Policy recommendations}
 

### 2021-07-26 article/draft.tex
some updates in the discussion

@@
 We have provided a methodology that can be useful for third-party monitoring.
-The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, and we hope it can be useful to those working on addressing online misinformation.
+The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, and we hope it can be a useful ressource for those working on addressing online misinformation.
+
+% For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab} and to read the related article.
+
+\smallskip
+
+%\subsection{Data related recommendations}
+
 In the light of the present research, we discuss in this section data and policy related recommandations.
-
-% For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab} and to read the related article.
-
-\smallskip
-
-%\subsection{Data related recommendations}
-
 Mainstream platforms such as Facebook, Twitter and Youtube are increasingly working towards higher data transparency (see links that redirect to the respective transparency centers in Appendix \ref{links}).
 Yet the present research sheds light on the lack and the splintering of data, which impede the academic community from studying successfully online misinformation and assessing the impact of platforms' interventions regarding this phenomenon.
-Hence, few comments are in order regarding the lack of data, the lack of transparency regarding misinformation related interventions and the splintering of data.
+Hence, few comments are in order regarding the lack of data, the lack of transparency regarding misinformation related interventions, the splintering of data and the lack of interventions designed specifically for misinformation.
 
@@
 This hampers the investigation of how platforms moderate content.
-To further illustrate this point, in a related research project (see Thero and Vincent (2020)~\cite{therovincent}) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$.
-We selected $94$ Facebook pages corresponding to our criteria.
-We then tried to collect the posts on these pages in January $2021$.
-But we discovered that $11$ pages could no longer be found and that the related data had disappeared from the CrowdTangle API.
-Similarly, when a YouTube channel gets suspended or a YouTube video is deleted the data related to them is removed from the YouTube API.
-For instance, the original list of YouTube videos from table \ref{tab2} with failed fact-checks, had over $200$ YouTube videos available in March $2021$.
+To further illustrate this point, the original list of YouTube videos summarized in table \ref{tab2} with failed fact-checks, had over $200$ YouTube videos available in March $2021$.
 However, by June $2021$, thirty videos had disappeared both from YouTube and the YouTube API for policy violation.
+Similarly, in a related research project (see Thero and Vincent (2020)~\cite{therovincent}) we searched on CrowdTangle for $94$ public accounts sharing specific content associated with misinformation in November $2020$.
+We tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
 
@@
 Aside from the lack of data due to suspensions, some essential metrics for the study of misinformation are not accessible via main APIs.
-In particular, the $reach$ of posts on Facebook {\color{red}(i.e.
-the number of people who actually see a given post)} cannot be recovered from the CrowdTangle API and researchers can only build proxies for this metric from the available data (see section \ref{reduce_fb} for an example).
-Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs (with the only exceptions of two types of interstitials in Twitter API).
-For the purposes of the present research we thus had to scrape this information from Facebook, Twitter and YouTube (see section \ref{flags}).
-Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact {\color{red} Misinformation review REF + others to show that we are not the only ones to say that}.
-
+In particular, the $reach$ of posts on Facebook, which is the number of people who actually see a given post, cannot be recovered from the CrowdTangle API.
+Hence, researchers can only build proxies for this metric based on available data (see section \ref{reduce_fb} for an example).
+Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs; with the exception of the {\it withheld}  and {\it possibly sensitive content} interstitials in the Twitter API v2.
+For the purposes of the present research we thus had to scrape this information from Facebook, Twitter and YouTube.
+Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact.
+We refer the reader to the insightful commentary by Pasquetto, Swire-Thompson, Amazeen et al.
+(2020)~\cite{pasquetto} and the references therein, for a discussion on partial or biased social media data.
+
+%{\color{red} Misinformation review REF + others to show that we are not the only ones to say that}.
 \smallskip
@@
 The broad lines of policies regarding misinformation are communicated via blog posts and are not typically part of the set of rules or community guidelines of mainstream platforms (see Appendix \ref{links}).
-{\color{red} For example, Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
-It is explained via a blog post on the facebook Newsroom.
-Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account.
-In a post on YouTube Official Blog, the platform explains its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
-Nevertheless, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube.} To provide an example, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content.
-More precisely, the academic community can only be aware of interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets.
+Yet, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube.
+To illustrate, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content.
+More precisely, platforms' official communication about misinformation interventions is scarce and the academic community, NGOs and data journalists, usually discover interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets.
 For example, while conducting the present research, it was brought to our attention that during our study, the Twitter account related to the domain name $globalresearch.ca$ was suspended.
-Yet, there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).
+But, there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).
 
@@
 This is because, the prospective aimed users might find means to circumvent the partly automated interventions.
-{\color{red} To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}).
-Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''.
-Similarly, we came across  notational variants on Twitter of domain names with several failed fact-checks.
-To provide an example, Twitter users introduce  the following notational variants when sharing an article from the website\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}} {\it off-guardian.org}: {\it off-guardian.
-org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}.
-For the case of this domain name, we successfully managed to post a Tweet containing the domain name {\it off-guardian.org}, which we deleted after a few seconds.
-In other words, users can include in their Tweets links containing  {\it off-guardian.org} and only a warning message appears when a user clicks on the link.} For this case, we failed to understand precisely what kind of intervention the users were circumventing.
-Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
+We noticed that some YouTube channels are trying to avoid the likely automated COVID-19 information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''.
+Similarly, we came across notational variants on Twitter of the domain name {\it off-guardian.org}\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}}, such as {\it off-guardian.
+org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}.\footnote{For this case, we failed to understand precisely what kind of intervention Twitter users were circumventing, since they could share in a Tweet an article redirecting to the website {\it off-guardian.org} with the correct notation and only a warning message would appear when one clicks on it.} Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
 
@@
 They do so, because multiple data sources can be complementary and no specific API has complete data.
-{\color{red} vs.
-scraping.
-[to be drafted by HT...
-and cite the article ~\cite{api} about APIs]...., article du NYTimes sur CT, APIs qui ouvrent et qui ferment, limites de l'API de Twitter entre la V1 et la V2.}
+{\color{pink} To be drafted by HT:  vs.
+scraping, cite the article ~\cite{api} about APIs, article du NYTimes sur CT, APIs qui ouvrent et qui ferment, limites de l'API de Twitter entre la V1 et la V2.}
 
@@
 
-{\bf Lack of coordination between platforms.}
-
-{\bf Policies recommandations.}
-
-\smallskip
-%\subsection{Policy recommendations}
-
-In this section, we further provide some policy recommendations. It is very likely that interventions used to tackle misinformation ...
-
-%what do i want to say ?
+{\bf Lack of misinformation specific interventions.}
+
+\smallskip
 
@@
 
-\noindent * Brouillon / esquisse / organisation des bullet points: (N.B. the bullet point ${\color{green}\surd}$ means that the item/idea was used in the above paragraphs)
+%\noindent * Brouillon / esquisse / organisation des bullet points: (N.B. the bullet point ${\color{green}\surd}$ means that the item/idea was used in the above paragraphs)
 
@@
 
-\item[Idea 1:] Not an exhaustive list of interventions + brief summary of what we do.
-
-	\begin{itemize}
-
-	\item[${\color{green}\surd}$] We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies, as other APIs and some databases could be useful for that matter.
+%\item[Idea 1:] Not an exhaustive list of interventions + brief summary of what we do. 
+%	
+%	\begin{itemize}
+%
+%	\item[${\color{green}\surd}$] We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies, as other APIs and some databases could be useful for that matter.
 We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
 For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
-
-	\item[${\color{green}\surd}$] We hope this paper can illustrate how the platforms policies can be verified.
+%
+%	\item[${\color{green}\surd}$] We hope this paper can illustrate how the platforms policies can be verified.
 All the code needed to collect the data, and create the figures can be found on a public GitHub repo: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, so that other researchers and journalists can easily implement and reproduce our methodology for the purposes of bringing to the society insights concerning the debate around misinformation.
-
-	\end{itemize}
-
-\item[Idea 2:] Lack of data. Scattered data, indirect methods.
-
-	\begin{itemize}
-
-		\item[${\color{green}\surd}$] For a previous research project (add reference to the article) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
+%	
+%	\end{itemize}
+
+%\item[Idea 2:] Lack of data. Scattered data, indirect methods.  
+%	
+%	
+%	\begin{itemize}
+
+%		\item[${\color{green}\surd}$] For a previous research project (add reference to the article) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
 We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
 This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.
-
-		\item[${\color{green}\surd}$] After a channel gets suspended or a video is deleted the data related to them is removed from the YouTube API.
+%		
+%		\item[${\color{green}\surd}$] After a channel gets suspended or a video is deleted the data related to them is removed from the YouTube API.
 This is a problem that affected the study to investigate the suspension reasons or the removal.
 For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from YouTube because they contain content that is against the YouTube guidelines and their data got removed from the API.
-
-		\item[${\color{green}\surd}$] Pas accès au ``reach" !  ranking not available. Fb nous a donné certaines données (les données Condor) et dedans on a le nombre de clicks par exemple
-
-		\item[${\color{green}\surd}$] Researchers should be able to access the data of deleted accounts on the main platforms.
-
-		\item[${\color{green}\surd}$] Currently the flag or notice banners data is not present in the platforms’ API datasource, and this prevents researchers and journalists from easily investigating that matter.
+%		
+%		\item[${\color{green}\surd}$] Pas accès au ``reach" !  ranking not available. Fb nous a donné certaines données (les données Condor) et dedans on a le nombre de clicks par exemple
+%	
+%		
+%		\item[${\color{green}\surd}$] Researchers should be able to access the data of deleted accounts on the main platforms.
+%		
+%		\item[${\color{green}\surd}$] Currently the flag or notice banners data is not present in the platforms’ API datasource, and this prevents researchers and journalists from easily investigating that matter.
 They have to use or build a scraper to access the data.
-
-		\item[${\color{green}\surd}$] Lack of transparency in the platforms’ communication that makes their policies harder to verify.
-
-		\item[${\color{green}\surd}$] To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
+%		
+%		\item[${\color{green}\surd}$] Lack of transparency in the platforms’ communication that makes their policies harder to verify.
+%		
+%		\item[${\color{green}\surd}$] To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
 But too much transparency on how the regulation policies are exactly implemented can actually backfire.
@@
 There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.
-
-		\item[${\color{green}\surd}$] Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook.
+%		
+%		\item[${\color{green}\surd}$] Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook.
 Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
@@
 In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
-
-		\item There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
+%		
+%		\item There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
 For example Newsguard, blablabla...
 In this tweet, we can see the interface of XXX being used in this study from a data journalist: \href{https://twitter.com/Shayan86/status/1394742784683298818/photo/2}{ex}
-
-		\item Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
+%			
+%		\item Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
 While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
@@
 Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
-
-	\end{itemize}
+%	
+%	\end{itemize}
 

### 2021-07-26 article/draft.tex
updates to the figures function + linked tex figures to parent folder

@@
 		%\begin{multicols}{1}
-			\includegraphics[scale=0.3]{./img/fb/fig1_fb.png}
+			\includegraphics[scale=0.4]{../figure/facebook_crowdtangle_trump.png}
 		%\end{multicols}
@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
+		\includegraphics[scale=0.3]{../figure/lifesite.jpg} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.34]{./img/lifesite_rolling_7_lifesite.jpg}
 	%\end{multicols}
@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.27]{./img/oann/fig1_oann.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.26]{./img/oann/fig2_oann.png} 
+		\includegraphics[scale=0.27]{../figure/OANN_videos_yt.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.27]{../figure/OANN_views_yt.png} 
 	%\end{multicols}
@@
 		%\begin{multicols}{1}
-			\includegraphics[scale=0.35]{./img/tony/fig1_tony.png}
-		%\end{multicols}
-		%\begin{multicols}{1}
-			\includegraphics[scale=0.34]{./img/tony/fig2_tony.png}
+			\includegraphics[scale=0.26]{../figure/Tony_Heller_videos_yt.png}
+		%\end{multicols}
+		%\begin{multicols}{1}
+			\includegraphics[scale=0.26]{../figure/Tony_Heller_views_yt.png}
 		%\end{multicols}

### 2021-07-26 code/create_figures.py

@@ -14,10 +14,6 @@ def import_data(file_name):
     df = pd.read_csv(data_path, low_memory=False)
     return df
 
-#note by shaden for Héloïse: I suggest for this function to use:
-# df = pd.concat([pd.read_csv(f) for f in glob.glob('./somefile_name_*.csv')], ignore_index = True)
-# because when we recollect the dates will change, like this in our function we can put facebook_crowdtangle_trump__*.csv for example
-
 def save_figure(figure_name):
     figure_path = os.path.join('.', 'figure', figure_name)
     plt.savefig(figure_path)
@@ -341,48 +337,54 @@ def create_twitter_Lifesite_figure(filename, figure_name, title, zeros):
     df['type_of_tweet'] = df['type_of_tweet'].replace(np.nan, 'created_content')
     df['total_engagement'] = (df['retweet_count'] + df['like_count'] + df['reply_count'])
     df['date'] = pd.to_datetime(df['created_at']).dt.date
-    df_volume = df.groupby(['date','type_of_tweet'], as_index=False).size()
+    #df_volume = df.groupby(['date','type_of_tweet'], as_index=False).size()
+    df_volume = df.groupby(['date'], as_index=False).size()
 
     if zeros == 1 :
-        add_zeros = [{'date': datetime.date(2019, 12, 10), 'type_of_tweet': 'created_content', 'size': 0}, {'date': datetime.date(2019, 12, 10), 'type_of_tweet': 'replied_to', 'size': 0},{'date': datetime.date(2019, 12, 10), 'type_of_tweet': 'quoted', 'size': 0}, {'date': datetime.date(2019, 12, 10), 'type_of_tweet': 'retweeted', 'size': 0},{'date': datetime.date(2020, 10, 11), 'type_of_tweet': 'created_content', 'size': 0}, {'date': datetime.date(2020, 10, 11), 'type_of_tweet': 'replied_to', 'size': 0}, {'date': datetime.date(2020, 10, 11), 'type_of_tweet': 'quoted', 'size': 0}, {'date': datetime.date(2020, 10, 11), 'type_of_tweet': 'retweeted', 'size': 0}, {'date': datetime.date(2021, 1, 25), 'type_of_tweet': 'created_content', 'size': 0}, {'date': datetime.date(2021, 5, 15), 'type_of_tweet': 'created_content', 'size': 0}]
[…]

### 2021-07-27 code/check_flag_youtube.py
Update: check_flag_youtube.py

@@ -3,6 +3,8 @@ import time
 
 from selenium import webdriver
 from selenium.common.exceptions import NoSuchElementException
+from webdriver_manager.chrome import ChromeDriverManager
+
 
 
 def check_exists_by_xpath(xpath, driver):
@@ -15,9 +17,7 @@ def check_exists_by_xpath(xpath, driver):
 
 def information_panel(video_id):
     try:
-        # replace with your driver path
-        chrome_path = '/usr/local/bin/chromedriver'
-        driver = webdriver.Chrome(chrome_path)
+        driver = webdriver.Chrome(ChromeDriverManager().install())
         web = 'https://www.youtube.com/watch?v='+video_id
         driver.get(web)
         time.sleep(5)

### 2021-07-27 article/draft.tex
updates in discussion + twitter code

@@
 
-Misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g.
+Misinformation related interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g.
 academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports.
@@
 
-		%To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
-But too much transparency on how the regulation policies are exactly implemented can actually backfire.
-For example YouTube is certainly applying an 'information' banner on all videos mentioning COVID-19 and related terms in their title.
-Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'.
-If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation.
-There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.
-
 \smallskip
@@
 
-{\bf Lack of misinformation specific interventions.}
-
-\smallskip
+{\bf Lack of misinformation specific interventions.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas.
+To illustrate, YouTube explicitly states that: {\it Several policies in our Community Guidelines are directly applicable to misinformation}; such as deceptive practices, impersonation and hate speech policy.
+
+\smallskip
+
+% points to make ? argument ? en gros, interventions existaient dejà on les utilise pour la mesinformation, la mesinformation n'est pas officiellemtn
 

### 2021-07-27 code/collect_twitter_globalresearch_domain_data.py

@@ -13,9 +13,9 @@ if __name__=="__main__":
 
     load_dotenv()
     collect_twitter_data(
-        query = 'globalresearch.ca',
+        query = 'globalresearch.ca -is:retweet',
         start_time = '2020-12-31T23:00:00Z',
-        end_time = '2021-07-01T23%3A59%3A59Z',
+        end_time = '2021-06-30T23%3A59%3A59Z',
         bearer_token= os.getenv('TWITTER_TOKEN'),
         filename = os.path.join('.', 'data', 'twitter_globalresearch_domain_name_' + str(date.today()) + '.csv'),
     )

### 2021-07-27 code/utils_twitter.py

@@ -155,10 +155,10 @@ def write_results(json_response, filename):
                             if "location" in user.keys():
                                 tweet['user_location'] = user['location']
 
-                            if "entities" in user.keys():
-                                if "url" in user['entities']:
-                                    if "urls" in user['entities']['url']:
-                                        tweet['user_expanded_url']=user['entities']['url']['urls'][0]['expanded_url']
+                            #if "entities" in user.keys():
+                            #    if "url" in user['entities']:
+                            #        if "urls" in user['entities']['url']:
+                            #            tweet['user_expanded_url']=user['entities']['url']['urls'][0]['expanded_url']
 
                 writer.writerow(tweet)
 

### 2021-07-28 article/draft.tex
some comments in YT subsection about recommendations
updates - discussion

@@
 
+{\color{red} explain experiment + make it only about health and add exact number (e.g. 45 health videos, 10 545 recommendations) .}
+
 To examine this effect, we designed an experiment that simulates user behavior in youtube using selenium library and python.
@@
 
+\smallskip
+
+{\color{red} Channel level ! }
+
 }
@@
 
-{\bf Lack of misinformation specific interventions.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas.
-To illustrate, YouTube explicitly states that: {\it Several policies in our Community Guidelines are directly applicable to misinformation}; such as deceptive practices, impersonation and hate speech policy.
+{\bf Lack of misinformation specific interventions.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
+To illustrate, YouTube explicitly states\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.} that: {\it Several policies in our Community Guidelines are directly applicable to misinformation}; such as deceptive practices, impersonation and hate speech policy.
+Similarly, Facebook took down four pages related to InfoWars and cited as a reason the repeated violations of Community Standards and not false news.\footnote{An article published \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{on Facebook Newsroom (2018)} states that : ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
+While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this''.}
+
+Naturally, the design of an intervention by a given online platform in order to moderate content should be adapted to the aimed policy area.
+Therefor, $classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech.
+Nevertheless, tackling online misinformation is an active area of research and interventions specifically designed for this $new$ policy area, might be required to avoid undesired effects.
+Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation.
+We invite the reader to see Rogers (2020)~\cite{rogers2020} for an excellent overview about de-platforming and see Robins-Early (2019)~\cite{huffpost} for a news article about Alex Jones's account suspension on Facebook.
 
@@
 
-		\item Networked public square / private companies / regulations...
+		\item Networked public square / private companies / regulations / coordination...
 
@@
 
-		\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+
+		%\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+
 
@@
 beauty of life, coordinated inauthentic behavior.
-\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
-
-		\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
+%\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
+
+		%\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
 While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
 
-		\item YouTube page that says, misinformation falls under other categories existing in the guidelines.
-
-		\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model
+		%\item YouTube page that says, misinformation falls under other categories existing in the guidelines.
+
+		%\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model
 

### 2021-07-29 article/draft.tex
updates to YT section

@@
 
+Title proposition 4: Misinformation related interventions by mainstream social media platforms: third-party monitoring, methods and illustration.
+
 \smallskip
@@
 
-{\color{pink}
-
-Youtube recommends content to the users based on the watch history and searchers they do in google and youtube.
-It is possible for the user to change the recommendation based on his preferences by removing videos from his history or by pausing the watch history.
-This type of system can influence what a user gets recommended in a negative way especially if the user is constantly watching misleading videos or conspiracy theory type of videos.
-Youtube says that they set out to prevent their systems from serving up content that could misinform users in a harmful way, particularly in domains that rely on veracity, such as science, medicine, news, or historical events.
-The way that youtube determines misinformation is by using external human evaluators and experts to examine if the video is promoting misleading information or conspiracy theories.
+%what about with search terms: most recommended channels?
+
+YouTube can reduce the visibility of some video content via its recommendation system, namely by recommending content from authoritative sources for topics related to science and health.
+This platform recommends content to the users based on the watch history and searched queries in google and YouTube; which can both be cleared via account settings.
+Moreover, a recommendation system based on preferences and history might have a down side, namely when a user repeatedly watches videos that might be misleading or that promote conspiracy theories.
+YouTube states that they set out to prevent their systems from serving up content that could misinform users in a harmful way, particularly in domains that rely on veracity, such as science, medicine, News, or historical events.
+YouTube identifies misinformation by using external human evaluators and experts to examine if a given video is promoting misleading information or conspiracy theories.
 Then using the feedback of the evaluators, they use machine learning systems to develop models that generate recommendations.
@@
 
-{\color{red} explain experiment + make it only about health and add exact number (e.g. 45 health videos, 10 545 recommendations) .}
-
-To examine this effect, we designed an experiment that simulates user behavior in youtube using selenium library and python.
-The experiment starts with one misleading video identified by fact checkers and a clean watch history.
-Then the system collects the recommendation for this video and clicks on the top 10 recommendations in sequential order and collects their recommendations.
-The experiment is repeated for 65 misleading videos.
-In addition, to copy the user behavior, the system watches the videos for a couple of minutes to half of it.
-After the data collection, a fact checker examined the top 80 recommended videos (Videos that have been recommended many times during the experiment).
-The results showed little misinformation (less than 10\%) in the top recommendations.
-Therefore, this can be the result of youtube reducing the visibility of videos with misinformation or there is little misinformation in youtube or the experiment setup didn’t influence the recommendation engine behavior since we start with only one misleading video every time.
-
-\smallskip
-
-{\color{red} Channel level ! }
-
-}
+To examine this effect, we designed an experiment that simulates a user's behavior on YouTube.
+We used a list of $45$ videos marked as {\it False} by Science Feedback and classified under the category ``health'' (see section \ref{youtube_panels} for the classification).
+The experiment starts with one video marked as ``False'' from our list of videos and a clean watch history.
+For each video, our automated program collects around $20$ recommendations and clicks on the top $10$ videos in sequential order.
+After that, for every video in set of top $10$ recommendations, it collects their top $20$ recommended videos.
+In addition, to simulate a user's behavior, the automated program watches each video for a few minutes\footnote{If the video duration is ten minutes or less, the automated program watches the whole video.
+If the video duration is strictly higher than ten minutes, then the automated program watches only five minutes.}.
+Doing so, we collected $10$ $549$ YouTube recommended video entries, among which only $3$ $895$ were unique.
+
+\smallskip
+
+To analyse the collected data, we ranked the recommended videos based on the number of times they got recommended.
+We then asked Science Feedback to fact-check the top 40 recommended videos, which amounts to $16\%$ of the data.
+Six videos (10.5\%) out of the top $40$ recommended videos were marked as misleading.
+This relatively small percentage points towards that idea that, YouTube is likely reducing the visibility of videos containing misinformation or alternatively maybe there is little misinformation on YouTube.
+Also it might be that the experiment setup did not influence the behavior of the recommendation engine, since we start with a single YouTube video marked as ``False'' every time.
+We further examined the top recommended channels in the collected data.
+We got $1$ $562$ different channels, and we counted the number of times every channel got recommended.
+Figure \ref{channels_yt} shows the top $10$ recommended channels, whose videos represent $30\%$ of the total set of recommended videos in our dataset.
+The top most recommended channel is Fox News, which has a ``mixed'' factual reporting level according to $iffy.news$ and has several failed fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/}.} Also in the top ten most recommended, there are two channels with a ``low'' factual reporting level: PrgerU and Sky news Australia.
+
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[scale=0.5]{./img/channel_youtube.png} 
+	\end{center}
+	\caption{Top ten recommended channels.}
+	\label{channels_yt}
+\end{figure}
 

### 2021-07-29 article/draft.tex
updates in YT section

@@
 Figure \ref{channels_yt} shows the top $10$ recommended channels, whose videos represent $30\%$ of the total set of recommended videos in our dataset.
-The top most recommended channel is Fox News, which has a ``mixed'' factual reporting level according to $iffy.news$ and has several failed fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/}.} Also in the top ten most recommended, there are two channels with a ``low'' factual reporting level: PrgerU and Sky news Australia.
+Among the top three most recommended channels, there is Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to $iffy.news$ and have several failed fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} Also in the top ten most recommended, we find PragerU, which has a ``low'' level of factual reporting according to iff.news.
 
@@
 	\begin{center}
-		\includegraphics[scale=0.5]{./img/channel_youtube.png} 
+		\includegraphics[scale=0.6]{./img/channel_youtube.png} 
 	\end{center}

### 2021-07-29 article/draft.tex
updates to YT section on recommendations

--- 2021-07-29 article/draft.tex
@@
 The experiment starts with one video marked as ``False'' from our list of videos and a clean watch history.
-For each video, our automated program collects around $20$ recommendations and clicks on the top $10$ videos in sequential order.
-After that, for every video in set of top $10$ recommendations, it collects their top $20$ recommended videos.
+For each video, our automated program collects around\footnote{...} $20$ recommendations and clicks on the top $10$ videos in sequential order.
+After that, for every video in the set of the top $10$ recommendations, we collect their top $20$ recommended videos.
 In addition, to simulate a user's behavior, the automated program watches each video for a few minutes\footnote{If the video duration is ten minutes or less, the automated program watches the whole video.
@@
 Doing so, we collected $10$ $549$ YouTube recommended video entries, among which only $3$ $895$ were unique.
-
-\smallskip
-
-To analyse the collected data, we ranked the recommended videos based on the number of times they got recommended.
-We then asked Science Feedback to fact-check the top 40 recommended videos, which amounts to $16\%$ of the data.
-Six videos (10.5\%) out of the top $40$ recommended videos were marked as misleading.
-This relatively small percentage points towards that idea that, YouTube is likely reducing the visibility of videos containing misinformation or alternatively maybe there is little misinformation on YouTube.
-Also it might be that the experiment setup did not influence the behavior of the recommendation engine, since we start with a single YouTube video marked as ``False'' every time.
-We further examined the top recommended channels in the collected data.
+To analyse the collected data, we look for misinformation: $(i)$ at the video level and $(ii)$ at the channel level.
+
+\smallskip
+
+{\bf Video Level.} We ranked the recommended videos based on the number of times they got recommended. We then asked Science Feedback to fact-check the top 40 recommended videos.
+Those $40$ videos were recommended $1$ $735$ times out of the $10$ $549$ YouTube recommended video entries (that is $16\%$ of the recommendations).
+Among the top 40 recommended videos, four unique videos were marked as {\it misleading} and they were recommended $132$ times out of the $1$ $735$ recommendations (that is $7.7\%$ of the recommendations).
+Four other videos were marked as {\it hyper-partisan} and they were recommended $184$ times ($10.7\%$).
+
+\smallskip
+
+{\bf Channel Level.} We examined the top recommended channels in the collected data.
 We got $1$ $562$ different channels, and we counted the number of times every channel got recommended.
 Figure \ref{channels_yt} shows the top $10$ recommended channels, whose videos represent $30\%$ of the total set of recommended videos in our dataset.
-The top most recommended channel is Fox News, which has a ``mixed'' factual reporting level according to $iffy.news$ and has several failed fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/}.} Also in the top ten most recommended, there are two channels with a ``low'' factual reporting level: PrgerU and Sky news Australia.
+Among the top three most recommended channels, there is Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to {\it iffy.news} and have several failed fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} Also in the top ten most recommended, we find PragerU, which has a ``low'' level of factual reporting according to {\it iffy.news}.
+
+\smallskip
+
+At the video level, we start at each round with a YouTube video marked as ``False'' and we expected to have a high proportion of misinformation videos.
+But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
+This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation.
+However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being recommended.
+Finally, notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general and even harder than on Facebook and Twitter.
 
@@
 	\begin{center}
-		\includegraphics[scale=0.5]{./img/channel_youtube.png} 
+		\includegraphics[scale=0.6]{./img/channel_youtube.png} 
 	\end{center}
-	\caption{Top ten recommended channels.}
+	\caption{Top ten recommended channels among the $1$ $562$ different channels, that have posted the recommended videos in our dataset.}
 	\label{channels_yt}
@@
 We have provided a methodology that can be useful for third-party monitoring.
-The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, and we hope it can be a useful ressource for those working on addressing online misinformation.
+The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, and we hope it can be a useful ressource for researchers, NGOs and journalists addressing online misinformation.
 
@@
 Yet the present research sheds light on the lack and the splintering of data, which impede the academic community from studying successfully online misinformation and assessing the impact of platforms' interventions regarding this phenomenon.
-Hence, few comments are in order regarding the lack of data, the lack of transparency regarding misinformation related interventions, the splintering of data and the lack of interventions designed specifically for misinformation.
+Hence, few comments are in order regarding the lack of data, the lack of transparency vis-\`{a}-vis misinformation related interventions, the splintering of data and the lack of interventions designed specifically for misinformation.
 

### 2021-07-29 code/create_figures.py

@@ -261,21 +261,21 @@ def plot_view_count_youtube(data, date_begin_sus, date_end_sus, date_begin_graph
     df_tlm_vol_rolling = df_tlm_vol.groupby(['published_at']).mean().rolling(window=window_num, win_type='triang',
                                                                              center=True).mean()
     df_tlm_vol_rolling['published_at'] = df_tlm_vol_rolling.index
-    fig, ax1 = plt.subplots(1, figsize=(15, 4))
+    fig, ax = plt.subplots(1, figsize=(15, 4))
     plt.locator_params(axis='y', nbins=4)
     plt.setp(ax1.get_xticklabels(), rotation=45)
 
-    ax1.xaxis.set_tick_params(length=0)
-    ax1.plot(df_tlm_vol_rolling_views['published_at'],
+    ax.xaxis.set_tick_params(length=0)
+    ax.plot(df_tlm_vol_rolling_views['published_at'],
              df_tlm_vol_rolling_views['view_counts'],
              color='red', label='view count')
-    ax1.set_xlim([date_begin_graph, date_end_graph])
+    ax.set_xlim([date_begin_graph, date_end_graph])
     plt.setp(ax1.get_xticklabels(), rotation=45)
-    ax1.spines['right'].set_visible(False)
-    ax1.spines['left'].set_visible(False)
-    ax1.spines['top'].set_visible(False)
-    ax1.grid(axis="y")
-    ax1.xaxis.set_tick_params(length=0)
+    ax.spines['right'].set_visible(False)
+    ax.spines['left'].set_visible(False)
+    ax.spines['top'].set_visible(False)
+    ax.grid(axis="y")
+    ax.xaxis.set_tick_params(length=0)
 
     plt.axvspan(np.datetime64(date_begin_sus), np.datetime64(date_end_sus),
                 ymin=0, ymax=200000, facecolor='r', alpha=0.05)

### 2021-07-29 article/draft.tex
yt section on recommendations

@@
 The experiment starts with one video marked as ``False'' from our list of videos and a clean watch history.
-For each video, our automated program collects around\footnote{...} $20$ recommendations and clicks on the top $10$ videos in sequential order.
+For each video, our automated program collects around\footnote{Notice that as we are simulating the behavior of a user, when we visit a video, we get a number of recommendations that vary between $18$ videos and $22$ videos.} $20$ recommendations and clicks on the top $10$ videos in sequential order.
 After that, for every video in the set of the top $10$ recommendations, we collect their top $20$ recommended videos.
@@
 
-\smallskip
-
-At the video level, we start at each round with a YouTube video marked as ``False'' and we expected to have a high proportion of misinformation videos.
-But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
-This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation.
-However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being recommended.
-Finally, notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general and even harder than on Facebook and Twitter.
-
 \begin{figure}[h]
@@
 \end{figure}
+
+\smallskip
+
+At the video level, we start at each round with a YouTube video marked as ``False'' and we expected to have a high proportion of misinformation videos.
+But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
+This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation.
+However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended.
+{\color{pink} mettre cl pour channel level}.
+Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general and even harder than on Facebook and Twitter.
 

### 2021-07-29 article/draft.tex
minor udpates YT and TW code

@@
 However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended.
-{\color{pink} mettre cl pour channel level}.
-Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general and even harder than on Facebook and Twitter.
+{\color{pink} mettre cl pour channel level, faire allusion à ce qu'ils disent}.
+{\color{pink} they do not act on the channel level ...
+hyper partisan/ misinformation ?
+} Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general and even harder than on Facebook and Twitter.
 

### 2021-07-29 code/collect_twitter_lifesitenews_domain_data.py

@@ -13,7 +13,7 @@ if __name__=="__main__":
 
     load_dotenv()
     collect_twitter_data(
-        query = 'lifesitenews.com',
+        query = 'lifesitenews.com -is:retweet',
         start_time = '2018-12-31T23:00:00Z',
         end_time = '2021-07-01T23%3A59%3A59Z',
         bearer_token= os.getenv('TWITTER_TOKEN'),

### 2021-07-29 code/create_figures.py

@@ -379,7 +379,7 @@ def create_twitter_Lifesite_figure(filename, figure_name, title, zeros):
     ax.plot(df_volume['date'],
         df_volume['size'],
         color='deepskyblue',
-        label='Tweets')
+        label='Number of Tweets per day')
 
     ax.set(
        title = title )
@@ -429,7 +429,7 @@ def create_twitter_figures():
     create_twitter_Lifesite_figure(
     filename = 'twitter_lifesitenews_2021-07-22.csv',
     figure_name = 'lifesite.jpg',
-    title = f"Total number of tweets per day of @LifeSite",
+    title = f"@LifeSite Twitter account",
     zeros = 1
     )
 

### 2021-07-30 article/draft.tex
code for figures harmonized for Tw and Yt + new figures linked to the tex

@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{../figure/lifesite.jpg} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.34]{./img/lifesite_rolling_7_lifesite.jpg}
+		\includegraphics[scale=0.27]{../figure/lifesite.jpg} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.27]{../figure/lifesite_domain.jpg}
 	%\end{multicols}
@@
 		%\begin{multicols}{1}
-			\includegraphics[scale=0.26]{../figure/Tony_Heller_videos_yt.png}
-		%\end{multicols}
-		%\begin{multicols}{1}
-			\includegraphics[scale=0.26]{../figure/Tony_Heller_views_yt.png}
+			\includegraphics[scale=0.27]{../figure/Tony_Heller_videos_yt.png}
+		%\end{multicols}
+		%\begin{multicols}{1}
+			\includegraphics[scale=0.27]{../figure/Tony_Heller_views_yt.png}
 		%\end{multicols}
@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
+		\includegraphics[scale=0.25]{../figure/facebook_crowdtangle_infowars_1.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.25]{../figure/facebook_crowdtangle_infowars_2.png} 
 	%\end{multicols}
@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
-	%\end{multicols}
-\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-Data collected via the Twitter API v2 on June $16$, 2021.
+		\includegraphics[scale=0.27]{../figure/globalresearch_domain.jpg} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.27]{../figure/globalresearch_domain_engagement.jpg}
+	%\end{multicols}
+\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.
+Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.
+Data collected via the Twitter API v2 on July $30$, 2021.
 }

### 2021-07-30 code/collect_twitter_lifesitenews_domain_data.py

@@ -8,7 +8,6 @@ from utils_twitter import toc
 tic()
 
 #collect tweets that share lifesitenews.com domain name
-
 if __name__=="__main__":
 
     load_dotenv()
@@ -17,6 +16,6 @@ if __name__=="__main__":
         start_time = '2018-12-31T23:00:00Z',
         end_time = '2021-07-01T23%3A59%3A59Z',
         bearer_token= os.getenv('TWITTER_TOKEN'),
-        filename = os.path.join('.', 'data', 'twitter_lifesitenews_domain_name_' + str(date.today()) + '.csv'),
+        filename = os.path.join('.', 'data', 'twitter_lifesitenews_domain_name_' + str(date.today()) + '.csv')
     )
     toc()

### 2021-07-30 code/create_figures.py

@@ -19,6 +19,24 @@ def save_figure(figure_name):
     plt.savefig(figure_path)
     print("The '{}' figure is saved.".format(figure_name))
 
+def plot_format(ax, plt):
+
+    ax.spines['right'].set_visible(False)
+    ax.spines['left'].set_visible(False)
+    ax.spines['top'].set_visible(False)
+    plt.locator_params(axis='y', nbins=4)
+    ax.xaxis.set_tick_params(length=0)
+
+    ax.grid(axis='y')
+    handles, labels = ax.get_legend_handles_labels()
+    patch = mpatches.Patch(color='pink',
+                           label='Suspension Period')
+    handles.append(patch)
+    plt.legend(handles=handles)
+
+    plt.setp(ax.get_xticklabels(), rotation=45)
+
+    plt.tight_layout()
 
 def arrange_plot(ax, df):
 
@@ -76,9 +94,11 @@ def create_buzzsumo_thebl_figure():
     df = clean_buzzsumo_data(df)
 
     fig = plt.figure(figsize=(10, 8))
+    #fig = plt.figure(figsize=(10, 4)) #
     fig.suptitle('The Beauty of Life (data from Buzzsumo)')
 
     ax = plt.subplot(211)
+    #ax = plt.subplot(111)#
     plt.plot(df.resample('D', on='date')['facebook_comments'].mean(),
         label="Facebook comments per article", color='lightskyblue')
     plt.plot(df.resample('D', on='date')['facebook_shares'].mean(),
@@ -89,7 +109,14 @@ def create_buzzsumo_thebl_figure():
     plt.axvline(np.datetime64("2019-12-01"), color='C3', linestyle='--')
     plt.ylim(-100, 10000)
 
+    #plt.tight_layout()#
+    #save_figure('facebook_buzzsumo_thebl_1.png')#
+
+    #fig = plt.figure(figsize=(10, 4)) #
+    #fig.suptitle('The Beauty of Life (data from Buzzsumo)')
+
     ax = plt.subplot(212)
+    #ax = plt.subplot(111) #
     plt.plot(df.resample('D', on='date')['date'].agg('count'),
             label='Number of articles published per day', color='grey')
     arrange_plot(ax, df)
@@ -97,6 +124,7 @@ def create_buzzsumo_thebl_figure():
     plt.ylim(0, 80)
 
     plt.tight_layout()
+    #save_figure('facebook_buzzsumo_thebl_2.png')#
     save_figure('facebook_buzzsumo_thebl.png')
 
 
[…]

### 2021-07-30 article/draft.tex
minor updates in the draft

@@
 
-\title{Preliminary Draft}
+\title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
 
@@
 
-Title proposition 1: ``Big Tech is censoring me'': using social media data to verify the platforms' regulation policies regarding misinformation.
-
-Title proposition 2: Illustrating Facebook, Twitter and YouTube regulation policies against misinformation with a few chosen examples
-
-Title proposition 3: Misinformation Policies of Mainstream Social Media Platforms: third-party monitoring, methods and illustration.
-
-Title proposition 4: Misinformation related interventions by mainstream social media platforms: third-party monitoring, methods and illustration.
-
-\smallskip
-
-{\color{pink} \noindent N.B: we will redo all the figures (to harmonize the legend, etc.) and the table of contents will be deleted.} 
-\tableofcontents
+%Title proposition 1: ``Big Tech is censoring me'': using social media data to verify the platforms' regulation policies regarding misinformation.
+
+%Title proposition 2: Illustrating Facebook, Twitter and YouTube regulation policies against misinformation with a few chosen examples
+
+%Title proposition 3: Misinformation Policies of Mainstream Social Media Platforms: third-party monitoring, methods and illustration.
+
+%Title proposition 4: Misinformation related interventions by Facebook, Twitter and YouTube: third-party monitoring, methods and illustration.
+
+%\smallskip
+
+%{\color{pink} \noindent N.B: we will redo all the figures (to harmonize the legend, etc.) and the table of contents will be deleted.} 
+%\tableofcontents
 
@@
 \centering
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.27]{../figure/globalresearch_domain.jpg} 
-	%\end{multicols}
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.27]{../figure/globalresearch_domain_engagement.jpg}
-	%\end{multicols}
 \caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.
@@
 However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended.
-{\color{pink} mettre cl pour channel level, faire allusion à ce qu'ils disent}.
-{\color{pink} they do not act on the channel level ...
-hyper partisan/ misinformation ?
-} Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general and even harder than on Facebook and Twitter.
+In other words, it is likely that YouTube acts on reducing the visibility of videos but not channels, via its recommendation system.
+Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general, given the complexity of their recommendation algorithm.
+%and this exercice seems harder Facebook and Twitter.
 
@@
 We invite the reader to see Rogers (2020)~\cite{rogers2020} for an excellent overview about de-platforming and see Robins-Early (2019)~\cite{huffpost} for a news article about Alex Jones's account suspension on Facebook.
-
-\smallskip
+{\color{pink} Make point / Recommendation: inform about sources, example inform users that this user/account/page/group/channel has shared x failed fact-checks over a x-months period.}
+%\smallskip
 
@@
 
-{ \color{pink} 
-\bigskip
+%{ \color{pink} 
+%\bigskip
 
@@
 
-\begin{itemize}
+%\begin{itemize}
 
@@
 
-\item[Idea 3:] Policies not specific to misinformation. New for smart design (recycling point) - New policy: coordination for informative notices, based on fact-checks.
-
-	\begin{itemize}
-
-		\item Networked public square / private companies / regulations / coordination...
-
-		\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
+%\item[Idea 3:] Policies not specific to misinformation. New for smart design (recycling point) - New policy: coordination for informative notices, based on fact-checks.
+
+	%\begin{itemize}
+
+		%\item Networked public square / private companies / regulations / coordination...
+
+		%\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
 
@@
 
-		\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason.
+		%\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason.
 E.g.
@@
 
-	\end{itemize}
-
-\end{itemize}
-}
+	%\end{itemize}
+
+%\end{itemize}
+%}
 

### 2021-08-16 code/create_figures.py
minor changes for the globalresearch.ca figures

@@ -442,6 +442,8 @@ def create_twitter_globalresearch_figure(filename, figure_name, title, zeros):
 
         ax.set_ylim([0, 600])
 
+        ax.set_xlim([datetime.date(2021,1,1), datetime.date(2021, 6, 30)])
+
     elif zeros == 0:
 
         df_s=df.groupby(['date'],as_index=False)[['like_count','retweet_count','reply_count']].sum()
@@ -460,12 +462,13 @@ def create_twitter_globalresearch_figure(filename, figure_name, title, zeros):
                 df_s_rolling['retweet_count'],
                 color='pink',label='Retweet Count')
 
-        #ax.set_ylim([0, 800000])
+        ax.set_ylim([0, 1500])
+        ax.set_xlim([datetime.date(2021,6,14), datetime.date(2021, 6, 30)])
 
     ax.set(
         title = title)
 
-    ax.set_xlim([datetime.date(2021,1,1), datetime.date(2021, 6, 30)])
+    #ax.set_xlim([datetime.date(2021,1,1), datetime.date(2021, 6, 30)])
     plt.axvspan(np.datetime64('2021-05-25'), np.datetime64('2021-06-30'),
             ymin=0, ymax=200000, facecolor='r', alpha=0.05)
 
@@ -500,15 +503,15 @@ def create_twitter_figures():
 
     create_twitter_globalresearch_figure(
     filename = 'twitter_globalresearch_domain_name_2021-07-29.csv',
-    figure_name = 'globalresearch_domain_engagement.jpg',
+    figure_name = 'globalresearch_domain_engagement_2.jpg',
     title = f"Tweets containing the domain name globalresearch.ca",
     zeros = 0
     )
 
 if __name__=="__main__":
 
-    #create_facebook_trump_figure()
-    #create_buzzsumo_thebl_figure()
+    create_facebook_trump_figure()
+    create_buzzsumo_thebl_figure()
     create_facebook_crowdtangle_infowars_figure()
     #create_facebook_buzzsumo_infowars_figure()
 

### 2021-08-17 article/draft.tex
add abstract

@@
 
+\section*{Abstract}
+
+There is growing pressure for mainstream platforms, such as Facebook, Twitter or YouTube, to moderate the available content. 
+Collecting social media data via API and scraping, we investigated their interventions through a series of examples. 
+These interventions can be classified into three broad categories: 
+(i) temporary or permanent suspension of users, 
+(ii) introducing flags and notices, and 
+(iii) reducing the visibility of some content. 
+Use cases belonging to each category will be shown for Facebook, Twitter and YouTube. 
+Finally, we discuss how an increased effort of transparency can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
+
 \section{Introduction}

### 2021-08-17 article/draft.tex
updates in seection 1 for FB and TW

@@
 However, when the suspension is permanent, in most cases, followers or subscribers have no longer access to the content prior to the suspension and the user can no longer use the account to create new content.
-In what follows, we focus on the implementation of this policy by several platforms and provide simple examples to illustrate.
+In what follows, we focus on the implementation of this policy by Facebook, Twitter and YouTube, and we provide simple examples to illustrate.
 
@@
 When an account is permanently suspended by Facebook, it disappears from the platform.
-That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged to.\footnote{See the \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{April 2021 report} as an example.} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.
+That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged to.\footnote{See the \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{April 2021 report} as an example.}
+But as long as external persons do not have access to historical data of deleted accounts, these reports cannot be verified by the academic community, NGOs and journalists.
 
@@
 For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API.
-Thus, after manually adding this page to the CrowdTangle dashboard, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used Minet command line tool \cite{minet} to collect the data.
+%Thus, after manually adding this page to the CrowdTangle dashboard, 
+Hence, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used Minet command line tool \cite{minet} to collect the data.
 We can verify on figure \ref{fig1_fb} that the {\it Donald J.
@@
 Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform.
-A list of notable Twitter temporary and permanent suspensions can be found on  \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{Wikipedia}.
-The 12-hour account lock is hard to observe in the data, especially for users who do not have an over the clock tweeting activity.
+A list of notable Twitter temporary and permanent suspensions can be found on  \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{Wikipedia}.\footnote{See \href{https://en.wikipedia.org/wiki/Twitter\_suspensions}{https://en.wikipedia.org/wiki/Twitter\_suspensions}.}
+The 12-hour account lock is hard to observe in the data, 
+especially for users who do not have an over the clock regular tweeting activity.\footnote{The following tool \href{https://makeadverbsgreatagain.org/allegedly/}{https://makeadverbsgreatagain.org/allegedly/} provides an overview of the daily and hourly tweeting activity, including repetition of Tweets for any given Twitter account.}
 In this section, we provide one example of a temporary suspension of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.
@@
 }.
-In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}.
+In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news and feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/} and \href{https://open.feedback.org/media/S4}{https://open.feedback.org/media/S4}.}.
 We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint.
@@
 
-To further assess the impact of this double temporary suspension, we collect via Minet Command Line Tool\cite{minet}, all the tweets that have shared during the same period a url link containing lifesitenews.com.
+To further assess the impact of this double temporary suspension, we collect via the Twitter API v2, all the tweets that have shared during the same period a url link containing lifesitenews.com.
 Panel $(b)$ of figure \ref{fig2}, shows that during both periods of temporary suspension, other users still shared lifesitenews.com links and that the level was only slightly below the tweeting and retweeting levels prior to the first temporary suspension.
 More specifically, there was an average of 960 tweets (including retweets) per day over the first temporary suspension period of 308 days from December 9, 2019 until October 12, 2020, against an average of 977 tweets (including retweets) per day during the exact same period one year earlier.
-Finally, panel $(b)$ points towards the limitations of suspending an account to limit the spread of its content.
+
+Finally, suspending a Twitter account is an intervention which aims at penalizing users, in order to make them respect the Twitter rules.
+In the case of Twitter accounts linked to domain names, the activity of the account usually consists in spreading on social media published articles on the website.
+Panel $(b)$ points towards the limitations of suspending the Twitter account $@LifeSite$, because the content created by the domain lifesitenews.com was still being actively shared by other Twitter users.
 

### 2021-08-17 article/draft.tex
few typos in intro + intro of section 1, EV

@@
 
-\section*{Abstract}
+\begin{abstract}
 
@@
 Finally, we discuss how an increased effort of transparency can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
+
+\end{abstract}
 
@@
 
-During the COVID-19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see Appendix \ref{links} for references).
+During the COVID-19 global health pandemic, platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see Appendix \ref{links} for references).
 Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
@@
 This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community.
-Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information.
+Hence, in the present article we explain how to verify
+mainstream platforms' current actions regarding content with low credibility or false information
+with data mining.
 We do so by providing a series of examples for different interventions and platforms.
@@
 retro-engineering the HMTL code of a web page to extract meaningful data, see Table \ref{tab1} for a summary.
-Minet \cite{minet}, a webmining tool developed by the Médialab SciencesPo, was often used, and we scripted our own data mining code when it was necessary.
+Minet \cite{minet}, a webmining tool developed by the SciencesPo médialab, was often used, and we scripted our own data mining code when it was necessary.
 
@@
 More specifically, we survey in this article a number of common policies against misinformation used by Facebook, Twitter and YouTube.
-We classified those common policies into three broad categories: $(i)$ temporary or permanent suspension of users, $(ii)$ introducing flags and notices, and $(iii)$ reducing the visibility of some content.
+We classified those common policies into three broad categories: $(i)$ temporary or permanent suspension of users, $(ii)$
+informing users with flags and notices, and $(iii)$ reducing the visibility of some content.
 We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
@@
 Account suspension can be temporary or permanent.
-When the suspension is temporary the user is prohibited for a limited period of time from posting content on their account, but created content prior to suspension remains available to the user and their followers.
-However, when the suspension is permanent, in most cases, followers or subscribers have no longer access to the content prior to the suspension and the user can no longer use the account to create new content.
+When the suspension is temporary the user is prohibited for a limited period of time from posting content on their account, but
+content created prior to suspension remains available to the user and their followers. However, when the suspension is permanent, in most cases, followers or subscribers 
+no longer have access to the content prior to the suspension and the user can no longer use the account to create new content.
 In what follows, we focus on the implementation of this policy by Facebook, Twitter and YouTube, and we provide simple examples to illustrate.

### 2021-08-17 article/draft.tex
reference OANN in YT section

@@
 To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two YouTube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
-The website of One America News Network has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/}.}  Tony Heller posts regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}} Both are active on YouTube and both have communicated via their Twitter account about restrictions applied by YouTube over their content (see figure \ref{fig2_oann}).
+The website of One America News Network has a ``low'' factual reporting score according to iffy.news and several inaccurate articles according to feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}  Tony Heller posts regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}} Both are active on YouTube and both have communicated via their Twitter account about restrictions applied by YouTube over their content (see figure \ref{fig2_oann}).
 

### 2021-08-17 article/draft.tex
figure global research

@@
 In the case of Twitter accounts linked to domain names, the activity of the account usually consists in spreading on social media published articles on the website.
-Panel $(b)$ points towards the limitations of suspending the Twitter account $@LifeSite$, because the content created by the domain lifesitenews.com was still being actively shared by other Twitter users.
+Panel $(b)$ points towards the limitations of suspending the Twitter account $@LifeSite$, because the
+articles published on lifesitenews.com were still being actively shared by other Twitter users.
 
@@
 
-In this section, we turn to the channel's temporary or permanent suspension policy of YouTube.
-Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed.
+In this section, we turn to the channel's temporary or permanent suspension policy of YouTube. When a YouTube channel violates the community guidelines, it can receive one or several strikes.
+%Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed.
 For the second time the channel will start receiving strikes.
-A first strike results in limiting the access of the YouTube channel  for one week, like uploading videos, streaming and other activities.
-Then a second strike is similar but the suspension will be for two weeks.
+A first strike results in limiting the access of the YouTube channel  for one week
+(e.g. video uploading). 
+Then a second strike is similar but the suspension lasts two weeks. 
 A third strike results in the termination of the channel.
@@
 \centering
-		\includegraphics[scale=0.27]{../figure/globalresearch_domain.jpg} 
-		\includegraphics[scale=0.27]{../figure/globalresearch_domain_engagement.jpg}
+		\includegraphics[scale=0.27]{../figure/globalresearch_domain_2021-08-17.jpg} 
+		\includegraphics[scale=0.27]{../figure/globalresearch_domain_engagement_2021-08-17.jpg}
 \caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.

### 2021-08-17 code/collect_twitter_globalresearch_domain_data.py

@@ -9,13 +9,16 @@ tic()
 
 #collect tweets that share globalresearch.ca domain name
 
+#start_time = '2020-12-31T23:00:00Z',
+#end_time = '2021-06-30T23%3A59%3A59Z',
+
 if __name__=="__main__":
 
     load_dotenv()
     collect_twitter_data(
         query = 'globalresearch.ca -is:retweet',
-        start_time = '2020-12-31T23:00:00Z',
-        end_time = '2021-06-30T23%3A59%3A59Z',
+        start_time = '2021-04-01T23:00:00Z',
+        end_time = '2021-08-01T23%3A59%3A59Z',
         bearer_token= os.getenv('TWITTER_TOKEN'),
         filename = os.path.join('.', 'data', 'twitter_globalresearch_domain_name_' + str(date.today()) + '.csv'),
     )

### 2021-08-17 code/create_figures.py

@@ -442,8 +442,6 @@ def create_twitter_globalresearch_figure(filename, figure_name, title, zeros):
 
         ax.set_ylim([0, 600])
 
-        ax.set_xlim([datetime.date(2021,1,1), datetime.date(2021, 6, 30)])
-
     elif zeros == 0:
 
         df_s=df.groupby(['date'],as_index=False)[['like_count','retweet_count','reply_count']].sum()
@@ -462,14 +460,17 @@ def create_twitter_globalresearch_figure(filename, figure_name, title, zeros):
                 df_s_rolling['retweet_count'],
                 color='pink',label='Retweet Count')
 
-        ax.set_ylim([0, 1500])
-        ax.set_xlim([datetime.date(2021,6,14), datetime.date(2021, 6, 30)])
+        ax.set_ylim([0, 2000])
+
+
+    ax.set_xlim([datetime.date(2021, 4, 1), datetime.date(2021, 8, 1)])
 
     ax.set(
         title = title)
 
     #ax.set_xlim([datetime.date(2021,1,1), datetime.date(2021, 6, 30)])
-    plt.axvspan(np.datetime64('2021-05-25'), np.datetime64('2021-06-30'),
+    plt.axvline(np.datetime64("2021-06-14"), color='C3', linestyle='--')
+    plt.axvspan(np.datetime64('2021-05-25'), np.datetime64('2021-08-01'),
             ymin=0, ymax=200000, facecolor='r', alpha=0.05)
 
 
@@ -495,15 +496,15 @@ def create_twitter_figures():
     )
 
     create_twitter_globalresearch_figure(
-    filename = 'twitter_globalresearch_domain_name_2021-07-29.csv',
-    figure_name = 'globalresearch_domain.jpg',
+    filename = 'twitter_globalresearch_domain_name_2021-08-17.csv',
+    figure_name = 'globalresearch_domain_2021-08-17.jpg',
     title = f"Tweets containing the domain name globalresearch.ca",
     zeros = 1
     )
 
     create_twitter_globalresearch_figure(
-    filename = 'twitter_globalresearch_domain_name_2021-07-29.csv',
-    figure_name = 'globalresearch_domain_engagement_2.jpg',
+    filename = 'twitter_globalresearch_domain_name_2021-08-17.csv',
+    figure_name = 'globalresearch_domain_engagement_2021-08-17.jpg',
     title = f"Tweets containing the domain name globalresearch.ca",
     zeros = 0
[…]

### 2021-08-17 code/collect_twitter_globalresearch_domain_data.py
figure global research

@@ -17,8 +17,8 @@ if __name__=="__main__":
     load_dotenv()
     collect_twitter_data(
         query = 'globalresearch.ca -is:retweet',
-        start_time = '2021-04-01T23:00:00Z',
-        end_time = '2021-08-01T23%3A59%3A59Z',
+        start_time = '2021-04-01T01:00:00Z',
+        end_time = '2021-08-16T23%3A59%3A59Z',
         bearer_token= os.getenv('TWITTER_TOKEN'),
         filename = os.path.join('.', 'data', 'twitter_globalresearch_domain_name_' + str(date.today()) + '.csv'),
     )

### 2021-08-17 code/create_figures.py

@@ -463,14 +463,14 @@ def create_twitter_globalresearch_figure(filename, figure_name, title, zeros):
         ax.set_ylim([0, 2000])
 
 
-    ax.set_xlim([datetime.date(2021, 4, 1), datetime.date(2021, 8, 1)])
+    ax.set_xlim([datetime.date(2021, 4, 1), datetime.date(2021, 8, 15)])
 
     ax.set(
         title = title)
 
     #ax.set_xlim([datetime.date(2021,1,1), datetime.date(2021, 6, 30)])
     plt.axvline(np.datetime64("2021-06-14"), color='C3', linestyle='--')
-    plt.axvspan(np.datetime64('2021-05-25'), np.datetime64('2021-08-01'),
+    plt.axvspan(np.datetime64('2021-05-25'), np.datetime64('2021-08-15'),
             ymin=0, ymax=200000, facecolor='r', alpha=0.05)
 
 

### 2021-08-17 article/draft.tex
rewrite a bit lack of data part

@@
 In this article we have assessed three broad categories of interventions to tackle misinformation by Facebook, Twitter and YouTube: suspension of accounts, introduction of notices and flags and reducing the visibility of content.
-We have provided a methodology that can be useful for third-party monitoring.
+\footnote{For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.}
+Furthermore, we have provided a methodology that can be useful for third-party monitoring. 
 The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, and we hope it can be a useful ressource for researchers, NGOs and journalists addressing online misinformation.
 
-% For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab} and to read the related article.
+%
 
@@
 
-In the light of the present research, we discuss in this section data and policy related recommandations.
 Mainstream platforms such as Facebook, Twitter and Youtube are increasingly working towards higher data transparency (see links that redirect to the respective transparency centers in Appendix \ref{links}).
-Yet the present research sheds light on the lack and the splintering of data, which impede the academic community from studying successfully online misinformation and assessing the impact of platforms' interventions regarding this phenomenon.
-Hence, few comments are in order regarding the lack of data, the lack of transparency vis-\`{a}-vis misinformation related interventions, the splintering of data and the lack of interventions designed specifically for misinformation.
-
-\smallskip
-
-{\bf Lack of data.} First, when Facebook, Twitter or YouTube intervene by suspending an account, a page or a channel, the data disappears.
-It can no longer be accessed via scraping or via the official APIs (Twitter, YouTube, CrowdTangle) for the purposes of scientific research.
+Yet the present research sheds light on the restrictions to access data and its limits, which impede the academic community from studying successfully online misinformation and assessing the impact of platforms' interventions regarding this phenomenon.
+Hence, few comments are in order regarding the limitations to access data, the lack of transparency vis-\`{a}-vis misinformation related interventions and the lack of interventions designed specifically for misinformation.
+
+\smallskip
+
+{\bf A need for more complete data.} When Facebook, Twitter or YouTube intervene by suspending an account, the data can no longer be accessed via scraping or via the official APIs (Twitter, YouTube, CrowdTangle) for the purposes of scientific research.
 This hampers the investigation of how platforms moderate content. 
-To further illustrate this point, the original list of YouTube videos summarized in table \ref{tab2} with failed fact-checks, had over $200$ YouTube videos available in March $2021$.
-However, by June $2021$, thirty videos had disappeared both from YouTube and the YouTube API for policy violation.
+To further illustrate this point, the original list of YouTube videos with failed fact-checks (summarized in Table \ref{tab2}), had over $200$ YouTube videos available in March $2021$. 
+However, by June $2021$, thirty videos had disappeared from the YouTube API for policy violation. 
 Similarly, in a related research project (see Thero and Vincent (2020)~\cite{therovincent}) we searched on CrowdTangle for $94$ public accounts sharing specific content associated with misinformation in November $2020$.
 We tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
-
-\smallskip
-
-Aside from the lack of data due to suspensions, some essential metrics for the study of misinformation are not accessible via main APIs.
-In particular, the $reach$ of posts on Facebook, which is the number of people who actually see a given post, cannot be recovered from the CrowdTangle API.
+It is of course not surprising that plaforms are regulating their content, sometimes by removing it, but we would argue that it could simplify the researchers' work if the deleted data could still be accessible in the APIs (Pasquetto, Swire-Thompson, Amazeen et al.
+(2020)~\cite{pasquetto}).
+
+\smallskip
+
+Aside from the disappearance of data due to content moderation, some essential metrics for the study of misinformation are not accessible via main APIs. 
+In particular, the $reach$ of posts on Facebook, which is the number of people who actually see a given post, cannot be recovered from the CrowdTangle API (REF). 
 Hence, researchers can only build proxies for this metric based on available data (see section \ref{reduce_fb} for an example). 
-Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs; with the exception of the {\it withheld}  and {\it possibly sensitive content} interstitials in the Twitter API v2.
+Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs, with the exception of the {\it withheld}  and {\it possibly sensitive content} interstitials in the Twitter API v2.
 For the purposes of the present research we thus had to scrape this information from Facebook, Twitter and YouTube. 
-Again, this disrupts the monitoring of platforms' interventions concerning misinformation and the assessment of their impact.
-We refer the reader to the insightful commentary by Pasquetto, Swire-Thompson, Amazeen et al.
-(2020)~\cite{pasquetto} and the references therein, for a discussion on partial or biased social media data.
-
-%{\color{red} Misinformation review REF + others to show that we are not the only ones to say that}.
-\smallskip
-
-{\bf Lack of transparency.} Second, mainstream platforms generally lack transparency regarding their misinformation related interventions.
+Again, this disrupts the monitoring of the platforms' interventions and the assessment of their impact (Pasquetto, Swire-Thompson, Amazeen et al. (2020)~\cite{pasquetto}).
+
+\smallskip
+
+{\color{brown} A last concern concerns the increasing restrictions to access data via APIs.
+
+1/ Restrictions to the Open Graph API with the Cambridge Analytica scandal.
+
+2/ Now CT exists but doubt were recently raised that this API will still be accessible for researchers and journalists.
+
+3/ Still access to the "official" APIs for Twitter and YouTube, although the access to Twitter API is very hard to justify if we say we are researchers.
+
+4/ Increasing volume restrictions on the Twitter API between V1 and V2.
+
+It should be noted that there are other ways to collect data than directly from the platforms' APIs.
+Indeed, other APIs are also aggregating data from multiple social platforms as there is a need for social marketing.
+CrowdTangle was actually first an independent social listening tool, before being bought and included within the Facebook organization.
+For example Newsguard, Buzzsumo, Linkfluence...
+Problem: often it is not clear how the data are collected, and at which frequency (more reliable to go to the "source", i.e.
+the official API).}
+
+\smallskip
+
+{\bf A need for more transparency.} Second, mainstream platforms generally lack transparency regarding their misinformation related interventions.
 The broad lines of policies regarding misinformation are communicated via blog posts and are not typically part of the set of rules or community guidelines of mainstream platforms (see Appendix \ref{links}).
@@
 
-{\bf Scattered data.} Third, to study online misinformation, researchers, NGOs and data journalists turn to multiple APIs besides the official ones managed by the mainstream platforms themselves (e.g.
-BuzzSumo).
-They do so, because multiple data sources can be complementary and no specific API has complete data.
-{\color{pink} To be drafted by HT:  vs.
-scraping, cite the article ~\cite{api} about APIs, article du NYTimes sur CT, APIs qui ouvrent et qui ferment, limites de l'API de Twitter entre la V1 et la V2.}
-
-%There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
-For example Newsguard, blablabla...
-In this tweet, we can see the interface of XXX being used in this study from a data journalist: \href{https://twitter.com/Shayan86/status/1394742784683298818/photo/2}{ex}
-
-{\bf Lack of misinformation specific interventions.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
+{\bf A need for a global and coherent misinformation policy.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
 To illustrate, YouTube explicitly states\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.} that: {\it Several policies in our Community Guidelines are directly applicable to misinformation}; such as deceptive practices, impersonation and hate speech policy.

### 2021-08-17 article/draft.tex
add the Shayan part

@@
 
-%
-
-\smallskip
-
-%\subsection{Data related recommendations}
+\smallskip
 
@@
 (2020)~\cite{pasquetto}).
+
+Although it is currently impossible to verify permanent deletions using social media data, their effects can be observed using an adapted methodology.
+Following the Capitol riots in January 2021, Twitter has announced the suspension of more than 70,000 accounts related to QAnon.
+\footnote{\url{https://blog.twitter.com/en_us/topics/company/2021/protecting--the-conversation-following-the-riots-in-washington--}} 
+A journalist has recently investigated the effects of this measure by counting the number of times some hashtags specific to the QAnon movement have been used over time, such as \#QAnon or \#WWG1WGA.
+A drastic reduction in hashtag use was found when comparing the first quarter of 2021 with the first quarter of 2021.
+\footnote{\url{https://twitter.com/Shayan86/status/1394742784683298818}}
+Thus, counting specific hashtag use over time allows to indirectly observe permanent suspensions on Twitter, and other similar methodologies can be found for the other platforms.
 

### 2021-08-18 article/draft.tex
finish the part about increasingly restricted APIs

@@
 We tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
-It is of course not surprising that plaforms are regulating their content, sometimes by removing it, but we would argue that it could simplify the researchers' work if the deleted data could still be accessible in the APIs (Pasquetto, Swire-Thompson, Amazeen et al.
-(2020)~\cite{pasquetto}).
+It is of course not surprising that plaforms are regulating their content, sometimes by removing it, but we would argue that it could simplify the researchers' work if deleted data could still be accessible in the APIs.
 
@@
 \footnote{\url{https://twitter.com/Shayan86/status/1394742784683298818}}
-Thus, counting specific hashtag use over time allows to indirectly observe permanent suspensions on Twitter, and other similar methodologies can be found for the other platforms.
+Thus, counting specific hashtag use over time allows to indirectly observe permanent suspensions on Twitter, and there is a need for similar methodologies to be experimented on the other platforms' data.
 
@@
 
-{\color{brown} A last concern concerns the increasing restrictions to access data via APIs.
-
-1/ Restrictions to the Open Graph API with the Cambridge Analytica scandal.
-
-2/ Now CT exists but doubt were recently raised that this API will still be accessible for researchers and journalists.
-
-3/ Still access to the "official" APIs for Twitter and YouTube, although the access to Twitter API is very hard to justify if we say we are researchers.
-
-4/ Increasing volume restrictions on the Twitter API between V1 and V2.
-
-It should be noted that there are other ways to collect data than directly from the platforms' APIs.
-Indeed, other APIs are also aggregating data from multiple social platforms as there is a need for social marketing.
-CrowdTangle was actually first an independent social listening tool, before being bought and included within the Facebook organization.
-For example Newsguard, Buzzsumo, Linkfluence...
-Problem: often it is not clear how the data are collected, and at which frequency (more reliable to go to the "source", i.e.
-the official API).}
+A last concern regards the increasing restrictions to access APIs \cite{api}.
+In April 2018, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs
+\footnote{https://about.fb.com/news/2018/04/restricting-data-access/}, 
+and CrowdTangle is today a reliable source for researchers to access Facebook data. 
+But CrowdTangle has recently been used by journalists to shown that Facebook is spreading biased information
+\footnote{\url{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}, \url{https://twitter.com/facebookstop10}. 
+The last link is a Twitter account showing each day the ten most shared link on Facebook, most of them coming from extreme right and misinformation sources. 
+Facebook has reacted to this here: \url{https://about.fb.com/news/2020/11/what-do-people-actually-see-on-facebook-in-the-us/}}
+, and a general suspicion is growing that journalists' researchers' access to the API might be shut down in a near future.
+\footnote{\url{https://www.nytimes.com/2021/07/14/technology/facebook-data.html}, \url{https://www.bloomberg.com/news/articles/2021-08-03/facebook-disables-accounts-tied-to-nyu-research-project}}
+Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs, although in our personal experience we never managed to get access to the Twitter API when we described our intend to use the Twitter developer platform as `academic'.
+\footnote{The token was given only when we described a `hobbyist' intent.}
+It should also be noted that the number of Tweets you can retrieve has decreased between the Twitter API V1 and V2. 
+In the V2, there is a monthly cap of 10,000,000 Tweets for academic research projects
+\footnote{https://developer.twitter.com/en/docs/projects/overview},
+while there was no monthly limit in the V1, only a limit in the number of requests that could be made in a 15-minute window
+\footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
+We thus noticed that we could get around 10 times more Tweets per month with the V1 than the V2 for one specific collection.
 
@@
 
-{\bf A need for a global and coherent misinformation policy.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
+{\bf A need for global and consistent policies.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
 To illustrate, YouTube explicitly states\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.} that: {\it Several policies in our Community Guidelines are directly applicable to misinformation}; such as deceptive practices, impersonation and hate speech policy.
@@
 We invite the reader to see Rogers (2020)~\cite{rogers2020} for an excellent overview about de-platforming and see Robins-Early (2019)~\cite{huffpost} for a news article about Alex Jones's account suspension on Facebook.
-{\color{pink} Make point / Recommendation: inform about sources, example inform users that this user/account/page/group/channel has shared x failed fact-checks over a x-months period.}
+
+{\color{brown} Make point / Recommendation: inform about sources, example inform users that this user / account / page / group / channel has shared x failed fact-checks over a x-months period.}
 %\smallskip

### 2021-08-18 article/draft.tex
add reference

@@
 Aside from the disappearance of data due to content moderation, some essential metrics for the study of misinformation are not accessible via main APIs. 
-In particular, the $reach$ of posts on Facebook, which is the number of people who actually see a given post, cannot be recovered from the CrowdTangle API (REF). 
+In particular, the $reach$ of posts on Facebook, which is the number of people who actually see a given post, cannot be recovered from the CrowdTangle API.
+\footnote{\url{https://help.crowdtangle.com/en/articles/4558716-understanding-and-citing-crowdtangle-data}} 
 Hence, researchers can only build proxies for this metric based on available data (see section \ref{reduce_fb} for an example). 
@@
 In April 2018, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs
-\footnote{https://about.fb.com/news/2018/04/restricting-data-access/}, 
+\footnote{\url{https://about.fb.com/news/2018/04/restricting-data-access/}, \url{http://thepoliticsofsystems.net/2018/08/facebooks-app-review-and-how-independent-research-just-got-a-lot-harder/}}, 
 and CrowdTangle is today a reliable source for researchers to access Facebook data. 

### 2021-08-19 article/draft.tex
rewrite discussion part 2

@@
 
-%As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset.
-We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.
-%\footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.}
-%We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments.
-An increase in engagement was also observed in $2020$.
-It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.
-
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
-%	\caption{Facebook engagement metrics (average number of reactions, shares and comments per article) %for the Infowars articles published in $2019-2020$ and gathered from the Buzzsumo API.
-The red line marks %the date of May $2$, $2019$, when Facebook has announced the ban regarding Infowars.}
-%	\label{infowars2}
-%\end{figure}
-
-%We found irregularities in the number of Infowars articles collected from Buzzsumo.
-While Infowars usually publishes around 800 articles per month, only 53 articles were collected between June 11 to July 11, 2020\footnote{In Figure \ref{infowars2} the engagement metrics were only shown for days in which at least 5 Infowars articles were collected from Buzzsumo, to ensure reliable results.}.
-A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
-Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
-
 Another measure that platforms can apply is to prevent users from sharing specific types of content, in this example URLs coming from a specific domain name.
-The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that {\it The BL is now banned from Facebook} for coordinated inauthentic behavior (see Facebook Newsroom (2019)~\cite{newsroom1}), which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content.
-Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested, according to the fact-checking organization Snopes which had reported about The BL’s activity to Facebook\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}}.
-
-To verify Facebook’s ban of The BL domain name, we first tested whether we could post a Facebook message containing a url from thebl.com.
+The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.
+\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} 
+Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook''.
+\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}}
+
+To verify Facebook’s ban, we first tested whether we could post a Facebook message containing a url from thebl.com.
 This turned out to be impossible.
@@
 The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban.
-We can note that although the ban was communicated in an article~\cite{newsroom1} published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
+We can note that although the ban was communicated in an article published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
 The communication around the ban appeared to have discouraged The Beauty of Life to proceed with their activity.
@@
 Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general, given the complexity of their recommendation algorithm.
-%and this exercice seems harder Facebook and Twitter.
 
@@
 
-{\bf A need for more complete data.} When Facebook, Twitter or YouTube intervene by suspending an account, the data can no longer be accessed via scraping or via the official APIs (Twitter, YouTube, CrowdTangle) for the purposes of scientific research.
+{\bf A need for more complete data.} 
+When Facebook, Twitter or YouTube intervene by suspending an account, the data can no longer be accessed via scraping or via the official APIs (Twitter, YouTube, CrowdTangle) for the purposes of scientific research.
 This hampers the investigation of how platforms moderate content. 
@@
 
-{\bf A need for more transparency.} Second, mainstream platforms generally lack transparency regarding their misinformation related interventions.
+{\bf A need for more transparency.} 
+Mainstream platforms generally lack transparency regarding their misinformation related interventions.
 The broad lines of policies regarding misinformation are communicated via blog posts and are not typically part of the set of rules or community guidelines of mainstream platforms (see Appendix \ref{links}).
 Yet, when navigating through the categories of policy areas, to the best of our knowledge, misinformation is absent from the data available on the transparency centers of Facebook, Twitter and YouTube.
-To illustrate, the $2021$ $Q1$ {\it Community Standards Enforcement Report} of Facebook, provides the volume of actioned content only regarding the following policy areas: (1) Adult Nudity \& Sexual Activity, (2) Bullying \& Harassement, (3) Child Nudity \& Sexual Exploitation, (4) Dangerous Orgs: Organized Hate, (5) Dangerous Orgs: Terrorism, (6) Fake Accounts, (7) Hate Speech, (8) Regulated Good: Drugs, (9) Regulated Good: Firearms, Spam, (10) Suicide and Self-injury, (11) Violent \& Graphic Content.
-More precisely, platforms' official communication about misinformation interventions is scarce and the academic community, NGOs and data journalists, usually discover interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets.
-For example, while conducting the present research, it was brought to our attention that during our study, the Twitter account related to the domain name $globalresearch.ca$ was suspended.
-But, there was no official communication or blog post by Twitter Safety team regarding this intervention (see section \ref{globalresearch}).
+Platforms' official communication about misinformation interventions is scarce and the academic community, NGOs and data journalists, usually discover interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in News outlets.
+For example, while conducting the present research, it was brought to our attention that the Twitter account related to the domain name $globalresearch.ca$ was suspended. 
+But, there was no official communication by the Twitter Safety team to explain the reasons of this suspension (see section \ref{globalresearch}).
 
 We are aware that full transparency regarding operational aspects of misinformation related interventions can backfire.
-This is because, the prospective aimed users might find means to circumvent the partly automated interventions.
+This is because the aimed users might find means to circumvent the interventions. 
 We noticed that some YouTube channels are trying to avoid the likely automated COVID-19 information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''. 
-Similarly, we came across notational variants on Twitter of the domain name {\it off-guardian.org}\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}}, such as {\it off-guardian.
-org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}.\footnote{For this case, we failed to understand precisely what kind of intervention Twitter users were circumventing, since they could share in a Tweet an article redirecting to the website {\it off-guardian.org} with the correct notation and only a warning message would appear when one clicks on it.} Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
-
-\smallskip
-
-{\bf A need for global and consistent policies.} It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
-To illustrate, YouTube explicitly states\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.} that: {\it Several policies in our Community Guidelines are directly applicable to misinformation}; such as deceptive practices, impersonation and hate speech policy.
-Similarly, Facebook took down four pages related to InfoWars and cited as a reason the repeated violations of Community Standards and not false news.\footnote{An article published \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{on Facebook Newsroom (2018)} states that : ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
-While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this''.}
-
-Naturally, the design of an intervention by a given online platform in order to moderate content should be adapted to the aimed policy area.
-Therefor, $classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech.
-Nevertheless, tackling online misinformation is an active area of research and interventions specifically designed for this $new$ policy area, might be required to avoid undesired effects.
+Similarly, we came across notational variants on Twitter of the domain name {\it off-guardian.org}
+\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}},
+such as {\it off-guardian. org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}.
+\footnote{For this case, we failed to understand precisely what kind of intervention Twitter users were circumventing, since they could share in a Tweet an article redirecting to the website {\it off-guardian.org} with the correct notation and only a warning message would appear when one clicks on it.}
+Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
+
+\smallskip
+
+In the examples shown in this paper, most of the platforms' interventions were actually motivated by other violations of the platforms' guidelines than misinformation.
+Although Donald Trump spread many misinformation during his governance
+\footnote{\url{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}}, 
+the official reason for his Twitter suspension was not misinformation, but rather that his last Tweets encouraging the Capitol's riot were in violation of Twitter's Glorification of Violence Policy.
+\footnote{\url{https://blog.twitter.com/en_us/topics/company/2020/suspension}}
+Similarly, when Facebook removed four pages related to the InfoWars website, the cited reason was repeated violations of Community Standards.
+Facebook Newsroom clearly stated that : ``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''.
+\footnote{\url{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}}
+For The Beauty of Life website, its ban was officially due to coordinated inauthentic behavior
+\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}}, 
+which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content. 
+According to Facebook, coordinated inauthentic behavior is a distinct phenomenon from disinformation, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false''.
+\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} 
+Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested and reported to Facebook.
+\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, 
+\href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, 
+\href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}}
+In these examples, the compagnies' communication was very clear on the reason of the interventions, but often no communication can be found on an oberved intervention.
+Because misinformation is often associated with creating fake accounts to spead it, and incitation to violence, it is sometimes unclear to distinguish between interventions due to misinsformation and interventions due to other guideline violations, and more transparent communication on platforms' actions would help monitor the interventions specifically related to misinformation.
+
+\smallskip
+
+{\bf A need for more consistent policies.}
+{\color{brown} why a difference between Infowars and The beauty of life? }
+
+It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
+To illustrate, YouTube explicitly states
+\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.}
+that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
+$Classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech. 
+Nevertheless, tackling online misinformation is an active area of research and adapted interventions might be required to avoid undesired effects. 
 Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation. 
@@
 
-{\color{brown} Make point / Recommendation: inform about sources, example inform users that this user / account / page / group / channel has shared x failed fact-checks over a x-months period.}
-%\smallskip
-
-% points to make ? argument ? en gros, interventions existaient dejà on les utilise pour la mesinformation, la mesinformation n'est pas officiellemtn
-
-%{ \color{pink} 
-%\bigskip
-
-%\noindent * Brouillon / esquisse / organisation des bullet points: (N.B. the bullet point ${\color{green}\surd}$ means that the item/idea was used in the above paragraphs)
-
-%\begin{itemize}
-
-%\item[Idea 1:] Not an exhaustive list of interventions + brief summary of what we do. 
-%	
-%	\begin{itemize}
-%
-%	\item[${\color{green}\surd}$] We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies, as other APIs and some databases could be useful for that matter.
-We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
-For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
-%
-%	\item[${\color{green}\surd}$] We hope this paper can illustrate how the platforms policies can be verified.
-All the code needed to collect the data, and create the figures can be found on a public GitHub repo: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, so that other researchers and journalists can easily implement and reproduce our methodology for the purposes of bringing to the society insights concerning the debate around misinformation.
-%	
-%	\end{itemize}
-
-%\item[Idea 2:] Lack of data. Scattered data, indirect methods.  
-%	
-%	
-%	\begin{itemize}
-
-%		\item[${\color{green}\surd}$] For a previous research project (add reference to the article) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
-We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
-This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.
-%		
-%		\item[${\color{green}\surd}$] After a channel gets suspended or a video is deleted the data related to them is removed from the YouTube API.
-This is a problem that affected the study to investigate the suspension reasons or the removal.
-For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from YouTube because they contain content that is against the YouTube guidelines and their data got removed from the API.
-%		
-%		\item[${\color{green}\surd}$] Pas accès au ``reach" !  ranking not available. Fb nous a donné certaines données (les données Condor) et dedans on a le nombre de clicks par exemple
-%	
-%		
-%		\item[${\color{green}\surd}$] Researchers should be able to access the data of deleted accounts on the main platforms.
-%		
-%		\item[${\color{green}\surd}$] Currently the flag or notice banners data is not present in the platforms’ API datasource, and this prevents researchers and journalists from easily investigating that matter.
-They have to use or build a scraper to access the data.
-%		
-%		\item[${\color{green}\surd}$] Lack of transparency in the platforms’ communication that makes their policies harder to verify.
-%		
-%		\item[${\color{green}\surd}$] To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
-But too much transparency on how the regulation policies are exactly implemented can actually backfire.
-For example YouTube is certainly applying an 'information' banner on all videos mentioning COVID-19 and related terms in their title.
-Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'.
-If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation.
-There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.
-%		
+{\color{brown} Recommendation: inform about sources, example inform users that this account has shared x failed fact-checks over a x-months period.}
+
+\smallskip
+
 %		\item[${\color{green}\surd}$] Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook.
@@
 In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
-%		
-%		\item There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
-For example Newsguard, blablabla...
-In this tweet, we can see the interface of XXX being used in this study from a data journalist: \href{https://twitter.com/Shayan86/status/1394742784683298818/photo/2}{ex}
-%			
-%		\item Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
-While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
-A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
-Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
-%	
-%	\end{itemize}
-
-%\item[Idea 3:] Policies not specific to misinformation. New for smart design (recycling point) - New policy: coordination for informative notices, based on fact-checks.
-
-	%\begin{itemize}
-
-		%\item Networked public square / private companies / regulations / coordination...
-
-		%\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
-
-		%\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+
-
-		%\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason.
-E.g.
-beauty of life, coordinated inauthentic behavior.
-%\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
-
-		%\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
-While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
-
-		%\item YouTube page that says, misinformation falls under other categories existing in the guidelines.
-
-		%\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model
-
-	%\end{itemize}
-
-%\end{itemize}
-%}
-
-%\begin{itemize}
-
-	%\item We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies, as other APIs and some databases could be useful for that matter.
-We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring.
-For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.
-
-	%\item For a previous research project (add reference to the article) we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria.
-We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore.
-This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.
-
-	%\item To facilitate the verification in the policy applications, we would generally recommend for the platforms to be more transparent.
-But too much transparency on how the regulation policies are exactly implemented can actually backfire.
-For example YouTube is certainly applying an 'information' banner on all videos mentioning COVID-19 and related terms in their title.
-Misinformation accounts are trying to avoid the official banners by using terms as 'C.O.V.I.D' or 'C O V I D'.
-If YouTube was totally transparent on that matter and published the list of 'dangerous' words that leads to an information banner, this list would of course help us to understand YouTube's policies but it would also help the misinformation actors to escape the regulation.
-There is thus a balance between communicating enough so the public can know precisely how the platforms are regulating their content, but without giving too much information that would allow the policies to be bypassed.
-
-	%\item There are other ways to collect data from platforms, and besides Buzzsumo, other API are also aggregating data from multiple social platforms.
-For example Newsguard, blablabla...
-In this tweet, we can see the interface of XXX being used in this study from a data journalist: \href{https://twitter.com/Shayan86/status/1394742784683298818/photo/2}{ex}
-
-	%\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
-
-	%\item Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+
-
-	%\item Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook
-
-	%\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason.
-E.g.
-beauty of life, coordinated inauthentic behavior.
-\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}
-
-	%\item After a channel gets suspended or a video is deleted the data related to them is removed from the YouTube API.
-This is a problem that affected the study to investigate the suspension reasons or the removal.
-For instance, the original list of videos from table 1 had more than 200 videos available in March 2021, however, by June 2021 30 videos got deleted from YouTube because they contain content that is against the YouTube guidelines and their data got removed from the API.
-
-	%\item User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model
-
-	%\item Pas accès au ``reach" !  ranking not available. Fb nous a donné certaines données (les données Condor) et dedans on a le nombre de clicks par exemple
-
-	%\item ``All four Pages have been unpublished for repeated violations of Community Standards and accumulating too many strikes.
-While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers and suggesting additional content, none of the violations that spurred today’s removals were related to this." \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{Newsroom}.
-	%\item Researchers should be able to access the data of deleted accounts on the main platforms.
-
-	%\item Currently the flag or notice banners data is not present in the platforms’ API datasource, and this prevents researchers and journalists from easily investigating that matter.
-They have to use or build a scraper to access the data.
-
-	%\item Lack of transparency in the platforms’ communication that makes their policies harder to verify.
-
-	%\item Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo.
-While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020.
-A temporary crawling problem coming from Buzzsumo may have caused this lack of data.
-Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
-
-	%\item We hope this paper can illustrate how the platforms policies can be verified.
-All the code needed to collect the data, and create the figures can be found on a public GitHub repo: https://github.com/medialab/truth-and-trust-online-2021/, so that other researchers and journalists can easily reuse our methodology.
-%\end{itemize}
+
+		%Networked public square / private companies / regulations / coordination...
+
+		%Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
+
+		%User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model
 
@@
 \bibliographystyle{plain}
-
-%\newpage
 

### 2021-08-19 article/draft.tex
start to write discussion part 3

@@
 
-{\bf A need for more consistent policies.}
-{\color{brown} why a difference between Infowars and The beauty of life? }
+{\bf A need for more consistent and adapted policies.}
+Both Infowars and The Beauty of Life domains are considered as spreading misinformation (they are both on the Iffy+ list\footnote{https://iffy.news/iffy-plus/}), and violated Facebook's guidelines (incitation to violence and coordinated unauthentic behavior).
+Yet one's distribution was reduced for only half a year, while the other one's links cannot be shared anymore on Facebook since the end of 2019, and it is not clear why such double standard was applied on these comparable websites.
+Misinformation on the web is a problem that is increasingly discussed since the 2016 American elections, and in the years that followed, the platforms may have decided manually and on a case-by-case basis which action to enforce.
+It is also possible that platforms usually follow specific rules on how to fight misinformation, but that sometimes the sudden mediatization of specific events leads them to take exceptional actions, such as with the Capitol riots and Trump's suspension from Facebook, Twitter and YouTube.
+
+\smallskip
 
@@
 that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
-$Classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech. 
-Nevertheless, tackling online misinformation is an active area of research and adapted interventions might be required to avoid undesired effects. 
-Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation. 
-We invite the reader to see Rogers (2020)~\cite{rogers2020} for an excellent overview about de-platforming and see Robins-Early (2019)~\cite{huffpost} for a news article about Alex Jones's account suspension on Facebook.
-
-{\color{brown} Recommendation: inform about sources, example inform users that this account has shared x failed fact-checks over a x-months period.}
-
-\smallskip
-
-%		\item[${\color{green}\surd}$] Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook.
-Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform.
-It is explained via a blog post on the facebook Newsroom.
+$Classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech, but tackling online misinformation might need adapted interventions.
+Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation (Rogers (2020)~\cite{rogers2020}, Robins-Early (2019)~\cite{huffpost}).
+
+\smallskip
+
+{\color{brown} Recommendation to fight misinformation: inform about sources, example inform users that this account has shared x failed fact-checks over a x-months period.}
+
+\smallskip
+
+{\color{brown} Tackling online misinformation is an active area of research and adapted interventions might be required to avoid undesired effects. 
+psychological and indirect effects (Pennycook, etc.). 
+How labels can work against their intent.}
+
+\smallskip
+
+{\color{brown} Make point about how the three platforms communicate differently about their policies. 
+Need for a consistent policy for all, but this will surely come only when a law against misinformation is issued. 
+Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. 
 Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. 
-In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
+In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).}
+
+\smallskip
 
@@
 
-		%Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.
-
-		%User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model
+%User side: indirect effects, strategies... business model
 

### 2021-08-19 article/draft.tex
comment last idea

@@
 
-{\color{brown} Make point about how the three platforms communicate differently about their policies. 
-Need for a consistent policy for all, but this will surely come only when a law against misinformation is issued. 
-Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. 
-Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. 
-In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).}
-
-\smallskip
-
 %Networked public square / private companies / regulations / coordination...
@@
 %User side: indirect effects, strategies... business model
+
+%Make point about how the three platforms communicate differently about their policies. 
+%Need for a consistent policy for all, but this will surely come only when a law against misinformation is issued. 
+%Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. 
+%Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. 
+%In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
 

### 2021-08-20 article/draft.tex
typose in the YT subsection, in suspension section

@@
 
+\begin{figure}[h]
+	\centering
+
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.21]{./img/oann/fig3_oann.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.31]{./img/tony/fig3_tony.png}
+	%\end{multicols}
+	\caption{Left Panel: Tweet announcing moving to Rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
+Right Panel: Tony Heller's tweet after getting suspended from YouTube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
+	\label{fig2_oann}
+\end{figure}
+
 To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two YouTube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
@@
 
-\begin{figure}[h]
-	\centering
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.21]{./img/oann/fig3_oann.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.31]{./img/tony/fig3_tony.png}
-	%\end{multicols}
-	\caption{Left Panel: Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
-Right Panel: Tony Heller's tweet after getting suspended from YouTube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
-	\label{fig2_oann}
-\end{figure}
-
 \smallskip
@@
 First, we investigate the temporary suspension of the YouTube channel of {\it One America News channel}.
-This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID-19 according to the News outlet NBCnews (2020)~\cite{nbcnews}.
-We collected the activity of the channel OANN (video counts, view counts) using  the YouTube API v3, between November $2020$ and January $2021$.
-For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June $2021$.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
-
-\begin{figure}[h]
-	\centering
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.27]{../figure/OANN_videos_yt.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.27]{../figure/OANN_views_yt.png} 
+According to the News outlet NBCnews (2020)~\cite{nbcnews}, this YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
+We collected the activity of the channel OANN (video counts and view counts) using  the YouTube API v3, between November $2020$ and January $2021$.
+For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the videos endpoint we retrieved the view counts on June $2021$.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
+
+\begin{figure}[h]
+\hspace{-2em}
+	%\centering
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.32]{../figure/OANN_videos_yt.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.32]{../figure/OANN_views_yt.png} 
 	%\end{multicols}
@@
 
-In addition, as shown in figure \ref{fig1_oann} when comparing the month before the suspension from 2020/10/24 to 2020/11/24 and one month after from 2020/12/01 to 2021/01/01 it was found that the view count decreased by -73\% and the videos uploaded by -55\%.
-Besides that, OANN decided to move officially to Rumble on March 17, 2021 as announced on their Twitter account (see figure \ref{fig2_oann}) and their upload activity on their YouTube channel is close to zero since that announcement.
-
-%\smallskip
-\begin{figure}[h]
-	\centering
-		%\begin{multicols}{1}
-			\includegraphics[scale=0.27]{../figure/Tony_Heller_videos_yt.png}
-		%\end{multicols}
-		%\begin{multicols}{1}
-			\includegraphics[scale=0.27]{../figure/Tony_Heller_views_yt.png}
-		%\end{multicols}
+The view count decreased by -73\% and the videos uploaded decreased by -55\% (see figure \ref{fig1_oann}), when comparing one month before the suspension from 2020/10/24 to 2020/11/24 and one month after from 2020/12/01 to 2021/01/01.
+Furthermore, the activity of the YouTube channel was close to zero, since the channel has announced via their Twitter account (see figure \ref{fig2_oann}) their migration to the alternative platform Rumble on March 17, 2021.
+
+\smallskip
+
+We now turn to a
+second example, the YouTube channel Tony Heller was also temporarily suspended. 
+This channel got its first strike after posting a video about an anti-covid-lockdown doctor getting arrested (see screenshot in figure \ref{fig2_oann}).
+The suspension period lasted one week from September $29$ until October $5$.
+We applied the same methods as in the previous example for the data collection.
+Figure \ref{fig1_tony} shows the daily number of videos uploaded by the channel.
+The suspension period can be observed clearly in the historical data of the channel.
+Using view counts one month before the suspension starting from $2020/08/28$ to $2020/09/28$ and one month after the suspension from $2020/10/05$ to $2020/11/05$, the channel witnessed a drop of view counts by $-69.5\%$ and the videos published in the channel were less by $-29\%$.
+This drop in views can show that the  suspension  period
+may  have  a  good  impact  on  reducing  the  audience interest or reach to the channel.
+
+\begin{figure}[h]
+\hspace{-2em}
+	%\centering
+			\includegraphics[scale=0.32]{../figure/Tony_Heller_videos_yt.png}
+			\includegraphics[scale=0.32]{../figure/Tony_Heller_views_yt.png}
 	\caption{Left Panel: Number of YouTube videos uploaded each day by the YouTube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
@@
 \end{figure}
-
-We now turn to our second example, the temporary suspension of the YouTube channel Tony Heller.
-This channel got its first strike after posting a video about an anti-covid-lockdown doctor getting arrested (see screenshot in figure \ref{fig2_oann}).
-The suspension period was for one week from September 29 until October 5.
-We applied the same methods as in the previous example for the data collection.
-Figure \ref{fig2_oann} shows the daily number of videos uploaded by the channel.
-The suspension period can be observed clearly in the historical data of the channel.
-observing the reach of the audience
-Figure 3: Tony heller tweet after getting suspended from YouTube (Twitter)
-using view counts one month before the suspension starting from 2020/08/28 to 2020/09/28 and one month after the suspension from 2020/10/05 to 2020/11/05 the channel witnessed a drop of view counts by $-69.5\%$ and the videos published in the channel were less by $-29\%$.
-This drop in views can show that the  suspension  period
-may  have  a  good  impact  on  reducing  the  audience interest or reach to the channel.
 

### 2021-08-20 article/draft.tex
typos FB section flags

@@
 
-\section{Flags, Notices and labels} \label{flags}
+\section{Flags, Notices and information panels} \label{flags}
+
+Mainstream platforms such as Facebook, Twitter and YouTube can resort to providing more context to users regarding a specific post, Tweet or video.
+This type of intervention takes different formats according to the platform and also has different denominations.
+Facebook for example refers to this intervention by mentioning ``flags", while Twitter  refers to ``notices" and ``interstitials" and YouTube uses the term ``information panels".
+In this section, we explain the specifics of this intervention for each platform and illustrate with examples.
 
@@
 
-To the best of our knowledge, two types of flags can currently be seen on Facebook posts, videos and pictures: $(i)$ information banners that do not refute the message in the post but that give a link to an authoritative source, such as ``Visit the COVID-19 Information Centre for vaccine resources'' and $(ii)$ fact-check flags that provide a ``judgement'' on the text of the post or the link, shared, such as ``False information Checked by independent fact-checkers'' (see Figure \ref{fb_flags}).
-The fact-check flags can be of varied nature : `False', `Partly false', `Missing context', `False headline', `Altered media', `Opinion', `Satire', `Not eligible' and even `True'.
+To the best of our knowledge, two types of flags can currently be displayed on Facebook posts: 
+$(i)$ information banners which do not refute the message in the post and provide a link which redirects to an authoritative source, such as ``Visit the COVID-19 Information Centre for vaccine resources'' and $(ii)$ fact-check flags that assigns a ``rating" for a text or a link in a given post, such as ``False information Checked by independent fact-checkers'' (see Figure \ref{fb_flags}).
+The fact-check flags display the following ratings : ``False", ``Partly false", ``Missing context", ``False headline", ``Altered media", ``Opinion", ``Satire", ``Not eligible" and ``True".\footnote{See \href{https://www.facebook.com/business/help/341102040382165}{https://www.facebook.com/business/help/341102040382165}.}
 
@@
 \caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners.
-Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/3835629366473816}).}
+Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/} \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{3835629366473816} .}
 \label{fb_flags}
@@
 
-No information regarding the flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data.
-The only way to verify Facebook’s flag policy is thus to scrap Facebook.
-For this paper, we added a new feature in minet to scrape Facebook posts and automatically verify for the presence of the flags.
-
-We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the {\it search} endpoint in minet\footnote{ Click \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{here} to access the link and  \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{its fact-check by Health Feedback}.}.
-Twenty Facebook posts were collected this way, and the newly developed scraper was used to verify whether they were flagged with an information banner, a fact-check flag, both or none.
+No information or available fields regarding the Facebook flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data.
+The only way to verify Facebook’s flagging policy is thus via scrapping publicly available content.
+To that end, we added a new feature in Minet~\cite{minet} which could automatically verify the presence or absence of flags.
+
+We first searched for all the Facebook posts having shared a specific link rated as ‘False’ by Science Feedback, a fact-checking organization which partners with Facebook.
+We used the {\it search} endpoint in Minet.\footnote{ Click \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{here} to access the link and  \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{its fact-check by Health Feedback}.}
+Twenty Facebook posts were collected this way, and the newly developed scraper was used to verify whether they contained an information banner, a fact-check flag, both or none.
 Three posts were unavailable, and thus could not be categorized by the scraper.
-As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.
+As Science Feedback has informed Facebook that they have assigned the rating ``False'' for this link, we expected that all these posts would contain a fact-check flag, but we had no expectations for the information banner.
 
@@
 
-Surprisingly only $11$ posts out of the remaining $17$ had a ‘False information’ flag  (Table \ref{tab_flags_fb}, see left panel of Figure \ref{fb_flags} for an example).
+Surprisingly only $11$ posts out of the remaining $17$ had a ``False information'' flag  (Table \ref{tab_flags_fb}, see left panel of Figure \ref{fb_flags} for an example).
 We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples).
-As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user is thus able to share a False link on Facebook without the ‘False information’ banner if the link is not expanded.
-
-\smallskip
-
-We also observed that most of the posts sharing this False link (13 out of 17, Table \ref{tab_flags_fb}) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}).
+As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user is thus able to share a ``False'' link on Facebook without the ``False'' flag if the link is not expanded.
+
+\smallskip
+
+We also observed that most of the posts sharing this ``False'' link (13 out of 17, Table \ref{tab_flags_fb}) had an information banner saying ``Visit the COVID-19 Information Centre for vaccine resources" (see the first two examples of Figure \ref{fb_flags}).
 We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example).

### 2021-08-23 code/create_figures.py
create figures, if condition for suspension + remove subplots BL

@@ -1,7 +1,8 @@
 import os
+#from datetime import timedelta, date
 from datetime import datetime, timedelta, date
 
-import datetime
+#import datetime
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
@@ -19,7 +20,7 @@ def save_figure(figure_name):
     plt.savefig(figure_path)
     print("The '{}' figure is saved.".format(figure_name))
 
-def plot_format(ax, plt):
+def plot_format(ax, plt, suspension):
 
     ax.spines['right'].set_visible(False)
     ax.spines['left'].set_visible(False)
@@ -29,9 +30,12 @@ def plot_format(ax, plt):
 
     ax.grid(axis='y')
     handles, labels = ax.get_legend_handles_labels()
-    patch = mpatches.Patch(color='pink',
-                           label='Suspension Period')
-    handles.append(patch)
+
+    if suspension == 1 :
+        patch = mpatches.Patch(color='pink',
+                               label='Suspension Period')
+        handles.append(patch)
+
     plt.legend(handles=handles)
 
     plt.setp(ax.get_xticklabels(), rotation=45)
@@ -93,12 +97,12 @@ def create_buzzsumo_thebl_figure():
     df = import_data('facebook_buzzsumo_thebl_2021-07-01.csv')
     df = clean_buzzsumo_data(df)
 
-    fig = plt.figure(figsize=(10, 8))
-    #fig = plt.figure(figsize=(10, 4)) #
+    #fig = plt.figure(figsize=(10, 8))
+    fig = plt.figure(figsize=(10, 4)) #
     fig.suptitle('The Beauty of Life (data from Buzzsumo)')
 
-    ax = plt.subplot(211)
-    #ax = plt.subplot(111)#
+    #ax = plt.subplot(211)
+    ax = plt.subplot(111)#
     plt.plot(df.resample('D', on='date')['facebook_comments'].mean(),
         label="Facebook comments per article", color='lightskyblue')
     plt.plot(df.resample('D', on='date')['facebook_shares'].mean(),
@@ -109,14 +113,14 @@ def create_buzzsumo_thebl_figure():
     plt.axvline(np.datetime64("2019-12-01"), color='C3', linestyle='--')
     plt.ylim(-100, 10000)
 
-    #plt.tight_layout()#
[…]

### 2021-08-23 article/draft.tex
create figures, if condition for suspension + remove subplots BL
typos in the section about flags

@@
 No information or available fields regarding the Facebook flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data.
-The only way to verify Facebook’s flagging policy is thus via scrapping publicly available content.
+The only way to verify Facebook’s flagging policy is thus via scraping publicly available content.
 To that end, we added a new feature in Minet~\cite{minet} which could automatically verify the presence or absence of flags.
@@
 
-To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
+To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet contains a notice or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
 Hence, in order to investigate the presence of labels of all types, we resorted to scrape Twitter data using Minet [5].
-This tool was recently enriched upon our request in order to capture whether a tweet contains a label or not, via the {\it minet twitter scrape} command.
+This tool was recently enriched upon our request in order to capture whether a tweet contains a notice or not, via the ``minet twitter scrape'' command.
 
@@
 This data collection resulted in $323$ $938$ tweets, excluding retweets.
-Only $28$ tweets contained the label { \it Get the facts about COVID-19}, $5$ tweets contained the label {\it Learn about US 2020 election security efforts} and only $1$ had the following label {\it This claim about election fraud is disputed}.
+Only $28$ tweets contained the label { \it ``Get the facts about COVID-19''}, $5$ tweets contained the label {\it ``Learn about US 2020 election security efforts''} and only $1$ had the following label {\it ``This claim about election fraud is disputed''}.
 Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same link, among the set of collected tweets.
 To give an example, $657$ tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}.
-Among those $657$ tweets only $3$ contained the label {\it Get the facts about COVID-19} (see figure \ref{fig8}).
+Among those $657$ tweets only $3$ contained the notice {\it ``Get the facts about COVID-19''} (see figure \ref{fig8}).
 This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by other users.
@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/beautyoflife/fb_bl_1.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{./img/beautyoflife/fb_bl_2.png} 
+		\includegraphics[scale=0.3]{../figure/facebook_buzzsumo_thebl_1.png}
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.3]{../figure/facebook_buzzsumo_thebl_2.png} 
 	%\end{multicols}

### 2021-08-23 article/draft.tex
typos in the Twitter section about flags

@@
 Labels are context specific (e.g.
-COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it Get the facts about COVID-19'} (see right panel of figure \ref{fig8}).
-Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example {\it The following media includes potentially sensitive content} (see left panel of figure \ref{fig_notice}).
+COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it ``Get the facts about COVID-19''} (see right panel of figure \ref{fig8}).
+Interstitials are presented as a greyed box on top of a tweet, which indicates sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example {\it ``The following media includes potentially sensitive content''} (see left panel of figure \ref{fig_notice}).
 At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.
@@
 	%\end{multicols}
-	\caption{Two tweets sharing the same link marked as False by Science Feedback, screenshots taken on June $20$, 2021.
+	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021.
 Left Panel: Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label.
@@
 
-To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet contains a notice or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.
-Hence, in order to investigate the presence of labels of all types, we resorted to scrape Twitter data using Minet [5].
+To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet contains a label or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the Twitter API v2.
+Hence, in order to investigate the presence of notices of all types, we resorted to scrape publicly available tweets, using Minet [5].
 This tool was recently enriched upon our request in order to capture whether a tweet contains a notice or not, via the ``minet twitter scrape'' command.
@@
 
-In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false.
-To that end, we gathered a set of $3094$ links redirecting to articles which were marked as $False$ between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
-As a second step, we collected (on June $30$, $2021$) via Minet Command line tool~\cite{minet} all the tweets that have shared a link which belongs to the set of $3094$ links marked as $False$.
+In this section, we take a deeper look at how labels and interstitials are introduced by Twitter, to indicate content which is inaccurate or false.
+To that end, we gathered a set of $3$ $094$ links redirecting to articles which were marked as ``False'' between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
+As a second step, we collected (on June $30$, $2021$) using Minet~\cite{minet} all the tweets that have shared a link which belongs to the set of $3$ $094$ links marked as $False$.
 This data collection resulted in $323$ $938$ tweets, excluding retweets.
@@
 To give an example, $657$ tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}.
-Among those $657$ tweets only $3$ contained the notice {\it ``Get the facts about COVID-19''} (see figure \ref{fig8}).
+Among those $657$ tweets only $3$ contained the label {\it ``Get the facts about COVID-19''} (see figure \ref{fig8}).
 This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by other users.
@@
 	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial.
-Right Panel: when clicking on $view$, to view the content hidden behind the interstitial.
+Right Panel: when clicking on $view$, to view the content hidden behind the interstitial in the left panel.
 Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}.
@@
 We further examine the placement of interstitials that indicate a possibly sensitive content.
-We find that only $9344$ ($2.97\%$) tweets out of $323$ $938$ containing a link marked as False, have an interstitial {\it potentially sensitive content}.
-To check whether the interstitial {\it potentially sensitive content} is automated or not, we pick out one tweet having shared a link marked as False\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.}, which also contains the interstitial {\it potentially sensitive content} (see figure \ref{fig_notice}).
+We find that only $9$ $344$ ($2.97\%$) tweets out of $323$ $938$ containing a link marked as False, have an interstitial {\it ``potentially sensitive content''}.
+To check whether the interstitial {\it ``potentially sensitive content''} is automated or not, we pick out one tweet having shared a link\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.} marked as ``False'', which also contains the interstitial {\it potentially sensitive content} (see figure \ref{fig_notice}).
 Then we look in the set of $323$ $938$ tweets for other tweets who have shared the exact same link.
@@
 
-Finally, the number of tweets containing the interstitial {\it potentially sensitive content} ($9344$ tweets) widely outnumbers the tweets which contain a flag ($32$ tweets), among the set of $323$ $938$ tweets containing a link marked as False (see table \ref{flags_tab}).
-Furthermore, we noticed that among the tweets which contain the interstitial {\it potentially sensitive content}, there are tweets which contain links redirecting to misleading articles about COVID-19 and yet they are not marked by the flag { \it Get the facts about COVID-19}.
-We also noticed that the $9344$ tweets marked with the interstitial {\it potentially sensitive content} do not necessarily contain graphic violent\footnote{The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.} content but rather links that redirect to articles marked as $False$ by Science Feedback.
-When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it potentially sensitive content} and flags which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".}
+Finally, the number of tweets containing the interstitial {\it ``potentially sensitive content''} ($9$ $344$ tweets) widely outnumbers the tweets which contain a flag ($32$ tweets), among the set of $323$ $938$ tweets containing a link marked as ``False'' (see table \ref{flags_tab}).
+Furthermore, we noticed that among the tweets which contain the interstitial {\it ``potentially sensitive content''}, there are tweets which contain links redirecting to misleading articles about COVID-19 and yet they do not contain the label { \it ``Get the facts about COVID-19''}.
+We also noticed that the $9$ $344$ tweets which contain the interstitial {\it ``potentially sensitive content''} do not necessarily contain graphic violent content\footnote{The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.} but rather links that redirect to articles marked as ``False'' by Science Feedback.
+When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it ``potentially sensitive content''} and labels which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".}
 

### 2021-08-23 article/draft.tex
few typos in YT section about flags

@@
 We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page.
-Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about Climate change, COVID-19 Vaccine, COVID-19 and US elections.\footnote{See: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{youtube.com/watch?v=8PAwc8nlE\_Q}.
+Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about Climate change, COVID-19 Vaccine, COVID-19 and US elections.\footnote{See: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/} \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{youtube.com/watch?v=8PAwc8nlE\_Q}.
 Last accessed on  21/07/2021.
@@
 Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID-19 but contained misinformation concerning cures for cancer, abortion, and viruses.
-Therefore, it is likely that YouTube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID-19, flat earth and vaccine.
-It appears as if YouTube is focusing its efforts on the current ``hot'' topics with a wide public impact (elections, COVID), leaving room for misinformation to spread concerning other topics.
+Therefore, it is likely that YouTube adds information panels below videos including controversial topics and that can contain misleading information like the climate change, COVID-19 and vaccines. 
+It seems that YouTube is focusing its efforts on current ``hot'' topics with a potentially wide public impact (e.g.
+elections, COVID-19), leaving room for misinformation related to other topics to spread.
 

### 2021-08-23 article/draft.tex
typos and updates in the section Tw reducing the visibility

@@
 Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID-19 but contained misinformation concerning cures for cancer, abortion, and viruses.
-Therefore, it is likely that YouTube adds information panels below videos including controversial topics and that can contain misleading information like the climate change, COVID-19 and vaccines. 
+Therefore, it is likely that YouTube adds information panels below videos including controversial topics and that can contain misleading information like climate change, COVID-19 and vaccines. 
 It seems that YouTube is focusing its efforts on current ``hot'' topics with a potentially wide public impact (e.g.
@@
 
-Mainstream social media platforms can reduce the visibility of the content created or shared by specific users, whenever they violate the platforms' rules.
+Mainstream social media platforms can reduce the visibility of content created or shared by users, whenever they violate the platforms' rules. 
 The implementation of this policy varies across platforms and is not easy to verify ex-post.
-In what follows we provide means to verify this policy on Twitter and Facebook.
+In what follows we provide indirect methods to explore how reducing the visibility of content works on Facebook, Twitter and YouTube.
 
@@
 
-One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through their ranking system.
-Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed.
+To tackle misinformation, Facebook can reduce the spread of misleading content through their built-in ranking system. 
+More specifically, Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed.
 Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure (see the article on Facebook Newsroom (2018)~\cite{newsroom2}).
-This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the APIs used to access Facebook data: CrowdTangle or Buzzsumo.
-Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available on CrowdTangle and Buzzsumo.
+This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the APIs used to access Facebook data: CrowdTangle or BuzzSumo.
+Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available on CrowdTangle and BuzzSumo.
 If a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.
@@
 
-The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel).
-Thus the measure announced by Facebook doesn't seem to have prevented users from sharing an $Infowars$ link.
-Nevertheless, a clear drop in engagement was observed on May 2, 2019 (see figure \ref{infowars1} bottom panel).
-The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May 2, 2019.
+The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} left panel). 
+Thus the measure announced by Facebook does not seem to have prevented users from sharing an $Infowars$ link.
+Nevertheless, a clear drop in engagement was observed on May $2$, $2019$ (see figure \ref{infowars1} right panel).
+The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May $2$, $2019$.
 This suggests the measure taken by Facebook in May $2019$, is not a ban per se, but rather a $reduce$ measure.
@@
 
-Another measure that platforms can apply is to prevent users from sharing specific types of content, in this example URLs coming from a specific domain name.
+Another measure that platforms can apply is to prevent users from sharing specific types of content, like URLs belonging to a specific domain name.  
 The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.
@@
 But such manual verification cannot inform us whether the ban applies indeed to all Facebook users and accounts (as we used only our own personal accounts), nor when it has started.
-To further investigate this policy, we collected data from the Buzzsumo API\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.}.
+To further investigate this policy, we collected data from the BuzzSumo API\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.}.
 We used the ``/search/articles'' endpoint to collect the engagement metrics of the $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.
@@
 
-Using Buzzsumo data, we ascertained that links from thebl.com were not shared on Facebook anymore. The ban started on December $1$, $2019$, and appeared to be still enforced in June 2021.
+Using BuzzSumo data, we ascertained that links from thebl.com were not shared on Facebook anymore. The ban started on December $1$, $2019$, and appeared to be still enforced in June 2021.
 
@@
 Twitter can take action against a tweet which violates the Twitter rules, by limiting its visibility\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.} on users' timelines and in search results.
-To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://open.feedback.org/media/AEKA}{Feedback.org} and \href{https://iffy.news}{iffy.news} - two websites which provides databases of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://open.feedback.org/media/AEKA}{open.feedback.org/media/AEKA} and \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
+To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://open.feedback.org/media/AEKA}{Feedback.org} and \href{https://iffy.news}{iffy.news} - two websites which provide databases of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://open.feedback.org/media/AEKA}{open.feedback.org/media/AEKA} and \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
 
@@
 		\caption{Screenshots taken on June 14, 2021.
-Left Panel: screenshot that shows that no results can be found when searching for $globalresearch.ca$ via the Twitter search box.
+Left Panel: screenshot that shows that no results can be found when searching for articles linked to the domain name $globalresearch.ca$ via the Twitter search box.
 Right Panel: example of a tweet posted on June $14$ containing the domain name {\it globalresearch.ca}.
@@
 
-The website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}.
 When a user searches via the twitter search-box for this domain name, no results appear as shown in the screenshot in the left panel of figure \ref{fig3}, taken on June $14$, $2021$.
-To further investigate the possible implementation of a reduced visibility measure, we search via the Twitter API for tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$.
-As shown in the left panel in figure \ref{fig4}, we find a strictly positive number of tweets containing the domain name {\it globalresearch.ca} throughout May $2021$ and the first week of June $2021$.
+To further investigate the possible implementation of a reduced visibility measure, we searched via the Twitter API v2 for tweets, excluding retweets, containing the query {\it globalresearch.ca} from April $15$, $2021$ until August $15$, $2021$.
+As shown in the left panel in figure \ref{fig4}, we find a strictly positive number of tweets containing the domain name {\it globalresearch.ca} after the date on which the screenshot was taken (left panel of figure \ref{fig3}).
 Hence, the visibility of tweets containing this domain name has been reduced because users can no longer access tweets containing the domain name {\it globalresearch.ca} via the search box.
@@
 Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
-Hence, the users who tweet articles from the {\it globalresearch.ca} website receive tweet level engagement from their own followers.
+Hence, the users who post tweets including articles from the {\it globalresearch.ca} website receive tweet level engagement from their own followers.
 
@@
 Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.
-Data collected via the Twitter API v2 on July $30$, 2021.
+Data collected via the Twitter API v2 on August $17$, 2021.
 }
@@
 
-Finally, the above mentioned account was recently suspended from Twitter.
+Finally, the website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$} and it was recently suspended from Twitter.
 We noticed the message about the account suspension (see the right panel in figure \ref{fig4bis}) on May $25$, 2021.

### 2021-08-23 code/create_figures.py

@@ -2,7 +2,7 @@ import os
 #from datetime import timedelta, date
 from datetime import datetime, timedelta, date
 
-#import datetime
+import datetime
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
@@ -445,6 +445,7 @@ def create_twitter_globalresearch_figure(filename, figure_name, title, zeros):
                 label='Number of Tweets per day')
 
         ax.set_ylim([0, 600])
+        plt.text(np.datetime64("2021-06-15"), 420, "screenshot date", fontsize=10, color='C3')
 
     elif zeros == 0:
 
@@ -466,14 +467,17 @@ def create_twitter_globalresearch_figure(filename, figure_name, title, zeros):
 
         ax.set_ylim([0, 2000])
 
+        plt.text(np.datetime64("2021-06-15"), 1400, "screenshot date", fontsize=10, color='C3')
 
-    ax.set_xlim([datetime.date(2021, 4, 1), datetime.date(2021, 8, 15)])
+    ax.set_xlim([datetime.date(2021, 4, 15), datetime.date(2021, 8, 15)])
 
     ax.set(
         title = title)
 
     #ax.set_xlim([datetime.date(2021,1,1), datetime.date(2021, 6, 30)])
     plt.axvline(np.datetime64("2021-06-14"), color='C3', linestyle='--')
+
+
     #plt.axvspan(np.datetime64('2021-05-25'), np.datetime64('2021-08-15'),
     #        ymin=0, ymax=200000, facecolor='r', alpha=0.05)
 
@@ -518,7 +522,7 @@ if __name__=="__main__":
     create_facebook_trump_figure()
     create_buzzsumo_thebl_figure()
     create_facebook_crowdtangle_infowars_figure()
-    #create_facebook_buzzsumo_infowars_figure()
+    create_facebook_buzzsumo_infowars_figure()
 
     create_youtube_graph()
 

### 2021-08-23 article/draft.tex
typose reducing the visibility Tw + discussion

@@
 
-In this article we have assessed three broad categories of interventions to tackle misinformation by Facebook, Twitter and YouTube: suspension of accounts, introduction of notices and flags and reducing the visibility of content.
+In this article we have assessed three broad categories of interventions to tackle misinformation by Facebook, Twitter and YouTube: $(i)$ suspension of accounts, $(ii)$ introduction of flags, labels and information panels and $(iii)$ reducing the visibility of content.
 \footnote{For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.}
@@
 Although it is currently impossible to verify permanent deletions using social media data, their effects can be observed using an adapted methodology.
-Following the Capitol riots in January 2021, Twitter has announced the suspension of more than 70,000 accounts related to QAnon.
+Following the Capitol riots in January 2021, Twitter has announced the suspension of more than $70$ $000$ accounts related to QAnon.
 \footnote{\url{https://blog.twitter.com/en_us/topics/company/2021/protecting--the-conversation-following-the-riots-in-washington--}} 
 A journalist has recently investigated the effects of this measure by counting the number of times some hashtags specific to the QAnon movement have been used over time, such as \#QAnon or \#WWG1WGA.
-A drastic reduction in hashtag use was found when comparing the first quarter of 2021 with the first quarter of 2021.
+A drastic reduction in hashtag use was found when comparing the first quarter of $2021$ with the first quarter of $2021$.
 \footnote{\url{https://twitter.com/Shayan86/status/1394742784683298818}}
@@
 
-A last concern regards the increasing restrictions to access APIs \cite{api}.
+A last concern regards the growing restrictions to access APIs \cite{api}.
 In April 2018, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs
@@
 and CrowdTangle is today a reliable source for researchers to access Facebook data. 
-But CrowdTangle has recently been used by journalists to shown that Facebook is spreading biased information
+But CrowdTangle has recently been used by journalists to show that Facebook is spreading biased information
 \footnote{\url{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}, \url{https://twitter.com/facebookstop10}. 
@@
 Facebook has reacted to this here: \url{https://about.fb.com/news/2020/11/what-do-people-actually-see-on-facebook-in-the-us/}}
-, and a general suspicion is growing that journalists' researchers' access to the API might be shut down in a near future.
+, and a general suspicion is growing that the access of journalists and researchers to the API might be shut down in a near future.
 \footnote{\url{https://www.nytimes.com/2021/07/14/technology/facebook-data.html}, \url{https://www.bloomberg.com/news/articles/2021-08-03/facebook-disables-accounts-tied-to-nyu-research-project}}
-Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs, although in our personal experience we never managed to get access to the Twitter API when we described our intend to use the Twitter developer platform as `academic'.
-\footnote{The token was given only when we described a `hobbyist' intent.}
-It should also be noted that the number of Tweets you can retrieve has decreased between the Twitter API V1 and V2. 
-In the V2, there is a monthly cap of 10,000,000 Tweets for academic research projects
+Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs.%, although in our personal experience we never managed to get access to the Twitter API when we described our intend to use the Twitter developer platform as `academic'.\footnote{The token was given only when we described a `hobbyist' intent.}
+It should also be noted that the number of Tweets that can be retrieved has decreased between the Twitter API v1 and v2. 
+In the v2, there is a monthly cap of 10,000,000 Tweets for the academic research track
 \footnote{https://developer.twitter.com/en/docs/projects/overview},
-while there was no monthly limit in the V1, only a limit in the number of requests that could be made in a 15-minute window
+while there was no monthly limit in the v1, only a limit in the number of requests that could be made in a 15-minute window
 \footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
-We thus noticed that we could get around 10 times more Tweets per month with the V1 than the V2 for one specific collection.
+We thus noticed that we could get around 10 times more Tweets per month with the v1 when compared to the v2 for one specific collection.
 
@@
 
-In the examples shown in this paper, most of the platforms' interventions were actually motivated by other violations of the platforms' guidelines than misinformation.
-Although Donald Trump spread many misinformation during his governance
-\footnote{\url{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}}, 
-the official reason for his Twitter suspension was not misinformation, but rather that his last Tweets encouraging the Capitol's riot were in violation of Twitter's Glorification of Violence Policy.
-\footnote{\url{https://blog.twitter.com/en_us/topics/company/2020/suspension}}
+%In the examples shown in this paper, most of the platforms' interventions were actually motivated by other violations of the platforms' guidelines than misinformation.
+Platform interventions that concern accounts related to domain names who repeatedly share inaccurate, false or misleading content according to fact-checking organizations, are usually not motivated by content moderation to limit misinformation but they  are rather motivated by other rule violations; such as coordinated inauthentic behavior or glorification of violence.
+In what follows, we cite few specific examples to illustrate this point.
+%Although Donald Trump spread many misinformation during his governance 
+The official reason for the suspension of the official Twitter account of Donald Trump was the violation of Twitter's Glorification of Violence Policy in his last tweets encouraging the Capitol's riot\footnote{\url{https://blog.twitter.com/en_us/topics/company/2020/suspension}} and not misinformation\footnote{Although Donald Trump spread many misinformation during his governance \url{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}}.
 Similarly, when Facebook removed four pages related to the InfoWars website, the cited reason was repeated violations of Community Standards.
-Facebook Newsroom clearly stated that : ``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''.
-\footnote{\url{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}}
-For The Beauty of Life website, its ban was officially due to coordinated inauthentic behavior
-\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}}, 
+Facebook Newsroom clearly stated that : ``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''.\footnote{\url{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}}
+For The Beauty of Life website, its ban was officially due to coordinated inauthentic behavior\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}},
 which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content. 
@@
 \footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} 
-Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested and reported to Facebook.
-\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, 
-\href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, 
+Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested and reported to Facebook by the fact-checking organization Snopes.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/},
+\href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-} \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{fake-profiles/} , 
 \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}} 
-In these examples, the compagnies' communication was very clear on the reason of the interventions, but often no communication can be found on an oberved intervention.
-Because misinformation is often associated with creating fake accounts to spead it, and incitation to violence, it is sometimes unclear to distinguish between interventions due to misinsformation and interventions due to other guideline violations, and more transparent communication on platforms' actions would help monitor the interventions specifically related to misinformation.
+In the above ``known'' examples, the compagnies' communication was very clear on the reason of the interventions, but often no communication can be found for a specific intervention observed in collected data.
+Because misinformation is often associated with creating fake accounts to speed its spread, and incitation to violence, it is sometimes unclear to distinguish between interventions due to misinformation and interventions due to other guideline violations, and more transparent communication on platforms' actions would help monitor the interventions specifically related to misinformation.
 

### 2021-08-23 article/draft.tex
modify a bit paragraph about platforms' motivation to intervene

@@
 
-%In the examples shown in this paper, most of the platforms' interventions were actually motivated by other violations of the platforms' guidelines than misinformation.
-Platform interventions that concern accounts related to domain names who repeatedly share inaccurate, false or misleading content according to fact-checking organizations, are usually not motivated by content moderation to limit misinformation but they  are rather motivated by other rule violations; such as coordinated inauthentic behavior or glorification of violence.
-In what follows, we cite few specific examples to illustrate this point.
-%Although Donald Trump spread many misinformation during his governance 
-The official reason for the suspension of the official Twitter account of Donald Trump was the violation of Twitter's Glorification of Violence Policy in his last tweets encouraging the Capitol's riot\footnote{\url{https://blog.twitter.com/en_us/topics/company/2020/suspension}} and not misinformation\footnote{Although Donald Trump spread many misinformation during his governance \url{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}}.
-Similarly, when Facebook removed four pages related to the InfoWars website, the cited reason was repeated violations of Community Standards.
-Facebook Newsroom clearly stated that : ``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''.\footnote{\url{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}}
-For The Beauty of Life website, its ban was officially due to coordinated inauthentic behavior\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}},
+In certain cases, the platform interventions were not motivated by content moderation to limit misinformation, but rather by other rule violations.
+For example, the official reason for the suspension of Donald Trump's Twitter account was not misinformation\footnote{Although Donald Trump spread many misinformation during his governance \url{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}},
+but the violation of Twitter's Glorification of Violence Policy, with his last tweets encouraging the Capitol's riot\footnote{\url{https://blog.twitter.com/en_us/topics/company/2020/suspension}}.
+Similarly, when Facebook removed four pages related to the InfoWars website, the cited reason was repeated violations of Community Standards: 
+``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''.\footnote{\url{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}}
+Regarding The Beauty of Life website, its ban was officially due to coordinated inauthentic behavior\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}},
 which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content. 
@@
 \footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} 
-Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior were attested and reported to Facebook by the fact-checking organization Snopes.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/},
+Nevertheless, both misinformation and coordinated inauthentic behavior were attested for the Beauty of Life, and reported to Facebook by the fact-checking organization Snopes.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/},
 \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-} \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{fake-profiles/} , 
 \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}} 
-In the above ``known'' examples, the compagnies' communication was very clear on the reason of the interventions, but often no communication can be found for a specific intervention observed in collected data.
+In the above ``known'' examples, the compagnies' communication was very clear on the reason of the interventions (although one can suspect that the official reason given can depart from the real motivation behind an intervention).
+But often no communication can be found for a specific intervention observed in collected data. 
 Because misinformation is often associated with creating fake accounts to speed its spread, and incitation to violence, it is sometimes unclear to distinguish between interventions due to misinformation and interventions due to other guideline violations, and more transparent communication on platforms' actions would help monitor the interventions specifically related to misinformation.

### 2021-08-23 article/draft.tex
edit discussion

@@
 A last concern regards the growing restrictions to access APIs \cite{api}.
-In April 2018, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs
-\footnote{\url{https://about.fb.com/news/2018/04/restricting-data-access/}, \url{http://thepoliticsofsystems.net/2018/08/facebooks-app-review-and-how-independent-research-just-got-a-lot-harder/}}, 
+In April 2018, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs\footnote{\url{https://about.fb.com/news/2018/04/restricting-data-access/}, \url{http://thepoliticsofsystems.net/2018/08/facebooks-app-review-and-how-independent-research-just-got-a-lot-harder/}},
 and CrowdTangle is today a reliable source for researchers to access Facebook data. 
-But CrowdTangle has recently been used by journalists to show that Facebook is spreading biased information
-\footnote{\url{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}, \url{https://twitter.com/facebookstop10}. 
+However, it should be noted that CrowdTangle has been recently used by journalists to show that Facebook is spreading biased information\footnote{\url{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}, \url{https://twitter.com/facebookstop10}.
 The last link is a Twitter account showing each day the ten most shared link on Facebook, most of them coming from extreme right and misinformation sources. 
-Facebook has reacted to this here: \url{https://about.fb.com/news/2020/11/what-do-people-actually-see-on-facebook-in-the-us/}}
-, and a general suspicion is growing that the access of journalists and researchers to the API might be shut down in a near future.
-\footnote{\url{https://www.nytimes.com/2021/07/14/technology/facebook-data.html}, \url{https://www.bloomberg.com/news/articles/2021-08-03/facebook-disables-accounts-tied-to-nyu-research-project}}
-Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs.%, although in our personal experience we never managed to get access to the Twitter API when we described our intend to use the Twitter developer platform as `academic'.\footnote{The token was given only when we described a `hobbyist' intent.}
-It should also be noted that the number of Tweets that can be retrieved has decreased between the Twitter API v1 and v2. 
-In the v2, there is a monthly cap of 10,000,000 Tweets for the academic research track
-\footnote{https://developer.twitter.com/en/docs/projects/overview},
-while there was no monthly limit in the v1, only a limit in the number of requests that could be made in a 15-minute window
-\footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
+Facebook has reacted to this here: \url{https://about.fb.com/news/2020/11/what-do-people-actually-see-on-facebook-in-the-us/}}, 
+and a general suspicion is growing that its access might be shut down in a near future to journalists and researchers.\footnote{\url{https://www.nytimes.com/2021/07/14/technology/facebook-data.html}, \url{https://www.bloomberg.com/news/articles/2021-08-03/facebook-disables-accounts-tied-to-nyu-research-project}}
+Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs, although the number of Tweets that can be retrieved has decreased between the Twitter API v1 and v2.
+In the v2, there is a monthly cap of 10,000,000 Tweets for the academic research track\footnote{https://developer.twitter.com/en/docs/projects/overview},
+while there was no monthly limit in the v1, only a limit in the number of requests that could be made in a 15-minute window\footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
 We thus noticed that we could get around 10 times more Tweets per month with the v1 when compared to the v2 for one specific collection.
@@
 It is also possible that platforms usually follow specific rules on how to fight misinformation, but that sometimes the sudden mediatization of specific events leads them to take exceptional actions, such as with the Capitol riots and Trump's suspension from Facebook, Twitter and YouTube.
+We would argue that to efficiently curb the spread of misinformation, policies should be clearly stated and consistently applied, instead of inteventions being implemented on a case-by-case basis and decided in response to the latest news events.
 
@@
 
-{\color{brown} Recommendation to fight misinformation: inform about sources, example inform users that this account has shared x failed fact-checks over a x-months period.}
-
-\smallskip
-
 {\color{brown} Tackling online misinformation is an active area of research and adapted interventions might be required to avoid undesired effects. 
@@
 
-%Networked public square / private companies / regulations / coordination...
-
-%User side: indirect effects, strategies... business model
-
-%Make point about how the three platforms communicate differently about their policies. 
+% Recommendation to fight misinformation: inform about sources, example inform users that this account has shared x failed fact-checks over a x-months period.
+
+% Networked public square / private companies / regulations / coordination...
+
+% User side: indirect effects, strategies... business model
+
+% Make point about how the three platforms communicate differently about their policies. 
 %Need for a consistent policy for all, but this will surely come only when a law against misinformation is issued. 

### 2021-08-23 article/draft.tex
write last paragraph of discussion

@@
 
-A last concern regards the growing restrictions to access APIs \cite{api}.
+A last concern regards the growing restrictions to access APIs (Perriam et al. 2019~\cite{api}).
 In April 2018, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs\footnote{\url{https://about.fb.com/news/2018/04/restricting-data-access/}, \url{http://thepoliticsofsystems.net/2018/08/facebooks-app-review-and-how-independent-research-just-got-a-lot-harder/}},
@@
 
-{\color{brown} Tackling online misinformation is an active area of research and adapted interventions might be required to avoid undesired effects. 
-psychological and indirect effects (Pennycook, etc.). 
-How labels can work against their intent.}
+How to best tackle online misinformation is an active area of research, and developing effective interventions against misinformation depends on understanding the psychology of interacting with social media (Pennycook et Rand 2021~\cite{pennycook2021psychology}).
+Adding fact-checking labels to controversial content is certainly the intervention whose effectiveness was the most studied so far. 
+It was shown that credibility indicators do reduce misperceptions and sharing, although their impact varied vastly depending on the presentation of the warnings (Yaqub 2020~\cite{yaqub2020effects}, Sharevski 2021~\cite{sharevski2021misinformation}).
+Moreover, a fact-checking label can lead to unpredicted consequences depending on the perception of the person reading it.
+On Facebook, Twitter and YouTube, fact-checking messages are currently applied only to some content, while the rest of the platform remains unlabelled. 
+Such sparce application of warnings can lead to an `implied truth' effect where users may assume that content without warnings have actually been verified and shown to be true (Pennycook et al.
+2020~\cite{pennycook2020implied}).
+Using another approach, Mosleh et al. (\cite{mosleh2021perverse}) identified Twitter users sharing false news and replied to their false tweets with links to fact-checking websites.
+They observed a decrease in quality and accuracy of the content subsequently shared by the corrected user. 
+These works highlight the necessity to investigate potential unintended effects of well-meaning interventions.
+The methods presented in this paper can help to monitor not only the platforms' actions against misinformations, but also their subsequent consequences in real-life settings.
 

### 2021-08-24 article/draft.tex
add Beatrice's point about the natural disappearance of data

@@
 \footnote{\url{https://twitter.com/Shayan86/status/1394742784683298818}}
-Thus, counting specific hashtag use over time allows to indirectly observe permanent suspensions on Twitter, and there is a need for similar methodologies to be experimented on the other platforms' data.
+Thus, counting specific hashtag use over time allows to indirectly observe permanent suspensions on Twitter, and there is a need for similar methodologies to be experimented on data from other platforms.
+However, a point of concern is that data can also disappear because of other factors than the interventions of platforms.
+As an example, in 2012, McMinn et al. \cite{mcminn2013building} collected 120 millions of Tweets on very general topics. 
+The published set of Tweet IDs was then used to re-run the same collection in 2018, but only 67 millions of Tweets (55\%) were retrieved, probably due to tweets beeing removed by users and Twitter accounts being closed (Mazoyer et al.
+2020~\cite{mazoyer2020french}).
+As data naturally disappear from platforms over time, it hard to identify whether platforms or users are the ones responsible for their removal. 
+Even in the case of the QAnon accounts, it is hard to say how much of the drop in hashtag use is due to the Twitter intervention or to accounts moving to other platforms out of fear of being shut down.
 
@@
 2020~\cite{pennycook2020implied}).
-Using another approach, Mosleh et al. (\cite{mosleh2021perverse}) identified Twitter users sharing false news and replied to their false tweets with links to fact-checking websites.
+Using another approach, Mosleh et al. \cite{mosleh2021perverse} identified Twitter users sharing false news and replied to their false tweets with links to fact-checking websites.
 They observed a decrease in quality and accuracy of the content subsequently shared by the corrected user. 

### 2021-08-25 article/draft.tex
few minor updates and typos in the discussion

--- 2021-08-23 article/draft.tex
@@
 
-There is growing pressure for mainstream platforms, such as Facebook, Twitter or YouTube, to moderate the available content. 
-Collecting social media data via API and scraping, we investigated their interventions through a series of examples. 
-These interventions can be classified into three broad categories: 
-(i) temporary or permanent suspension of users, 
-(ii) introducing flags and notices, and 
-(iii) reducing the visibility of some content. 
-Use cases belonging to each category will be shown for Facebook, Twitter and YouTube. 
-Finally, we discuss how an increased effort of transparency can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.
-
+There is growing pressure for mainstream platforms, such as Facebook, Twitter or YouTube, to fight misinformation by moderating the content that spreads on their site.
+We investigated the interventions of the platforms by collecting social media data via APIs and scraping.
+These interventions can be classified into three broad categories: (i) temporary or permanent suspension of users, (ii) displaying flags and information panels, and (iii) reducing the visibility of some content.
+We provide examples illustrating how researchers can monitor the interventions within each of the three categories for each platform.
+Finally, we discuss the restrictions to access data and the lack of transparency regarding misinformation related interventions, and how to help the academic community, NGOs and data journalists to successfully study online misinformation.
 \end{abstract}
@@
 
-In this article we have assessed three broad categories of interventions to tackle misinformation by Facebook, Twitter and YouTube: $(i)$ suspension of accounts, $(ii)$ introduction of flags, labels and information panels and $(iii)$ reducing the visibility of content.
-\footnote{For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.}
+In this article we have assessed three broad categories of interventions to tackle misinformation by Facebook, Twitter and YouTube: $(i)$ suspension of accounts, $(ii)$ introduction of flags, labels and information panels and $(iii)$ reducing the visibility of content.\footnote{For a detailed list of interventions of multiple platforms, we invite the reader to navigate through the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.}
 Furthermore, we have provided a methodology that can be useful for third-party monitoring. 
@@
 We tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
-It is of course not surprising that plaforms are regulating their content, sometimes by removing it, but we would argue that it could simplify the researchers' work if deleted data could still be accessible in the APIs.
-
-Although it is currently impossible to verify permanent deletions using social media data, their effects can be observed using an adapted methodology.
-Following the Capitol riots in January 2021, Twitter has announced the suspension of more than $70$ $000$ accounts related to QAnon.
-\footnote{\url{https://blog.twitter.com/en_us/topics/company/2021/protecting--the-conversation-following-the-riots-in-washington--}} 
-A journalist has recently investigated the effects of this measure by counting the number of times some hashtags specific to the QAnon movement have been used over time, such as \#QAnon or \#WWG1WGA.
-A drastic reduction in hashtag use was found when comparing the first quarter of $2021$ with the first quarter of $2021$.
-\footnote{\url{https://twitter.com/Shayan86/status/1394742784683298818}}
-Thus, counting specific hashtag use over time allows to indirectly observe permanent suspensions on Twitter, and there is a need for similar methodologies to be experimented on the other platforms' data.
+It is of course not surprising that platforms are regulating their content, sometimes by removing it. 
+Nevertheless, researchers' work could be simplified, if deleted data could still be accessible via the APIs.
+
+Although it is currently impossible to verify permanent deletions using available social media data, their effects can be observed using an adapted methodology.
+Following the Capitol riots in January $2021$, Twitter has announced the suspension of more than $70$ $000$ accounts related to QAnon.\footnote{\href{https://blog.twitter.com/en\_us/topics/company/2021/protecting--the-conversation-following-the-riots-in-washington--}{https://blog.twitter.com/en\_us/topics/company/2021/protecting--the-conversation-following-the-riots-in-washington--}.}
+A journalist has recently investigated the effects of this measure by counting the number of times hashtags related to the QAnon movement have been used over time, such as \#QAnon or \#WWG1WGA.
+A drastic reduction in hashtag use was found when comparing the first quarter of $2021$ with the first quarter of $2021$.\footnote{See \href{https://twitter.com/Shayan86/status/1394742784683298818}{https://twitter.com/Shayan86/status/1394742784683298818}.}
+Thus, counting specific hashtag use over time allows to indirectly observe permanent suspensions on Twitter and there is a need for similar methodologies to be experimented on data from other platforms.
+However, a point of concern is that data can also disappear because of other factors independent of platforms' content moderation.
+To provide an example, McMinn et al. (2012)\cite{mcminn2013building} collected $120$ million tweets related to general topics. 
+The same published set of Tweet IDs was then used by Mazoyer et al.
+(2020)~\cite{mazoyer2020french}, to run the same collection in $2018$.
+Mazoyer et al.
+2020~\cite{mazoyer2020french} were only able to retrieve $67$ millions of tweets (55\%).
+The authors argue that this drop is probably due to tweets having been removed by users and Twitter accounts being shut by the users themselves.
+As data can disappear from platforms over time, it is hard to distinguish whether platforms or users are the ones responsible for data removal. 
+Hence in the special case of Twitter accounts related to QAnon, it is hard to identify how much of the drop in QAnon related hashtag use is due to the Twitter intervention or to accounts migrating to other platforms out of fear of having their accounts suspended by the platform.
 
@@
 In particular, the $reach$ of posts on Facebook, which is the number of people who actually see a given post, cannot be recovered from the CrowdTangle API.
-\footnote{\url{https://help.crowdtangle.com/en/articles/4558716-understanding-and-citing-crowdtangle-data}} 
+\footnote{See \href{https://help.crowdtangle.com/en/articles/4558716-understanding-and-citing-crowdtangle-data}{https://help.crowdtangle.com/en/articles/4558716-understanding-and-citing-crowdtangle-data}.}
 Hence, researchers can only build proxies for this metric based on available data (see section \ref{reduce_fb} for an example). 
 Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs, with the exception of the {\it withheld}  and {\it possibly sensitive content} interstitials in the Twitter API v2.
-For the purposes of the present research we thus had to scrape this information from Facebook, Twitter and YouTube. 
+For the purposes of the present research we thus had to scrape this information from publicly available content on Facebook, Twitter and YouTube. 
 Again, this disrupts the monitoring of the platforms' interventions and the assessment of their impact (Pasquetto, Swire-Thompson, Amazeen et al. (2020)~\cite{pasquetto}).
@@
 
-A last concern regards the growing restrictions to access APIs (Perriam et al. 2019~\cite{api}).
-In April 2018, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs\footnote{\url{https://about.fb.com/news/2018/04/restricting-data-access/}, \url{http://thepoliticsofsystems.net/2018/08/facebooks-app-review-and-how-independent-research-just-got-a-lot-harder/}},
+A last concern regards the growing restrictions to access APIs (Perriam et al.(2019)~\cite{api}).
+In April $2018$, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs\footnote{See \href{https://about.fb.com/news/2018/04/restricting-data-access/}{https://about.fb.com/news/2018/04/restricting-data-access/} and \href{http://thepoliticsofsystems.net/2018/08/facebooks-app-review-and-how-independent-research-just-got-a-lot-harder/}{http://thepoliticsofsystems.net/2018/08/} \href{http://thepoliticsofsystems.net/2018/08/facebooks-app-review-and-how-independent-research-just-got-a-lot-harder/}{/facebooks-app-review-and-how-independent-research-just-got-a-lot-harder/}.}
 and CrowdTangle is today a reliable source for researchers to access Facebook data. 
-However, it should be noted that CrowdTangle has been recently used by journalists to show that Facebook is spreading biased information\footnote{\url{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}, \url{https://twitter.com/facebookstop10}.
+However, it should be noted that CrowdTangle has been recently used by journalists to show that Facebook is spreading biased information\footnote{See the news article \href{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news} and the tweet \href{https://twitter.com/facebookstop10}{https://twitter.com/facebookstop10}.
 The last link is a Twitter account showing each day the ten most shared link on Facebook, most of them coming from extreme right and misinformation sources. 
-Facebook has reacted to this here: \url{https://about.fb.com/news/2020/11/what-do-people-actually-see-on-facebook-in-the-us/}}, 
-and a general suspicion is growing that its access might be shut down in a near future to journalists and researchers.\footnote{\url{https://www.nytimes.com/2021/07/14/technology/facebook-data.html}, \url{https://www.bloomberg.com/news/articles/2021-08-03/facebook-disables-accounts-tied-to-nyu-research-project}}
-Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs, although the number of Tweets that can be retrieved has decreased between the Twitter API v1 and v2.
-In the v2, there is a monthly cap of 10,000,000 Tweets for the academic research track\footnote{https://developer.twitter.com/en/docs/projects/overview},
-while there was no monthly limit in the v1, only a limit in the number of requests that could be made in a 15-minute window\footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
-We thus noticed that we could get around 10 times more Tweets per month with the v1 when compared to the v2 for one specific collection.
+Facebook has reacted to this here: \href{https://about.fb.com/news/2020/11/what-do-people-actually-see-on-facebook-in-the-us/}{https://about.fb.com/news/2020/11/what-do-people-actually-see-on-facebook-in-the-us/}.}
+and a general suspicion is growing that its access might be shut down in a near future to journalists and researchers.\footnote{See the news articles \href{https://www.nytimes.com/2021/07/14/technology/facebook-data.html}{https://www.nytimes.com/2021/07/14/technology/facebook-data.html} and \href{https://www.bloomberg.com/news/articles/2021-08-03/facebook-disables-accounts-tied-to-nyu-research-project}{https://www.bloomberg.com/news/articles/2021-08-03/facebook-disables-accounts-tied-to-nyu-research-project}.}
+Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs.
+Nevertheless the number of Tweets that can be retrieved has decreased between the Twitter API v1 and v2.
+In the v2, there is a monthly cap of $10,000,000$ Tweets for the academic research track\footnote{https://developer.twitter.com/en/docs/projects/overview},
+while in the v1 there was no monthly limit and only a limit on the number of requests that could be made in a 15-minute window\footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
+We thus noticed that we could get around $10$ times more Tweets per month with the v1 when compared to the v2 for one specific collection.
 
@@
 For example, while conducting the present research, it was brought to our attention that the Twitter account related to the domain name $globalresearch.ca$ was suspended. 
-But, there was no official communication by the Twitter Safety team to explain the reasons of this suspension (see section \ref{globalresearch}).
+But to the best of our knowledge, there was no official communication by the Twitter Safety team to explain the reasons of this suspension (see section \ref{globalresearch}).
 
@@
 Similarly, we came across notational variants on Twitter of the domain name {\it off-guardian.org}
-\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}},
-such as {\it off-guardian. org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}.
-\footnote{For this case, we failed to understand precisely what kind of intervention Twitter users were circumventing, since they could share in a Tweet an article redirecting to the website {\it off-guardian.org} with the correct notation and only a warning message would appear when one clicks on it.}
+\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}}
+such as {\it off-guardian.
+org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}.\footnote{For this case, we failed to understand precisely what kind of intervention Twitter users were circumventing, since they could share in a Tweet an article redirecting to the website {\it off-guardian.org} with the correct notation and only a warning message would appear when one clicks on it.}
 Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
@@
 In certain cases, the platform interventions were not motivated by content moderation to limit misinformation, but rather by other rule violations.
-For example, the official reason for the suspension of Donald Trump's Twitter account was not misinformation\footnote{Although Donald Trump spread many misinformation during his governance \url{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}},
-but the violation of Twitter's Glorification of Violence Policy, with his last tweets encouraging the Capitol's riot\footnote{\url{https://blog.twitter.com/en_us/topics/company/2020/suspension}}.
+For example, the official reason for the suspension of Donald Trump's Twitter account was not misinformation\footnote{Although Donald Trump may have spread many misinformation during his governance, see for example: \href{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}.}
+but the violation of Twitter's Glorification of Violence Policy, with his last tweets encouraging the Capitol's riot.\footnote{See \href{https://blog.twitter.com/en\_us/topics/company/2020/suspension}{https://blog.twitter.com/en\_us/topics/company/2020/suspension}.}
 Similarly, when Facebook removed four pages related to the InfoWars website, the cited reason was repeated violations of Community Standards: 
-``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''.\footnote{\url{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}}
-Regarding The Beauty of Life website, its ban was officially due to coordinated inauthentic behavior\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}},
+``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''.\footnote{See the article \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}.}
+Regarding The Beauty of Life website, its ban was officially due to coordinated inauthentic behavior,\footnote{See \href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}
 which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content. 
-According to Facebook, coordinated inauthentic behavior is a distinct phenomenon from disinformation, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false''.
-\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.} 
-Nevertheless, both misinformation and coordinated inauthentic behavior were attested for the Beauty of Life, and reported to Facebook by the fact-checking organization Snopes.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/},
-\href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-} \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{fake-profiles/} , 
-\href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}} 
+According to Facebook, coordinated inauthentic behavior is a distinct phenomenon from disinformation, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false''.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.}
+Nevertheless, both misinformation and coordinated inauthentic behavior were attested for the Beauty of Life, and reported to Facebook by the fact-checking organization Snopes.\footnote{See \href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/},
+\href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-} \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{fake-profiles/}  and 
+\href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}.} 
 In the above ``known'' examples, the compagnies' communication was very clear on the reason of the interventions (although one can suspect that the official reason given can depart from the real motivation behind an intervention).
-But often no communication can be found for a specific intervention observed in collected data. 
+However, very often no official communication on behalf of the platforms can be found for a specific interventions observed in collected data. 
 Because misinformation is often associated with creating fake accounts to speed its spread, and incitation to violence, it is sometimes unclear to distinguish between interventions due to misinformation and interventions due to other guideline violations, and more transparent communication on platforms' actions would help monitor the interventions specifically related to misinformation.
@@
 
-{\bf A need for more consistent and adapted policies.}
-Both Infowars and The Beauty of Life domains are considered as spreading misinformation (they are both on the Iffy+ list\footnote{https://iffy.news/iffy-plus/}), and violated Facebook's guidelines (incitation to violence and coordinated unauthentic behavior).
-Yet one's distribution was reduced for only half a year, while the other one's links cannot be shared anymore on Facebook since the end of 2019, and it is not clear why such double standard was applied on these comparable websites.
-Misinformation on the web is a problem that is increasingly discussed since the 2016 American elections, and in the years that followed, the platforms may have decided manually and on a case-by-case basis which action to enforce.
-It is also possible that platforms usually follow specific rules on how to fight misinformation, but that sometimes the sudden mediatization of specific events leads them to take exceptional actions, such as with the Capitol riots and Trump's suspension from Facebook, Twitter and YouTube.
-We would argue that to efficiently curb the spread of misinformation, policies should be clearly stated and consistently applied, instead of inteventions being implemented on a case-by-case basis and decided in response to the latest news events.
-
-\smallskip
-
-It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
+{\bf A need for more consistent and adapted policies.} Misinformation on the web is a problem that is increasingly discussed since the $2016$ American elections and in the years that followed, platforms may have decided on a case-by-case basis which actions to enforce.
+Infowars and The Beauty of Life domains have both several failed fact-checks\footnote{They are both on the Iffy+ list, see \href{https://iffy.news/iffy-plus/}{https://iffy.news/iffy-plus/}.} and have both violated Facebook's community guidelines (incitation to violence and coordinated unauthentic behavior).
+Yet one's distribution was reduced for only half of a year, while the other one's links cannot be shared anymore on Facebook since the end of $2019$, and it is not clear why such double standard was applied on these comparable websites.
+It is also possible that platforms usually follow specific rules on how to fight misinformation, but that sometimes the sudden media coverage of specific events leads them to take exceptional actions, such as with the Capitol riots and Trump's suspension from Facebook, Twitter and YouTube.
+We would argue that to efficiently curb the spread of misinformation, policies should be clearly stated and consistently applied, rather than implementing interventions on a case-by-case basis and in response to the latest news events.
+
+\smallskip
+
+Furthermore, it is likely that most interventions used to tackle online misinformation correspond to interventions that were designed for earlier policy areas.
 To illustrate, YouTube explicitly states
@@
 that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
-$Classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech, but tackling online misinformation might need adapted interventions.
+Hence interventions such as content deletion or account suspension, might be efficient for policy areas for which they were designed, such as Adult Nudity \& Sexual Activity or Hate Speech.
+Nevertheless, tackling online misinformation might need adapted interventions.
 Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation (Rogers (2020)~\cite{rogers2020}, Robins-Early (2019)~\cite{huffpost}).
@@
 
-How to best tackle online misinformation is an active area of research, and developing effective interventions against misinformation depends on understanding the psychology of interacting with social media (Pennycook et Rand 2021~\cite{pennycook2021psychology}).
+How to best tackle online misinformation is an active area of research, and developing effective interventions against misinformation depends on understanding the psychology of interacting with social media (Pennycook and Rand (2021)~\cite{pennycook2021psychology}).
 Adding fact-checking labels to controversial content is certainly the intervention whose effectiveness was the most studied so far. 
-It was shown that credibility indicators do reduce misperceptions and sharing, although their impact varied vastly depending on the presentation of the warnings (Yaqub 2020~\cite{yaqub2020effects}, Sharevski 2021~\cite{sharevski2021misinformation}).
+It was shown that credibility indicators do reduce misperceptions and sharing, although their impact varied vastly depending on the presentation of the warnings (Yaqub (2020)~\cite{yaqub2020effects}, Sharevski (2021)~\cite{sharevski2021misinformation}).
 Moreover, a fact-checking label can lead to unpredicted consequences depending on the perception of the person reading it.
@@
 Such sparce application of warnings can lead to an `implied truth' effect where users may assume that content without warnings have actually been verified and shown to be true (Pennycook et al.
-2020~\cite{pennycook2020implied}).
-Using another approach, Mosleh et al. (\cite{mosleh2021perverse}) identified Twitter users sharing false news and replied to their false tweets with links to fact-checking websites.
+(2020)~\cite{pennycook2020implied}).
+Using another approach, Mosleh et al. (2021)~\cite{mosleh2021perverse} identified Twitter users sharing false news and replied to their false tweets with links to fact-checking websites.
 They observed a decrease in quality and accuracy of the content subsequently shared by the corrected user. 

### 2021-08-25 article/draft.tex
cosmetic changes in the discussion + figure size

@@
 		%\begin{multicols}{1}
-			\includegraphics[scale=0.4]{../figure/facebook_crowdtangle_trump.png}
+			\includegraphics[scale=0.32]{../figure/facebook_crowdtangle_trump.png}
 		%\end{multicols}
@@
 \begin{figure}[h]
-\centering
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.27]{../figure/lifesite.jpg} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.27]{../figure/lifesite_domain.jpg}
+\hspace{-2em}
+%\centering
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.32]{../figure/lifesite.jpg} 
+	%\end{multicols}
+	%\begin{multicols}{1}
+		\includegraphics[scale=0.32]{../figure/lifesite_domain.jpg}
 	%\end{multicols}
@@
 	%\centering
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.32]{../figure/OANN_videos_yt.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.32]{../figure/OANN_views_yt.png} 
-	%\end{multicols}
 	\caption{Left Panel: Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
@@
 \begin{figure}[h]
-	\centering
-
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.25]{../figure/facebook_crowdtangle_infowars_1.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.25]{../figure/facebook_crowdtangle_infowars_2.png} 
-	%\end{multicols}
-
+\hspace{-2em}
+	%\centering
+		\includegraphics[scale=0.32]{../figure/facebook_crowdtangle_infowars_1.png}
+		\includegraphics[scale=0.32]{../figure/facebook_crowdtangle_infowars_2.png} 
 	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API.
@@
 \begin{figure}[h]
-	\centering
-
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{../figure/facebook_buzzsumo_thebl_1.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.3]{../figure/facebook_buzzsumo_thebl_2.png} 
-	%\end{multicols}
-
+\hspace{-2em}
+	%\centering
+		\includegraphics[scale=0.32]{../figure/facebook_buzzsumo_thebl_1.png}
+		\includegraphics[scale=0.32]{../figure/facebook_buzzsumo_thebl_2.png} 
 	\caption{Articles from The Beauty of Life website (thebl.com) published between January 1, 2019 and June 15, 2021 and gathered from the Buzzsumo API.
@@
 \end{figure}
-%BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.
 
@@
 
-%\smallskip
-
-%To illustrate we provide two examples linked to the Twitter accounts of the websites $globalresearch.ca$ and $off$-$guardian.org$.
-Both websites have several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and for $off-guardian.org$ see \href{https://mediabiasfactcheck.com/offguardian/}{https://mediabiasfactcheck.com/offguardian/}.
-}
 \begin{figure}[h]
 	\centering
-		%\begin{multicols}{1}	
-					\includegraphics[scale=0.35]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
-		%\end{multicols}
-		%\begin{multicols}{1}
+%\hspace{-2em}
+	\includegraphics[scale=0.32]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
 	\includegraphics[scale=0.32]{./img/globalresearch/tweet.png}
-		%\end{multicols}
+
 	\caption{Screenshots taken on June 14, 2021.
@@
 \begin{figure}[h]
-\centering
-		\includegraphics[scale=0.27]{../figure/globalresearch_domain_2021-08-17.jpg} 
-		\includegraphics[scale=0.27]{../figure/globalresearch_domain_engagement_2021-08-17.jpg}
+%\centering
+\hspace{-2em}
+		\includegraphics[scale=0.32]{../figure/globalresearch_domain_2021-08-17.jpg} 
+		\includegraphics[scale=0.32]{../figure/globalresearch_domain_engagement_2021-08-17.jpg}
 \caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.
@@
 \subsection{YouTube}
-
-%what about with search terms: most recommended channels?
 
@@
 
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[scale=0.45]{./img/channel_youtube.png} 
+	\end{center}
+	\caption{Top ten recommended channels among the $1$ $562$ different channels, that have posted the recommended videos in our dataset.}
+	\label{channels_yt}
+\end{figure}
+
 {\bf Channel Level.} We examined the top recommended channels in the collected data.
@@
 Among the top three most recommended channels, there is Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to {\it iffy.news} and have several failed fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} Also in the top ten most recommended, we find PragerU, which has a ``low'' level of factual reporting according to {\it iffy.news}.
-
-\begin{figure}[h]
-	\begin{center}
-		\includegraphics[scale=0.6]{./img/channel_youtube.png} 
-	\end{center}
-	\caption{Top ten recommended channels among the $1$ $562$ different channels, that have posted the recommended videos in our dataset.}
-	\label{channels_yt}
-\end{figure}
 
@@
 that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
-Hence interventions such as content deletion or account suspension, might be efficient for policy areas for which they were designed, such as Adult Nudity \& Sexual Activity or Hate Speech.
+Hence interventions such as content deletion or account suspension, might be efficient for policy areas for which they were specifically designed, such as the policy area {\it Adult Nudity \& Sexual Activity}.
 Nevertheless, tackling online misinformation might need adapted interventions.
-Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation (Rogers (2020)~\cite{rogers2020}, Robins-Early (2019)~\cite{huffpost}).
-
-\smallskip
-
-How to best tackle online misinformation is an active area of research, and developing effective interventions against misinformation depends on understanding the psychology of interacting with social media (Pennycook and Rand (2021)~\cite{pennycook2021psychology}).
+Namely, account suspensions or content deletion motivated by the spread of inaccurate information can be perceived as censorship by the targeted users.
+In particular, such interventions can generate platform migrations towards new alternative social media platforms (e.g.
+Telegram, Gab, Minds) with little or no content moderation (see Rogers (2020)~\cite{rogers2020}).
+
+\smallskip
+
+Finally, the means to tackle online misinformation is an active area of research and developing effective interventions against misinformation depends on understanding the psychology of interacting with social media (Pennycook and Rand (2021)~\cite{pennycook2021psychology}).
 Adding fact-checking labels to controversial content is certainly the intervention whose effectiveness was the most studied so far. 
-It was shown that credibility indicators do reduce misperceptions and sharing, although their impact varied vastly depending on the presentation of the warnings (Yaqub (2020)~\cite{yaqub2020effects}, Sharevski (2021)~\cite{sharevski2021misinformation}).
+It was shown that credibility indicators do reduce misperceptions and sharing, although their impact varied vastly depending on the presentation of the warnings (see Yaqub (2020)~\cite{yaqub2020effects} and Sharevski (2021)~\cite{sharevski2021misinformation}).
 Moreover, a fact-checking label can lead to unpredicted consequences depending on the perception of the person reading it.
-On Facebook, Twitter and YouTube, fact-checking messages are currently applied only to some content, while the rest of the platform remains unlabelled. 
-Such sparce application of warnings can lead to an `implied truth' effect where users may assume that content without warnings have actually been verified and shown to be true (Pennycook et al.
+On Facebook, Twitter and YouTube, fact-checking messages are currently applied only to some content, while the rest of the content on a given platform remains naturally unlabelled. 
+Such sparse application of warnings can lead to an ``implied truth'' effect, where users may assume that content without warnings have actually been verified and shown to be true (Pennycook et al.
 (2020)~\cite{pennycook2020implied}).
-Using another approach, Mosleh et al. (2021)~\cite{mosleh2021perverse} identified Twitter users sharing false news and replied to their false tweets with links to fact-checking websites.
-They observed a decrease in quality and accuracy of the content subsequently shared by the corrected user. 
-These works highlight the necessity to investigate potential unintended effects of well-meaning interventions.
-The methods presented in this paper can help to monitor not only the platforms' actions against misinformations, but also their subsequent consequences in real-life settings.
-
-\smallskip
+Using a different approach, Mosleh et al.
+(2021)~\cite{mosleh2021perverse} identified Twitter users sharing false news and replied to their false tweets with links redirecting to fact-checking websites.
+They observed a decrease in the quality and accuracy of the content subsequently shared by the corrected user. 
+These research papers highlight the necessity to investigate potential unintended effects of well-meaning interventions.
+The methods presented in this paper can help to monitor not only the platforms' actions against misinformation, but also their subsequent consequences in real-life settings.
+
+%\smallskip
 
@@
 
-\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}} Flags, Notice \\ and Information Panels \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}}    \end{tabular}                            \\ \cline{2-3}
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}} Flags, Notice \\ and Information Panels \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}}  \href{https://www.facebook.com/business/help/341102040382165}{https://www.facebook.com/business/help/341102040382165}   \end{tabular}                            \\ \cline{2-3}
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   &  \begin{tabular}[c]{@{}cl@{}} \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}    \end{tabular}    \\ \cline{2-3}

### 2021-08-26 code/collect_facebook_crowdtangle_false_link.sh
update code to new minet command

@@ -1,14 +1,0 @@
-#!/bin/bash
-
-TODAY_DATE=$(date +"%Y-%m-%d")
-
-minet ct search \
-"https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html" \
-  --search-field include_query_strings --platform facebook --start-date 2019-01-01 > \
-  "./data/facebook_crowdtangle_raw_false_link_${TODAY_DATE}.csv"
-
-# On minet's new banch only for now. 
-# TO DO: change when minet's new version will be released.
-
-lminet fb post-stats post_url "./data/facebook_crowdtangle_raw_false_link_${TODAY_DATE}.csv" \
-  -s post_url > "./data/facebook_crowdtangle_false_link_${TODAY_DATE}.csv"

### 2021-08-26 code/collect_flags_facebook.sh

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+TODAY_DATE=$(date +"%Y-%m-%d")
+
+minet ct summary url "./data/appearances_july.csv" \
+ --posts "./data/facebook_false_links_${TODAY_DATE}.csv" \
+ --sort-by total_interactions --start-date 2021-01-01 --platforms facebook
+
+# On minet's new banch only for now. 
+
+lminet fb post-flags post_url "./data/facebook_false_links_${TODAY_DATE}.csv" \
+  -s post_url > "./data/facebook_false_links_flags_${TODAY_DATE}.csv"
+
+# minet ct search \
+# "https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html" \
+#   --search-field include_query_strings --platform facebook --start-date 2019-01-01 > \
+#   "./data/facebook_crowdtangle_raw_false_link_${TODAY_DATE}.csv"

### 2021-08-26 article/draft.tex
link about misinfo YT added to the summary table in Appendix

@@
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   &        \\ \cline{2-3} 
-                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}  \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}  \\ \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}    \end{tabular}                            \\ \hline
+                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}  \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}  \\ \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/} \\ \href{https://blog.youtube/inside-youtube/tackling-misinfo}{https://blog.youtube/inside-youtube/tackling-misinfo}    \end{tabular}                            \\ \hline
 

### 2021-08-26 article/draft.tex
rewrite a bit YouTube remove

--- 2021-08-25 article/draft.tex
@@
 
-To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two YouTube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
-The website of One America News Network has a ``low'' factual reporting score according to iffy.news and several inaccurate articles according to feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}  Tony Heller posts regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}} Both are active on YouTube and both have communicated via their Twitter account about restrictions applied by YouTube over their content (see figure \ref{fig2_oann}).
-
-\smallskip
-
-First, we investigate the temporary suspension of the YouTube channel of {\it One America News channel}.
+To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following YouTube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
+The website of One America News Network has a ``low'' factual reporting score according to iffy.news and several inaccurate articles according to feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}
+Tony Heller posts regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}}
+Both are active on YouTube and both have communicated via their Twitter account about restrictions applied by YouTube over their content (see figure \ref{fig2_oann}).
+
+\smallskip
+
+First, we investigate the temporary suspension of the YouTube channel of One America News Networks.
 According to the News outlet NBCnews (2020)~\cite{nbcnews}, this YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
 We collected the activity of the channel OANN (video counts and view counts) using the YouTube API v3, between November $2020$ and January $2021$.
-For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the videos endpoint we retrieved the view counts on June $2021$.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
+For the video counts, we used the {\it playlists} endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the {\it videos} endpoint we retrieved the view counts on June $2021$.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
+
+\smallskip
+
+Figure \ref{fig1_oann} shows the daily number of videos uploaded by the channel, and its number of views. 
+We can clearly see the suspension period in the data, as the number of published video is down to zero for one week after the strike on November $24$, $2020$. 
+Because no videos were published during this period, the number of views were also nul.
+When comparing one month before and after the suspension, the view count decreased by -73\%, indicating that the videos uploaded after the suspension were less popular. 
+Furthermore, the activity of the channel was close to zero after March 2021, and OANN's Twitter account has announced their migration from YouTube to Rumble on March 17, 2021.
 
@@
 	%\centering
-		\includegraphics[scale=0.32]{../figure/OANN_videos_yt.png}
-		\includegraphics[scale=0.32]{../figure/OANN_views_yt.png} 
+		\includegraphics[scale=0.32]{../figure/delete_youtube_1_oann.png}
+		\includegraphics[scale=0.32]{../figure/delete_youtube_2_oann.png} 
 	\caption{Left Panel: Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021.
 Right Panel: accumulated view counts for videos.
-The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints.
+The metrics correspond to the videos’  publishing date and the data is retrieved from the YouTube API with the {\it playlists} and  {\it videos} endpoints.
 }
@@
 
-The view count decreased by -73\% and the videos uploaded decreased by -55\% (see figure \ref{fig1_oann}), when comparing one month before the suspension from 2020/10/24 to 2020/11/24 and one month after from 2020/12/01 to 2021/01/01.
-Furthermore, the activity of the YouTube channel was close to zero, since the channel has announced via their Twitter account (see figure \ref{fig2_oann}) their migration to the alternative platform Rumble on March 17, 2021.
-
-\smallskip
-
-We now turn to a
-second example, the YouTube channel Tony Heller was also temporarily suspended. 
+\smallskip
+
+We now turn to a second example, the YouTube channel Tony Heller. 
 This channel got its first strike after posting a video about an anti-covid-lockdown doctor getting arrested (see screenshot in figure \ref{fig2_oann}). 
 The suspension period lasted one week from September $29$ until October $5$.
-We applied the same methods as in the previous example for the data collection.
-Figure \ref{fig1_tony} shows the daily number of videos uploaded by the channel.
-The suspension period can be observed clearly in the historical data of the channel.
-Using view counts one month before the suspension starting from $2020/08/28$ to $2020/09/28$ and one month after the suspension from $2020/10/05$ to $2020/11/05$, the channel witnessed a drop of view counts by $-69.5\%$ and the videos published in the channel were less by $-29\%$.
-This drop in views can show that the  suspension  period
-may  have  a  good  impact  on  reducing  the  audience interest or reach to the channel.
+We applied the same methods as in the previous example to collect data.
+Again the one-week suspension period can be observed clearly in the daily number of uploaded videos and of views.
+Comparing one month before and after the suspension, this channel also witnessed a drop of view counts by $-70\%$.
 
@@
 	%\centering
-			\includegraphics[scale=0.32]{../figure/Tony_Heller_videos_yt.png}
-			\includegraphics[scale=0.32]{../figure/Tony_Heller_views_yt.png}
+			\includegraphics[scale=0.32]{../figure/delete_youtube_3_tony_heller.png}
+			\includegraphics[scale=0.32]{../figure/delete_youtube_4_tony_heller.png}
 	\caption{Left Panel: Number of YouTube videos uploaded each day by the YouTube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020.
@@
 \end{figure}
+
+[CONCLUSION]
+This drop in views can show that the  suspension  period may  have  a  good impact on reducing  the  audience interest or reach to the channel.
 

### 2021-08-26 code/create_figures.py

@@ -382,17 +382,17 @@ def create_youtube_graph():
 
     oann, tony_heller = preprocess_youtube_data()
     plot_view_count_youtube(oann, '2020-11-25', '2020-12-01', date(2020, 11, 1), date(2021, 1, 1),
-                            2680000,'OANN_views_yt.png',
+                            2680000,'delete_youtube_2_oann.png',
                             title = 'View count of videos by the YouTube channel OANN')
     plot_view_count_youtube(tony_heller, '2020-09-29', '2020-10-05', date(2020, 9, 1),
-                            date(2020, 11, 15), 1500000,'Tony_Heller_views_yt.png',
+                            date(2020, 11, 15), 1500000,'delete_youtube_4_tony_heller.png',
                             title = 'View count of videos by the YouTube channel Tony Heller')
 
     plot_video_count_youtube(oann, '2020-11-25', '2020-12-01', date(2020, 11, 1), date(2021, 1, 1),
-                             32,'OANN_videos_yt.png',
+                             32,'delete_youtube_1_oann.png',
                             title = 'Video uploads by the YouTube channel OANN')
     plot_video_count_youtube(tony_heller, '2020-09-29', '2020-10-05', date(2020, 9, 1),
-                             date(2020, 11, 15), 10,'Tony_Heller_videos_yt.png',
+                             date(2020, 11, 15), 10,'delete_youtube_3_tony_heller.png',
                              title = 'Video uploads by the YouTube channel Tony Heller')
 
 
@@ -549,6 +549,7 @@ if __name__=="__main__":
     create_buzzsumo_thebl_figure()
     create_facebook_crowdtangle_infowars_figure()
     create_facebook_buzzsumo_infowars_figure()
+    
     create_youtube_graph()
 
     create_twitter_figures()

### 2021-08-27 code/create_figures.py
Update create_figure: youtube

@@ -365,13 +365,13 @@ def create_plot_top_channel_youtube(path_to_data):
     plt.xticks(alpha=0.7)
     # Create names on the x-axis
     plt.yticks(y_pos, channel_fre['index'], alpha=0.7)
-    ax.set_xlabel('Number of videos recommended')
+    ax.set_xlabel('Number of video recommendations at the Channel level')
     ax.spines['right'].set_visible(False)
     ax.spines['left'].set_visible(False)
     ax.spines['top'].set_visible(False)
     ax.spines['bottom'].set_visible(False)
     ax.yaxis.set_label_position("right")
-    ax.yaxis.tick_right()
+    #ax.yaxis.tick_right()
     plt.gca().invert_yaxis()
     fig_name = "channel_youtube_top_10"
     figure_path = os.path.join('.', 'figure', fig_name)
@@ -544,7 +544,7 @@ def create_twitter_figures():
 
 
 if __name__=="__main__":
-
+    '''
     create_facebook_trump_figure()
     create_buzzsumo_thebl_figure()
     create_facebook_crowdtangle_infowars_figure()
@@ -553,3 +553,5 @@ if __name__=="__main__":
     create_youtube_graph()
 
     create_twitter_figures()
+    '''
+    create_plot_top_channel_youtube('/home/dana/Desktop/WebclimProject/truth-and-trust-online-2021/data/02L_LUpSqeA_experiment_2.csv')

### 2021-08-30 article/draft.tex
rewrite the YouTube flags section

@@
 \usepackage{lscape}
+\usepackage{makecell}
 \usetikzlibrary{shapes,snakes}
@@
 \begin{tabular}[c]{@{}c@{}}with the interstitial\\ ``potentially sensitive \\ content'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Get the facts \\ about COVID-19'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Learn about US \\ 2020 election \\ security efforts'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag\\ ``This claim about \\ election fraud \\ is disputed''\end{tabular} \\ \hline
-\begin{tabular}[c]{@{}c@{}}9344\\ ( 2.88450 \%)\end{tabular}                                  & \begin{tabular}[c]{@{}c@{}}28\\ (0.00864\%)\end{tabular}                              & \begin{tabular}[c]{@{}c@{}}5\\ (0.00154\%)\end{tabular}                                                & \begin{tabular}[c]{@{}c@{}}1\\ (0.00030\%)\end{tabular}                                             \\ \hline
+\begin{tabular}[c]{@{}c@{}}9344\\ (2.88450 \%)\end{tabular}                                  & \begin{tabular}[c]{@{}c@{}}28\\ (0.00864 \%)\end{tabular}                              & \begin{tabular}[c]{@{}c@{}}5\\ (0.00154 \%)\end{tabular}                                                & \begin{tabular}[c]{@{}c@{}}1\\ (0.00030 \%)\end{tabular}                                             \\ \hline
 \end{tabular}
@@
 YouTube may provide an information panel for videos with topics that are prone to misinformation like COVID-19, moon landing, and climate change. 
-Information panels provide ressources concerning a potentially controversial topic from independent third parties or authoritative ressources.
-YouTube states that these panels exist regardless of the point of view expressed in a given video.
-In addition, these panels are not yet available in all languages and countries.
-%(“Information panel giving topical context”)
-
-\smallskip
-
-To further study the assignment of information panels to videos, we compiled a list of $171$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information.
+Information panels provide ressources concerning a potentially controversial topic from independent third parties or authoritative ressources {\color{red} [LIKE blablabla]}. 
+Importantly, YouTube states that these panels exist regardless of the point of view expressed in a given video. {\color{red} [REF??]}
+%It should be noted that these panels are not yet available in all languages and countries.
+
+\smallskip
+
+To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information.
 We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page. 
-Four types of information panels were found in the list of visited videos as shown in figure \ref{fig9}:  information about Climate change, COVID-19 Vaccine, COVID-19 and US elections.\footnote{See: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/} \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{youtube.com/watch?v=8PAwc8nlE\_Q}.
-Last accessed on  21/07/2021.
-}
-%\footnote{The links of the YouTube videos where the information panel appeared are the following: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{youtube.com/watch?v=OwqIy8Ikv-c}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{youtube.com/watch?v=9sW0OmzcmL0}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{youtube.com/watch?v=usyQgPU-VrI} and \href{https://www.youtube.com/watch?v=8PAwc8nlE_Q}{youtube.com/watch?v=8PAwc8nlE_Q}.
-}
+Five types of information panels were found in the list of visited videos regarding climate change, COVID-19 Vaccine, COVID-19, vaccine hesitancy and US elections, as shown in figure \ref{youtube_panel_screenshots}.
+{\color{red} [ADD Vaccine hesitancy screenshot + REARRANGE SCREENSHOT IN FREQUENCY ORDER]}
 
@@
 	%\end{multicols}
-	\caption{Screenshots taken on July 21, 2021.
-Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}.
-}
-	\label{fig9}
-\end{figure}
-%Nevertheless, we noticed that duplicates of the same YouTube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
-
-We classified the list of $171$ YouTube videos by topic based on its content as shown in table \ref{tab2}.
-We recorded the number of videos containing an information panel within each category.
-For COVID-19 and COVID-19 vaccine related videos, more than half of the videos contained an information panel.
-Nevertheless we noticed that among a set of duplicates of the exact same YouTube video uploaded with different video titles, some contained an information panel while others did not (see figure \ref{duplicates_yt} for an example).
-In addition, we noticed for COVID-19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID-19, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C O V I D 19 or Cv19) it wouldn’t include a panel either.
-Therefore, we suspect that YouTube is automatically adding panels to the videos based on the video title and not the content of the video.
+	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}.
+The videos were accessed on July 21, 2021 from a US server.}
+	\label{youtube_panel_screenshots}
+\end{figure}
+
+\smallskip
+
+We found that almost half (44 \%) of the videos containing misinformation actually had no information panel (Table \ref{youtube_panel_proportions}).
+For the rest of videos, the most frequent information panels found concerned COVID-19 (42 \%) and COVID-19 vaccine (11 \%).
+It is possible that YouTube is currently focusing its efforts on the current `hot' controversial topics with a potentially wide public impact, leaving room for misinformation related to other topics to spread, but more research is needed to formally compare misinformation videos about COVID-19 and about other subjects.
+
+\begin{table}[h] 
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multicolumn{6}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
+\makecell{Without \\ any \\ panel} & 
+\makecell{With a \\ `COVID-19' \\ panel} & 
+\makecell{With a \\ `COVID-19 vaccine' \\ panel} &
+\makecell{With a \\ `climate change' \\ panel} &
+\makecell{With a \\ `U.S. elections' \\ panel} &
+\makecell{With a \\ `vaccine hesitancy' \\ panel}  
+\\ \hline
+\makecell{74 \\ (44 \%)} &
+\makecell{71 \\ (42 \%)} &
+\makecell{19 \\ (11 \%)} &
+\makecell{4 \\ (2 \%)} &
+\makecell{1 \\ (0.5 \%)} &
+\makecell{1 \\ (0.5 \%)}
+\\ \hline
+\end{tabular}
+\caption{Summary of the number of YouTube videos wich contain a certain information panel, among the set of videos marked as false or inaccurate by Science Feedback.}
+\label{youtube_panel_proportions}
+\end{table}
+
+\smallskip
+
+In our list, we noticed that the same video was sometimes uploaded multiple times and thus appeared on different YouTube links. 
+One YouTube link might contain an information panel while its duplicates did not (see figure \ref{duplicates_yt} for an example).  
+In addition, we noticed that some keywords in the video titles were often associated with an information panel, such as `COVID-19', `coronavirus', `pandemic' and `testing', while some notational variants like `C O V I D 19' or `Cv19' were not associated with a panel.
+Therefore, we suspect that YouTube is automatically adding information panels based on the presence of certain keywords in the video title (and maybe in the video description), independently of the content of the video.
+Note that in figure \ref{duplicates_yt}, the video with `C.O.V.I.D.19' in its title had an information panel, hinting that YouTube might adapt its list of `suspect' keywords as new notational variants for COVID-19 appear.
 
@@
 	\centering
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/graph_with_banner.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/news_with_banner.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/graph_no_banner.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.2]{./img/youtube_panels/news_without_banner.png} 
-	%\end{multicols}
-	\caption{Screenshots taken on July 21, 2021.
-The screenshots show two duplicates of the same YouTube video uploaded under different titles.
-Top panels: a YouTube video about COVID-19 which contains an information panel, see \href{https://www.youtube.com/watch?v=d9GbVZOcT18}{https://www.youtube.com/watch?v=d9GbVZOcT18}.
-Bottom panels: a duplicate of the YouTube video in the top panels uploaded under a different title and it does not contain an information panel, see \href{https://www.youtube.com/watch?v=A4RvrEKoNxc}{https://www.youtube.com/watch?v=A4RvrEKoNxc}.
-}
+		\includegraphics[scale=0.24]{./img/youtube_panels/graph_no_banner.png} 
+		\includegraphics[scale=0.24]{./img/youtube_panels/graph_with_banner.png} 
+		%\includegraphics[scale=0.2]{./img/youtube_panels/news_with_banner.png}
+		%\includegraphics[scale=0.2]{./img/youtube_panels/news_without_banner.png} 
+	\caption{Screenshots showing two duplicates of the same video, taken on July 21, 2021. 
+Left panel: a \href{https://www.youtube.com/watch?v=d9GbVZOcT18}{YouTube video} about COVID-19 without an information panel. 	
+Right panel: a \href{https://www.youtube.com/watch?v=A4RvrEKoNxc}{duplicate of the same video} uploaded under a different title and with a `COVID-19 vaccine' information panel.}
 	\label{duplicates_yt}
@@
 
-\smallskip
-
-For climate change we found that most of the videos ($13$ out of $18$) did not display an information panel.
-Lastly, no information panels were found in the general health category set, that included videos that were not related to COVID-19 but contained misinformation concerning cures for cancer, abortion, and viruses.
-Therefore, it is likely that YouTube adds information panels below videos including controversial topics and that can contain misleading information like climate change, COVID-19 and vaccines. 
-It seems that YouTube is focusing its efforts on current ``hot'' topics with a potentially wide public impact (e.g.
-elections, COVID-19), leaving room for misinformation related to other topics to spread.
-
-%drop last colum
-%add % in a second line
-\begin{table}[] 
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-Category       & \begin{tabular}[c]{@{}c@{}}Number of YouTube videos {\bf with} an \\ information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of YouTube videos {\bf without} an \\ information panel\end{tabular}    \\ \hline
-
-\begin{tabular}[c]{@{}c@{}}  Climate change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
-%
-COVID-19 Vaccine        & \begin{tabular}[c]{@{}c@{}} 21     \\ (75\%) \end{tabular}   & \begin{tabular}[c]{@{}c@{}}  7 \\ (25\%)  \end{tabular}     \\ \hline
-%
-COVID-19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
-%
-\begin{tabular}[c]{@{}c@{}} General Health \end{tabular} & \begin{tabular}[c]{@{}c@{}} 0  \\ (0\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 11 \\ (100\%) \end{tabular}         \\ \hline
-\end{tabular}
-\caption{}
-\label{tab2}
-\end{table}
-
 %\subsection{Blocking links}
-
-%
 

### 2021-08-30 article/draft.tex
YT flags: check for clarity and add source

@@
 
-YouTube may provide an information panel for videos with topics that are prone to misinformation like COVID-19, moon landing, and climate change. 
-Information panels provide ressources concerning a potentially controversial topic from independent third parties or authoritative ressources {\color{red} [LIKE blablabla]}. 
-Importantly, YouTube states that these panels exist regardless of the point of view expressed in a given video. {\color{red} [REF??]}
-%It should be noted that these panels are not yet available in all languages and countries.
+YouTube provide information panel at the top of search results or under a video related to topics prone to misinformation.
+Information panels provide more context on a controversial matter, with a link to an independent, third-party partner's website such as Wikipedia or the World Health Organization. 
+Importantly, YouTube states that these panels exist regardless of the point of view expressed in a given video.\footnote{https://support.google.com/youtube/answer/9004474}
 
@@
 To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information.
-We collected the information panels, when present, in each video by connecting to a US server and scraping the content of the web page. 
-Five types of information panels were found in the list of visited videos regarding climate change, COVID-19 Vaccine, COVID-19, vaccine hesitancy and US elections, as shown in figure \ref{youtube_panel_screenshots}.
-{\color{red} [ADD Vaccine hesitancy screenshot + REARRANGE SCREENSHOT IN FREQUENCY ORDER]}
+We collected the information panels, when present, under each video by connecting to a US server and scraping the content of the web page. 
+Five types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19, vaccine hesitancy and US elections, as shown in figure \ref{youtube_panel_screenshots}.
+{\color{red} [ADD Vaccine hesitancy screenshot]}
 
@@
 	\centering
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.29]{./img/youtube_panels/yt_2.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.294]{./img/youtube_panels/yt_3.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.3]{./img/youtube_panels/yt_4.png} 
-	%\end{multicols}
 	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}.
@@
 
-We found that almost half (44 \%) of the videos containing misinformation actually had no information panel (Table \ref{youtube_panel_proportions}).
-For the rest of videos, the most frequent information panels found concerned COVID-19 (42 \%) and COVID-19 vaccine (11 \%).
+Almost half (44 \%) of the videos containing misinformation were shown without any information panel (Table \ref{youtube_panel_proportions}).
+For the rest of videos, the most frequent information panels concerned COVID-19 (42 \%) and COVID-19 vaccine (11 \%).
 It is possible that YouTube is currently focusing its efforts on the current `hot' controversial topics with a potentially wide public impact, leaving room for misinformation related to other topics to spread, but more research is needed to formally compare misinformation videos about COVID-19 and about other subjects.
@@
 
-In our list, we noticed that the same video was sometimes uploaded multiple times and thus appeared on different YouTube links. 
+We noticed that the same video was sometimes uploaded multiple times and thus appeared on different YouTube links. 
 One YouTube link might contain an information panel while its duplicates did not (see figure \ref{duplicates_yt} for an example).  
@@
 Therefore, we suspect that YouTube is automatically adding information panels based on the presence of certain keywords in the video title (and maybe in the video description), independently of the content of the video.
-Note that in figure \ref{duplicates_yt}, the video with `C.O.V.I.D.19' in its title had an information panel, hinting that YouTube might adapt its list of `suspect' keywords as new notational variants for COVID-19 appear.
+Note that in figure \ref{duplicates_yt}, the video with `C.O.V.I.D.19' in its title had an information panel, hinting that YouTube might adapt its list of suspect keywords as new notational variants for COVID-19 appear, or that some information panels might be added manually (by content regulators or when a video is flagged by many users).
 
@@
 	\centering
-		\includegraphics[scale=0.24]{./img/youtube_panels/graph_no_banner.png} 
+		\begin{multicols}{1}
+		\includegraphics[scale=0.24]{./img/youtube_panels/graph_no_banner.png} &
 		\includegraphics[scale=0.24]{./img/youtube_panels/graph_with_banner.png} 
+		\end{multicols}
 		%\includegraphics[scale=0.2]{./img/youtube_panels/news_with_banner.png}

### 2021-08-30 article/draft.tex
rewrite conclusion for YT remove section

@@
 
-In this section, we turn to the channel's temporary or permanent suspension policy of YouTube. When a YouTube channel violates the community guidelines, it can receive one or several strikes.
+In this section, we turn to the channel's temporary or permanent suspension policy of YouTube. 
+When a YouTube channel violates the community guidelines, it can receive one or several strikes.
 %Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed.
@@
 
-[CONCLUSION]
-This drop in views can show that the  suspension  period may  have  a  good impact on reducing  the  audience interest or reach to the channel.
+As most YouTube channels upload videos on a weekly or even a monthly basis, a one-week suspension appears not very restrictive at first sight. 
+But we observed that the intervention was followed by a reduction in the number of view for the two channels investigated, with one channel even stopping its YouTube activity in the following months. 
+Although more research is needed before drawing a definitive conclusion, it is possible that the one-week suspension following a strike might reduce the reach of the very active YouTube channels.
 

### 2021-08-30 article/draft.tex
remove the disappeared information panel

@@
 We collected the information panels, when present, under each video by connecting to a US server and scraping the content of the web page. 
-Five types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19, vaccine hesitancy and US elections, as shown in figure \ref{youtube_panel_screenshots}.
-{\color{red} [ADD Vaccine hesitancy screenshot]}
+Four types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19 and US elections, as shown in figure \ref{youtube_panel_screenshots}.
 
@@
 
-\smallskip
-
-Almost half (44 \%) of the videos containing misinformation were shown without any information panel (Table \ref{youtube_panel_proportions}).
-For the rest of videos, the most frequent information panels concerned COVID-19 (42 \%) and COVID-19 vaccine (11 \%).
-It is possible that YouTube is currently focusing its efforts on the current `hot' controversial topics with a potentially wide public impact, leaving room for misinformation related to other topics to spread, but more research is needed to formally compare misinformation videos about COVID-19 and about other subjects.
-
 \begin{table}[h] 
-\begin{tabular}{|c|c|c|c|c|c|}
+\centering
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-\multicolumn{6}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
+\multicolumn{5}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
 \makecell{Without \\ any \\ panel} & 
@@
 \makecell{With a \\ `climate change' \\ panel} &
-\makecell{With a \\ `U.S. elections' \\ panel} &
-\makecell{With a \\ `vaccine hesitancy' \\ panel}  
+\makecell{With a \\ `U.S. elections' \\ panel}  
 \\ \hline
-\makecell{74 \\ (44 \%)} &
+\makecell{75 \\ (44 \%)} &
 \makecell{71 \\ (42 \%)} &
@@
 \makecell{4 \\ (2 \%)} &
-\makecell{1 \\ (0.5 \%)} &
-\makecell{1 \\ (0.5 \%)}
+\makecell{1 \\ (0.6 \%)}
 \\ \hline
@@
 
+Almost half (44 \%) of the videos containing misinformation were shown without any information panel (Table \ref{youtube_panel_proportions}).
+For the rest of videos, the most frequent information panels concerned COVID-19 (42 \%) and COVID-19 vaccine (11 \%).
+It is possible that YouTube is currently focusing its efforts on the current `hot' controversial topics with a potentially wide public impact, leaving room for misinformation related to other topics to spread, but more research is needed to formally compare misinformation videos about COVID-19 and about other subjects.
+
+\smallskip
+
 We noticed that the same video was sometimes uploaded multiple times and thus appeared on different YouTube links. 
@@
 		\begin{multicols}{1}
-		\includegraphics[scale=0.24]{./img/youtube_panels/graph_no_banner.png} &
+		\includegraphics[scale=0.24]{./img/youtube_panels/graph_no_banner.png}
 		\includegraphics[scale=0.24]{./img/youtube_panels/graph_with_banner.png} 

### 2021-08-30 article/draft.tex
add the information panel about vaccination information

--- 2021-08-30 article/draft.tex
@@
 We collected the information panels, when present, under each video by connecting to a US server and scraping the content of the web page. 
-Five types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19, vaccine hesitancy and US elections, as shown in figure \ref{youtube_panel_screenshots}.
-{\color{red} [ADD Vaccine hesitancy screenshot]}
+Five types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19, U.S. elections and vaccination information, as shown in figure \ref{youtube_panel_screenshots}.
 
@@
 		\includegraphics[scale=0.294]{./img/youtube_panels/yt_3.png}
-		\includegraphics[scale=0.3]{./img/youtube_panels/yt_4.png} 
-	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}.
+		\includegraphics[scale=0.305]{./img/youtube_panels/yt_4.png} 
+		\includegraphics[scale=0.193]{./img/youtube_panels/yt_5.png} 
+	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19}, \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections} and \href{https://www.youtube.com/watch?v=OuQYMjpCwfU}{vaccination information}.
 The videos were accessed on July 21, 2021 from a US server.}
@@
 
-\smallskip
-
-Almost half (44 \%) of the videos containing misinformation were shown without any information panel (Table \ref{youtube_panel_proportions}).
-For the rest of videos, the most frequent information panels concerned COVID-19 (42 \%) and COVID-19 vaccine (11 \%).
-It is possible that YouTube is currently focusing its efforts on the current `hot' controversial topics with a potentially wide public impact, leaving room for misinformation related to other topics to spread, but more research is needed to formally compare misinformation videos about COVID-19 and about other subjects.
-
 \begin{table}[h]
+\centering
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 \makecell{With a \\ `COVID-19' \\ panel} & 
-\makecell{With a \\ `COVID-19 vaccine' \\ panel} &
+\makecell{With a \\ `COVID-19 \\ vaccine' panel} &
 \makecell{With a \\ `climate change' \\ panel} &
 \makecell{With a \\ `U.S. elections' \\ panel} &
-\makecell{With a \\ `vaccine hesitancy' \\ panel}  
+\makecell{With a \\ `vaccination \\ information' panel}  
 \\ \hline

### 2021-08-30 article/draft.tex
add ref + polish section about YouTube remove

@@
 
-In this section, we turn to the channel's temporary or permanent suspension policy of YouTube. 
-When a YouTube channel violates the community guidelines, it can receive one or several strikes.
-%Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed.
-For the second time the channel will start receiving strikes.
-A first strike results in limiting the access of the YouTube channel for one week
-(e.g. video uploading). 
-Then a second strike is similar but the suspension lasts two weeks. 
-A third strike results in the termination of the channel. 
-The strike count of a channel lasts 90 days.  
-In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning.
-
-\smallskip
-
-\begin{figure}[h]
-	\centering
-
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.21]{./img/oann/fig3_oann.png}
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.31]{./img/tony/fig3_tony.png}
-	%\end{multicols}
-	\caption{Left Panel: Tweet announcing moving to Rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
-Right Panel: Tony Heller's tweet after getting suspended from YouTube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
-	\label{fig2_oann}
-\end{figure}
-
-To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following YouTube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
+In this section, we turn to the suspension policy of YouTube. 
+When a YouTube channel publishes a video that violates the community guidelines for the first time, it will usually receive a warning. 
+But for the second violation, the channel receives its first strike.
+A strike means that users are not allowed to post content on their YouTube channel for one week.
+A strike remains associated to a channel for 90 days, and if a second strike occurs in same 90-day period as the first strike, the suspension will then last for two weeks.
+A third strike results in the termination of the channel.\footnote{https://support.google.com/youtube/answer/2802032}
+To illustrate the implementation of this policy, we use the following YouTube channels as two examples of  one-week suspensions: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
+
+\smallskip
+
 The website of One America News Network has a ``low'' factual reporting score according to iffy.news and several inaccurate articles according to feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}
-Tony Heller posts regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}}
-Both are active on YouTube and both have communicated via their Twitter account about restrictions applied by YouTube over their content (see figure \ref{fig2_oann}).
-
-\smallskip
-
-First, we investigate the temporary suspension of the YouTube channel of One America News Networks.
-According to the News outlet NBCnews (2020)~\cite{nbcnews}, this YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
-We collected the activity of the channel OANN (video counts and view counts) using the YouTube API v3, between November $2020$ and January $2021$.
-For the video counts, we used the {\it playlists} endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the {\it videos} endpoint we retrieved the view counts on June $2021$.%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
-
-\smallskip
-
-Figure \ref{fig1_oann} shows the daily number of videos uploaded by the channel, and its number of views. 
-We can clearly see the suspension period in the data, as the number of published video is down to zero for one week after the strike on November $24$, $2020$. 
-Because no videos were published during this period, the number of views were also nul.
-When comparing one month before and after the suspension, the view count decreased by -73\%, indicating that the videos uploaded after the suspension were less popular. 
-Furthermore, the activity of the channel was close to zero after March 2021, and OANN's Twitter account has announced their migration from YouTube to Rumble on March 17, 2021.
+According to NBC news (2020)~\cite{nbcnews}, the YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
+We collected the number of video uploaded and the number of view of this channel using the YouTube API v3, between November $2020$ and January $2021$.
+For the video counts, we used the {\it playlists} endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the {\it videos} endpoint we retrieved the view counts on June $2021$.
+%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}
 
@@
 }
-	\label{fig1_oann}
-\end{figure}
-
-\smallskip
-
-We now turn to a second example, the YouTube channel Tony Heller. 
-This channel got its first strike after posting a video about an anti-covid-lockdown doctor getting arrested (see screenshot in figure \ref{fig2_oann}). 
-The suspension period lasted one week from September $29$ until October $5$.
+	\label{delete_youtube_oann}
+\end{figure}
+
+\smallskip
+
+Figure \ref{delete_youtube_oann} shows the daily number of videos uploaded by the channel, and its number of views. 
+We can clearly see the suspension period in the data, as the number of published video is down to zero for one week after the strike on November $24$, $2020$. 
+Because no videos were published during this period, the number of views were also nul.
+When comparing one month before and after the suspension, the view count decreased by -73\%, indicating that the videos uploaded after the suspension were less popular. 
+Furthermore, the activity of the channel was close to zero after March 2021, and OANN's Twitter account has announced their migration from YouTube to Rumble on March 17, 2021 (see the left panel of Figure \ref{tweets_about_yt_suspensions}).
+
+\begin{figure}[h]
+	\centering
+		\includegraphics[scale=0.21]{./img/oann/fig3_oann.png}
+		\includegraphics[scale=0.31]{./img/tony/fig3_tony.png}
+	\caption{Left Panel: Tweet announcing OANN moving to Rumble, Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
+Right Panel: Tony Heller's tweet after getting suspended from YouTube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
+	\label{tweets_about_yt_suspensions}
+\end{figure}
+
+\smallskip
+
+Tony Heller writes regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}}
+Tony Heller tweeted on September 29, 2020 about his YouTube channel being `shut down' because of a video about an anti-covid-lockdown doctor getting arrested (see the right panel of Figure \ref{tweets_about_yt_suspensions}).
 We applied the same methods as in the previous example to collect data.
-Again the one-week suspension period can be observed clearly in the daily number of uploaded videos and of views.
+Again a one-week suspension period from September $29$ until October $5$ can be observed clearly in the daily number of uploaded videos and of views (see Figure \ref{delete_youtube_tony}).
 Comparing one month before and after the suspension, this channel also witnessed a drop of view counts by $-70\%$.
@@
 }
-	\label{fig1_tony}
-\end{figure}
+	\label{delete_youtube_tony}
+\end{figure}
+
+\smallskip
 

### 2021-08-30 code/create_figures.py
rename yt reduce figure

@@ -373,9 +373,10 @@ def create_plot_top_channel_youtube(path_to_data):
     ax.yaxis.set_label_position("right")
     #ax.yaxis.tick_right()
     plt.gca().invert_yaxis()
-    fig_name = "channel_youtube_top_10"
+    fig_name = "reduce_youtube"
     figure_path = os.path.join('.', 'figure', fig_name)
     plt.savefig(figure_path, bbox_inches="tight")
+    print("The '{}' figure is saved.".format(fig_name))
 
 
 def create_youtube_graph():
@@ -544,7 +545,7 @@ def create_twitter_figures():
 
 
 if __name__=="__main__":
-    '''
+
     create_facebook_trump_figure()
     create_buzzsumo_thebl_figure()
     create_facebook_crowdtangle_infowars_figure()
@@ -553,5 +554,5 @@ if __name__=="__main__":
     create_youtube_graph()
 
     create_twitter_figures()
-    '''
-    create_plot_top_channel_youtube('/home/dana/Desktop/WebclimProject/truth-and-trust-online-2021/data/02L_LUpSqeA_experiment_2.csv')
+    
+    create_plot_top_channel_youtube('./data/experiment2_health_full_data.csv')

### 2021-08-30 article/draft.tex
rename yt reduce figure
polish the section about YT reduce

@@
 
-YouTube can reduce the visibility of some video content via its recommendation system, namely by recommending content from authoritative sources for topics related to science and health.
-This platform recommends content to the users based on the watch history and searched queries in google and YouTube; which can both be cleared via account settings.
-Moreover, a recommendation system based on preferences and history might have a down side, namely when a user repeatedly watches videos that might be misleading or that promote conspiracy theories.
-YouTube states that they set out to prevent their systems from serving up content that could misinform users in a harmful way, particularly in domains that rely on veracity, such as science, medicine, News, or historical events.
-YouTube identifies misinformation by using external human evaluators and experts to examine if a given video is promoting misleading information or conspiracy theories.
-Then using the feedback of the evaluators, they use machine learning systems to develop models that generate recommendations.
-The models work on reviewing videos daily to reduce the spread of misinformation.
+YouTube can reduce the visibility of certain video via its recommendation system, namely by recommending content from authoritative sources.
+The platform usually recommends content to the users based on the watch history and searched queries in google and YouTube {\color{red} [REF]}; which can both be cleared via account settings.
+A recommendation system based on previous preferences has a downside, namely when a user repeatedly watches videos that might be misleading or that promote conspiracy theories and gets recommended similar videos {\color{red} [REF]}.
+YouTube states that they set out to prevent their systems from serving up content that could misinform users in a harmful way, particularly in domains that rely on veracity, such as science, medicine, news, or historical events.
+YouTube identifies misinformation by using external human evaluators and experts to examine if a given video is promoting misleading information or conspiracy theories, and then use machine learning systems to discard misinformation from their recommendations {\color{red} [REF]}.
 
@@
 To examine this effect, we designed an experiment that simulates a user's behavior on YouTube. 
-We used a list of $45$ videos marked as {\it False} by Science Feedback and classified under the category ``health'' (see section \ref{youtube_panels} for the classification).
+We used a list of $45$ videos marked as {\it False} by Science Feedback and classified under the category ``health''.
 The experiment starts with one video marked as ``False'' from our list of videos and a clean watch history.
-For each video, our automated program collects around\footnote{Notice that as we are simulating the behavior of a user, when we visit a video, we get a number of recommendations that vary between $18$ videos and $22$ videos.} $20$ recommendations and clicks on the top $10$ videos in sequential order.
-After that, for every video in the set of the top $10$ recommendations, we collect their top $20$ recommended videos.
+For each video, our automated program collects around\footnote{When we visit a video, we get a number of recommendations that vary between $18$ videos and $22$ videos.}
+$20$ recommendations and clicks on the top $10$ videos in sequential order. 
+After that, for every video in the set of the top $10$ recommendations, we collect their own top $20$ recommended videos.
 In addition, to simulate a user's behavior, the automated program watches each video for a few minutes\footnote{If the video duration is ten minutes or less, the automated program watches the whole video.
 If the video duration is strictly higher than ten minutes, then the automated program watches only five minutes.}.
-Doing so, we collected $10$ $549$ YouTube recommended video entries, among which only $3$ $895$ were unique.
-To analyse the collected data, we look for misinformation: $(i)$ at the video level and $(ii)$ at the channel level.
-
-\smallskip
-
-{\bf Video Level.} We ranked the recommended videos based on the number of times they got recommended. We then asked Science Feedback to fact-check the top 40 recommended videos.
-Those $40$ videos were recommended $1$ $735$ times out of the $10$ $549$ YouTube recommended video entries (that is $16\%$ of the recommendations).
-Among the top 40 recommended videos, four unique videos were marked as {\it misleading} and they were recommended $132$ times out of the $1$ $735$ recommendations (that is $7.7\%$ of the recommendations).
-Four other videos were marked as {\it hyper-partisan} and they were recommended $184$ times ($10.7\%$).
+Doing so, we collected $10$ $549$ YouTube recommended video entries, among which $3$ $895$ were unique. 
+To analyse the collected data, we look for misinformation: $(i)$ at the channel level and $(ii)$ at the video level.
+
+\smallskip
+
+{\bf Channel Level.} 
+The $3$ $895$ unique videos came from $1$ $562$ different channels, and we counted the number of times every channel got recommended.
+Figure \ref{reduce_youtube} shows the top $10$ recommended channels, whose videos represent $30\%$ of the recommendations.
+Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to {\it iffy.news} and have several failed fact-checks,\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} are at the first and third place respectively.
+PragerU is also among the list of the 10 most recommended channel, with a ``low'' level of factual reporting according to {\it iffy.news}.
 
@@
 	\begin{center}
-		\includegraphics[scale=0.45]{./img/channel_youtube.png} 
+		\includegraphics[scale=0.45]{../figure/reduce_youtube.png} 
 	\end{center}
 	\caption{Top ten recommended channels among the $1$ $562$ different channels, that have posted the recommended videos in our dataset.}
-	\label{channels_yt}
-\end{figure}
-
-{\bf Channel Level.} We examined the top recommended channels in the collected data.
-We got $1$ $562$ different channels, and we counted the number of times every channel got recommended.
-Figure \ref{channels_yt} shows the top $10$ recommended channels, whose videos represent $30\%$ of the total set of recommended videos in our dataset.
-Among the top three most recommended channels, there is Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to {\it iffy.news} and have several failed fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} Also in the top ten most recommended, we find PragerU, which has a ``low'' level of factual reporting according to {\it iffy.news}.
-
-\smallskip
-
-At the video level, we start at each round with a YouTube video marked as ``False'' and we expected to have a high proportion of misinformation videos.
+	\label{reduce_youtube}
+\end{figure}
+
+\smallskip
+
+{\bf Video Level.} 
+We then ranked the videos based on the number of times they got recommended, and asked Science Feedback to fact-check the top 40 recommended videos (those videos were recommended $1$ $735$ times, which represents $16\%$ of the recommendations).
+Among the 40 examined videos, four videos were marked as {\it misleading} and they were recommended $132$ times out of the $1$~$735$ recommendations (that is $7.7\%$ of the recommendations).
+Four other videos were marked as {\it hyper-partisan} and they were recommended $184$ times ($10.7\%$).
+
+\smallskip
+
+As we collected the recommendations of misinformation videos, we expected to find a high proportion of videos of questionable content.
 But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
@@
 However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended.
-In other words, it is likely that YouTube acts on reducing the visibility of videos but not channels, via its recommendation system.
-Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general, given the complexity of their recommendation algorithm.
+It appears that the recommendation system of YouTube is reducing the visibility of certain videos but not of unauthoritative channels.
 

### 2021-08-31 article/draft.tex
add detail about yt policy

@@
 Information panels provide more context on a controversial matter, with a link to an independent, third-party partner's website such as Wikipedia or the World Health Organization. 
-Importantly, YouTube states that these panels exist regardless of the point of view expressed in a given video.\footnote{https://support.google.com/youtube/answer/9004474}
+Importantly, YouTube states that these panels exist regardless of the point of view expressed in a given video.
+YouTube also specifies that information panels may not be available in all countries/regions and languages.\footnote{https://support.google.com/youtube/answer/9004474}
 
@@
 Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to {\it iffy.news} and have several failed fact-checks,\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} are at the first and third place respectively.
-PragerU is also among the list of the 10 most recommended channel, with a ``low'' level of factual reporting according to {\it iffy.news}.
+PragerU is also among the list of the 10 most recommended channels, with a ``low'' level of factual reporting according to {\it iffy.news}.
 

### 2021-08-31 code/create_figures.py
fix the datetime bug

@@ -1,8 +1,6 @@
 import os
-#from datetime import timedelta, date
 from datetime import datetime, timedelta, date
 
-import datetime
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
@@ -409,14 +407,25 @@ def create_twitter_Lifesite_figure(filename, figure_name, title, zeros):
     df_volume = df.groupby(['date'], as_index=False).size()
 
     if zeros == 1 :
-        add_zeros = [{'date': datetime.date(2019, 12, 10), 'type_of_tweet': 'created_content', 'size': 0}, {'date': datetime.date(2019, 12, 10), 'type_of_tweet': 'replied_to', 'size': 0},{'date': datetime.date(2019, 12, 10), 'type_of_tweet': 'quoted', 'size': 0}, {'date': datetime.date(2019, 12, 10), 'type_of_tweet': 'retweeted', 'size': 0},{'date': datetime.date(2020, 10, 11), 'type_of_tweet': 'created_content', 'size': 0}, {'date': datetime.date(2020, 10, 11), 'type_of_tweet': 'replied_to', 'size': 0}, {'date': datetime.date(2020, 10, 11), 'type_of_tweet': 'quoted', 'size': 0}, {'date': datetime.date(2020, 10, 11), 'type_of_tweet': 'retweeted', 'size': 0}, {'date': datetime.date(2021, 1, 25), 'type_of_tweet': 'created_content', 'size': 0}, {'date': datetime.date(2021, 6, 30), 'type_of_tweet': 'created_content', 'size': 0}]
+        add_zeros = [
+            {'date': date(2019, 12, 10), 'type_of_tweet': 'created_content', 'size': 0}, 
+            {'date': date(2019, 12, 10), 'type_of_tweet': 'replied_to', 'size': 0},
+            {'date': date(2019, 12, 10), 'type_of_tweet': 'quoted', 'size': 0}, 
+            {'date': date(2019, 12, 10), 'type_of_tweet': 'retweeted', 'size': 0},
+            {'date': date(2020, 10, 11), 'type_of_tweet': 'created_content', 'size': 0}, 
+            {'date': date(2020, 10, 11), 'type_of_tweet': 'replied_to', 'size': 0}, 
+            {'date': date(2020, 10, 11), 'type_of_tweet': 'quoted', 'size': 0}, 
[…]

### 2021-09-02 article/draft.tex
change youtube panels results after running the scraper without connecting to a US server

@@
 To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information.
-We collected the information panels, when present, under each video by connecting to a US server and scraping the content of the web page. 
-Five types of information panels were found regarding climate change, COVID-19 Vaccine, COVID-19, U.S. elections and vaccination information, as shown in figure \ref{youtube_panel_screenshots}.
-
-\begin{figure}[h]
-	\centering
-		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
-		\includegraphics[scale=0.29]{./img/youtube_panels/yt_2.png} 
-		\includegraphics[scale=0.294]{./img/youtube_panels/yt_3.png}
-		\includegraphics[scale=0.305]{./img/youtube_panels/yt_4.png} 
-		\includegraphics[scale=0.193]{./img/youtube_panels/yt_5.png} 
-	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19}, \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections} and \href{https://www.youtube.com/watch?v=OuQYMjpCwfU}{vaccination information}.
-The videos were accessed on July 21, 2021 from a US server.}
+We collected the information panels, when present, under each video by scraping the content of the web page. 
+Three types of information panels were found regarding COVID-19, COVID-19 Vaccine, and climate change, as shown in figure \ref{youtube_panel_screenshots}.
+
+\begin{figure}[h]
+	\centering
+		\includegraphics[scale=0.2]{./img/youtube_panels/youtube_panel_covid.png} 
+		\includegraphics[scale=0.2]{./img/youtube_panels/youtube_panel_covid_vaccine.png} 
+		\includegraphics[scale=0.2]{./img/youtube_panels/youtube_panel_climate.png}
+	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=O1cFVdC2rZQ}{COVID-19}, \href{https://www.youtube.com/watch?v=v0-6JTr2Ifo}{COVID-19 Vaccine} and \href{https://www.youtube.com/watch?v=4U8kgiiVj5Q}{climate change}.
+The videos were accessed on September 2, 2021.}
 	\label{youtube_panel_screenshots}
@@
 \centering
-\begin{tabular}{|c|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|}
 \hline
-\multicolumn{6}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
-\makecell{Without \\ any \\ panel} & 
+\multicolumn{4}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
+\makecell{Without \\ any panel} & 
 \makecell{With a \\ `COVID-19' \\ panel} & 
-\makecell{With a \\ `COVID-19 \\ vaccine' panel} &
-\makecell{With a \\ `climate change' \\ panel} &
-\makecell{With a \\ `U.S. elections' \\ panel} &
-\makecell{With a \\ `vaccination \\ information' panel}  
+\makecell{With a \\ `COVID-19 vaccine' \\ panel} &
+\makecell{With a \\ `climate change' \\ panel}
 \\ \hline
-\makecell{74 \\ (44 \%)} &
+\makecell{78 \\ (46 \%)} &
 \makecell{71 \\ (42 \%)} &
-\makecell{19 \\ (11 \%)} &
-\makecell{4 \\ (2 \%)} &
-\makecell{1 \\ (0.5 \%)} &
-\makecell{1 \\ (0.5 \%)}
+\makecell{15 \\ (9 \%)} &
+\makecell{6 \\ (3 \%)}
 \\ \hline
@@
 
-Almost half (44 \%) of the videos containing misinformation were shown without any information panel (Table \ref{youtube_panel_proportions}).
-For the rest of videos, the most frequent information panels concerned COVID-19 (42 \%) and COVID-19 vaccine (11 \%).
+Almost half (46 \%) of the videos containing misinformation were shown without any information panel (Table \ref{youtube_panel_proportions}).
+For the rest of videos, the most frequent information panel concerned COVID-19 (42 \%), followed by COVID-19 vaccine (9 \%).
 It is possible that YouTube is currently focusing its efforts on the current `hot' controversial topics with a potentially wide public impact, leaving room for misinformation related to other topics to spread, but more research is needed to formally compare misinformation videos about COVID-19 and about other subjects.

### 2021-09-02 code/check_flag_youtube.py
automatize more the code to run youtube panels collection

@@ -1,37 +1,0 @@
-import sys
-import time
-
-from selenium import webdriver
-from selenium.common.exceptions import NoSuchElementException
-from webdriver_manager.chrome import ChromeDriverManager
-
-
-
-def check_exists_by_xpath(xpath, driver):
-    try:
-        driver.find_element_by_xpath(xpath)
-    except NoSuchElementException:
-        return False
-    return True
-
-
-def information_panel(video_id):
-    try:
-        driver = webdriver.Chrome(ChromeDriverManager().install())
-        web = 'https://www.youtube.com/watch?v='+video_id
-        driver.get(web)
-        time.sleep(5)
-
-        exist = check_exists_by_xpath('//*[@id="clarify-box"]',driver)
-        if (exist ==True):
-             content = driver.find_element_by_xpath('//*[@id="clarify-box"]').text
-        else:
-            content =''
-        driver.close()
-        return content
-    except:
-        return 'Error'
-
-
-if __name__ == "__main__":
-    print(information_panel(sys.argv[1]))

### 2021-09-02 code/collect_youtube_panels.py

@@ -1,0 +1,36 @@
+import csv
+import time
+
+from selenium import webdriver
+from selenium.common.exceptions import NoSuchElementException
+from webdriver_manager.chrome import ChromeDriverManager
+import pandas as pd
+
+
+def get_information_panel_content(video_id):
+
+    browser = webdriver.Chrome(ChromeDriverManager().install())
+    browser.get('https://www.youtube.com/watch?v=' + video_id)
+    time.sleep(10)
+
+    try:
+        information_panel_content = browser.find_element_by_xpath('//*[@id="clarify-box"]').text
+    except NoSuchElementException:
+        information_panel_content = ''
+
+    browser.quit()
+    
+    return information_panel_content
+
+
+if __name__ == "__main__":
+
+    df = pd.read_csv('./data/youtube_flags.csv')
+
+    with open('./data/youtube_flags_new.csv', "w") as csv_file:
+        
+        writer = csv.writer(csv_file, delimiter=',')
+        writer.writerow(['video_id', 'information_panel_content'])
+
+        for video_id in df.video_id.values:
+            writer.writerow([video_id, get_information_panel_content(video_id)])

### 2022-02-08 article/draft.tex
new figures twitter

@@
 \title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
-
+\author{Webclim team}
+\date{September 27, 2021}
 \maketitle
@@
 
-\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}} Strike System \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}} See in the following link the section {\it What is the number of strikes a person or } \\ { \it Page has to get to before you ban them?} \\  \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}   \end{tabular}                            \\ \cline{2-3}
+\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}} Strike System \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}} See in the following link the section {\it What is the number of strikes a person or } \\ { \it Page has to get to before you ban them?} \\  \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/} \\ \href{https://transparency.fb.com/en-gb/enforcement/taking-action/counting-strikes/}{https://transparency.fb.com/en-gb/enforcement/taking-action/counting-strikes/} (updated July 29,2021)   \end{tabular}                            \\ \cline{2-3}
                                            & \includegraphics[scale=0.007]{./img/tw_logo.png}   &  \begin{tabular}[c]{@{}cl@{}}  See in the following links the section:  {\it Account locks and permanent suspension }   \\ \href{https://help.twitter.com/en/rules-and-policies/election-integrity-policy}{help.twitter.com/en/rules-and-policies/election-integrity-policy}  \\ \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy}  \end{tabular}    \\ \cline{2-3}

### 2022-02-08 code/create_figures.py

@@ -408,15 +408,15 @@ def create_twitter_Lifesite_figure(filename, figure_name, title, zeros):
 
     if zeros == 1 :
         add_zeros = [
-            {'date': date(2019, 12, 10), 'type_of_tweet': 'created_content', 'size': 0}, 
+            {'date': date(2019, 12, 10), 'type_of_tweet': 'created_content', 'size': 0},
             {'date': date(2019, 12, 10), 'type_of_tweet': 'replied_to', 'size': 0},
-            {'date': date(2019, 12, 10), 'type_of_tweet': 'quoted', 'size': 0}, 
+            {'date': date(2019, 12, 10), 'type_of_tweet': 'quoted', 'size': 0},
             {'date': date(2019, 12, 10), 'type_of_tweet': 'retweeted', 'size': 0},
-            {'date': date(2020, 10, 11), 'type_of_tweet': 'created_content', 'size': 0}, 
-            {'date': date(2020, 10, 11), 'type_of_tweet': 'replied_to', 'size': 0}, 
-            {'date': date(2020, 10, 11), 'type_of_tweet': 'quoted', 'size': 0}, 
-            {'date': date(2020, 10, 11), 'type_of_tweet': 'retweeted', 'size': 0}, 
-            {'date': date(2021, 1, 25), 'type_of_tweet': 'created_content', 'size': 0}, 
+            {'date': date(2020, 10, 11), 'type_of_tweet': 'created_content', 'size': 0},
+            {'date': date(2020, 10, 11), 'type_of_tweet': 'replied_to', 'size': 0},
+            {'date': date(2020, 10, 11), 'type_of_tweet': 'quoted', 'size': 0},
+            {'date': date(2020, 10, 11), 'type_of_tweet': 'retweeted', 'size': 0},
+            {'date': date(2021, 1, 25), 'type_of_tweet': 'created_content', 'size': 0},
             {'date': date(2021, 6, 30), 'type_of_tweet': 'created_content', 'size': 0}
         ]
         df_volume = df_volume.append(add_zeros , ignore_index = True)
@@ -456,6 +456,84 @@ def create_twitter_Lifesite_figure(filename, figure_name, title, zeros):
     save_figure(figure_name)
     #plt.show()
 
+def create_twitter_Lifesite_figure_engagement(filename, figure_name, title, zeros):
+
+    df = import_data(filename)
+    df = df.drop_duplicates()
+
[…]

### 2022-04-08 code/create_figures.py
pie figures

@@ -7,6 +7,9 @@ import matplotlib.pyplot as plt
 import matplotlib.patches as mpatches #new addition to create the boxes in the legend for the shaded areas
 import ural
 
+from matplotlib_venn import venn2, venn2_circles, venn2_unweighted
+from matplotlib_venn import venn3
+
 
 def import_data(file_name):
     data_path = os.path.join(".", "data", file_name)
@@ -15,7 +18,7 @@ def import_data(file_name):
 
 def save_figure(figure_name):
     figure_path = os.path.join('.', 'figure', figure_name)
-    plt.savefig(figure_path)
+    plt.savefig(figure_path, bbox_inches='tight')
     print("The '{}' figure is saved.".format(figure_name))
 
 def plot_format(ax, plt, suspension):
@@ -638,6 +641,73 @@ def create_twitter_figures():
     # zeros = 0
     # )
 
+def create_pie_pp(figure_name):
+
+    fig = plt.figure(figsize=(10, 10))
+    ax = fig.add_axes([0,0,1,1])
+    ax.axis('equal')
+
+    labels= ['Without an Information Panel', 'With COVID-19\nPanel', "With COVID-19\nVaccine Panel", "With Climate\n Change Panel",]
+    categories = [78, 71, 15, 6]
+    #ax.set_title(title,
+    #        fontsize=60)
+
+    #cmap = plt.get_cmap('PiYG')
+    colors = ['red', "lightseagreen", "mediumturquoise", "azure"]
+
+    ax.pie(
+    categories,
+    labels = labels,
+    autopct='%.0f%%',
+    textprops={'fontsize': 29},
+    colors=colors,
+    rotatelabels = False)
+
+    save_figure(figure_name)
+
+def create_pie_pp_tw(figure_name):
+
+    fig = plt.figure(figsize=(12, 12))
+    ax = fig.add_axes([0,0,1,1])
+    ax.axis('equal')
+
+    labels= [ 'Without interstitial \nor label', 'With interstitial', "With label"]
+    categories = [314560, 9344, 34]
+
+    #ax.set_title(title,
+    #        fontsize=60)
+
+    #cmap = plt.get_cmap('PiYG')
+    colors = ["deepskyblue", 'red', "azure"]
+
+    ax.pie(
+    categories,
+    labels = labels,
+    autopct='%.2f%%',
+    textprops={'fontsize': 17},
+    labeldistance = 0.72,
[…]

### 2022-04-25 article/draft.tex
updates
updated figures

@@
 \title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
-\author{Webclim team}
+\author{Dana Almanla, Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, M\'{e}dialab SciencesPo.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{heloise.thero@sciencespo.fr, M\'{e}dialab SciencesPo.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, M\'{e}dialab SciencesPo.}}
 \date{September 27, 2021}
 \maketitle
-
-%Title proposition 1: ``Big Tech is censoring me'': using social media data to verify the platforms' regulation policies regarding misinformation.
 
@@
 
-\begin{table}[h]
-\begin{tabular}{|c|c|c|c|}
-\hline
-\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
-without a flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check and an \\  information flags\end{tabular} \\ \hline
-0            & 7                        & 4                      & 7                                                                                     \\ \hline
-\end{tabular}
-\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
+%\begin{table}[h]
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
+%without a flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check and an \\  information flags\end{tabular} \\ \hline
+%0            & 7                        & 4                      & 7                                                                                     \\ \hline
+%\end{tabular}
+%\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
+%\label{tab_flags_fb}
+%\end{table}
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.5]{../figure/facebook_pie_flags.png}
+\caption{Count of different flags for 17 Facebook posts who have shared the exact same link, fact-checked False by one of Facebook’s partners.
+The claim fact checked as False appeared in the following article on beforeitsnews.com:  ``Stay Away From The Vaxxed, It Is Official, From Pfizer’s Own Documents".
+}
 \label{tab_flags_fb}
-\end{table}
-
-\smallskip
-
-Surprisingly only $11$ posts out of the remaining $17$ had a ``False information'' flag  (Table \ref{tab_flags_fb}, see left panel of Figure \ref{fb_flags} for an example).
+\end{figure}
+
+\smallskip
+
+Surprisingly only $11$ posts out of the remaining $17$ had a ``False information'' flag  (see Figure \ref{tab_flags_fb} and left panel of Figure \ref{fb_flags} for an example).
 We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples).
@@
 
-Finally, the number of tweets containing the interstitial {\it ``potentially sensitive content''} ($9$ $344$ tweets) widely outnumbers the tweets which contain a flag ($32$ tweets), among the set of $323$ $938$ tweets containing a link marked as ``False'' (see table \ref{flags_tab}).
+Finally, the number of tweets containing the interstitial {\it ``potentially sensitive content''} ($9$ $344$ tweets) widely outnumbers the tweets which contain a flag ($32$ tweets), among the set of $323$ $938$ tweets containing a link marked as ``False'' (see Figure \ref{flags_tab}).
 Furthermore, we noticed that among the tweets which contain the interstitial {\it ``potentially sensitive content''}, there are tweets which contain links redirecting to misleading articles about COVID-19 and yet they do not contain the label { \it ``Get the facts about COVID-19''}.
@@
 
-\begin{table}[h]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-\multicolumn{4}{|c|}{$323$ $938$ Tweets containing a link marked as False}                                                                                                                                                                                                                                                                                                                           \\ \hline
-\begin{tabular}[c]{@{}c@{}}with the interstitial\\ ``potentially sensitive \\ content'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Get the facts \\ about COVID-19'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Learn about US \\ 2020 election \\ security efforts'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag\\ ``This claim about \\ election fraud \\ is disputed''\end{tabular} \\ \hline
-\begin{tabular}[c]{@{}c@{}}9344\\ (2.88450 \%)\end{tabular}                                  & \begin{tabular}[c]{@{}c@{}}28\\ (0.00864 \%)\end{tabular}                              & \begin{tabular}[c]{@{}c@{}}5\\ (0.00154 \%)\end{tabular}                                                & \begin{tabular}[c]{@{}c@{}}1\\ (0.00030 \%)\end{tabular}                                             \\ \hline
-\end{tabular}
-\caption{Summary of the number of tweets among the set of collected tweets containing a link marked as False by Science Feedback, which contain a flag or an interstitial.}
+%\begin{table}[h]
+%\centering
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%\multicolumn{4}{|c|}{$323$ $938$ Tweets containing a link marked as False}                                                                                                                                                                                                                                                                                                                           \\ \hline
+%\begin{tabular}[c]{@{}c@{}}with the interstitial\\ ``potentially sensitive \\ content'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Get the facts \\ about COVID-19'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Learn about US \\ 2020 election \\ security efforts'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag\\ ``This claim about \\ election fraud \\ is disputed''\end{tabular} \\ \hline
+%\begin{tabular}[c]{@{}c@{}}9344\\ (2.88450 \%)\end{tabular}                                  & \begin{tabular}[c]{@{}c@{}}28\\ (0.00864 \%)\end{tabular}                              & \begin{tabular}[c]{@{}c@{}}5\\ (0.00154 \%)\end{tabular}                                                & \begin{tabular}[c]{@{}c@{}}1\\ (0.00030 \%)\end{tabular}                                             \\ \hline
+%\end{tabular}
+%\caption{Summary of the number of tweets among the set of collected tweets containing a link marked as False by Science Feedback, which contain a flag or an interstitial.}
+%\label{flags_tab}
+%\end{table}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.4]{../figure/twitter_pie_flags.png}
+	\caption{Summary of the number of tweets among the set of $323$ $938$ Tweets containing a link marked as False, by Science Feedback, which contain a flag or an interstitial or none.}
 \label{flags_tab}
-\end{table}
+\end{figure}
 
@@
 
-\begin{table}[h]
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-\multicolumn{4}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
-\makecell{Without \\ any panel} & 
-\makecell{With a \\ `COVID-19' \\ panel} & 
-\makecell{With a \\ `COVID-19 vaccine' \\ panel} &
-\makecell{With a \\ `climate change' \\ panel}
-\\ \hline
-\makecell{78 \\ (46 \%)} &
-\makecell{71 \\ (42 \%)} &
-\makecell{15 \\ (9 \%)} &
-\makecell{6 \\ (3 \%)}
-\\ \hline
-\end{tabular}
-\caption{Summary of the number of YouTube videos wich contain a certain information panel, among the set of videos marked as false or inaccurate by Science Feedback.}
+%\begin{table}[h]
+%\centering
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%\multicolumn{4}{|c|}{$170$ YouTube videos marked as false or inaccurate}                                                                                                                                                                                                                                                                                                                           \\ \hline
+%\makecell{Without \\ any panel} & 
+%\makecell{With a \\ `COVID-19' \\ panel} & 
+%\makecell{With a \\ `COVID-19 vaccine' \\ panel} &
+%\makecell{With a \\ `climate change' \\ panel}
+%\\ \hline
+%\makecell{78 \\ (46 \%)} &
+%\makecell{71 \\ (42 \%)} &
+%\makecell{15 \\ (9 \%)} &
+%\makecell{6 \\ (3 \%)}
+%\\ \hline
+%\end{tabular}
+%\caption{Summary of the number of YouTube videos wich contain a certain information panel, among the set of videos marked as false or inaccurate by Science Feedback.}
+%\label{youtube_panel_proportions}
+%\end{table}
+
+\begin{figure}[h]
+	\centering
+		\includegraphics[scale=0.3]{../figure/youtube_pie_flags.png}
+		\caption{Summary of the number of YouTube videos which contain an information panel, among the set of videos marked as false by Science Feedback.}
 \label{youtube_panel_proportions}
-\end{table}
-
-\smallskip
-
-Almost half (46 \%) of the videos containing misinformation were shown without any information panel (Table \ref{youtube_panel_proportions}).
+\end{figure}
+
+\smallskip
+
+Almost half (46 \%) of the videos containing misinformation were shown without any information panel (Figure \ref{youtube_panel_proportions}).
 For the rest of videos, the most frequent information panel concerned COVID-19 (42 \%), followed by COVID-19 vaccine (9 \%).
@@
 \begin{figure}[h]
-%\centering
+\centering
 \hspace{-2em}
-		\includegraphics[scale=0.32]{../figure/globalresearch_domain_2021-08-17.jpg} 
-		\includegraphics[scale=0.32]{../figure/globalresearch_domain_engagement_2021-08-17.jpg}
+		\includegraphics[scale=0.4]{../figure/globalresearch_domain_2021-08-17.jpg} 
+		\includegraphics[scale=0.4]{../figure/globalresearch_domain_engagement_2021-08-17.jpg}
 \caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.
@@
 This hampers the investigation of how platforms moderate content. 
-To further illustrate this point, the original list of YouTube videos with failed fact-checks (summarized in Table \ref{tab2}), had over $200$ YouTube videos available in March $2021$. 
+To further illustrate this point, the original list of YouTube videos with failed fact-checks (summarized in Figure \ref{youtube_panel_proportions}), had over $200$ YouTube videos available in March $2021$.
 However, by June $2021$, thirty videos had disappeared from the YouTube API for policy violation. 

### 2022-04-25 code/create_figures.py

@@ -667,25 +667,25 @@ def create_pie_pp(figure_name):
 
 def create_pie_pp_tw(figure_name):
 
-    fig = plt.figure(figsize=(12, 12))
+    fig = plt.figure(figsize=(7, 7))
     ax = fig.add_axes([0,0,1,1])
     ax.axis('equal')
 
-    labels= [ 'Without interstitial \nor label', 'With interstitial', "With label"]
+    labels= [ 'Without interstitial \nor notice', 'With interstitial', "With notice"]
     categories = [314560, 9344, 34]
 
     #ax.set_title(title,
     #        fontsize=60)
 
     #cmap = plt.get_cmap('PiYG')
-    colors = ["deepskyblue", 'red', "azure"]
+    colors = ["deepskyblue", 'lightcoral', "azure"]
 
     ax.pie(
     categories,
     labels = labels,
     autopct='%.2f%%',
-    textprops={'fontsize': 17},
-    labeldistance = 0.72,
+    textprops={'fontsize': 12},
+    #labeldistance = 0.92,
     colors=colors,
     rotatelabels = False)
 
@@ -705,9 +705,9 @@ def create_pie_pp_fb(figure_name):
 
 def create_pie_figures():
 
-    create_pie_pp_fb('facebook_pie_flags')
+    #create_pie_pp_fb('facebook_pie_flags')
     create_pie_pp_tw('twitter_pie_flags')
-    create_pie_pp('youtube_pie_flags')
+    #create_pie_pp('youtube_pie_flags')
 
 if __name__=="__main__":
 

### 2022-04-27 article/draft.tex
cosmetic changes

@@
 \title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
-\author{Dana Almanla, Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, M\'{e}dialab SciencesPo.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{heloise.thero@sciencespo.fr, M\'{e}dialab SciencesPo.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, M\'{e}dialab SciencesPo.}}
+\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, M\'{e}dialab SciencesPo.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{heloise.thero@sciencespo.fr, M\'{e}dialab SciencesPo.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, M\'{e}dialab SciencesPo.}}
 \date{September 27, 2021}
@@
 
-Furthermore, mainstream platforms are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated.
+Furthermore, mainstream platforms are increasingly engaging in editorial-like tasks by implementing targeted policies to insure that each platform's rules are not violated.
 Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see Appendix \ref{links} for references).
 While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation.
-The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g.
+The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies point towards the idea that misinformation is a small subset of the total supply of information on online social networking platforms (e.g.
 Grinberg et al.
@@
 (2018)~\cite{lazer}).
-The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
+The misinformation phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
 The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
 Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources.
-In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral.
+In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society when it goes viral.
 This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
@@
 
-More specifically, we survey in this article a number of common policies against misinformation used by Facebook, Twitter and YouTube.
+More specifically, in this article, we survey a number of common policies against misinformation used by Facebook, Twitter and YouTube.
 We classified those common policies into three broad categories: $(i)$ temporary or permanent suspension of users, $(ii)$
 informing users with flags and notices, and $(iii)$ reducing the visibility of some content.
-We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
+We compile in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
 Furthermore, the examples provided to illustrate how to monitor a given policy were picked out of a list of domain names with several failed fact-checks.
@@
 }.
-In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news and feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/} and \href{https://open.feedback.org/media/S4}{https://open.feedback.org/media/S4}.}.
+In particular, this website has several failed fact-checks concerning the published articles, according to Media Bias Fact Check and open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/} and \href{https://open.feedback.org/media/S4}{https://open.feedback.org/media/S4}.}.
 We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint.
@@
 Finally, suspending a Twitter account is an intervention which aims at penalizing users, in order to make them respect the Twitter rules.
-In the case of Twitter accounts linked to domain names, the activity of the account usually consists in spreading on social media published articles on the website.
+In the case of Twitter accounts linked to domain names, the activity of the account usually consists in spreading on social media articles published on their website.
 Panel $(b)$ points towards the limitations of suspending the Twitter account $@LifeSite$, because the
@@
 A strike means that users are not allowed to post content on their YouTube channel for one week.
-A strike remains associated to a channel for 90 days, and if a second strike occurs in same 90-day period as the first strike, the suspension will then last for two weeks.
+A strike remains associated to a channel for 90 days, and if a second strike occurs in the same 90-day period as the first strike, the suspension will then last for two weeks.
 A third strike results in the termination of the channel.\footnote{https://support.google.com/youtube/answer/2802032}
@@
 
-The website of One America News Network has a ``low'' factual reporting score according to iffy.news and several inaccurate articles according to feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}
+The website of One America News Network has a ``low'' factual reporting score according to the website Media Bias Fact Check and several inaccurate articles according to open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}
 According to NBC news (2020)~\cite{nbcnews}, the YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
@@
 
-Tony Heller writes regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}}
+Tony Heller writes regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to the website Media Bias Fact Check.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}}
 Tony Heller tweeted on September 29, 2020 about his YouTube channel being `shut down' because of a video about an anti-covid-lockdown doctor getting arrested (see the right panel of Figure \ref{tweets_about_yt_suspensions}).
@@
 
-As most YouTube channels upload videos on a weekly or even a monthly basis, a one-week suspension appears not very restrictive at first sight. 
+As most YouTube channels upload videos on a weekly or even a monthly basis, a one-week suspension does not appear very restrictive at first sight. 
 But we observed that the intervention was followed by a reduction in the number of view for the two channels investigated, with one channel even stopping its YouTube activity in the following months. 
@@
 $(i)$ information banners which do not refute the message in the post and provide a link which redirects to an authoritative source, such as ``Visit the COVID-19 Information Centre for vaccine resources'' and $(ii)$ fact-check flags that assigns a ``rating" for a text or a link in a given post, such as ``False information Checked by independent fact-checkers'' (see Figure \ref{fb_flags}).
-The fact-check flags display the following ratings : ``False", ``Partly false", ``Missing context", ``False headline", ``Altered media", ``Opinion", ``Satire", ``Not eligible" and ``True".\footnote{See \href{https://www.facebook.com/business/help/341102040382165}{https://www.facebook.com/business/help/341102040382165}.}
+The fact-check flags can display one of the following ratings : ``False", ``Partly false", ``Missing context", ``False headline", ``Altered media", ``Opinion", ``Satire", ``Not eligible" and ``True".\footnote{See \href{https://www.facebook.com/business/help/341102040382165}{https://www.facebook.com/business/help/341102040382165}.}
 
@@
 \includegraphics[scale=0.49]{./img/fb_flags/fb_flag_3.png}
-\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners.
+\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021.} 
+\label{fb_flags}
+\end{figure}
+%\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners.
 Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/} \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{3835629366473816} .}
-\label{fb_flags}
-\end{figure}
-
 No information or available fields regarding the Facebook flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data.
@@
 	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021.
+Left Panel: Tweet without an information notice.
+Right Panel: Tweet containing an information notice.}
+	\label{fig8}
+\end{figure}
+
+%	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021.
 Left Panel: Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label.
 Right Panel: Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
-	\label{fig8}
-\end{figure}
 
@@
 
-In this section, we take a deeper look at how labels and interstitials are introduced by Twitter, to indicate content which is inaccurate or false.
+In this section, we take a deeper look at how labels and interstitials are introduced by Twitter, to add context to potentially inaccurate or misleading content.
 To that end, we gathered a set of $3$ $094$ links redirecting to articles which were marked as ``False'' between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
@@
 Right Panel: when clicking on $view$, to view the content hidden behind the interstitial in the left panel.
+Screenshots taken on July 1, 2021.
+}
+	\label{fig_notice}
+\end{figure}
+%	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial.
+Right Panel: when clicking on $view$, to view the content hidden behind the interstitial in the left panel.
 Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}.
@@
 }
-	\label{fig_notice}
-\end{figure}
-
 \smallskip
@@
 
-To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information.
+To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing inaccurate information.
 We collected the information panels, when present, under each video by scraping the content of the web page. 
@@
 This website appears in the Misinformation Directory of FactCheck.org, among other websites who have posted deceptive content\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}.
-Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news and it has several failed fact-checks reported by Feedback.org.\footnote{See the Iffy.news page \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/} and Feedback.org \href{https://open.feedback.org/media/RM}{https://open.feedback.org/media/RM}.}
+Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the website Media Bias Fact Check and it has several failed fact-checks reported by open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/} and open.feedback.org \href{https://open.feedback.org/media/B9}{https://open.feedback.org/media/B9}.}
 
@@
 Another measure that platforms can apply is to prevent users from sharing specific types of content, like URLs belonging to a specific domain name.  
-The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.
+The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company operated by The Epoch Times that shares pro-Trump views and conspiracy theories such as QAnon.
 \footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} 
@@
 The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban.
-We can note that although the ban was communicated in an article published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
+We note that although the ban was communicated in an article published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
 The communication around the ban appeared to have discouraged The Beauty of Life to proceed with their activity.
@@
 Twitter can take action against a tweet which violates the Twitter rules, by limiting its visibility\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.} on users' timelines and in search results.
-To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://open.feedback.org/media/AEKA}{Feedback.org} and \href{https://iffy.news}{iffy.news} - two websites which provide databases of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://open.feedback.org/media/AEKA}{open.feedback.org/media/AEKA} and \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
+To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://open.feedback.org/media/AEKA}{open.feedback.org} and Media Bias Fact Check - two websites which provide databases of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://open.feedback.org/media/AEKA}{open.feedback.org/media/AEKA} and \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
 
@@
 
-Finally, the website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$} and it was recently suspended from Twitter.
-We noticed the message about the account suspension (see the right panel in figure \ref{fig4bis}) on May $25$, 2021.
+Finally, the website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}, which was suspended from Twitter on May $25$, 2021 as shown in a message about the account's suspension (see the right panel in figure \ref{fig4bis}).
 To the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
@@
 YouTube can reduce the visibility of certain video via its recommendation system, namely by recommending content from authoritative sources.
-The platform usually recommends content to the users based on the watch history and searched queries in google and YouTube {\color{red} [REF]}; which can both be cleared via account settings.
-A recommendation system based on previous preferences has a downside, namely when a user repeatedly watches videos that might be misleading or that promote conspiracy theories and gets recommended similar videos {\color{red} [REF]}.
+The platform usually recommends content to the users based on the watch history and searched queries in google and YouTube; which can both be cleared via account settings.
+A recommendation system based on previous preferences has a downside, namely when a user repeatedly watches videos that might be misleading or that promote conspiracy theories and gets recommended similar videos.
 YouTube states that they set out to prevent their systems from serving up content that could misinform users in a harmful way, particularly in domains that rely on veracity, such as science, medicine, news, or historical events.
-YouTube identifies misinformation by using external human evaluators and experts to examine if a given video is promoting misleading information or conspiracy theories, and then use machine learning systems to discard misinformation from their recommendations {\color{red} [REF]}.
+YouTube identifies misinformation by using external human evaluators and experts to examine if a given video is promoting misleading information or conspiracy theories, and then use machine learning systems to discard misinformation from their recommendations.\footnote{See the page \href{https://www.youtube.com/intl/ALL_ca/howyoutubeworks/our-commitments/fighting-misinformation/}{``How does YouTube address misinformation?"}}
 
@@
 Figure \ref{reduce_youtube} shows the top $10$ recommended channels, whose videos represent $30\%$ of the recommendations.
-Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to {\it iffy.news} and have several failed fact-checks,\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} are at the first and third place respectively.
-PragerU is also among the list of the 10 most recommended channels, with a ``low'' level of factual reporting according to {\it iffy.news}.
-
+Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to the website Media Bias Fact Check and have several failed fact-checks,\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} are at the first and third place respectively.
+PragerU is also among the list of the 10 most recommended channels, with a ``low'' level of factual reporting according to the website Media Bias Fact check. 
 \smallskip
@@
 However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended.
-It appears that the recommendation system of YouTube is reducing the visibility of certain videos but not of unauthoritative channels.
+It appears that the recommendation system of YouTube is reducing the visibility of certain videos but not of unreliable channels.
 
@@
 Furthermore, we have provided a methodology that can be useful for third-party monitoring. 
-The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{https://github.com/medialab/truth-and-trust-online-2021/}{https://github.com/medialab/truth-and-trust-online-2021/}, and we hope it can be a useful ressource for researchers, NGOs and journalists addressing online misinformation.
+The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{https://github.com/medialab/webclim_misinformation_related_interventions}{github.com/medialab/webclim\_misinformation\_related\_interventions}, and we hope it can be a useful ressource for researchers, NGOs and journalists addressing online misinformation.
 
@@
 However, by June $2021$, thirty videos had disappeared from the YouTube API for policy violation. 
-Similarly, in a related research project (see Thero and Vincent (2020)~\cite{therovincent}) we searched on CrowdTangle for $94$ public accounts sharing specific content associated with misinformation in November $2020$.
-We tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
+Similarly, in a related research project, Thero and Vincent (2020)~\cite{therovincent}) searched on CrowdTangle for $94$ public accounts sharing specific content associated with misinformation in November $2020$.
+They tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
 It is of course not surprising that platforms are regulating their content, sometimes by removing it. 
-Nevertheless, researchers' work could be simplified, if deleted data could still be accessible via the APIs.
+Nevertheless, researchers' work could be simplified, if metadata for content posted by removed accounts could still be accessible via the APIs.
 
@@
 A journalist has recently investigated the effects of this measure by counting the number of times hashtags related to the QAnon movement have been used over time, such as \#QAnon or \#WWG1WGA.
-A drastic reduction in hashtag use was found when comparing the first quarter of $2021$ with the first quarter of $2021$.\footnote{See \href{https://twitter.com/Shayan86/status/1394742784683298818}{https://twitter.com/Shayan86/status/1394742784683298818}.}
+A drastic reduction in hashtag use was found when comparing the first quarter of $2021$ with the first quarter of $2020$.\footnote{See \href{https://twitter.com/Shayan86/status/1394742784683298818}{https://twitter.com/Shayan86/status/1394742784683298818}.}
 Thus, counting specific hashtag use over time allows to indirectly observe permanent suspensions on Twitter and there is a need for similar methodologies to be experimented on data from other platforms.
@@
 and CrowdTangle is today a reliable source for researchers to access Facebook data. 
-However, it should be noted that CrowdTangle has been recently used by journalists to show that Facebook is spreading biased information\footnote{See the news article \href{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news} and the tweet \href{https://twitter.com/facebookstop10}{https://twitter.com/facebookstop10}.
+However, it should be noted that CrowdTangle has been recently used by journalists to show that Facebook is disproportionally favoring highly partisan information\footnote{See the news article \href{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news} and the tweet \href{https://twitter.com/facebookstop10}{https://twitter.com/facebookstop10}.
 The last link is a Twitter account showing each day the ten most shared link on Facebook, most of them coming from extreme right and misinformation sources. 
@@
 We are aware that full transparency regarding operational aspects of misinformation related interventions can backfire.
-This is because the aimed users might find means to circumvent the interventions. 
+This is because the aimed users might find ways to circumvent the interventions. 
 We noticed that some YouTube channels are trying to avoid the likely automated COVID-19 information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''. 
@@
 {\bf A need for more consistent and adapted policies.} Misinformation on the web is a problem that is increasingly discussed since the $2016$ American elections and in the years that followed, platforms may have decided on a case-by-case basis which actions to enforce.
-Infowars and The Beauty of Life domains have both several failed fact-checks\footnote{They are both on the Iffy+ list, see \href{https://iffy.news/iffy-plus/}{https://iffy.news/iffy-plus/}.} and have both violated Facebook's community guidelines (incitation to violence and coordinated unauthentic behavior).
-Yet one's distribution was reduced for only half of a year, while the other one's links cannot be shared anymore on Facebook since the end of $2019$, and it is not clear why such double standard was applied on these comparable websites.
+Infowars and The Beauty of Life domains have both several failed fact-checks\footnote{See \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}  and \href{https://mediabiasfactcheck.com/the-bl/}{https://mediabiasfactcheck.com/the-bl/}.} and have both violated Facebook's community guidelines (incitation to violence and coordinated unauthentic behavior).
+Yet one's distribution was reduced for only half of a year, while the other one's links cannot be shared anymore on Facebook since the end of $2019$, and it is not clear why such different enforcements were applied to these comparable websites.
 It is also possible that platforms usually follow specific rules on how to fight misinformation, but that sometimes the sudden media coverage of specific events leads them to take exceptional actions, such as with the Capitol riots and Trump's suspension from Facebook, Twitter and YouTube.
@@
 Namely, account suspensions or content deletion motivated by the spread of inaccurate information can be perceived as censorship by the targeted users.
-In particular, such interventions can generate platform migrations towards new alternative social media platforms (e.g.
-Telegram, Gab, Minds) with little or no content moderation (see Rogers (2020)~\cite{rogers2020}).
-
-\smallskip
-
-Finally, the means to tackle online misinformation is an active area of research and developing effective interventions against misinformation depends on understanding the psychology of interacting with social media (Pennycook and Rand (2021)~\cite{pennycook2021psychology}).
+In particular, such interventions can generate platform migrations (see Rogers (2020)~\cite{rogers2020}) towards new alternative social media platforms (e.g.
+Telegram, Gab, Minds) with little or no content moderation.
+
+\smallskip
+
+Finally, the means to tackle online misinformation is an active area of research.
+Developing effective interventions against misinformation depends on understanding the interventions currently used by platforms (e.g.
+for labeling, see Morrow et al.
+(2021)~\cite{morrow}) along with the psychology of interaction with social media (Pennycook and Rand (2021)~\cite{pennycook2021psychology}).
 Adding fact-checking labels to controversial content is certainly the intervention whose effectiveness was the most studied so far. 
@@
 These research papers highlight the necessity to investigate potential unintended effects of well-meaning interventions.
+Furthermore, misinformation related interventions can be poorly misunderstood.
+Based on survey data, Saltz et al.
+(2021)~\cite{saltzbarrari} show that $40\%$ of the survey respondents (wrongly) believed that content is mostly or all fact-checked.
+To date, research about misinformation related interventions by platforms is still scarce and addressing the specific needs in terms of data for auditing and monitoring tasks can greatly help in improving our understanding of these interventions and study their impact.
 The methods presented in this paper can help to monitor not only the platforms' actions against misinformation, but also their subsequent consequences in real-life settings.
@@
 %https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works
+\noindent {\bf Funding} \\
+This research was supported by the Make Our Planet Great Again’ French state aid managed by the Agence Nationale de la Recherche under the ’Investissements d’avenir’ program with the reference ANR-19-MPGA-0005.
+\bigskip
+
+\noindent {\bf Competing interests } \\
+We have no conflicts of interest to disclose. \bigskip
+
+\noindent {\bf Ethics} \\
+The data collection and processing complied with the EU General Data Protection Regulation (GDPR).
 \end{document}

### 2022-04-27 article/draft.tex
typo

@@
 (2020)~\cite{broniatowski}).
-Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense.
-\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.}
+Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense.\footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.}
 

### 2022-04-27 article/draft.tex
cosmetic changes

@@
 \title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
-\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, M\'{e}dialab SciencesPo.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{heloise.thero@sciencespo.fr, M\'{e}dialab SciencesPo.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, M\'{e}dialab SciencesPo.}}
+\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, Sciences Po, m\'{e}dialab .}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{thero.heloise@gmail.com, Sciences Po, m\'{e}dialab.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, Sciences Po, m\'{e}dialab.}}
 \date{September 27, 2021}

### 2022-05-02 article/draft.tex
added logo in footer
text modifications/suggestions by HT

--- 2022-04-27 article/draft.tex
@@
 
+\usepackage{url}
+\usepackage{background}
+\usepackage{lastpage}
+
+\backgroundsetup{
+  scale=1,
+  color=black,
+  opacity=1,
+  angle=0,
+  position=current page.south,
+  vshift=60pt,
+  contents={%
+  \small\sffamily%
+  \begin{minipage}{.18\textwidth}
+  \includegraphics[width=\linewidth,height=70pt,keepaspectratio]{./img/logo.png}
+  \end{minipage}\hspace{.02\textwidth}%
+   \begin{minipage}{.8\textwidth}
+  %\parbox[b]{.6\textwidth}{%
+   % Page \thepage\ of   \pageref{LastPage}}
+   \hfill
+  \parbox[b]{.4\textwidth}{%
+    \raggedleft Working paper, $2022$-$1$, April $2022$}\\
+ % \textcolor{red}{\rule{\textwidth}{1.5pt}}\\
+  %\url{www.mycompany.com}
+  \end{minipage}
+  }
+}
+
 \begin{document}
@@
 \title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
-\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, M\'{e}dialab SciencesPo.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{heloise.thero@sciencespo.fr, M\'{e}dialab SciencesPo.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, M\'{e}dialab SciencesPo.}}
-\date{September 27, 2021}
+\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, Sciences Po, m\'{e}dialab.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{thero.heloise@gmail.com, Sciences Po, m\'{e}dialab.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, Sciences Po, m\'{e}dialab.}}
+\date{April 29, 2022}
 \maketitle
@@
 For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.
-Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
+The company uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy.
 The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1.
@@
 
+%\begin{table}[h]
+%\centering
+%\begin{tabular}{|l|c|l|l|l}
+%
+%\hline
+%&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
+% \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} and  \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{Code created for this article}
+%\\ \hline
+% \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API v2} & \multicolumn{1}{l|}{ \href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{minet tw scrape} }                                                                                                                                                                           \\ \hline
+% \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API v3}      &                                                                                                                            \multicolumn{1}{l|}{Code created for this article}                                                                                                                                                                           \\ \hline
+%\end{tabular}
+%\caption{Summary of ressources used for data collection.}
+%\label{tab1}
+%\end{table}
+
 \begin{table}[h]
 \centering
-\begin{tabular}{|l|c|l|l|l}
-
-\hline
-&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
- \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} and  \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{Code created for this article}
-\\ \hline
- \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API v2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
- \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API v3}      &                                                                                                                            \multicolumn{1}{l|}{Code created for this article}                                                                                                                                                                           \\ \hline
+\begin{tabular}{|c|c|c|l}
+\cline{1-3}
+ & {\bf Application Programming Interface (API)} & {\bf Web Scrapping}  &  \\  \cline{1-3}
+\includegraphics[scale=0.035]{./img/fb_logo.png}  & \href{https://www.crowdtangle.com}{CrowdTangle API} and \href{https://buzzsumo.com}{Buzzsumo API}  & Code created for this article &  \\ \cline{1-3}
+ \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2}  & \href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{minet tw scrape} &  \\ \cline{1-3}
+ \includegraphics[scale=0.03]{./img/yt_logo.png} & \href{https://developers.google.com/youtube/v3}{YouTube API V3} & Code created for this article &  \\ \cline{1-3}
 \end{tabular}
@@
 informing users with flags and notices, and $(iii)$ reducing the visibility of some content.
-We compile in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
+We compile in Table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.
 Furthermore, the examples provided to illustrate how to monitor a given policy were picked out of a list of domain names with several failed fact-checks.
@@
 %Thus, after manually adding this page to the CrowdTangle dashboard, 
-Hence, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used Minet command line tool \cite{minet} to collect the data.
-We can verify on figure \ref{fig1_fb} that the {\it Donald J.
+Hence, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} The minet Python library\cite{minet} was used to collect the data.
+We can verify on Figure \ref{fig1_fb} that the {\it Donald J.
 Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.
@@
 %paragraph strike system + say following example is a manual decision. 
-Twitter has implemented a strike system as part of their Civic Integrity Policy and their COVID-19 misleading information policy.
+Twitter has implemented a strike system as part of their Civic Integrity Policy and their COVID-19 misleading information policy (see Table \ref{summary} in Appendix \ref{links}).
 Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform.
@@
 }.
-In particular, this website has several failed fact-checks concerning the published articles, according to Media Bias Fact Check and open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/} and \href{https://open.feedback.org/media/S4}{https://open.feedback.org/media/S4}.}.
-We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint.
-We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}).
+In particular, this website has several failed fact-checks concerning the published articles, according to Media Bias Fact Check and open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/} and \href{https://open.feedback.org/media/CM}{https://open.feedback.org/media/CM}.}.
+We collected the activity (Tweets, Replies, Quotes, Retweets) on their Twitter account via the Twitter API, using the historical search endpoint.
+We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in the left panel of Figure \ref{fig2}.
 The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.
@@
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.32]{../figure/lifesite.jpg} 
+		\includegraphics[scale=0.32]{../figure/lifesite_updated_legend.jpg} 
 	%\end{multicols}
 	%\begin{multicols}{1}
-		\includegraphics[scale=0.32]{../figure/lifesite_domain.jpg}
+		\includegraphics[scale=0.32]{../figure/lifesite_domain_updated_legend.jpg}
 	%\end{multicols}
-\caption{Left Panel: number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021.
-Right Panel: number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021.
+\caption{Left Panel: number of Tweets (including Retweets, Replies, Quotes) per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021.
+Right Panel: number of Tweets (including Retweets, Replies, Quotes) per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021.
 }
@@
 
-To further assess the impact of this double temporary suspension, we collect via the Twitter API v2, all the tweets that have shared during the same period a url link containing lifesitenews.com.
-Panel $(b)$ of figure \ref{fig2}, shows that during both periods of temporary suspension, other users still shared lifesitenews.com links and that the level was only slightly below the tweeting and retweeting levels prior to the first temporary suspension.
-More specifically, there was an average of 960 tweets (including retweets) per day over the first temporary suspension period of 308 days from December 9, 2019 until October 12, 2020, against an average of 977 tweets (including retweets) per day during the exact same period one year earlier.
+To further assess the impact of this double temporary suspension, we collect via the Twitter API v2, all the Tweets that have shared during the same period a url link containing lifesitenews.com.
+The right panel of Figure \ref{fig2}, shows that during both periods of temporary suspension, other users still shared lifesitenews.com links and that the level was only slightly below the tweeting and retweeting levels prior to the first temporary suspension.
+More specifically, there was an average of 960 Tweets (including Retweets, Replies, Quotes) per day over the first temporary suspension period of 308 days from December 9, 2019 until October 12, 2020, against an average of 977 Tweets (including Retweets, Replies, Quotes) per day during the exact same period one year earlier.
 
@@
 In the case of Twitter accounts linked to domain names, the activity of the account usually consists in spreading on social media articles published on their website.
-Panel $(b)$ points towards the limitations of suspending the Twitter account $@LifeSite$, because the
+The right panel of Figure \ref{fig2} points towards the limitations of suspending the Twitter account $@LifeSite$, because the
 articles published on lifesitenews.com were still being actively shared by other Twitter users.
@@
 A strike remains associated to a channel for 90 days, and if a second strike occurs in the same 90-day period as the first strike, the suspension will then last for two weeks.
-A third strike results in the termination of the channel.\footnote{https://support.google.com/youtube/answer/2802032}
-To illustrate the implementation of this policy, we use the following YouTube channels as two examples of  one-week suspensions: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.
-
-\smallskip
-
-The website of One America News Network has a ``low'' factual reporting score according to the website Media Bias Fact Check and several inaccurate articles according to open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}
+A third strike results in the termination of the channel.\footnote{\href{https://support.google.com/youtube/answer/2802032}{https://support.google.com/youtube/answer/2802032}.}
+To illustrate the implementation of this policy, we use the following YouTube channels as two examples of  one-week suspensions: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/channel/UCprclkVrNPls7PR-nHhf1Ow}{Tony Heller}.
+
+\smallskip
+
+The website of One America News Network has a ``low'' factual reporting score according to the website Media Bias Fact Check and several inaccurate articles according to open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/5M}{https://open.feedback.org/media/5M}.}
 According to NBC news (2020)~\cite{nbcnews}, the YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
@@
 The only way to verify Facebook’s flagging policy is thus via scraping publicly available content.
-To that end, we added a new feature in Minet~\cite{minet} which could automatically verify the presence or absence of flags.
-
-We first searched for all the Facebook posts having shared a specific link rated as ‘False’ by Science Feedback, a fact-checking organization which partners with Facebook.
-We used the {\it search} endpoint in Minet.\footnote{ Click \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{here} to access the link and  \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{its fact-check by Health Feedback}.}
-Twenty Facebook posts were collected this way, and the newly developed scraper was used to verify whether they contained an information banner, a fact-check flag, both or none.
+
+We first searched for all the Facebook posts having shared a specific link\footnote{ Click \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{here} to access the link and  \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{its fact-check by Health Feedback}.} rated as ‘False’ by Science Feedback, a fact-checking organization which partners with Facebook.
+To do so, we used the `search' endpoint in CrowdTangle API.
+Twenty Facebook posts were collected this way, and we scripted an adapted scraping code to verify whether they contained an information banner, a fact-check flag, both or none.
 Three posts were unavailable, and thus could not be categorized by the scraper.
@@
 \centering
-\includegraphics[scale=0.5]{../figure/facebook_pie_flags.png}
-\caption{Count of different flags for 17 Facebook posts who have shared the exact same link, fact-checked False by one of Facebook’s partners.
-The claim fact checked as False appeared in the following article on beforeitsnews.com:  ``Stay Away From The Vaxxed, It Is Official, From Pfizer’s Own Documents".
-}
+\includegraphics[scale=0.4]{../figure/facebook_pie_flags_updated.png}
+\caption{Count of different flags for 17 Facebook posts who have shared the exact same link, fact-checked False by one of Facebook’s partners. }
 \label{tab_flags_fb}
@@
 
-We also observed that most of the posts sharing this ``False'' link (13 out of 17, Table \ref{tab_flags_fb}) had an information banner saying ``Visit the COVID-19 Information Centre for vaccine resources" (see the first two examples of Figure \ref{fb_flags}).
+We also observed that most of the posts sharing this ``False'' link (13 out of 17, Figure \ref{tab_flags_fb}) had an information banner saying ``Visit the COVID-19 Information Centre for vaccine resources" (see the first two examples of Figure \ref{fb_flags}).
 We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example).
@@
 
-Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.
-At the tweet level, notices take the form of a label or an interstitial.
+Alongside other social networking platforms, when the content of a Tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.
+At the Tweet level, notices take the form of a label or an interstitial.
 Labels are context specific (e.g.
-COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it ``Get the facts about COVID-19''} (see right panel of figure \ref{fig8}).
-Interstitials are presented as a greyed box on top of a tweet, which indicates sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example {\it ``The following media includes potentially sensitive content''} (see left panel of figure \ref{fig_notice}).
+COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it ``Get the facts about COVID-19''} (see right panel of Figure \ref{fig8}).
+Interstitials are presented as a greyed box on top of a Tweet, which indicates sensitive content, violations of Twitter rules, withheld Tweets for violation of local laws or even Tweets from suspended accounts, for example {\it ``The following media includes potentially sensitive content''} (see left panel of Figure \ref{fig_notice}).
 At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.
@@
 \centering
-	%\begin{multicols}{1}
 		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
-   	 %\end{multicols}
-	%\begin{multicols}{1} 
 		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
-	%\end{multicols}
-	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021.
+	\caption{Two Tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021.
 Left Panel: Tweet without an information notice.
@@
 
+\begin{figure}[h]
+	\centering
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
+		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
+	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial.
+Right Panel: when clicking on $view$, to view the content hidden behind the interstitial in the left panel.
+Screenshots taken on July 1, 2021.
+}
+	\label{fig_notice}
+\end{figure}
 %	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021.
@@
 Right Panel: Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
-
-\smallskip
-
-To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet contains a label or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the Twitter API v2.
-Hence, in order to investigate the presence of notices of all types, we resorted to scrape publicly available tweets, using Minet [5].
-This tool was recently enriched upon our request in order to capture whether a tweet contains a notice or not, via the ``minet twitter scrape'' command.
-
-\smallskip
-
-In this section, we take a deeper look at how labels and interstitials are introduced by Twitter, to add context to potentially inaccurate or misleading content.
-To that end, we gathered a set of $3$ $094$ links redirecting to articles which were marked as ``False'' between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
-As a second step, we collected (on June $30$, $2021$) using Minet~\cite{minet} all the tweets that have shared a link which belongs to the set of $3$ $094$ links marked as $False$.
-This data collection resulted in $323$ $938$ tweets, excluding retweets.
-Only $28$ tweets contained the label { \it ``Get the facts about COVID-19''}, $5$ tweets contained the label {\it ``Learn about US 2020 election security efforts''} and only $1$ had the following label {\it ``This claim about election fraud is disputed''}.
-Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same link, among the set of collected tweets.
-To give an example, $657$ tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}.
-Among those $657$ tweets only $3$ contained the label {\it ``Get the facts about COVID-19''} (see figure \ref{fig8}).
-This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by other users.
-
-\begin{figure}[h]
-	\centering
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
-	%\end{multicols}
-	%\begin{multicols}{1}
-		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
-	%\end{multicols}
-	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial.
-Right Panel: when clicking on $view$, to view the content hidden behind the interstitial in the left panel.
-Screenshots taken on July 1, 2021.
-}
-	\label{fig_notice}
-\end{figure}
 %	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial.
@@
 }
+
+\smallskip
+
+To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a Tweet contains a label or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the Twitter API v2.
+Hence, in order to investigate the presence of notices of all types, we resorted to scrape publicly available Tweets, using minet~\cite{minet}.
+This tool was recently enriched upon our request in order to capture whether a Tweet contains a notice or not, via the ``minet twitter scrape'' command.
+
+\smallskip
+
+In this section, we take a deeper look at how labels and interstitials are introduced by Twitter, to add context to potentially inaccurate or misleading content.
+To that end, we gathered a set of $3$ $094$ links redirecting to articles which were marked as ``False'' between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
+As a second step, we collected on June $30$, $2021$ all the Tweets that have shared at least one link out of the set of $3$ $094$ links marked as $False$.
+This data collection resulted in $323$ $938$ Tweets, excluding Retweets.
+Only $28$ Tweets contained the label { \it ``Get the facts about COVID-19''}, $5$ Tweets contained the label {\it ``Learn about US 2020 election security efforts''} and only $1$ had the following label {\it ``This claim about election fraud is disputed''}.
+Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of Tweets sharing the exact same link, among the set of collected Tweets.
+To give an example, $657$ Tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}.
+Among those $657$ Tweets only $3$ contained the label {\it ``Get the facts about COVID-19''} (see Figure \ref{fig8}).
+This points towards the non-automation of the Tweet labelling process and that it might be that these $3$ Tweets were the only ones reported by other users.
+
 \smallskip
@@
 We further examine the placement of interstitials that indicate a possibly sensitive content.
-We find that only $9$ $344$ ($2.97\%$) tweets out of $323$ $938$ containing a link marked as False, have an interstitial {\it ``potentially sensitive content''}.
-To check whether the interstitial {\it ``potentially sensitive content''} is automated or not, we pick out one tweet having shared a link\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.} marked as ``False'', which also contains the interstitial {\it potentially sensitive content} (see figure \ref{fig_notice}).
-Then we look in the set of $323$ $938$ tweets for other tweets who have shared the exact same link.
-We find a total of $32$ tweets.
-Among those $32$ tweets only $5$ tweets had the interstitial ``potentially sensitive content''.
-Again this points towards the non-automation of interstitials placement.
+We find that only $9$ $344$ ($2.97\%$) Tweets out of $323$ $938$ containing a link marked as False, have an interstitial {\it ``potentially sensitive content''}.
+To check whether the interstitial {\it ``potentially sensitive content''} is automated or not, we pick out one Tweet having shared a link\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.} marked as ``False'', which also contains the interstitial {\it potentially sensitive content} (see Figure \ref{fig_notice}).
+Among the $32$ Tweets that have shared the exact same link, only $5$ tweets had the interstitial ``potentially sensitive content''.
+Again this points towards the non-automation of interstitials placement based on a specific URL.
 Furthermore, notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations.
@@
 
-\smallskip
-
-Finally, the number of tweets containing the interstitial {\it ``potentially sensitive content''} ($9$ $344$ tweets) widely outnumbers the tweets which contain a flag ($32$ tweets), among the set of $323$ $938$ tweets containing a link marked as ``False'' (see Figure \ref{flags_tab}).
-Furthermore, we noticed that among the tweets which contain the interstitial {\it ``potentially sensitive content''}, there are tweets which contain links redirecting to misleading articles about COVID-19 and yet they do not contain the label { \it ``Get the facts about COVID-19''}.
-We also noticed that the $9$ $344$ tweets which contain the interstitial {\it ``potentially sensitive content''} do not necessarily contain graphic violent content\footnote{The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.} but rather links that redirect to articles marked as ``False'' by Science Feedback.
-When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it ``potentially sensitive content''} and labels which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".}
-
-%\begin{table}[h]
-%\centering
-%\begin{tabular}{|c|c|c|c|}
-%\hline
-%\multicolumn{4}{|c|}{$323$ $938$ Tweets containing a link marked as False}                                                                                                                                                                                                                                                                                                                           \\ \hline
-%\begin{tabular}[c]{@{}c@{}}with the interstitial\\ ``potentially sensitive \\ content'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Get the facts \\ about COVID-19'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag \\ ``Learn about US \\ 2020 election \\ security efforts'' \end{tabular} & \begin{tabular}[c]{@{}c@{}}with the flag\\ ``This claim about \\ election fraud \\ is disputed''\end{tabular} \\ \hline
-%\begin{tabular}[c]{@{}c@{}}9344\\ (2.88450 \%)\end{tabular}                                  & \begin{tabular}[c]{@{}c@{}}28\\ (0.00864 \%)\end{tabular}                              & \begin{tabular}[c]{@{}c@{}}5\\ (0.00154 \%)\end{tabular}                                                & \begin{tabular}[c]{@{}c@{}}1\\ (0.00030 \%)\end{tabular}                                             \\ \hline
-%\end{tabular}
-%\caption{Summary of the number of tweets among the set of collected tweets containing a link marked as False by Science Feedback, which contain a flag or an interstitial.}
-%\label{flags_tab}
-%\end{table}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.4]{../figure/twitter_pie_flags.png}
-	\caption{Summary of the number of tweets among the set of $323$ $938$ Tweets containing a link marked as False, by Science Feedback, which contain a flag or an interstitial or none.}
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.4]{../figure/twitter_pie_flags_updated.png}
+	\caption{Summary of the number of Tweets among the set of $323$ $938$ Tweets containing a link marked as False, by Science Feedback, which contain a flag or an interstitial or none.}
 \label{flags_tab}
 \end{figure}
+
+\smallskip
+
+Finally, the $9$ $344$ Tweets containing the interstitial ``potentially sensitive content'' widely outnumber the $32$ tweets which contain a label (see Figure \ref{flags_tab}).
+Furthermore, we noticed that among the Tweets which contain the interstitial {\it ``potentially sensitive content''}, there are Tweets which contain links redirecting to misleading articles about COVID-19 and yet they do not contain the label { \it ``Get the facts about COVID-19''}.
+We also noticed that the $9$ $344$ Tweets which contain the interstitial {\it ``potentially sensitive content''} do not necessarily contain graphic violent content\footnote{The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.} but rather links that redirect to articles marked as ``False'' by Science Feedback.
+When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it ``potentially sensitive content''} and labels which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label Tweets that may contain misleading information around COVID-19 vaccinations".}
 
@@
 We collected the information panels, when present, under each video by scraping the content of the web page. 
-Three types of information panels were found regarding COVID-19, COVID-19 Vaccine, and climate change, as shown in figure \ref{youtube_panel_screenshots}.
+Three types of information panels were found regarding COVID-19, COVID-19 Vaccine, and climate change, as shown in Figure \ref{youtube_panel_screenshots}.
 
@@
 We noticed that the same video was sometimes uploaded multiple times and thus appeared on different YouTube links. 
-One YouTube link might contain an information panel while its duplicates did not (see figure \ref{duplicates_yt} for an example).  
+One YouTube link might contain an information panel while its duplicates did not (see Figure \ref{duplicates_yt} for an example).  
 In addition, we noticed that some keywords in the video titles were often associated with an information panel, such as `COVID-19', `coronavirus', `pandemic' and `testing', while some notational variants like `C O V I D 19' or `Cv19' were not associated with a panel.
 Therefore, we suspect that YouTube is automatically adding information panels based on the presence of certain keywords in the video title (and maybe in the video description), independently of the content of the video.
-Note that in figure \ref{duplicates_yt}, the video with `C.O.V.I.D.19' in its title had an information panel, hinting that YouTube might adapt its list of suspect keywords as new notational variants for COVID-19 appear, or that some information panels might be added manually (by content regulators or when a video is flagged by many users).
+Note that in Figure \ref{duplicates_yt}, the video with `C.O.V.I.D.19' in its title had an information panel, hinting that YouTube might adapt its list of suspect keywords as new notational variants for COVID-19 appear, or that some information panels might be added manually (by content regulators or when a video is flagged by many users).
 
@@
 More specifically, Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed.
-Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure (see the article on Facebook Newsroom (2018)~\cite{newsroom2}).
+Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure (see Facebook Newsroom (2018)~\cite{newsroom2}).
 This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the APIs used to access Facebook data: CrowdTangle or BuzzSumo.
@@
 The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars.
-(Top panel) Number of daily posts.
-(Bottom panel) Engagement metrics: average number of reactions, shares and comments per post.
+Left panel: Number of daily posts.
+Right panel: Engagement metrics: average number of reactions, shares and comments per post.
 }
@@
 
-The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} left panel). 
+The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see Figure \ref{infowars1} left panel). 
 Thus the measure announced by Facebook does not seem to have prevented users from sharing an $Infowars$ link.
-Nevertheless, a clear drop in engagement was observed on May $2$, $2019$ (see figure \ref{infowars1} right panel).
+Nevertheless, a clear drop in engagement was observed on May $2$, $2019$ (see Figure \ref{infowars1} right panel).
 The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May $2$, $2019$.
@@
 
-Another measure that platforms can apply is to prevent users from sharing specific types of content, like URLs belonging to a specific domain name.  
-The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company operated by The Epoch Times that shares pro-Trump views and conspiracy theories such as QAnon.
-\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} 
-Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook''.
-\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}}
-
-To verify Facebook’s ban, we first tested whether we could post a Facebook message containing a url from thebl.com.
+Furthermore, Facebook has also announced on December $20$, $2019$ that ``The BL is now banned from Facebook''.\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}} The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company operated by The Epoch Times that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} To verify Facebook’s ban, we first tested whether we could post a Facebook message containing a url from thebl.com.
 This turned out to be impossible.
@@
 
-The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban.
+The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see Figure \ref{fb_bl} left panel), indicating the start of the ban.
 We note that although the ban was communicated in an article published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$.
 The communication around the ban appeared to have discouraged The Beauty of Life to proceed with their activity.
-Indeed the number of articles they published daily was around $50$ until December $20$, $2019$, when it decreased drastically to reach around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).
+Indeed the number of articles they published daily was around $50$ until December $20$, $2019$, when it decreased drastically to reach around $5$ to $10$ articles published per day (see Figure \ref{fb_bl} right panel).
 
@@
 
-Twitter can take action against a tweet which violates the Twitter rules, by limiting its visibility\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.} on users' timelines and in search results.
-To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to \href{https://open.feedback.org/media/AEKA}{open.feedback.org} and Media Bias Fact Check - two websites which provide databases of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://open.feedback.org/media/AEKA}{open.feedback.org/media/AEKA} and \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
+Twitter can take action against a Tweet which violates the Twitter rules, by limiting its visibility\footnote{See the paragraph {\it Limiting Tweet visibility}: \href{https://help.twitter.com/en/rules-and-policies/enforcement-options}{https://help.twitter.com/en/rules-and-policies/enforcement-options}.} on users' timelines and in search results.
+To illustrate we provide an example for the website $globalresearch.ca$, which has several failed fact-checks according to Media Bias Fact Check, a website which provides a measure of factual reporting of several media outlets based on available fact-checks.\footnote{See \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/}.}
 
@@
 Left Panel: screenshot that shows that no results can be found when searching for articles linked to the domain name $globalresearch.ca$ via the Twitter search box.
-Right Panel: example of a tweet posted on June $14$ containing the domain name {\it globalresearch.ca}.
+Right Panel: example of a Tweet posted on June $14$ containing the domain name {\it globalresearch.ca}.
 }
@@
 
-When a user searches via the twitter search-box for this domain name, no results appear as shown in the screenshot in the left panel of figure \ref{fig3}, taken on June $14$, $2021$.
-To further investigate the possible implementation of a reduced visibility measure, we searched via the Twitter API v2 for tweets, excluding retweets, containing the query {\it globalresearch.ca} from April $15$, $2021$ until August $15$, $2021$.
-As shown in the left panel in figure \ref{fig4}, we find a strictly positive number of tweets containing the domain name {\it globalresearch.ca} after the date on which the screenshot was taken (left panel of figure \ref{fig3}).
-Hence, the visibility of tweets containing this domain name has been reduced because users can no longer access tweets containing the domain name {\it globalresearch.ca} via the search box.
-Nevertheless users are not restrained from posting tweets containing this domain name, as shown in the screenshot in panel $(b)$ of figure \ref{fig3}, found by taking the tweet ID of one of the collected tweets via the Twitter API.
-Furthermore, those collected Tweets have strictly positive engagement metrics as shown in panel $(b)$ of figure \ref{fig4}.
-Hence, the users who post tweets including articles from the {\it globalresearch.ca} website receive tweet level engagement from their own followers.
+When a user searches via the twitter search-box for this domain name, no results appear as shown in the screenshot in the left panel of Figure \ref{fig3}, taken on June $14$, $2021$.
+To further investigate the possible implementation of a reduced visibility measure, we searched via the Twitter API v2 for Tweets, excluding Retweets, containing the query {\it globalresearch.ca} from April $15$, $2021$ until August $15$, $2021$.
+As shown in the left panel in Figure \ref{fig4}, we find a strictly positive number of Tweets containing the domain name {\it globalresearch.ca} after the date on which the screenshot was taken (left panel of Figure \ref{fig3}).
+Hence, the visibility of Tweets containing this domain name has been reduced because users can no longer access Tweets containing the domain name {\it globalresearch.ca} via the search box.
+Nevertheless users are not restrained from posting Tweets containing this domain name (see right panel of Figure \ref{fig3}).
+Furthermore, those collected Tweets have strictly positive engagement metrics as shown in the right panel of Figure \ref{fig4}.
+Hence, the users who post Tweets including articles from the {\it globalresearch.ca} website receive Tweet level engagement from their own followers.
 
@@
 		\includegraphics[scale=0.4]{../figure/globalresearch_domain_engagement_2021-08-17.jpg}
-\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.
+\caption{Left Panel: daily number of Tweets, excluding Retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.
 Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$.
@@
 
-Finally, the website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}, which was suspended from Twitter on May $25$, 2021 as shown in a message about the account's suspension (see the right panel in figure \ref{fig4bis}).
+Finally, the website $globalresearch.ca$ is linked to the Twitter account {$@CRG\_CRM$}, which was suspended from Twitter on May $25$, 2021 as shown in a message about the account's suspension (see the right panel in Figure \ref{fig4bis}).
 To the best of our knowledge, no official communication by Twitter has announced the suspension nor the exact date at which it was implemented.
 Hence the account may have gotten suspended before that date.
-Furthermore when a user attempts to click on a link which contains {\it globalresearch.ca} in a Tweet, a warning message appears and indicates that the link may be unsafe (see the left panel in figure \ref{fig4bis}).
+Furthermore when a user attempts to click on a link which contains {\it globalresearch.ca} in a Tweet, a warning message appears and indicates that the link may be unsafe (see the left panel in Figure \ref{fig4bis}).
 For the case of this Twitter account, it is likely that a mix of interventions was used: reducing the visibility via the search box, suspending the related Twitter account and returning a warning message when users click on a link containing this domain name.
@@
 
-YouTube can reduce the visibility of certain video via its recommendation system, namely by recommending content from authoritative sources.
+YouTube can reduce the visibility of certain videos via its recommendation system, namely by recommending content from authoritative sources.
 The platform usually recommends content to the users based on the watch history and searched queries in google and YouTube; which can both be cleared via account settings.
@@
 
-{\bf Channel Level.} 
 The $3$ $895$ unique videos came from $1$ $562$ different channels, and we counted the number of times every channel got recommended.
@@
 	\end{center}
-	\caption{Top ten recommended channels among the $1$ $562$ different channels, that have posted the recommended videos in our dataset.}
+	\caption{Top 10 channels recommended by YouTube when we simulated a user that starts by watching a video fact-checked as False and then follows the top recommendations.}
 	\label{reduce_youtube}
@@
 
-{\bf Video Level.} 
 We then ranked the videos based on the number of times they got recommended, and asked Science Feedback to fact-check the top 40 recommended videos (those videos were recommended $1$ $735$ times, which represents $16\%$ of the recommendations).
@@
 However, by June $2021$, thirty videos had disappeared from the YouTube API for policy violation. 
-Similarly, in a related research project, Thero and Vincent (2020)~\cite{therovincent}) searched on CrowdTangle for $94$ public accounts sharing specific content associated with misinformation in November $2020$.
+Similarly, in a related research project, Th\'{e}ro and Vincent (2020)~\cite{therovincent} searched on CrowdTangle for $94$ public accounts sharing specific content associated with misinformation in November $2020$.
 They tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
@@
 However, a point of concern is that data can also disappear because of other factors independent of platforms' content moderation.
-To provide an example, McMinn et al. (2012)\cite{mcminn2013building} collected $120$ million tweets related to general topics. 
+To provide an example, McMinn et al. (2012)\cite{mcminn2013building} collected $120$ million Tweets related to general topics. 
 The same published set of Tweet IDs was then used by Mazoyer et al.
@@
 Mazoyer et al.
-2020~\cite{mazoyer2020french} were only able to retrieve $67$ millions of tweets (55\%).
-The authors argue that this drop is probably due to tweets having been removed by users and Twitter accounts being shut by the users themselves.
+(2020)~\cite{mazoyer2020french} were only able to retrieve $67$ millions of Tweets (55\%).
+The authors argue that this drop is probably due to Tweets having been removed by users and Twitter accounts being shut by the users themselves.
 As data can disappear from platforms over time, it is hard to distinguish whether platforms or users are the ones responsible for data removal. 
@@
 and CrowdTangle is today a reliable source for researchers to access Facebook data. 
-However, it should be noted that CrowdTangle has been recently used by journalists to show that Facebook is disproportionally favoring highly partisan information\footnote{See the news article \href{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news} and the tweet \href{https://twitter.com/facebookstop10}{https://twitter.com/facebookstop10}.
+However, it should be noted that CrowdTangle has been recently used by journalists to show that Facebook is disproportionally favoring highly partisan information\footnote{See the news article \href{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news} and the Tweets from \href{https://twitter.com/facebookstop10}{https://twitter.com/facebookstop10}.
 The last link is a Twitter account showing each day the ten most shared link on Facebook, most of them coming from extreme right and misinformation sources. 
@@
 For example, the official reason for the suspension of Donald Trump's Twitter account was not misinformation\footnote{Although Donald Trump may have spread many misinformation during his governance, see for example: \href{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}{http://allianceforscience.cornell.edu/blog/2020/10/what-drove-the-covid-misinformation-infodemic/}.}
-but the violation of Twitter's Glorification of Violence Policy, with his last tweets encouraging the Capitol's riot.\footnote{See \href{https://blog.twitter.com/en\_us/topics/company/2020/suspension}{https://blog.twitter.com/en\_us/topics/company/2020/suspension}.}
+but the violation of Twitter's Glorification of Violence Policy, with his last Tweets encouraging the Capitol's riot.\footnote{See \href{https://blog.twitter.com/en\_us/topics/company/2020/suspension}{https://blog.twitter.com/en\_us/topics/company/2020/suspension}.}
 Similarly, when Facebook removed four pages related to the InfoWars website, the cited reason was repeated violations of Community Standards: 
@@
 To illustrate, YouTube explicitly states
-\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.}
+\footnote{See \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{What policies exist to fight misinformation on Youtube?}.}
 that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
@@
 Using a different approach, Mosleh et al.
-(2021)~\cite{mosleh2021perverse} identified Twitter users sharing false news and replied to their false tweets with links redirecting to fact-checking websites.
+(2021)~\cite{mosleh2021perverse} identified Twitter users sharing false news and replied to their false Tweets with links redirecting to fact-checking websites.
 They observed a decrease in the quality and accuracy of the content subsequently shared by the corrected user. 

### 2022-05-02 code/create_figures.py

@@ -434,7 +434,7 @@ def create_twitter_Lifesite_figure(filename, figure_name, title, zeros):
     ax.plot(df_volume['date'],
         df_volume['size'],
         color='deepskyblue',
-        label='Number of Tweets per day')
+        label='Number of Tweets (including Retweets, Replies, Quotes) per day')
 
     ax.set(
        title = title )
@@ -457,7 +457,6 @@ def create_twitter_Lifesite_figure(filename, figure_name, title, zeros):
     plot_format(ax, plt, suspension = 1)
 
     save_figure(figure_name)
-    #plt.show()
 
 def create_twitter_Lifesite_figure_engagement(filename, figure_name, title, zeros):
 
@@ -467,12 +466,6 @@ def create_twitter_Lifesite_figure_engagement(filename, figure_name, title, zero
     df['type_of_tweet'] = df['type_of_tweet'].replace(np.nan, 'created_content')
     df['total_engagement'] = (df['retweet_count'] + df['like_count'] + df['reply_count'])
     df['date'] = pd.to_datetime(df['created_at']).dt.date
-    #df_volume = df.groupby(['date','type_of_tweet'], as_index=False).size()
-    #df_volume = df.groupby(['date'], as_index=False).size()
-
-    # df_s=df.groupby(['date'],as_index=False)[['like_count','retweet_count','reply_count']].sum()
-    # df_s_rolling=df_s.groupby(['date'])[['like_count','retweet_count','reply_count']].sum().rolling(window=1, win_type='triang', center=True).mean()
-    # df_s_rolling['date'] = df_s_rolling.index
 
     df_s=df.groupby(['date'],as_index=False)[['total_engagement']].sum()
     df_s_rolling=df_s.groupby(['date'])[['total_engagement']].sum().rolling(window=7, win_type='triang', center=True).mean()
@@ -504,14 +497,6 @@ def create_twitter_Lifesite_figure_engagement(filename, figure_name, title, zero
             df_s_rolling['total_engagement'],
             color='lightgreen',label='Like + Reply + Retweet Count')
 
-    # ax.plot(df_s_rolling['date'],
-    #         df_s_rolling['reply_count'],
-    #         color='lightgreen',label='Reply Count')
-    #
-    # ax.plot(df_s_rolling['date'],
-    #         df_s_rolling['retweet_count'],
[…]

### 2022-05-02 article/draft.tex
new twitter donut figure

@@
 
-To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a Tweet contains a label or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the Twitter API v2.
+To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a Tweet contains a notice or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the Twitter API v2.
 Hence, in order to investigate the presence of notices of all types, we resorted to scrape publicly available Tweets, using minet~\cite{minet}.
@@
 
-In this section, we take a deeper look at how labels and interstitials are introduced by Twitter, to add context to potentially inaccurate or misleading content.
+In this section, we take a deeper look at how notices and interstitials are introduced by Twitter, to add context to potentially inaccurate or misleading content.
 To that end, we gathered a set of $3$ $094$ links redirecting to articles which were marked as ``False'' between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information.
@@
 This data collection resulted in $323$ $938$ Tweets, excluding Retweets.
-Only $28$ Tweets contained the label { \it ``Get the facts about COVID-19''}, $5$ Tweets contained the label {\it ``Learn about US 2020 election security efforts''} and only $1$ had the following label {\it ``This claim about election fraud is disputed''}.
+Only $28$ Tweets contained the notice { \it ``Get the facts about COVID-19''}, $5$ Tweets contained the notice {\it ``Learn about US 2020 election security efforts''} and only $1$ had the following notice {\it ``This claim about election fraud is disputed''}.
 Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of Tweets sharing the exact same link, among the set of collected Tweets.
 To give an example, $657$ Tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}.
-Among those $657$ Tweets only $3$ contained the label {\it ``Get the facts about COVID-19''} (see Figure \ref{fig8}).
+Among those $657$ Tweets only $3$ contained the notice {\it ``Get the facts about COVID-19''} (see Figure \ref{fig8}).
 This points towards the non-automation of the Tweet labelling process and that it might be that these $3$ Tweets were the only ones reported by other users.
@@
 Again this points towards the non-automation of interstitials placement based on a specific URL.
+To date, no data is available to verify whether some interstitials or notices were placed based on: Tweet reporting by other users, or Twitter moderators, or algorithmic rules.
 Furthermore, notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations.
@@
 	\centering
-	\includegraphics[scale=0.4]{../figure/twitter_pie_flags_updated.png}
-	\caption{Summary of the number of Tweets among the set of $323$ $938$ Tweets containing a link marked as False, by Science Feedback, which contain a flag or an interstitial or none.}
+	\includegraphics[scale=0.5]{../figure/donut_twitter.png}
+	\caption{Summary of the number of Tweets among the set of $323$ $938$ Tweets containing a link marked as False, by Science Feedback, which contain a notice or a Possibly sensitive interstitial or none.}
 \label{flags_tab}
@@
 
-Finally, the $9$ $344$ Tweets containing the interstitial ``potentially sensitive content'' widely outnumber the $32$ tweets which contain a label (see Figure \ref{flags_tab}).
-Furthermore, we noticed that among the Tweets which contain the interstitial {\it ``potentially sensitive content''}, there are Tweets which contain links redirecting to misleading articles about COVID-19 and yet they do not contain the label { \it ``Get the facts about COVID-19''}.
+Finally, the $9$ $344$ Tweets containing the interstitial ``potentially sensitive content'' widely outnumber the $34$ tweets which contain a notice (see Figure \ref{flags_tab}).
+We noticed that among the Tweets which contain the interstitial {\it ``potentially sensitive content''}, there are Tweets which contain links redirecting to misleading articles about COVID-19 and yet they do not contain the label { \it ``Get the facts about COVID-19''}.
 We also noticed that the $9$ $344$ Tweets which contain the interstitial {\it ``potentially sensitive content''} do not necessarily contain graphic violent content\footnote{The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.} but rather links that redirect to articles marked as ``False'' by Science Feedback.
-When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it ``potentially sensitive content''} and labels which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label Tweets that may contain misleading information around COVID-19 vaccinations".}
+When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it ``potentially sensitive content''} and notices which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label Tweets that may contain misleading information around COVID-19 vaccinations".}
 
@@
 	\centering
-		\includegraphics[scale=0.3]{../figure/youtube_pie_flags.png}
+		\includegraphics[scale=0.2]{../figure/youtube_pie_flags.png}
 		\caption{Summary of the number of YouTube videos which contain an information panel, among the set of videos marked as false by Science Feedback.}
 \label{youtube_panel_proportions}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+		\begin{multicols}{1}
+		\includegraphics[scale=0.22]{./img/youtube_panels/graph_no_banner.png}
+		\includegraphics[scale=0.22]{./img/youtube_panels/graph_with_banner.png} 
+		\end{multicols}
+	\caption{Screenshots showing two duplicates of the same video, taken on July 21, 2021. 
+Left panel: a \href{https://www.youtube.com/watch?v=d9GbVZOcT18}{YouTube video} about COVID-19 without an information panel. 	
+Right panel: a \href{https://www.youtube.com/watch?v=A4RvrEKoNxc}{duplicate of the same video} uploaded under a different title and with a `COVID-19 vaccine' information panel.}
+	\label{duplicates_yt}
 \end{figure}
@@
 It is possible that YouTube is currently focusing its efforts on the current `hot' controversial topics with a potentially wide public impact, leaving room for misinformation related to other topics to spread, but more research is needed to formally compare misinformation videos about COVID-19 and about other subjects.
-
 \smallskip
@@
 Note that in Figure \ref{duplicates_yt}, the video with `C.O.V.I.D.19' in its title had an information panel, hinting that YouTube might adapt its list of suspect keywords as new notational variants for COVID-19 appear, or that some information panels might be added manually (by content regulators or when a video is flagged by many users).
-
-\begin{figure}[h]
-	\centering
-		\begin{multicols}{1}
-		\includegraphics[scale=0.24]{./img/youtube_panels/graph_no_banner.png}
-		\includegraphics[scale=0.24]{./img/youtube_panels/graph_with_banner.png} 
-		\end{multicols}
-		%\includegraphics[scale=0.2]{./img/youtube_panels/news_with_banner.png}
-		%\includegraphics[scale=0.2]{./img/youtube_panels/news_without_banner.png} 
-	\caption{Screenshots showing two duplicates of the same video, taken on July 21, 2021. 
-Left panel: a \href{https://www.youtube.com/watch?v=d9GbVZOcT18}{YouTube video} about COVID-19 without an information panel. 	
-Right panel: a \href{https://www.youtube.com/watch?v=A4RvrEKoNxc}{duplicate of the same video} uploaded under a different title and with a `COVID-19 vaccine' information panel.}
-	\label{duplicates_yt}
-\end{figure}
-
-%\subsection{Blocking links}
-
-%\subsubsection{Twitter}
-
-%\href{https://help.twitter.com/en/safety-and-security/phishing-spam-and-malware-links}{link}
 

### 2022-05-02 code/create_figures.py

@@ -657,10 +657,6 @@ def create_pie_pp_tw(figure_name):
     labels= [ 'Without interstitial \nor notice', 'With interstitial \n Possibly Sensitive', "With notice"]
     categories = [314560, 9344, 34]
 
-    #ax.set_title(title,
-    #        fontsize=60)
-
-    #cmap = plt.get_cmap('PiYG')
     colors = ["deepskyblue", 'lightcoral', "azure"]
 
     ax.pie(
@@ -674,6 +670,38 @@ def create_pie_pp_tw(figure_name):
 
     save_figure(figure_name)
 
+def create_donut(figure_name):
+
+    fig, ax = plt.subplots(figsize=(6, 15), subplot_kw=dict(aspect="equal"))
+
+    ratings = ['Tweets without notices\nor Possibly Sensitive\n interstettial (314 560)', 'Tweets with a notice (34)', 'Tweets with the Possibly Sensitive interstitials (9 344)']
+    data = [314560, 34, 9344]
+
+    cmap = plt.get_cmap('coolwarm')
+    colors = ['deepskyblue', 'pink', 'lightcoral']
+
+    wedges, texts = ax.pie(data, wedgeprops=dict(width=0.4), startangle=210, colors = colors)
+
+    bbox_props = dict(boxstyle="square,pad=0.2", fc="w", ec="k", lw=0.72)
+
+    kw = dict(arrowprops=dict(arrowstyle="-"),
+              bbox=bbox_props, zorder=0, va="center")
+
+    plt.text(0, 0, "Tweets with links\nfact checked as\n false", ha='center', va='center', fontsize=14)
+
+    for i, p in enumerate(wedges):
+
+        ang = (p.theta2 - p.theta1)/2. + p.theta1
+        y = np.sin(np.deg2rad(ang))
+        x = np.cos(np.deg2rad(ang))
+        horizontalalignment = {-1: "right", 1: "left"}[int(np.sign(x))]
+        connectionstyle = "angle,angleA=0,angleB={}".format(ang)
+        kw["arrowprops"].update({"connectionstyle": connectionstyle})
+        ax.annotate(ratings[i], xy=(x, y), xytext=(1.3*np.sign(x), 1.3*y),
+                    horizontalalignment=horizontalalignment, **kw)
+
+    save_figure(figure_name)
+
 def create_pie_pp_fb(figure_name):
 
     fig = plt.figure(figsize=(10, 6))
[…]

### 2022-05-04 article/draft.tex
ref added

@@
 Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see Appendix \ref{links} for references).
-While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation.
+While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation (see Fathaigh et al.
+(2021)~\cite{fathaigh} for a discussion for the case of the EU).
 The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies point towards the idea that misinformation is a small subset of the total supply of information on online social networking platforms (e.g.
@@
 such as {\it off-guardian.
-org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}.\footnote{For this case, we failed to understand precisely what kind of intervention Twitter users were circumventing, since they could share in a Tweet an article redirecting to the website {\it off-guardian.org} with the correct notation and only a warning message would appear when one clicks on it.}
-Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
+org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}.\footnote{For this case, we failed to understand precisely what kind of intervention Twitter users were circumventing, since they could share in a Tweet an article redirecting to the website {\it off-guardian.org} with the correct notation and only a warning message would appear when one clicks on it.} Furthermore there is little information about how algorithms are practically used as a tool for content moderation; since they can be used to reduce the visibility of some content or even prevent problematic content from being recommended.
+Hence researchers have to resort to proxy measures and simulated experiments to have a better understanding the impact of algorithmic design.
+Based on a sample of $23$ YouTube studies, Yesilada and Lewandowsky (2022)~\cite{yesilada} find that YouTube recommender system could lead users to problematic content, but highlight the limitations of this conclusion since there is an incomplete understanding of the recommendation system and models built might not reflect the actual functioning of YouTube recommendation algorithm.
+%point here about algorithms and cite Yesilada and Lewandowsky (2022)~\cite{yesilada}
+Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that both users and researchers can understand and investigate how the platforms are regulating content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.
 
@@
 %https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works
+\noindent {\bf Acknowledgments} \\
+We thank our colleagues at Sciences Po m\'{e}dialab for their feedback and suggestions. \bigskip
+
 \noindent {\bf Funding} \\
@@
 The data collection and processing complied with the EU General Data Protection Regulation (GDPR).
+
 \end{document}

### 2022-05-06 article/draft.tex
ignore screenshots

@@
 They tried to collect the posts from those $94$ pages in January $2021$, to only discover that $11$ pages had disappeared from the CrowdTangle API.
-It is of course not surprising that platforms are regulating their content, sometimes by removing it. 
-Nevertheless, researchers' work could be simplified, if metadata for content posted by removed accounts could still be accessible via the APIs.
+Researchers' work could be simplified, if metadata for content posted by removed accounts could still be accessible via the APIs.
 

### 2022-05-06 code/create_figures.py

@@ -406,7 +406,6 @@ def create_twitter_Lifesite_figure(filename, figure_name, title, zeros):
     df['type_of_tweet'] = df['type_of_tweet'].replace(np.nan, 'created_content')
     df['total_engagement'] = (df['retweet_count'] + df['like_count'] + df['reply_count'])
     df['date'] = pd.to_datetime(df['created_at']).dt.date
-    #df_volume = df.groupby(['date','type_of_tweet'], as_index=False).size()
     df_volume = df.groupby(['date'], as_index=False).size()
 
     if zeros == 1 :
@@ -495,7 +494,7 @@ def create_twitter_Lifesite_figure_engagement(filename, figure_name, title, zero
 
     ax.plot(df_s_rolling['date'],
             df_s_rolling['total_engagement'],
-            color='lightgreen',label='Like + Reply + Retweet Count')
+            color='lightgreen', label='Like + Reply + Retweet Count')
 
     ax.set(
        title = title )
@@ -578,11 +577,6 @@ def create_twitter_globalresearch_figure(filename, figure_name, title, zeros):
     #ax.set_xlim([date(2021,1,1), date(2021, 6, 30)])
     plt.axvline(np.datetime64("2021-06-14"), color='C3', linestyle='--')
 
-
-    #plt.axvspan(np.datetime64('2021-05-25'), np.datetime64('2021-08-15'),
-    #        ymin=0, ymax=200000, facecolor='r', alpha=0.05)
-
-
     plot_format(ax, plt, suspension = 0)
 
     save_figure(figure_name)
@@ -602,27 +596,27 @@ def create_twitter_figures():
     title = f"Tweets containing the domain name lifesitenews.com",
     zeros = 0
     )
-    #
-    # create_twitter_Lifesite_figure_engagement(
-    # filename = 'twitter_lifesitenews_domain_name_2021-07-29.csv',
-    # figure_name = 'lifesite_domain_engagement.jpg',
-    # title = f"Tweets containing the domain name lifesitenews.com",
-    # zeros = 0
-    # )
+    
+    create_twitter_Lifesite_figure_engagement(
+    filename = 'twitter_lifesitenews_domain_name_2021-07-29.csv',
+    figure_name = 'lifesite_domain_engagement.jpg',
+    title = f"Tweets containing the domain name lifesitenews.com",
+    zeros = 0
+    )
 
-    # create_twitter_globalresearch_figure(
[…]

### 2022-05-06 code/utils_twitter.py

@@ -1,142 +1,89 @@
-#from __future__ import absolute_import
-
 import requests
 import csv
-#import dotenv
 import time
 import json
 import os
 import os.path
 
 from csv import writer
-#from dotenv import load_dotenv
 from time import sleep
 
-#documentation: https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all
-#max_results: A number between 10 and the system limit (currently 500). By default, a request response will return 10 results.
+'''Functions to collect historical search twitter data from the API v2'''
+
 #300 requests per 15-minute window (app auth)
-#Updates: max results is now 100
+#Updates: max results is now 100!
 
-
-def connect_to_endpoint(bearer_token, query, start_time, end_time, next_token=None):
+def connect_to_endpoint_historical_search(bearer_token, query, start_time, end_time, next_token=None):
 
     max_results=100
 
-    headers = {"Authorization": "Bearer {}".format(bearer_token)}
+    headers = {'Authorization': 'Bearer {}'.format(bearer_token)}
 
-    params = {"tweet.fields" : "in_reply_to_user_id,author_id,context_annotations,created_at,public_metrics,entities,geo,id,possibly_sensitive,lang,referenced_tweets", "user.fields":"username,name,description,location,created_at,entities,public_metrics","expansions":"author_id,referenced_tweets.id"}
+    params = {'tweet.fields' : 'in_reply_to_user_id,author_id,context_annotations,created_at,public_metrics,entities,geo,id,possibly_sensitive,lang,referenced_tweets', 'user.fields':'username,name,description,location,created_at,entities,public_metrics','expansions':'author_id,referenced_tweets.id,attachments.media_keys'}
 
     if (next_token is not None):
-        url = "https://api.twitter.com/2/tweets/search/all?max_results={}&query={}&start_time={}&end_time={}&next_token={}".format(max_results, query, start_time, end_time, next_token)
+        url = 'https://api.twitter.com/2/tweets/search/all?max_results={}&query={}&start_time={}&end_time={}&next_token={}'.format(max_results, query, start_time, end_time, next_token)
     else:
-        url = "https://api.twitter.com/2/tweets/search/all?max_results={}&start_time={}&end_time={}&query={}".format(max_results, start_time, end_time, query)
+        url = 'https://api.twitter.com/2/tweets/search/all?max_results={}&start_time={}&end_time={}&query={}'.format(max_results, start_time, end_time, query)
 
[…]

### 2022-05-06 code/create_figures.py
create main figures

@@ -596,7 +596,7 @@ def create_twitter_figures():
     title = f"Tweets containing the domain name lifesitenews.com",
     zeros = 0
     )
-    
+
     create_twitter_Lifesite_figure_engagement(
     filename = 'twitter_lifesitenews_domain_name_2021-07-29.csv',
     figure_name = 'lifesite_domain_engagement.jpg',
@@ -709,18 +709,21 @@ def create_pie_pp_fb(figure_name):
 
 def create_pie_figures():
 
-    #create_pie_pp_fb('facebook_pie_flags_updated')
-    #create_pie_pp_tw('twitter_pie_flags_updated')
-    #create_pie_pp('youtube_pie_flags')
+    create_pie_pp_fb('facebook_pie_flags_updated')
+    create_pie_pp('youtube_pie_flags')
     create_donut('donut_twitter')
+
+def main():
+
+    create_facebook_trump_figure()
+    create_buzzsumo_thebl_figure()
+    create_facebook_crowdtangle_infowars_figure()
+    create_facebook_buzzsumo_infowars_figure()
+    create_youtube_graph()
+    create_pie_figures()
+    create_plot_top_channel_youtube('./data/experiment2_health_full_data.csv')
+    create_twitter_figures()
 
 if __name__=="__main__":
 
-    # create_facebook_trump_figure()
-    # create_buzzsumo_thebl_figure()
-    # create_facebook_crowdtangle_infowars_figure()
-    # create_facebook_buzzsumo_infowars_figure()
-    # create_youtube_graph()
-    create_pie_figures()
-    # create_plot_top_channel_youtube('./data/experiment2_health_full_data.csv')
-    #create_twitter_figures()
+    main()

### 2022-05-06 article/draft.tex
typos

@@
 In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society when it goes viral.
-This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.
+This gave rise to a set of heterogenous policies across mainstream platforms, mainly based on fact-checking but also content moderators and users' reporting.
 For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.
@@
 Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc.
-As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms.
+As each platform is a private company, those policies are generally not coordinated and are implemented in different ways across platforms.
 Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.
@@
 Misinformation related interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g.
-academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports.
+academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and to date, it does not explicitly appear as a separate category in available transparency reports.
 This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community.
@@
 
-Mainstream platforms such as Facebook, Twitter and Youtube are increasingly working towards higher data transparency (see links that redirect to the respective transparency centers in Appendix \ref{links}).
+Mainstream platforms such as Facebook, Twitter and Youtube are increasingly working towards higher data transparency.
+We invite the reader to see links that redirect to the respective transparency centers in Appendix \ref{links}.
 Yet the present research sheds light on the restrictions to access data and its limits, which impede the academic community from studying successfully online misinformation and assessing the impact of platforms' interventions regarding this phenomenon.
@@
 As data can disappear from platforms over time, it is hard to distinguish whether platforms or users are the ones responsible for data removal. 
-Hence in the special case of Twitter accounts related to QAnon, it is hard to identify how much of the drop in QAnon related hashtag use is due to the Twitter intervention or to accounts migrating to other platforms out of fear of having their accounts suspended by the platform.
+Hence in the special case of Twitter accounts related to QAnon, it is hard to identify how much of the drop in QAnon related hashtag use is due to the Twitter intervention or to accounts migrating to other platforms out of fear of having their accounts suspended by the platform or simply a drop in using the hashtag for other unidentified factors.
 
@@
 Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs.
-Nevertheless the number of Tweets that can be retrieved has decreased between the Twitter API v1 and v2.
-In the v2, there is a monthly cap of $10,000,000$ Tweets for the academic research track\footnote{https://developer.twitter.com/en/docs/projects/overview},
-while in the v1 there was no monthly limit and only a limit on the number of requests that could be made in a 15-minute window\footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
-We thus noticed that we could get around $10$ times more Tweets per month with the v1 when compared to the v2 for one specific collection.
+%Nevertheless the number of Tweets that can be retrieved has decreased between the Twitter API v1 and v2.
+%In the v2, there is a monthly cap of $10,000,000$ Tweets for the academic research track\footnote{https://developer.twitter.com/en/docs/projects/overview},
+%while in the v1 there was no monthly limit and only a limit on the number of requests that could be made in a 15-minute window\footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
+%We thus noticed that we could get around $10$ times more Tweets per month with the v1 when compared to the v2 for one specific collection.
 
@@
 \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}.} 
-In the above ``known'' examples, the compagnies' communication was very clear on the reason of the interventions (although one can suspect that the official reason given can depart from the real motivation behind an intervention).
+In the above examples, the compagnies' communication was very clear on the reason of the interventions (although one can suspect that the official reason given can depart from the real motivation behind an intervention).
 However, very often no official communication on behalf of the platforms can be found for a specific interventions observed in collected data. 
@@
 It is also possible that platforms usually follow specific rules on how to fight misinformation, but that sometimes the sudden media coverage of specific events leads them to take exceptional actions, such as with the Capitol riots and Trump's suspension from Facebook, Twitter and YouTube.
-We would argue that to efficiently curb the spread of misinformation, policies should be clearly stated and consistently applied, rather than implementing interventions on a case-by-case basis and in response to the latest news events.
-
-\smallskip
-
-Furthermore, it is likely that most interventions used to tackle online misinformation correspond to interventions that were designed for earlier policy areas.
+We would argue that policies should be clearly stated and carefully designed, rather than implementing interventions on a case-by-case basis and in response to the latest news events.
+
+\smallskip
+
+Furthermore, it is likely that some interventions used to tackle online misinformation correspond to interventions that were designed for earlier policy areas.
 To illustrate, YouTube explicitly states
-\footnote{See \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{What policies exist to fight misinformation on Youtube?}.}
+\footnote{See \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{What policies exist to fight misinformation on Youtube?} (Last visited September 2021).}
 that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
@@
 In particular, such interventions can generate platform migrations (see Rogers (2020)~\cite{rogers2020}) towards new alternative social media platforms (e.g.
-Telegram, Gab, Minds) with little or no content moderation.
-
-\smallskip
-
-Finally, the means to tackle online misinformation is an active area of research.
-Developing effective interventions against misinformation depends on understanding the interventions currently used by platforms (e.g.
+Telegram, Gab, Minds).
+\smallskip
+
+Finally, the means to tackle online misinformation and understanding the phenomenon itself, is an active area of research.
+Developing pertinent interventions against misinformation depends on understanding the interventions currently used by platforms (e.g.
 for labeling, see Morrow et al.

### 2022-05-09 article/draft.tex
final typose

@@
 (2018)~\cite{lazer}).
-The misinformation phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
+The misinformation phenomenon is still ill-defined, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.
 The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation.
@@
 	\caption{Left Panel: Tweet announcing OANN moving to Rumble, Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.
-Right Panel: Tony Heller's tweet after getting suspended from YouTube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
+Right Panel: Tony Heller's tweet after getting temporally suspended from YouTube.}
 	\label{tweets_about_yt_suspensions}
 \end{figure}
-
+%Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}
 \smallskip
@@
 Tony Heller writes regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to the website Media Bias Fact Check.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}}
-Tony Heller tweeted on September 29, 2020 about his YouTube channel being `shut down' because of a video about an anti-covid-lockdown doctor getting arrested (see the right panel of Figure \ref{tweets_about_yt_suspensions}).
+He tweeted on September 29, 2020 about his YouTube channel being `shut down' because of a video about an anti-covid-lockdown doctor getting arrested (see the right panel of Figure \ref{tweets_about_yt_suspensions}).
 We applied the same methods as in the previous example to collect data.
@@
 But we observed that the intervention was followed by a reduction in the number of view for the two channels investigated, with one channel even stopping its YouTube activity in the following months. 
-Although more research is needed before drawing a definitive conclusion, it is possible that the one-week suspension following a strike might reduce the reach of the very active YouTube channels.
+Although more research is needed, it is possible that the one-week suspension following a strike might reduce the reach of active YouTube channels.
 
@@
 As Science Feedback has informed Facebook that they have assigned the rating ``False'' for this link, we expected that all these posts would contain a fact-check flag, but we had no expectations for the information banner.
-
-%\begin{table}[h]
-%\begin{tabular}{|c|c|c|c|}
-%\hline
-%\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
-%without a flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check and an \\  information flags\end{tabular} \\ \hline
-%0            & 7                        & 4                      & 7                                                                                     \\ \hline
-%\end{tabular}
-%\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
-%\label{tab_flags_fb}
-%\end{table}
 
@@
 At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.
-
-%\smallskip
 
@@
 However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended.
-It appears that the recommendation system of YouTube is reducing the visibility of certain videos but not of unreliable channels.
+It appears that the recommendation system of YouTube is reducing the visibility at the video level but not necessarily at the channel level.
 

### 2023-02-24 article/draft_v_2_jan_2023.tex
updates

\documentclass[Afour,sageh,times]{sagej}

\usepackage{moreverb,url}

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2023}

\begin{document}

\runninghead{Shabayek, Théro, Almanla, Vincent}

%\title{Misinformation policies of large platforms: methods \& illustration}
\title{Misinformation policies of large platforms: methods and illustration}

\author{Shaden Shabayek\affilnum{1}, H\'{e}lo\"{i}se Th\'{e}ro\affilnum{2}, Dana Almanla\affilnum{3}, Emmanuel Vincent\affilnum{4}}

\affiliation{\affilnum{1}Post-doctoral researcher at Universit\'{e} Paris-Saclay \& associate researcher at Medialab SciencesPo\\
\affilnum{2} xxxx \\ 
\affilnum{3} xxxx \\
\affilnum{4} xxxx}

\corrauth{Shaden Shabayek}

\email{shaden.shabayek@sciencespo.fr}

\begin{abstract}
There is growing pressure for very large online platforms, such as Facebook, Twitter or YouTube, to deal with misinformation by moderating content deemed as harmful and misleading. We investigate platforms' interventions by collecting social media data via APIs and scraping. These interventions can be classified into three broad categories: (i) displaying flags and information panels,  (ii) reducing the visibility of content at the post or account level and (iii) temporary or permanent suspension of users and content deletion. We provide examples illustrating how researchers can monitor misinformation related interventions within each of these three categories. Finally, we discuss the restrictions to access data, the lack of meaningful transparency and the necessity of independent audits.
\end{abstract}

\keywords{Misinformation, content moderation, large platforms.}

\maketitle

\section{Introduction}

Section $230$ in the Communications Decency Act (1996) in the US and articles $12$ and $15$ in the e-commerce Directive (2000) in the EU,  provide immunity for website platforms against the content created by users. This regulatory framework was meant to help internet service providers and online intermediaries to develop. About two decades later, the initial project of a decentralised internet where users can communicate, express themselves, acquire and build collectively new knowledge, has been replaced by a centralised cyberspace dominated by a handful of tech giants.  This market concentration has been accompanied over the years by growing concerns about informational disorders, including the propagation of misleading content concerning matters of public interest or the normalisation of hate speech. Being subject to public pressure, large social media platforms, such as Facebook, Twitter or YouTube, have adopted a model of self-regulation to tackle these informational disorders and have each practiced some form of content moderation (see \cite{gillespie2018custodians} and  \cite{kaye2019speech} for a discussion). Namely, large platforms have tailored {\it terms of service} that users are bound to respect in order to be able to use the offered products, such as access to one's account or the possibility to publish content. Large platforms themselves are in charge of making sure these rules are not violated. In particular, they take explicit actions when content is in violation of local laws in different jurisdictions, such as laws regarding defamation of a racial nature or privacy protection.\endnote{Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020. See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}. We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} While each large platform has its own original identity as a private company which provides means of communication and a space for expression for millions of users worldwide, their growing influence on public conversations has made several actors question their legitimacy and capacity to govern what has come to be a new online public sphere. The recent adoption of the Digital Services Act (hereafter \cite{dsa}) in Europe marks a shift in paradigm, as the transparency and accountability of large platforms constitute the main pillars of this new regulatory framework, see \cite{hoboken2022dsa} for a discussion about enforcement. 
% focus: too big to let them be on their own 
% toO big, big impact , that their could be big harm that collective effort is needed to govern this space.
% work has been done on policy areas nudity child safety etc mdoerators + algorithms but not misleading content a big issue that we cant rly handle ?

\smallskip

Community guidelines of Facebook, Twitter and YouTube can be summarised in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam. While specific to each platform, the previously cited categories correspond in most cases to well defined concepts, for which there exists legal frameworks in many countries. However, misleading content suffers from a lack of a pertinent and consensual definition (\cite{fathaigh}, \cite{lazer}) and is often subject to misconceptions (\cite{Berriche2023}). It is difficult to identify and qualify a piece of online content as inaccurate, misleading and harmful, among a large volume of daily produced content including opinions, satire and parody. During the COVID-19 global health pandemic, platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content. One novel policy by \cite{facebookcovid} and \cite{twittercovid} consisted in listing a number of claims deemed as misleading or false and announcing clearly that the platform will remove these statements. \endnote{Notice that for Twitter the Policy has been suspended since November 23, 2022.}
%\endnote{See the archived version of Facebook's covid 19 policy \href{https://archive.ph/PaQW8}{https://archive.ph/PaQW8}. Notice that for Twitter the Policy has been suspended since November 23, 2022. See \href{https://archive.ph/ez3eO}{https://archive.ph/ez3eO}.} 
Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation. Yet it also sheds light on the lack of specific consensual policies to deal with misinformation in general, resulting from a collective and inclusive conversation about whether and how misleading content should be actioned in times of a global pandemic, elections, conflict or war.

There is a growing academic literature on misinformation, which relies on fact-checked articles or annotated data as a starting point. Yet many open questions remain, such as the actual prevalence of misinformation on social networks (\cite{grinberg}, \cite{guess2019less}, \cite{broniatowski}) and whether exposure to misleading content necessarily translates into a change in behaviour or decision making (\cite{valensise}, \cite{greene}). In the present article, to get a better understanding of the misinformation phenomena, we choose a different perspective and take as a starting point the study of large platforms' content moderation policies regarding misinformation. We ask several research questions: 
%\begin{itemize}
	%\item 
what content moderation policies linked to misinformation, do large platforms such as Facebook, YouTube and twitter, currently use? How can we study these policies? Can we evaluate their efficacy? Can we say something about their pertinence?

\subsection{Misinformation policies are hard to grasp}
Misinformation related interventions are poorly understood, mainly due to a lack of communication and clarity about how rules are implemented. Based on survey data, \cite{saltzbarrari} show that $40\%$ of the survey respondents (wrongly) believed that content is mostly or all fact-checked. Moreover, algorithms are often used for content moderation, as they can reduce the visibility of some content or even prevent problematic content from being recommended (\cite{gillespie2022not}). Beyond users own personal experience  with algorithms (\cite{cotter2021shadowbanning}, \cite{cotter2019playing}, \cite{bishop2019managing}) and academic literature on algorithmic content moderation focused on earlier policy areas such as copyrights, terrorism or toxic speech (\cite{gorwa2020algorithmic}), there is little information about the actual functioning of algorithms and how they are used for misinformation related interventions. Hence researchers have to resort to proxy measures and experiments to get a better understanding of the impact of algorithmic design on the spread of problematic content. Based on a sample of $23$ YouTube studies, \cite{yesilada} find that YouTube recommender system could lead users to problematic content, but highlight the limitations of this conclusion since there is an incomplete understanding of the recommendation system and models built might not reflect the actual functioning of YouTube recommendation algorithm. Furthermore, lack of information and transparency about content moderation policies have lead to accusations of political bias by large platforms. \cite{yang2022twitter} study empirically the potential anti-conservative bias of Twitter. They find that the observed asymmetry of account suspension when comparing Democratic users and Republicans could be explained by misinformation sharing: {\it Republican users shared more links to misinformation sites than Democratic users}. Finally, understanding recommendation systems as a tool to moderate and limit the spread of misleading content is difficult not only because of the lack of access to information and their complexity, but also because recommendation algorithms are ever-changing (see \cite{llanso2020artificial}).

%%%%%%

\subsection{Misinformation policies are hard to investigate}
The difficulty to qualify content as misleading and harmful, gave rise to a set of heterogenous policies across mainstream platforms, based on a mixture of algorithms and humans, namely fact-checking journalists, moderators and flagging mechanisms (\cite{crawford2016flag}) for users. This is because, so far, understanding the cultural component in a post or hidden meanings, requires human beings acquainted with a given culture and language. For example, Facebook has a substantial partnership program with over $80$ fact-checking partners over the world. The company uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\endnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter has a different approach focused on providing context rather than fact-checking\endnote{The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system called $Birdwatch$ based on the wisdom of the crowds to tackle misinformation. YouTube uses the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels.
%
The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report}''. In particular, policies regarding misinformation are generally not part of the set of platform rules or community guidelines (as of July 2021). \cite{facebookmisinfo2022} has recently included misinformation as part of their policy areas but no related data appears yet in the last available community standards enforcement report $Q3$ 2022.\endnote{See the listed policies in the column Overview via the following archived link: \href{https://archive.ph/sHEkD}{https://archive.ph/sHEkD}. } it is likely that some interventions used to tackle online misinformation correspond to interventions that were designed for earlier policy areas. To illustrate, YouTube explicitly states\endnote{See \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{What policies exist to fight misinformation on Youtube?} (Last visited September 2021).} that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies. Hence, using interventions designed for earlier policy areas raises the question of whether they are adapted to deal with misinformation and whether they can entail indirect effects. For example, content deletion or account suspension is likely to be efficient to deal with the policy area {\it Adult Nudity \& Sexual Activity}, but it can be perceived as censorship when dealing with textual content identified as misleading or problematic. \cite{rogers2020} studies de-platforming of internet celebrities off of large platforms and their re-platforming on new alternative social media platforms (e.g. Telegram).

Hence in the present article, we aim to contribute to the debate on the moderation of misleading content : (i) by surveying the current policies that are deployed by very large online platforms, (ii) by giving practical examples of how these policies could be studied  (iii) by highlighting the aspects that need to be improved for better monitoring of large platforms policies, especially since the recent adoption of the Digital Services Act in Europe.

\section{Methodological Note}

\begin{table*}[h]
\small\sf\centering
\caption{Ressources.\label{tab1}}
\begin{tabular}{lll}
\toprule
Platform & Ressource & Link\\  
\midrule
Facebook & \texttt{Community Standards}& \href{https://transparency.fb.com/policies/community-standards}{transparency.fb.com/policies/community-standards}\\
& \texttt{Transparency Center}&\href{https://transparency.fb.com/}{transparency.fb.com/}\\
&\texttt{Rating options}& \href{https://www.facebook.com/business/help/341102040382165?id=673052479947730}{https://www.facebook.com/business/help/341102040382165?id=673052479947730}\\
& \texttt{Strike System} & \href{https://transparency.fb.com/enforcement/taking-action/restricting-accounts/}{https://transparency.fb.com/enforcement/taking-action/restricting-accounts/} \\
& \texttt{COVID-19 policy} & \href{https://archive.ph/PaQW8}{archive.ph/PaQW8} (Archived version January 5, 2023)\\
&&\\ 
YouTube & \texttt{Community Guidelines} & \href{https://www.youtube.com/intl/ALL_ca/howyoutubeworks/policies/community-guidelines/}{youtube.com/intl/ALL\_ca/howyoutubeworks/policies/community-guidelines/}\\
&\texttt{Transparency Center}  &\href{https://transparencyreport.google.com/youtube-policy}{transparencyreport.google.com/youtube-policy}\\
&\texttt{Information Panels}& \href{https://archive.ph/vRukr}{support.google.com/youtube/answer/9891785}\\
& \texttt{Strike System} & \href{https://support.google.com/youtube/answer/2802032}{https://support.google.com/youtube/answer/2802032} \\
&\texttt{COVID-19 policy} &\href{https://archive.ph/DfLNa}{archive.ph/DfLNa} (Archived version October 30, 2022)\\
&&\\
Twitter & \texttt{Rules} & \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules} \\
&\texttt{Transparency Center}&\href{https://transparency.twitter.com/}{transparency.twitter.com/}\\
& \texttt{Notices on Twitter}& \href{https://archive.ph/1f9Mz}{help.twitter.com/en/rules-and-policies/notices-on-twitter}\\
& \texttt{Strike System} & \href{https://archive.is/3lAXF
}{https://archive.is/3lAXF} (medical misinformation) \& \href{https://archive.is/niXnH}{https://archive.is/niXnH} (civic Integrity) \\
&\texttt{COVID-19 policy} & \href{https://archive.ph/ez3eO}{archive.ph/ez3eO} (Archived version November 30, 2022) \\
\bottomrule
\end{tabular}\\[10pt]
\end{table*}
First, we survey common policies linked to misinformation by Facebook, Twitter and YouTube based on available resources online (see Table \ref{tab1}). As a second step, we explain how to investigate these misinformation related policies with data mining. We do so by providing a series of examples. The objective is to use the data in order to investigate a given policy and obtain out of this exercice meaningful elements which could inform us about its effectiveness and pertinence.

We chose to focus on three platforms: Facebook, Twitter and YouTube. 
Both Facebook and YouTube are in the top three most popular social media platforms in terms of number of users according to the website \cite{Statistajan2021}. 
We further include Twitter because it is a social networking platform with the most news-focused users, according to ~\cite{pew1}. 
To collect data from these three platforms, we either used Application Programming Interfaces (hereafter APIs) or web scraping only when the information was visible to the public eye and was not accessible via an API. 
For Facebook, we used CrowdTangle API and Buzzsumo API. {CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.}  
BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms. 
For Twitter and YouTube we used respectively  Twitter API V2 and YouTube API V3. 
Minet \cite{minet}, a webmining tool developed by the SciencesPo médialab, was used and we scripted our own data mining code when it was necessary.

The examples of accounts used to illustrate how to monitor a given policy were picked out based on one of the following criteria: the account is linked to a domain name with several failed fact-checks, a platform has communicated (e.g. Facebook Newsroom) regarding an intervention applied for a specific account or messages by the targeted user via other social media channels. 
We are aware that the investigation needs to be run on a larger scale, which is not possible to date due to the lack of pertinent data. 
For example, platforms do not provide data about which accounts were targeted or challenged so that, third parties could independently investigate the impact of a given misinformation policy on a larger pool of accounts. 
They do not provide either data on the specific policy that a suspended account has violated.

\section{How do Facebook, YouTube and Twitter action content deemed as misleading?}

Policies related to problematic content, as announced by the three large platforms, can be classified into three broad categories: (i) temporary or permanent suspension of users and content deletion, (ii) informing users with flags and notices and, (iii) algorithmic reduction of the visibility of some content. 
These broad categories only include policies that could be investigated by independent third parties, should all the needed data be provided within the boundaries of data privacy protection laws. Hence we do not include any intervention which would only appear on a user's screen. 
Policies only observable at the user level include ``nudges". 
Twitter for example can prompt a message to ask whether a user would like to read before retweeting (\cite{twittersafetynudge}).

\subsection{(i) Account suspensions and content deletion}

Mainstream social media platforms can suspend accounts and delete content when they deem that the platforms' rules have been violated. Account suspensions can be temporary or permanent.  
When the suspension is temporary the user is prohibited for a limited period of time from posting content on their account, but  content created prior to suspension remains available to the user, to other users and on APIs when the account is public.  
When an account is permanently suspended by Facebook, Twitter or YouTube, the data disappears from the official APIs.

\cite{facebookstrikes}, \cite{youtubestrikes} and Twitter have strike systems which consist in sending a number of warnings to an account owner to inform them that they have violated a rule and an increasing number of warnings entails increasing restrictions. For Facebook, two strikes lead to one day restriction from creating content and five or more strikes can lead to a $30$ day account restriction. For YouTube, one strike means that users are not allowed to post content on their channel for one week and a strike remains associated to a channel for 90 days. Furthermore getting a third strike results in the termination of the channel. As for Twitter, strikes lead to a a twelve hour account lock and five or more strikes lead to a permanent suspension. A list of notable Twitter temporary and permanent suspensions can be found on \cite{twittersuspensions}. The twelve hour account lock is hard to observe in the data, especially for users who do not have an over the clock regular tweeting activity.

\subsection{(ii) Informing users with contextual messages}

Platforms can resort to providing more context to users regarding a specific post, Tweet or video. This type of intervention takes different formats according to the platform and also has different denominations. Facebook for example refers to this intervention by mentioning ``flags", while Twitter  refers to ``notices" and ``interstitials" and YouTube uses the term ``information panels".

To the best of our knowledge, two types of flags can currently be displayed on Facebook posts: information banners which do not refute the message in the post and provide a link which redirects to an authoritative source, such as ``Visit the COVID-19 Information Centre for vaccine resources'' and fact-check flags that assign a ``rating" (\cite{facebookratings}) for a text or a link in a given post, such as ``False information Checked by independent fact-checkers'' (see Figure \ref{fb_flags}).

YouTube can place information panels at the top of search results or under a video. 
Information panels provide more context for  a topic deemed to be controversial, with a link to an independent, third-party partner's website such as Wikipedia, WHO or CDC. 
YouTube states that these panels exist regardless of the point of view expressed in a given video. 
YouTube also specifies that information panels may not be available in all countries/regions and languages.

Alongside other social networking platforms, when the content of a Tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center. 
At the Tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it ``Get the facts about COVID-19''} (see right panel of Figure \ref{fig8}). 
Interstitials are presented as a greyed box on top of a Tweet, which indicates sensitive content, violations of Twitter rules, withheld Tweets for violation of local laws or even Tweets from suspended accounts (see left panel of Figure \ref{fig_notice}).

\subsection{(iii) Algorithmic reduction of visibility}

Given the abundance of content, large platforms rely on algorithms for many policy areas. 
In particular, they can reduce the visibility of content by either down-ranking it on the timeline of a given user or via reduced recommendation. 
It's very challenging to investigate how algorithms are used when dealing with misleading content because it's hard to disentangle, whether impressions and engagements are lowered due to an algorithmic decision or because users were less interested.

Facebook can reduce the spread of misleading content through their built-in ranking system. More specifically, Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed. 
Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure by \cite{newsroom2}). 
This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the APIs used to access Facebook data: CrowdTangle or BuzzSumo. Hence we can indirectly investigate the ``reduce" measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available on CrowdTangle and BuzzSumo. 
If a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.

Similarly, \cite{twittervisibility} can take action against a Tweet which violates their rules, by limiting its visibility on users' timelines and in search results. 
More specifically, Tweets can be made less visible by becoming ineligible for amplification in the section ``Top" when searching for content by using a down-ranking system and on the timelines of the followers of the user who created the Tweet.

YouTube can reduce the visibility of certain videos via its recommendation system, namely by recommending content from authoritative sources. 
The platform usually recommends content to the users based on the watch history and searched queries in google and YouTube; which can both be cleared via account settings. 
A recommendation system based on previous preferences can have a downside, namely when a user repeatedly watches videos that might be misleading or that promote conspiracy theories and gets recommended similar videos. 
\cite{youtubemisinfo} states that they prevent their systems from serving up content that could misinform users in a harmful way, particularly in domains that rely on veracity, such as science, medicine, news, or historical events. 
YouTube identifies misinformation by using external human evaluators and experts to examine if a given video is promoting misleading information or conspiracy theories, and then use machine learning systems to discard misinformation from their recommendations. %{[\bf link here changed]}

\section{How can we investigate temporary suspensions?}

Permanent suspensions of accounts due to publishing misleading content are nearly impossible to investigate with available data, because the data simply disappears. 
Even by gathering from news articles names of accounts that were suspended in relation to misinformation it's also impossible to prove that it was a misinformation related intervention. 
This is because the specific policy violation, potentially linked to misinformation, is generally not indicated. 
Hence, in this section we investigate temporary suspensions because they can be observed in the data only when the suspension period is higher than the average pace of content creation of a given account. 
Our main focus is to assess the impact of these temporary suspensions.

\subsection{Facebook.}

\begin{figure}[h]
	\centering
			\includegraphics[scale=0.32]{../figure/facebook_crowdtangle_trump.png}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}
We start with the famous example of  Donald Trump’s official \href{https://www.facebook.com/DonaldTrump/}{Facebook page} that was suspended temporarily since January 6, 2021 (see \cite{facebookzuck}). 
The page’s data was still present in the CrowdTangle API. 
Hence, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint through the minet Python library by \cite{minet} . 
We can see in Figure \ref{fig1_fb} that the {\it Donald J. Trump} page has not published any content since January $6$, 2021, and that this behaviour is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension. 
\cite{facebooktrump} has recently announced that they will end this suspension. 
Finally, making available data of permenantly suspended accounts, whether users are public figures or less visible users, is essential to investigate whether the content deemed as misleading was harmful and/or unlawful, especially that the legal framework and perception of freedom of expression can vary across countries. Moreover giving access to the content of suspended accounts leaves room to enrich misinformation studies by investigating the context and socio-metric dimensions linked to the targeted users.

\subsection{Twitter}

For Twitter we illustrate with the temporary suspension of the account $@LifeSite$ linked to LifeSiteNews, an advocacy website and news publication. 
This website has several failed fact-checks according to the websites \cite{MBFClifesite} and \cite{openfeedbacklifesite}. 
The linked Twitter account has been temporarily suspended\endnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}} twice. 
We collected their Tweets via Twitter API V2, using the historical search endpoint. 
The top panel of Figure  \ref{fig2} shows the activity of the account from January 2019 until June 2021, where the two periods of temporary suspension can be clearly observed in the data.

\begin{figure}[h]
		\includegraphics[scale=0.32]{../figure/lifesite_updated_legend.jpg} 
		\includegraphics[scale=0.32]{../figure/lifesite_domain_updated_legend.jpg}
\caption{Top panel: number of Tweets (including Retweets, Replies, Quotes) per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Bottom panel: number of Tweets (including Retweets, Replies, Quotes) per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

To assess the impact of this double temporary suspension, we also collected all the Tweets posted by other accounts, during the same period, including a url link with the domain name lifesitenews.com. 
The bottom panel of Figure \ref{fig2}, shows that during both periods of temporary suspension, other users still shared lifesitenews.com links and that the level was only slightly below the tweeting and retweeting levels prior to the first temporary suspension.
Suspending a Twitter account is an intervention which aims at penalising users, in order to make them respect the Twitter rules.  The activity of accounts linked to websites usually consists in sharing on social media their own published articles. 
The bottom panel of Figure \ref{fig2} points towards the limitations of suspending the Twitter account $@LifeSite$, because the 
articles published on lifesitenews.com were still being actively shared by other Twitter users. 
Finally, \cite{LifeSiteNews} has announced on their website that they were using alternative platforms in response to multiple suspensions on large platforms. 
Figure \ref{telegram} shows the creation of their Telegram channel in early 2021 and their level of activity throughout the second suspension period on Twitter, illustrating a case study of platform migration. 
It should be noted that the Number of followers on Telegram is 13.4k (Feb 2023) against 58.6k (Feb 2023) on Twitter. 
Finally, the Twitter account of LifeSiteNews has been recently activated in October 2022. 
\begin{figure}[h]
\includegraphics[scale=0.34]{../figure/lifesite_2022_01_04.jpg} 
\caption{Number of posts per day on the Telegram Public channel LifeSiteNews, created on January 9, 2021. }
\label{telegram}
\end{figure}

\subsection{YouTube}

Turning to YouTube, we investigate the case of the YouTube channel associated to  One America News Network, a cable news channel, with several failed fact-checks according to \cite{MBFCoann} and \cite{openfeedbackoann}. 
Their temporary suspension on YouTube in relation to medical misinformation was announced in several media outlets, see for example ~\cite{nbcnews}. 
We collected for this channel, the video count (number of uploaded videos) and the view count using the YouTube API v3, between November $2020$ and January $2021$.\endnote{For the video count, we used the {\it playlists} endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the {\it videos} endpoint we retrieved the view count during the month of June $2021$.}

\begin{figure}[h]
\hspace{-2em}
		\includegraphics[scale=0.32]{../figure/delete_youtube_1_oann.png} \hspace{4em}
		\includegraphics[scale=0.33]{../figure/delete_youtube_2_oann.png} 
	\caption{Top panel: Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Bottom panel: accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the YouTube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{delete_youtube_oann}
\end{figure}

\smallskip

Figure \ref{delete_youtube_oann} shows the daily number of videos uploaded and their view count. 
We can clearly see the suspension period in the data, as the number of published videos is down to zero for one week after the strike announced by media outlets on November $24$, $2020$. 
When comparing the average view count during one week before the suspension and one week after the suspension, we observe a clear drop, while the video uploads one week and one week after where of the same magnitude.
%When comparing one month before and after the suspension, the view count decreased by -73\%. 
It is unclear wether this drop in view count is linked to a lower organic engagement or an algorithmic intervention by YouTube.
However, the activity of the channel in terms of videos uploads has drastically decreased by mid-December 2020 and was close to zero after March 2021. OANN's Twitter account has announced their migration from YouTube to Rumble on March 17, 2021 (see Figure \ref{tweets_about_yt_suspensions}). 
This case study illustrates on the short run some potential indirect effects of content moderation policies in terms of platform migration.

\begin{figure}[h]
	\centering
		\includegraphics[scale=0.3]{./img/oann/fig3_oann.png}
		\caption{Tweet announcing OANN's migration to Rumble, Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}.} 
	\label{tweets_about_yt_suspensions}
\end{figure}

\section{How can we investigate Flags, Notices and information panels?} \label{flags}

Platforms can provide more context to users by attributing a label or an information panel to a piece of content. This intervention is well documented in the literature, in terms of functioning, effectiveness and perception, see \cite{crawford2016flag}, \cite{morrow}, \cite{yaqub2020effects}, \cite{sharevski2021misinformation}, \cite{pennycook2020implied}. 
However information and data about whether a piece of content was flagged, labelled or contains an information panel is not available on official APIs. 
Hence it's challenging to understand the specific rules applied, whether content is labelled due to an algorithmic decision or users reports or moderators. 
In this section, for each platform, we rely on a set of links fact-checked as false and investigate whether they contained a flag, a label or an information panel. 
Since the information cannot be found on APIs the only way to investigate the presence of labels is by scraping publicly available content.

\subsection{Facebook}

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
\includegraphics[scale=0.49]{./img/fb_flags/fb_flag_3.png}
\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021.} 
\label{fb_flags}
\end{figure}
%\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/} \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{3835629366473816} .} 
%No information or available fields regarding the Facebook flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data. The only way to verify Facebook’s flagging policy is thus via scraping publicly available content.

We first searched for all the Facebook posts having shared one specific link\endnote{ Click \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{here} to access the link and  \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{its fact-check by Health Feedback}.} rated as ‘False’ by Science Feedback, one of Facebook's fact-checking partners. We used the `search' endpoint available on the CrowdTangle API to search for these posts.
Doing so, we collected 20 Facebook posts. 
Then we scripted an adapted scraping code to verify whether they contained an information panel, a fact-check flag, both or none (see Figure \ref{fb_flags}). 
Three posts were unavailable, and thus could not be categorised by the scraper. %As Science Feedback has informed Facebook that they have assigned the rating ``False'' for this link, we expected that all these posts would contain a fact-check flag, but we had no expectations for the information banner.

\begin{figure}[h]
\centering
\includegraphics[scale=0.4]{../figure/facebook_pie_flags_updated.png}
\caption{Count of different flags for 17 Facebook posts who have shared the exact same link, fact-checked False by one of Facebook’s partners. }
\label{tab_flags_fb}
\end{figure}

Only $11$ posts out of the remaining $17$ had a ``False information'' flag, see Figure \ref{tab_flags_fb}. 
We observed that the flagged posts were also the ones in which the false link was expanded, which means that a banner was visible with an image of the linked article on which users can click. 
As the ‘False information’ flag is applied on the link banner, and not on the link itself when it appears in the text of a post, we found cases where a user is thus able to share a link fact-checked as ``False''  by one of Facebook's partners, without receiving a ``False'' flag if the link is not expanded, see Figure \ref{fb_flags}.
We could not identify why information panels ``Visit the COVID-19 Information Centre for vaccine resources", were applied on some posts and not on others, as we observed no clear difference in the content of the post in terms of keywords. 
It should be noted that some posts displayed both the information and the fact-check banners, as in the second panel of Figure \ref{fb_flags}.

\subsection{Twitter}

When using the Twitter API V2, there is no field which indicates whether a Tweet contains a notice or not; with the exception of the interstitial ``possibly sensitive'' (see the top panel of Figure \ref{fig_notice}) and ``withheld" are both Tweet fields that can be recovered from the Twitter API V2. 
We take a deeper look at how notices and interstitials are introduced by Twitter. 
%links: $3$ $094$
%tweets $323$ $938$

First, we gathered a set of around $3$K  links redirecting to articles which were marked as ``False'' between April $2019$ and February $2021$ by Science Feedback. As a second step, we collected on June $30$, $2021$ all the Tweets that have shared at least one of these links, using minet~\cite{minet}. 
This tool was recently enriched upon our request via Github in order to capture whether a Tweet contains a notice or not, when using the ``minet twitter scrape'' command. 
The Tweet collection resulted in around $320$K Tweets, excluding Retweets. Only $28$ Tweets contained the notice { \it ``Get the facts about COVID-19''}, five Tweets contained the notice {\it ``Learn about US 2020 election security efforts''} and only one had the following notice {\it ``This claim about election fraud is disputed''}.

Furthermore, we noticed that the labelling rule is not applied uniformly on a given set of Tweets sharing the exact same link. To illustrate, $657$ Tweets contained the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}. 
Among those $657$ Tweets only three had the notice {\it ``Get the facts about COVID-19''} (see the bottom panel of Figure \ref{fig8}).
It might be that these three Tweets were the only ones reported by other users, since the labelling seems not to be automated with respect to a specific link redirecting to a fact-checked article. 
\begin{figure}[h]
\centering
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	\caption{Two Tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021. Top panel: a Tweet without an information notice. Bottom panel: a Tweet containing an information notice.}
	\label{fig8}
\end{figure}

\begin{figure}[h]
	\centering
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
	\caption{Top panel: Tweet containing a URL link hidden behind an interstitial. Bottom panel: when clicking on $view$, to view the content hidden behind the interstitial in the top panel. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}
%tweets possibly sensitive $9$ $344$
We further examine the placement of interstitials that indicate a possibly sensitive content. We find that around $9$K Tweets ($3\%$) out of the collected $320$K, contain the interstitial {\it ``potentially sensitive content''}. 
Again, to investigate whether the interstitial {\it ``potentially sensitive content''} is automated or not, we pick out one Tweet having shared a link\endnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.} marked as ``False'', which also contains the interstitial {\it potentially sensitive content} (see the top panel of Figure \ref{fig_notice}). 
There were $32$ Tweets that have shared the exact same link and only five of those Tweets contained the interstitial ``potentially sensitive content'', although they contained no graphic violence. To date, no data is available to verify whether some interstitials or notices were placed based on: Tweet reporting by other users or Twitter moderators or algorithmic rules or a mixture of all the previous.\endnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label Tweets that may contain misleading information around COVID-19 vaccinations".}   
The appearance of interstitials may depend on the settings of a user's account and country or language specific regulations. In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}.

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.4]{../figure/donut_twitter_2022_01_04.png}
	\caption{Summary of the number of Tweets among the set of $323$ $938$ Tweets containing a link marked as False, by Science Feedback, which contain a notice or a Possibly sensitive interstitial or none.}
\label{flags_tab}
\end{figure}

\smallskip

Finally, the Tweets containing the interstitial ``potentially sensitive content'' widely outnumber the tweets which contain a notice (see Figure \ref{flags_tab}). 
We observed that among the Tweets which contain the interstitial {\it ``potentially sensitive content''}, there are Tweets which contain links redirecting to misleading articles about COVID-19 and yet they do not contain the label { \it ``Get the facts about COVID-19''}. 
The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.  
However we noticed that the Tweets which contain the interstitial {\it ``potentially sensitive content''} do not necessarily contain graphic violent content, but rather links that redirect to articles marked as ``False'' by Science Feedback. 
It is possible that the possibly sensitive content interstitial is used as a type of soft moderation to reduce the visibility of a link.

\subsection{YouTube} \label{youtube_panels}

To study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing inaccurate information. 
We collected the information panels, when present, under each video by scraping the content of the web page because this information is not available on the YouTube API. 
Several types of information panels were found, see Figure \ref{youtube_panel_screenshots}.

\begin{figure}[h]
	\centering
		\includegraphics[scale=0.1]{./img/youtube_panels/youtube_panel_covid.png} \vspace{0.3cm}

		\includegraphics[scale=0.1]{./img/youtube_panels/youtube_panel_covid_vaccine.png} 
		\vspace{0.3cm}

		\includegraphics[scale=0.1]{./img/youtube_panels/youtube_panel_climate.png}
	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=O1cFVdC2rZQ}{COVID-19}, \href{https://www.youtube.com/watch?v=v0-6JTr2Ifo}{COVID-19 Vaccine} and \href{https://www.youtube.com/watch?v=4U8kgiiVj5Q}{climate change}. The videos were accessed on September 2, 2021.}
	\label{youtube_panel_screenshots}
\end{figure}

\begin{figure}[h]
	\centering
		\includegraphics[scale=0.2]{../figure/youtube_pie_flags.png}
		\caption{Summary of the number of YouTube videos which contain an information panel, among the set of videos marked as false by Science Feedback.}
\label{youtube_panel_proportions}
\end{figure}

\begin{figure}[h]
	\centering
		\includegraphics[scale=0.22]{./img/youtube_panels/graph_no_banner.png}
		\vspace{0.4cm}
		\includegraphics[scale=0.22]{./img/youtube_panels/graph_with_banner.png} 
	\caption{Screenshots showing two duplicates of the same video, taken on July 21, 2021. 
Top panel: a \href{https://www.youtube.com/watch?v=d9GbVZOcT18}{YouTube video} about COVID-19 without an information panel. 	
Bottom panel: a \href{https://www.youtube.com/watch?v=A4RvrEKoNxc}{duplicate of the same video} uploaded under a different title and with a `COVID-19 vaccine' information panel.}
	\label{duplicates_yt}
\end{figure}

\smallskip

Almost half (46 \%) of the YouTube videos fact-checked as misleading by Science Feedback, were shown without any information panel (Figure \ref{youtube_panel_proportions}).
For the remaining videos, the most frequent information panel were COVID-19 (42 \%), followed by COVID-19 vaccine (9 \%), which is probably linked to a higher likelihood of fact-checking medical misinformation given the ongoing events at that time.
We noticed that the same video was sometimes uploaded multiple times with different YouTube links and different titles. 
One YouTube link might contain an information panel while its duplicates did not, see Figure \ref{duplicates_yt} for an example.  
In addition, we noticed that some keywords in the video titles were often associated with an information panel, such as ``COVID-19", ``coronavirus", ``pandemic" and ``testing", while some notational variants like ``C O V I D 19" or ``Cv19" were not associated with a panel.
Therefore, we suspect that YouTube is automatically adding information panels based on the presence of certain keywords in the video title and maybe in the video description, independently of the content of the video.
Note that in Figure \ref{duplicates_yt}, the video with ``C.O.V.I.D.19" in its title had an information panel, hinting that YouTube might adapt its list of keywords as new notational variants for COVID-19 appear or that some information panels might be added manually, by content content moderators or following users' reports or a mixture of the previous.

\section{Can we investigate algorithmic reduction of visibility of posts or accounts?}
We turn to the last family of content moderation policies linked to misinformation: reducing the visibility of a piece of misleading content as a mean of soft moderation. It is often referred to as ``shadow banning". Given the abundance of content, opting for this intervention allocates to algorithms the role of gatekeepers and it raises several concerns. This is because,  algorithmic interventions linked to misinformation are hard to investigate. On the one hand, by design these interventions are undetectable by the public eye and on the other hand the algorithmic rules used are not transparent. \cite{kokil2023silenced} investigate ``shadow banning" on Twitter and their findings show that it remains a rare event. \cite{LEERSSEN2023105790} discusses visibility reduction from a legal perspective and outlines the challenges related to accountability in relation to the Digital Services Act in the EU. In this section, again based on media outlets with failed fact-checks, we provide several illustrations and methodologies to investigate this intervention.

\subsection{Facebook} \label{reduce_fb}

First, we investigate the famous case of the website $Infowars$. This website appears in the Misinformation Directory by \cite{misinformationdirectory}, it also has {\it very low}  factual reporting according to \cite{MBFCinfowars} and several failed fact-checks reported by \cite{openfeedbackinfowars}.  \cite{facebookinfowars} explicitly stated the following: {\it ``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address by demoting links marked wrong by fact checkers"}. According to a news article published on May 2, 2019 by \cite{wiredalexjones}, Facebook announced that they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.

To audit this intervention, we used the ``/posts/search'' endpoint of the CrowdTangle API and  collected $37~242$ Facebook public posts containing the domain name ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$. We found in the collected data some Facebook posts that did not directly share an Infowars link, but rather a YouTube or Facebook video containing an Infowars link in its description. Thus we excluded such posts from our data and kept $27$ $721$ posts directly sharing an Infowars link.

\begin{figure}[h]
\hspace{-2em}
		\includegraphics[scale=0.32]{../figure/facebook_crowdtangle_infowars_1.png}
		\includegraphics[scale=0.32]{../figure/facebook_crowdtangle_infowars_2.png} 
	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API. The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars. top panel: Number of daily posts. Bottom panel: Engagement metrics: average number of reactions, shares and comments per post. }
	\label{infowars1}
\end{figure}

The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see Figure \ref{infowars1} top panel). 
Thus the measure announced by Facebook does not seem to have prevented users from sharing an $Infowars$ link. Nevertheless, a clear drop in engagement was observed on May $2$, $2019$ (see Figure \ref{infowars1} bottom panel). 
The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May $2$, $2019$. This suggests the measure taken by Facebook in May $2019$, is not a ban per se, but rather a $reduce$ measure. This is because users could still post $Infowars$ links, but these posts generated less engagement. It should be noted that the engagement metrics increased again by the end of $2019$ / beginning of $2020$, suggesting that the $reduce$ measure may have been lifted a few months after its implementation.

\subsection{Twitter}  \label{globalresearch}

Turning to Twitter, we present a case study where two interventions that reduce the visibility were applied at the same time. We investigate the case of the website $globalresearch.ca$, with a low factual-reporting according to \cite{MBFCgloabalresearch} and which is linked to the Twitter account {$@CRG\_CRM$} (indicated on their website).

When a user searches via the Twitter search-box for the domain name $globalresearch.ca$, no results appear as shown in the screenshot in the top left panel of Figure \ref{fig3}, taken on June $14$, $2021$. To investigate whether this was an intervention or simply no Tweets contained this domain name, we searched via the Twitter API v2 for Tweets with the query {\it globalresearch.ca} three months before and after the date of the screenshot. We found a strictly positive number of Tweets containing this domain name with strictly positive engagement metrics, as shown in the top and bottom panel in Figure \ref{fig4}. It's likely that users who post Tweets including articles from the {\it globalresearch.ca} website receive Tweet level engagement from their own followers. Furthermore when a user attempts to click on a link which contains {\it globalresearch.ca} in a Tweet (top right panel in Figure \ref{fig3}), a warning message appears and indicates that the link may be unsafe (bottom left panel \ref{fig3}) - hence acting as a second layer of visibility reduction. Furthermore, we noticed on May $25$, 2021 that the Twitter account {$@CRG\_CRM$} linked to the website $globalresearch.ca$ was suspended, see the bottom right panel in Figure \ref{fig3}.

For the case of this Twitter account and the linked website, it is likely that a mix of interventions was used: reducing the visibility via the search box, reducing the visibility by introducing a warning message and suspending the related Twitter account.

\begin{figure}[h]
\centering
	\includegraphics[width=3.7cm, height=2.5cm]{./img/globalresearch_14_06_2021_16pm_UTC.png}  
	\includegraphics[width=3.7cm, height=2.5cm]{./img/globalresearch/tweet.png} 
	\includegraphics[width=3.7cm, height=2.5cm]{./img/globalresearch/warning.png} 	
	\includegraphics[width=3.7cm, height=2.5cm]{./img/globalresearch/globalresearch_2021-06-14.png}
	\caption{Screenshots taken on June 14, 2021. Top left panel: no results can be found when searching for Tweets with the domain name $globalresearch.ca$ via the Twitter search box. Top right panel: example of a Tweet containing the domain name {\it globalresearch.ca}. Bottom left panel: warning message that appears when a user attempts to click on a link which contains the domain name {\it globalresearch.ca}. Bottom right panel: account suspension message of $@CRG$\_$CRM$ linked to {\it globalresearch.ca}.}
		\label{fig3}
\end{figure}

\begin{figure}[h]
\centering
\hspace{-2em}
		\includegraphics[scale=0.4]{../figure/globalresearch_domain_2021-08-17.jpg}  		\includegraphics[scale=0.4]{../figure/globalresearch_domain_engagement_2021-08-17.jpg}
\caption{Top Panel: daily number of Tweets, excluding Retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Bottom Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Data collected via the Twitter API v2 on August $17$, 2021.   }
\label{fig4}
\end{figure}

\subsection{YouTube}

YouTube can reduce the visibility of certain videos via its recommendation system, namely by recommending content from authoritative sources. They also state that they set out to prevent their systems from serving up content that could misinform users in a harmful way, particularly in domains such as science, medicine, news, or historical events.

To investigate how recommendations can be used to reduce the visibility of potentially harmful and misleading content, we designed an experiment that simulates a user's behaviour on YouTube using an automated program. The results are to be explored with caution as no clear instructions about how exactly the recommendation algorithms of YouTube address videos identified as misleading. 
\subsubsection{Experiment description.} 
We used a list of $45$ YouTube videos marked as {\it False} by Science Feedback and classified under the category ``health''.
First, we visit the YouTube videos marked as ``False'' from our list of videos and a clean watch history.
Second, for each YouTube video (parent), our automated program collects around $20$ recommendations\endnote{When we visit a video, we get a number of recommendations that vary between $18$ videos and $22$ videos.} and clicks on the top $10$ videos (children) in sequential order. 
Third, for every video in the set of the top $10$ recommended YouTube videos (children), we collect their own top $20$ recommended videos (grand-children).
In addition, to simulate a user's behaviour, the automated program watches each video for a few minutes. If the video duration is ten minutes or less, the automated program watches the whole video. If the video duration is strictly higher than ten minutes, then the automated program watches only five minutes.
\subsubsection{Experiment results.} 
Doing so, we collected $10~549$ recommended YouTube video entries, among which $3~895$ were unique. 
To analyse the collected data, we look for videos belonging to medical misinformation: $(i)$ at the channel level and $(ii)$ at the video level.

The $3~895$ unique YouTube videos belonged to $1~562$ unique channels, and then we counted the number of times videos from each channel got recommended.
Figure \ref{reduce_youtube} shows the top ten recommended channels, whose videos represent $30\%$ of the recommendations.
Fox News and Sky News Australia - which both have a ``mixed'' factual reporting level according to the website \cite{MBFCfoxnews} with several failed fact-checks - are at the first and third place respectively.
PragerU - a website with a ``low" level of factual reporting according to \cite{MBFCprageru} - is also among the list of the ten most recommended channels.

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.45]{../figure/reduce_youtube.png} 
	\end{center}
	\caption{Top ten channels recommended by YouTube when we simulated a user that starts by watching a video fact-checked as False and then follows the top recommendations.}
	\label{reduce_youtube}
\end{figure}

Furthermore, we ranked the videos based on the number of times they got recommended and asked Science Feedback to fact-check the top 40 recommended videos. 
Those videos were recommended $1~735$ times, which represents $16\%$ of the total recommended videos.
Among the 40 examined videos, four videos were marked as {\it misleading} and they were recommended $132$ times out of the $1~735$ recommendations (i.e. $7.7\%$).
Four other videos were marked as {\it hyper-partisan} and they were recommended $184$ times (i.e. $10.7\%$).
As we collected the recommendations of misinformation videos, we expected to find a high proportion of videos of questionable content.
But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation. 
However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being recommended.
It might be that the recommendation system of YouTube is reducing the visibility at the video level but not necessarily at the channel level. These findings are preliminary and experiments on larger sets of potentially misleading YouTube videos need to be conducted.

\section{Discussion}

In this article we have assessed three broad categories of interventions to tackle misinformation by Facebook, Twitter and YouTube: $(i)$ suspension of accounts, $(ii)$ introduction of flags, labels and information panels and $(iii)$ reducing the visibility of content. Mainstream platforms such as Facebook, Twitter and Youtube are increasingly working towards higher data transparency. 
Yet the present research sheds light on the restrictions to access data and its limits, which impede the academic community from studying successfully online misinformation and assessing the impact and pertinence of platforms' interventions regarding this phenomenon. 
In this section, we provide a discussion regarding the limitations to access data and the lack of transparency regarding misinformation related interventions.

\subsection{A need for complete \& pertinent data}

When Facebook, Twitter or YouTube intervene by suspending an account, the data can no longer be accessed via scraping or via official APIs (Twitter, YouTube, CrowdTangle) for the purposes of scientific research. This hampers the investigation of how platforms moderate content, especially content deletion which is often perceived by users as censorship.

For example, the original list of YouTube videos with failed fact-checks (summarized in Figure \ref{youtube_panel_proportions}), had over $200$ YouTube videos available in March $2021$. 
However, by June $2021$, thirty videos had disappeared from the YouTube API for policy violation and we could no longer examine them. 
To avoid interrupting research following data deletion by a given large platform, it seems essential to make available at least some metadata of the content posted by the suspended accounts.

Currently it is impossible to study permanent deletions using available social media data but they could be investigated indirectly (and imperfectly) using an adapted methodology.
Following the Capitol riots in January $2021$, \cite{twitterdc} has announced the suspension of more than $70~000$ accounts related to QAnon.
A BBC journalist has recently shared in a \cite{tweetBBC}, the effects of this measure by counting the number of times hashtags related to the QAnon movement have been used over time, such as \#QAnon or \#WWG1WGA.
A drastic reduction in hashtag use was found when comparing the first quarter of $2021$ with the first quarter of $2020$.

However, data can also disappear due to other factors independent of platforms' content moderation policies and it is hard to identify how much of the drop in QAnon related hashtags is due to the Twitter intervention or to accounts migrating to other platforms or simply a drop in using the hashtag for other unidentified factors.
To illustrate, \cite{mcminn2013building} collected $120$ million Tweets related to general topics. 
The same published set of Tweet IDs was then used by \cite{mazoyer2020french}. The authors ran the same Tweet collection in $2018$ and they only found $67$ millions of Tweets (55\%). The authors argue that this drop is probably due to Tweets having been removed by users and Twitter accounts being shut by the users themselves.
As data can disappear from platforms over time, it is hard to distinguish whether platforms or users are the ones responsible for data removal. Hence it is essential that platforms communicate this information via Tweet metadata so that the academic community can assess rigourously content deletion related to content moderation.

Aside from the disappearance of data due to content moderation, some essential metrics for the study of misinformation are not accessible via main APIs. 
In particular, the $reach$ of posts on Facebook, which is the number of people who actually see a given post, cannot be recovered from the CrowdTangle API. Hence, researchers can only build proxies for this metric based on available data, such as engagement metrics. The reach, impressions or view count is an essential metric to assess ``viral" content, as the number of users who see a post is generally different from the number of users who engage with a post.  Notice that this metric was recently made available via the Twitter API since December 22, 2022.

Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs, with the exception of the {\it withheld}  and {\it possibly sensitive content} interstitials in the Twitter API v2. This information does not seem to be sensitive and can be very useful for misinformation research studies to asses the impact and pertinence of information panels on a larger scale. To illustrate, information panels on YouTube, Twitter and Facebook have been used in the US for elections integrity following the controversy about elections' results. \cite{therodefacto} shows in a research note that information panels have been placed under YouTube videos including political figures, during the 2022 French presidential elections, while there was no controversy regarding the results. More research needs to be conducted to assess the pertinence of US-centric interventions when the targeted users are in other geographic zones.

Finally, there are growing restrictions to access APIs, see \cite{api}.
In April $2018$, likely as a response to the Cambridge Analytica scandal, \cite{facebookdata} severely limited the access to their official APIs, see the commentary by \cite{bernhard}.  
CrowdTangle is today a reliable source for researchers, journalists and the civil society to access Facebook data. 
To illustrate, CrowdTangle has been recently used by \cite{theeconomist} to show that Facebook might be disproportionally favouring highly partisan information. Along the same lines, the Twitter account \cite{facebookstop10} shows each day the ten top performing link posts by U.S. Facebook pages in the last 24 hours, where right leaning sources such as Fox news or Breitbart appear often. 
\cite{facebookapptop10} has reacted to such rankings based on CrowdTangle data, by saying that {\it ``Ranking top Page posts by reactions, comments, etc. doesn’t paint a full picture of what people actually see on Facebook"}. There is a general suspicion that access to Facebook data might be further restricted in a near future, see for example the articles by \cite{nytimestheshift} in the New York Times or \cite{bloomberg} in Bloomberg. Regarding the other large platforms, \cite{twitterdev} has recently announced restrictions to access their API by no longer supporting free access, even for their academic track.

\subsection{A need for meaningful transparency.} 
Large platforms populate their own transparency centres and provide aggregate figures by policy area. When navigating through the categories of policy areas in available enforcement reports, by Facebook, YouTube or Twitter, to the best of our knowledge, misinformation is absent from the data available on their transparency centres - in spite of clear evidence that content that is considered as misleading and harmful is actioned by these platforms.  
Platforms' official communication about misinformation interventions is scarce and researchers, journalists and the civil society, usually discover interventions related to misinformation via monitoring social media accounts related to domain names with several failed fact-checks or via articles in news outlets.

We are aware that full transparency regarding operational aspects of misinformation related interventions can backfire.
This is because the aimed users might find ways to circumvent the interventions, for example by using notational variants that algorithms might use to target content. 
But, a balance needs to be found so that stakeholders can understand how the platforms are regulating content.

In certain cases, the platform interventions were not motivated by content moderation to limit misinformation, but rather by other rule violations. To illustrate, when \cite{facebookinfowars} removed four pages related to the InfoWars website, the cited reason was repeated violations of Community Standards: 
{\it ``While much of the discussion around Infowars has been related to false news, which is a serious issue that we are working to address [...], none of the violations that spurred today’s removals were related to this''}.

In the previous example, the compagnies' communication was very clear about the reason of the interventions. 
However, very often no official communication on behalf of the platforms can be found for specific interventions observed in collected data. 
Because misinformation is often associated with creating fake accounts to speed its spread, and incitation to violence, it is sometimes unclear to distinguish between interventions due to misinformation and interventions due to other guideline violations, and more transparent communication on platforms' actions would help monitor the interventions specifically related to misinformation. Platforms could explicitly provide via metadata the specific policy violation rather than just displaying on a piece of deleted content that the rules were violated.

\subsection{A need for independent audits} 
%dynamic aspect : changing rules covid. changing algorithms. 
%rules clear? 
%centralised internet 
To date, research about content moderation policies of very large online platforms related to misinformation is still scarce, mainly due to data and information availability as we have shown in the present research paper.

Large platforms choose today in a central and rather opaque matter which rules to set, facing pressure from the market due to multiple accusations of not providing a safe and healthy online space. These policies are de facto ``terms of service" of a small number of private companies that dominate the market,  that users are bound to respect.
But they raise the question of the choice of a model of governance to be adopted within these online spaces because they are frequented daily by millions (sometimes billions) of users around the world, with different values and perceptions of freedom of expression. 
The current model of self-regulation, where platforms create the rules, implement them and audit them themselves by publishing aggregate figures via their transparency centres is no longer satisfactory to many stakeholders. 
Especially that the rules evolve often as a function of ongoing events, such as the recent COVID-19 pandemic.

In a sense, reflecting on large platforms governance is both a contradiction and an aporia. On one hand, it can come as a contradiction,  because in the spirit of the internet pioneers, the members of the online community had their own values and their own way to self regulate (see for example \cite{barlow}) and the {\it code} or architecture was itself a sufficient mean to protect newly acquired freedoms, \cite{lessigcode1}. On the other hand, it is an aporia, because online spaces have drastically changed  and the high concentration of usage within few very large platforms gave rise to many new unforeseeable challenges, such as harassment, hate speech and harmful misleading content. Since these challenges concern millions of users around the world, it seems necessary that third parties take part in assessing and evaluating the pertinence and effects of content moderation policies. The methods presented in this paper can help to monitor not only the platforms' actions against misinformation, but also their subsequent consequences in real-life settings.

%It is also possible that platforms usually follow specific rules on how to fight misinformation, but that sometimes the sudden media coverage of specific events leads them to take exceptional actions, such as with the Capitol riots and Trump's suspension from Facebook, Twitter and YouTube.
%We would argue that policies should be clearly stated and carefully designed, rather than implementing interventions on a case-by-case basis and in response to the latest news events.

%It was shown that credibility indicators do reduce misperceptions and sharing, although their impact varied vastly depending on the presentation of the warnings, see \cite{yaqub2020effects} and \cite{sharevski2021misinformation}.
%Moreover \cite{pennycook2020implied} show that such sparse application of warnings can lead to an ``implied truth'' effect, where users may assume that content without warnings have actually been verified and shown to be true.
%Using a different approach, \cite{mosleh2021perverse} identified Twitter users sharing false news and replied to their false Tweets with links redirecting to fact-checking websites.
%They observed a decrease in the quality and accuracy of the content subsequently shared by the corrected user. 
%These research papers highlight the necessity to investigate the effects of content moderation policies linked to misinformation.

%{\color{red} \bf Ouverture TikTok, }

\theendnotes

\bibliography{proj1}{}
\bibliographystyle{SageH}

\section{Appendix}

\noindent {\bf Acknowledgments} \\
We thank our colleagues at Sciences Po m\'{e}dialab for their feedback and suggestions, especially Dominique Cardon, Manon Berriche and Valentine Crosset. \bigskip

\noindent {\bf Funding} \\
This research was supported by the Make Our Planet Great Again’ French state aid managed by the Agence Nationale de la Recherche under the ’Investissements d’avenir’ program with the reference ANR-19-MPGA-0005. \bigskip

\noindent {\bf Competing interests } \\
We have no conflicts of interest to disclose. \bigskip

\noindent {\bf Ethics} \\
The data collection and processing complied with the EU General Data Protection Regulation (GDPR).\bigskip

\noindent{\bf Data availability} \\
The code needed to collect the data and create the figures is available on the following public GitHub repository: \href{github.com/medialab/webclim misinformation_related_interventions}{github.com/medialab/webclim\_misinformation\_related interventions}.

\end{document}

### 2023-02-24 code/create_figures.py

@@ -668,7 +668,7 @@ def create_donut(figure_name):
 
     fig, ax = plt.subplots(figsize=(6, 15), subplot_kw=dict(aspect="equal"))
 
-    ratings = ['Tweets without notices\nor Possibly Sensitive\n interstettial (314 560)', 'Tweets with a notice (34)', 'Tweets with the Possibly Sensitive interstitials (9 344)']
+    ratings = ['Tweets without \n notices or \n Possibly Sensitive\n interstitial (314 560)', 'Tweets with a notice (34)\n \n', 'Tweets with the \n Possibly Sensitive \n interstitial (9 344)']
     data = [314560, 34, 9344]
 
     cmap = plt.get_cmap('coolwarm')
@@ -681,7 +681,7 @@ def create_donut(figure_name):
     kw = dict(arrowprops=dict(arrowstyle="-"),
               bbox=bbox_props, zorder=0, va="center")
 
-    plt.text(0, 0, "Tweets with links\nfact checked as\n false", ha='center', va='center', fontsize=14)
+    plt.text(0, 0, "Tweets containing \na link\nfact checked as\n false", ha='center', va='center', fontsize=14)
 
     for i, p in enumerate(wedges):
 
@@ -709,20 +709,125 @@ def create_pie_pp_fb(figure_name):
 
 def create_pie_figures():
 
-    create_pie_pp_fb('facebook_pie_flags_updated')
-    create_pie_pp('youtube_pie_flags')
-    create_donut('donut_twitter')
+    #create_pie_pp_fb('facebook_pie_flags_updated')
+    #create_pie_pp('youtube_pie_flags')
+    create_donut('donut_twitter_2022_01_04')
+
+def create_twitter_Lifesite_figure(filename, filename_2, figure_name, title, zeros):
+
+    df = import_data(filename)
+    df = df.drop_duplicates()
+
+    #df['type_of_tweet'] = df['type_of_tweet'].replace(np.nan, 'created_content')
+    df['total_engagement'] = (df['retweet_count'] + df['like_count'] + df['reply_count'])
+    df['date'] = pd.to_datetime(df['created_at']).dt.date
+    #df_volume = df.groupby(['date','type_of_tweet'], as_index=False).size()
+    df_volume = df.groupby(['date'], as_index=False).size()
+
+
+    df_tlm = import_data(filename_2)
+    df_tlm[df_tlm['date'].isnull()]
[…]
